### 2022-03-29 paper/main.tex
bare bones SoftwareX article outline

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt, a4paper]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
\usepackage{lineno}

\usepackage{float}
\restylefloat{table}

\journal{SoftwareX}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Title/Name of your software}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{A. Author}

\address{Your institute, some address}

\begin{abstract}
%% Text of abstract 
% Ca. 100 words

\end{abstract}

\begin{keyword}
%keyword 1 \sep keyword 2 \sep keyword 3

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

\section*{Required Metadata}
\label{}

\section*{Current code version}
\label{}

\begin{table}[H]
\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
\hline
\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
\hline
C1 & Current code version &  \\
\hline
C2 & Permanent link to code/repository used for this code version &  \\
\hline
C3 & Code Ocean compute capsule & \\
\hline
C4 & Legal Code License   &  \\
\hline
C5 & Code versioning system used &  \\
\hline
C6 & Software code languages, tools, and services used &  \\
\hline
C7 & Compilation requirements, operating environments \& dependencies & \\
\hline
C8 & If available Link to developer documentation/manual &  \\
\hline
C9 & Support email for questions & \\
\hline
\end{tabular}
\caption{Code metadata (mandatory)}
\label{} 
\end{table}

\linenumbers

%% main text

\section{Motivation and significance}
\label{}

\section{Software description}
\label{}

\subsection{Software Architecture}
\label{}

\subsection{Software Functionalities}
\label{}

\subsection{Sample code snippets analysis (optional)}
\label{}

\section{Illustrative Examples}
\label{}

\section{Impact}
\label{}

\section{Conclusions}
\label{}

\section{Conflict of Interest}

\section*{Acknowledgements}
\label{}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% References:
\bibliographystyle{elsarticle-num} 
\bibliography{main.bib}

\end{document}

### 2022-03-30 paper/main.tex
title page and metadata

@@
 
+\usepackage[hidelinks]{hyperref}
+\usepackage{breakurl}
+
 \journal{SoftwareX}
@@
 \begin{document}
-
 \begin{frontmatter}
 
-%% Title, authors and addresses
+\title{\texttt{davos}: The Python package smuggler}
+\author{Paxton C. Fitzpatrick}
+\author{Jeremy R. Manning\corref{cor}}
+\ead{Jeremy.R.Manning@Dartmouth.edu}
+\cortext[cor]{Corresponding author}
+\address{Department of Psychological and Brain Sciences\\Dartmouth College, Hanover, NH 03755}
 
-%% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
-%% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
-%% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
-%% use the ead command for the email address,
-%% and the form \ead[url] for the home page:
-%% \title{Title\tnoteref{label1}}
-%% \tnotetext[label1]{}
-%% \author{Name\corref{cor1}\fnref{label2}}
-%% \ead{email address}
-%% \ead[url]{home page}
-%% \fntext[label2]{}
-%% \cortext[cor1]{}
-%% \address{Address\fnref{label3}}
-%% \fntext[label3]{}
-
-\title{Title/Name of your software}
-
-%% use optional labels to link authors explicitly to addresses:
-%% \author[label1,label2]{}
-%% \address[label1]{}
-%% \address[label2]{}
-
-\author{A. Author}
-
-\address{Your institute, some address}
+% ------------------------------------------------------ ABSTRACT ------------------------------------------------------
 
 \begin{abstract}
-%% Text of abstract 
+% Text of abstract 
 % Ca. 100 words
@@
 \begin{keyword}
-%keyword 1 \sep keyword 2 \sep keyword 3
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-
+Python \sep Jupyter Notebook \sep Google Colaboratory \sep Reproducibility \sep Package management \sep Pip install
 \end{keyword}
@@
 
+% ------------------------------------------------------ METADATA ------------------------------------------------------
 \section*{Required Metadata}
-\label{}
 
 \section*{Current code version}
-\label{}
 
@@
 \hline
-C1 & Current code version &  \\
+C1 & Current code version &  v0.1.0 \\
 \hline
-C2 & Permanent link to code/repository used for this code version &  \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos} \\
 \hline
@@
 \hline
-C4 & Legal Code License   &  \\
+C4 & Legal Code License & MIT \\
 \hline
-C5 & Code versioning system used &  \\
+C5 & Code versioning system used & git \\
 \hline
-C6 & Software code languages, tools, and services used &  \\
+C6 & Software code languages, tools, and services used & Python, JavaScript, pip, IPython, Jupyter, Ipykernel, PyZMQ.
+Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & \\
+C7 & Compilation requirements, operating environments \& dependencies & Dependencies:~Python$>$=3.6, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+\\
 \hline
-C8 & If available Link to developer documentation/manual &  \\
+C8 & If available Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
 \hline
-C9 & Support email for questions & \\
+C9 & Support email for questions & contextualdynamics@gmail.com \\
 \hline
 \end{tabular}
-\caption{Code metadata (mandatory)}
+\caption{Code metadata}
 \label{}
@@
 \linenumbers
+%The permanent link to code/repository or the zip archive should include the following requirements:
 
-%% main text
+%README.txt and LICENSE.txt.
 
+%Source code in a src/ directory, not the root of the repository.
+
+%Tag corresponding with the version of the software that is reviewed.
+
+%Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
+
+% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
 \section{Motivation and significance}
-\label{}
 
+%Introduce the scientific background and the motivation for developing the software.
+
+%Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
+
+%Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
+
+%Provide a description of the experimental setting (how does the user use the software?).
+
+%Introduce related work in literature (cite or list algorithms used, other software etc.).
+
+% ------------------------------------------------ SOFTWARE DESCRIPTION ------------------------------------------------
 \section{Software description}
-\label{}
+% Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
 
 \subsection{Software Architecture}
-\label{}
+% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
 
 \subsection{Software Functionalities}
-\label{}
+% Present the major functionalities of the software.
 
 \subsection{Sample code snippets analysis (optional)}
-\label{}
 
+% ----------------------------------------------- ILLUSTRATIVE EXAMPLES ------------------------------------------------
 \section{Illustrative Examples}
-\label{}
+% Provide at least one illustrative example to demonstrate the major functions.
 
+% Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
+(Please upload any video as a single supplementary file with your article.
+Only one MP4 formatted, with 50MB maximum size, video is possible per article.
+Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second.
+Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$.
+This tool will display your video exactly in the same way as it will appear on ScienceDirect.).
+
+% ------------------------------------------------------- IMPACT -------------------------------------------------------
 \section{Impact}
-\label{}
 
+%\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+
+%Indicate in what way new research questions can be pursued as a result of the software (if any).
+
+%Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+
+%Indicate in what way the software has changed the daily practice of its users (if so).
+
+%Indicate how widespread the use of the software is within and outside the intended user group.
+
+%Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
+
+% ---------------------------------------------------- CONCLUSIONS -----------------------------------------------------
 \section{Conclusions}
-\label{}
+% Set out the conclusion of this original software publication.
 
-\section{Conflict of Interest}
+\section*{Funding}
+Our work was supported in part by NSF grant number 2145172 to J.R.M.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+
+\section*{Declaration of Competing Interest}
+We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
 
 \section*{Acknowledgements}
-\label{}
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% References:
+%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
 \bibliographystyle{elsarticle-num} 

### 2022-04-03 paper/main.tex
WIP motivation & significance section

@@
 
-\usepackage[hidelinks]{hyperref}
+\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
 \usepackage{breakurl}
@@
 \begin{abstract}
-% Text of abstract 
-% Ca. 100 words
+% 100-word limit (though many published articles don't seem to conform to this?)
+% \texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly in their code, and install them 
+% \texttt{davos} is a Python package that enables creating and sharing reproducible workflows as a single, ready-to-run IPython notebook. 
+\texttt{davos} is a Python package for sharing
 
@@
 \hline
-C1 & Current code version &  v0.1.0 \\
+C1 & Current code version &  v0.1.1 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
 \hline
@@
 \linenumbers
-%The permanent link to code/repository or the zip archive should include the following requirements:
-
-%README.txt and LICENSE.txt.
-
-%Source code in a src/ directory, not the root of the repository.
-
-%Tag corresponding with the version of the software that is reviewed.
-
-%Documentation in the repository in a docs/ directory, and/or READMEs, as appropriate.
 
@@
 \section{Motivation and significance}
+Modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work.
+Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, data analyses, tutorials, demos) that they may seek to share with a wide range of audiences, including collaborators, students, the broader scientific community, and the general public.
+Python has become one of the most widely used and fastest-growing scientific programming languages by offering both powerful research functionality and high-level accessibility \cite{MullEtal15}.
+In addition to the language’s intuitive, readable grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
+
+However, this also presents a challenge to sharing reproducible scientific Python code: different versions of a given package or library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
+While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
+Ensuring stable and reproducible results over time and across users therefore typically requires ensuring that shared code is always run with a specific set of versions for each package used.
+
+One common approach to solving this problem involves creating containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
+Authors may then share these environments alongside their code as configuration files from which users may build identical copies themselves.
+While effective, a significant drawback to this approach is that it introduces additional prerequisite knowledge
+
+% While effective, such tools can add a significant degree of complexity to the process of sharing research code for both the author and
+
+a significant drawback to this approach is that it adds to the requisite knowledge
+
+in many cases, it introduces a level of complexity beyond .
+For example, distributing research code that relies on a particular Docker image to run properly not only necessitates extra configuration files and setup steps, but requires that both the author and end user install and navigate additional software that is often more complicated and resource-intensive than the actual code being shared.
+These added prerequisites clash with the simplicity and accessibility that have helped popularize Python among researchers, and can create barriers to both contributing to and taking advantage of open science.
+\texttt{davos} was developed with the goal of addressing
 

### 2022-04-04 paper/main.tex
reframing motivation to include stability over time

@@
 \section{Motivation and significance}
-Modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work.
-Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, data analyses, tutorials, demos) that they may seek to share with a wide range of audiences, including collaborators, students, the broader scientific community, and the general public.
-Python has become one of the most widely used and fastest-growing scientific programming languages by offering both powerful research functionality and high-level accessibility \cite{MullEtal15}.
-In addition to the language’s intuitive, readable grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
+An essential feature of software used in scientific research is that it behaves consistently every time it is run.
+For example, stable code can be crucial to ensuring constant conditions during data collection (e.g., across recordings, trials, or subjects) and that accurate, reliable outputs from statistical analyses.
+Additionally, modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work.
+Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, analyses, tutorials, and demos) that they may seek to share with a wide range of audiences including collaborators, students, the broader scientific community, and the general public.
 
-However, this also presents a challenge to sharing reproducible scientific Python code: different versions of a given package or library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
+Python has become one of the most widely used and fastest-growing scientific programming languages by combining accessibility and readability with the availability of powerful research tools \cite{MullEtal15}.
+In addition to the language’s high-level, intuitive grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
+
+However, this also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of a third-party library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
 While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
-Ensuring stable and reproducible results over time and across users therefore typically requires ensuring that shared code is always run with a specific set of versions for each package used.
+Ensuring consistent behavior over time and across users therefore typically requires ensuring that code is shared and run with a specific set of versions for each package used.
 

### 2022-04-05 paper/main.tex
rework intro for clarity

--- 2022-04-03 paper/main.tex
@@
 \section{Motivation and significance}
-Modern open science practices encourage sharing code and data to enable others to explore, reproduce, learn from, and build upon existing work.
-Scientists, researchers, and educators produce many different forms of research-related code (e.g., experiments, data analyses, tutorials, demos) that they may seek to share with a wide range of audiences, including collaborators, students, the broader scientific community, and the general public.
-Python has become one of the most widely used and fastest-growing scientific programming languages by offering both powerful research functionality and high-level accessibility \cite{MullEtal15}.
-In addition to the language’s intuitive, readable grammar and large standard library, the Python ecosystem provides an extensive data science toolkit designed to facilitate rapid development and collaboration, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
+Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings via tutorials or public demos.
+One requirement common to nearly all research-related code it that its behavior and/or outputs must remain consistent and predictable every time it is run, both over time and across users.
+For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, consistent results.
+Additionally, modern open science practices encourage sharing code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
+Scientists, researchers, and educators may seek to share research-related code with a wide range of audiences including collaborators, students, the broader scientific community, and the general public.
 
-However, this also presents a challenge to sharing reproducible scientific Python code: different versions of a given package or library can behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
+Python has become one of the most widely used and fastest-growing scientific programming languages by combining an accessible, high-level syntax with the availability of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
+The Python ecosystem offers an extensive data science toolkit, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
+However, this also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same third-party library may behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
 While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
-Ensuring stable and reproducible results over time and across users therefore typically requires ensuring that shared code is always run with a specific set of versions for each package used.
+Ensuring consistent behavior over time and across users therefore typically requires ensuring that Python code is always run with a specific set of versions for each package used.
+
+One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
+Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and package versions, allowing others to build identical copies themselves.
+While powerful, this approach bears two significant drawbacks: First, it adds to the
 

### 2022-04-06 paper/main.tex
updates to motivation

@@
 \section{Motivation and significance}
-Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings via tutorials or public demos.
+Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings or techniques via tutorials or public demos.
 One requirement common to nearly all research-related code it that its behavior and/or outputs must remain consistent and predictable every time it is run, both over time and across users.
-For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, consistent results.
+For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, reliable results.
 Additionally, modern open science practices encourage sharing code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
-Scientists, researchers, and educators may seek to share research-related code with a wide range of audiences including collaborators, students, the broader scientific community, and the general public.
+Scientists, researchers, and educators may seek to share research code with audiences that have a wide range of scientific and technical backgrounds, including collaborators, students, the broader scientific community, and the general public.
 
 Python has become one of the most widely used and fastest-growing scientific programming languages by combining an accessible, high-level syntax with the availability of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
-The Python ecosystem offers an extensive data science toolkit, including platforms for interactive programming (e.g., Project Jupyter, \cite{KluyEtal16}; Google Colaboratory), community-maintained libraries for data manipulation (e.g., \texttt{NumPy} \cite{HarrEtal20}, \texttt{SciPy} \cite{VirtEtal20}, \texttt{Pandas} \cite{McKi10}) and visualization (e.g., \texttt{Matplotlib} \cite{Hunt07}, \texttt{seaborn} \cite{Wask21}), and myriad other tools.
-However, this also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same third-party library may behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
+The Python ecosystem offers an extensive data science toolkit, with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
+However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same package may behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
 While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
-Ensuring consistent behavior over time and across users therefore typically requires ensuring that Python code is always run with a specific set of versions for each package used.
+Ensuring Python code behaves consistently over time and across users therefore typically requires making sure it is always run with a specific set of versions for each package used.
+
+One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
+Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and versions, allowing other users to build identical copies for themselves.
+While effective, this approach bears two significant drawbacks: First it can substantially add to the technical knowledge, system resources, and setup required to share and run the encapsulated code.
 

### 2022-04-06 paper/main.tex
finish motivation

@@
 The Python ecosystem offers an extensive data science toolkit, with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
-However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same package may behave differently, use different syntax, add or drop support for specific functions or other libraries, address (or introduce) bugs, and so on.
+However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same library may behave differently, adopting different syntax, adding or dropping support for specific functions or other libraries, addressing (or introducing) bugs, and so on.
 While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
-Ensuring Python code behaves consistently over time and across users therefore typically requires making sure it is always run with a specific set of versions for each package used.
+Ensuring Python code behaves consistently over time and across users therefore typically requires making sure it is always run with the same specific set of versions for each package used.
 
 One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and versions, allowing other users to build identical copies for themselves.
-While effective, this approach bears two significant drawbacks: First it can substantially add to the technical knowledge, system resources, and setup required to share and run the encapsulated code.
+Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and versions, enabling other users to build identical copies for themselves.
+However, this approach comes with two major drawbacks: First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest.
+For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it supports.
+These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity among scientists, and can create significant barriers to both contributing to and taking advantage of open science resources.
 
-One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and package versions, allowing others to build identical copies themselves.
-While powerful, this approach bears two significant drawbacks: First, it adds to the
-
-One common approach to solving this problem involves creating containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Authors may then share these environments alongside their code as configuration files from which users may build identical copies themselves.
-While effective, a significant drawback to this approach is that it introduces additional prerequisite knowledge
-
-% While effective, such tools can add a significant degree of complexity to the process of sharing research code for both the author and
-
-a significant drawback to this approach is that it adds to the requisite knowledge
-
-in many cases, it introduces a level of complexity beyond .
-For example, distributing research code that relies on a particular Docker image to run properly not only necessitates extra configuration files and setup steps, but requires that both the author and end user install and navigate additional software that is often more complicated and resource-intensive than the actual code being shared.
-These added prerequisites clash with the simplicity and accessibility that have helped popularize Python among researchers, and can create barriers to both contributing to and taking advantage of open science.
-\texttt{davos} was developed with the goal of addressing
+Second, typical environment management tools don't enforce that a particular requirements \textit{remain} satisfied after they are initially installed.
+While this provides a degree of flexibility in certain use cases, it makes it easy to inadvertently alter the set of installed Python packages after this initial setup.
+For example, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis requiring ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgraded to accommodate this new requirement, potentially leading to inconsistent behavior of code that uses Package \textit{X} if this change goes unnoticed.
 

### 2022-04-07 paper/main.tex
use hyphenat package to allow linebreaks in \texttt
finished problems section

@@
 \usepackage{breakurl}
+\usepackage[htt]{hyphenat}
 
@@
 
-Second, typical environment management tools don't enforce that a particular requirements \textit{remain} satisfied after they are initially installed.
-While this provides a degree of flexibility in certain use cases, it makes it easy to inadvertently alter the set of installed Python packages after this initial setup.
-For example, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis requiring ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgraded to accommodate this new requirement, potentially leading to inconsistent behavior of code that uses Package \textit{X} if this change goes unnoticed.
+%Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed.
+This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them.
+For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement.
+potentially altering or breaking the previous analyses  in future runs, as well as for anyone with whom  analysis code.
+Further, if earlier analyses require functionality
+
+Second, although many tools exist for installing Python packages in an isolated environment from a fixed set of required packages (e.g., in a \texttt{requirements.txt}, \texttt{pyproject.toml}, \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN} instruction, etc.), few if any enforce that the specified requirements \textit{remain} satisfied after this initial setup.
+The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software as needed); however, it also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them.
+For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking prior analyses for both the researcher and anyone with whom their code may be shared.
+Further, if certain analyses require Package \textit{Y} while others rely on a feature of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in the environment.
 

### 2022-04-07 paper/main.tex
reorganized source to 1 sentence per line, recompiled pdf

@@
 % 100-word limit (though many published articles don't seem to conform to this?)
-% \texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly in their code, and install them 
-% \texttt{davos} is a Python package that enables creating and sharing reproducible workflows as a single, ready-to-run IPython notebook. 
-\texttt{davos} is a Python package for sharing
-
 \end{abstract}
@@
 One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Researchers can then share these environments alongside their code as configuration files that explicitly list required packages and versions, enabling other users to build identical copies for themselves.
-However, this approach comes with two major drawbacks: First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest.
-For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it supports.
-These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity among scientists, and can create significant barriers to both contributing to and taking advantage of open science resources.
+Researchers can then share these environments alongside their code as configuration files that explicitly list required package versions, enabling other users to build identical copies for themselves.
+While often effective, this approach comes with two notable drawbacks: 
+First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest. 
+For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it is used to manage.
+These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.
 
 %Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed. 
-This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them.
-For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement.
-potentially altering or breaking the previous analyses  in future runs, as well as for anyone with whom  analysis code.
-Further, if earlier analyses require functionality
+%This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them. 
+%For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."
+%If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement, potentially altering or breaking the previous analyses in future runs, as well as for anyone with whom  analysis code.
+%Further, if earlier analyses require functionality
 
@@
 The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software as needed); however, it also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them.
-For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking prior analyses for both the researcher and anyone with whom their code may be shared.
+For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."
+If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking prior analyses for both the researcher and anyone with whom their code may be shared.
 Further, if certain analyses require Package \textit{Y} while others rely on a feature of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in the environment.

### 2022-04-13 paper/main.tex
author contribution section
add current uses to impact section

@@
 \section{Impact}
+\comment{
+- research domain-independent application
+- applicability not limited to research
+  - regression (?) testing
+- mention something about not having to teach environment management to teach day 1 python lesson, or spend hours debugging conda installation in order to share tutorial or demo with students
+}
+
+Despite the short time since its conception and initial release, \texttt{davos} has already found use in a variety of applications. 
+In addition to managing data analysis environments for multiple ongoing research studies, \texttt{davos} is being used by both students and instructors in programming courses such as \href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling with Data}} \cite{Mann21b} (an open course on data science, visualization, and communication) to simplify distributing lessons and submitting assignments, as well as in online demos such as {\texttt{abstract2paper}} \cite{Mann21a} (an example application of \href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share ready-to-run code that installs dependencies automatically.
 
@@
 
+\section*{Author Contributions}
+\textbf{Paxton C.
+Fitzpatrick}: Conceptualization, Methodology, Software, Validation, Writing - Original Draft, Visualization.
+\textbf{Jeremy R.
+Manning}: Conceptualization, Resources, Writing - Review \& Editing, Supervision, Funding acquisition.
+
 \section*{Funding}

### 2022-08-10 paper/main.tex
software functionalities subsections
updates to first paragraph

@@
 \section{Motivation and significance}
-Modern scientific research often involves writing code for a variety of purposes throughout the research process, from designing experiments, to analyzing and visualizing data, to presenting findings or techniques via tutorials or public demos.
-One requirement common to nearly all research-related code it that its behavior and/or outputs must remain consistent and predictable every time it is run, both over time and across users. 
-For example, this stability can be critical to ensuring that data are collected under constant conditions (e.g., across recordings, trials, or subjects) and that statistical analyses yield accurate, reliable results.
-Additionally, modern open science practices encourage sharing code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work. 
-Scientists, researchers, and educators may seek to share research code with audiences that have a wide range of scientific and technical backgrounds, including collaborators, students, the broader scientific community, and the general public.
+Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process:
+researchers across disciplines design and implement experimental paradigms; collect, process, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
+However, one requirement common to nearly all research-related code is that it behave consistently and predictably every time it is run, both over time and across different users.
+This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects) over multiple months or years, and can be processed and analyzed consistently by collaborators across multiple institutions or countries.
+Additionally, modern open science practices encourage sharing research code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
+Much of the benefit afforded by freely available research code relies on users ability to execute it and achieve the same result as its original author.
 
@@
 
-\subsection{Software Functionalities}
+\subsection{Software functionalities}\label{sec:functionalities}
+
+\subsection{The \texttt{smuggle} statement}
+
+\subsection{The onion comment}
+
+\subsection{The \texttt{davos} config}
+
+\subsection{Additional functionality}
+
 % Present the major functionalities of the software.

### 2022-09-19 paper/main.tex
whitespace-only changes (pycharm removed trailing whitespace)
updates to paragraphs 1 & 2

@@
 \section{Motivation and significance}
-Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process:
-researchers across disciplines design and implement experimental paradigms; collect, process, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
-However, one requirement common to nearly all research-related code is that it behave consistently and predictably every time it is run, both over time and across different users.
-This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects) over multiple months or years, and can be processed and analyzed consistently by collaborators across multiple institutions or countries.
-Additionally, modern open science practices encourage sharing research code and data publicly to enable others to explore, reproduce, learn from, and build upon existing work.
-Much of the benefit afforded by freely available research code relies on users ability to execute it and achieve the same result as its original author.
+Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process.
+Researchers across disciplines may design and implement complex experiments; collect, store, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
+However, one requirement common to virtually all forms of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
+This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects)
+%^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
+over multiple months or years, and that they can be accessed, processed, and analyzed consistently by a research team that may be spread across multiple institutions or countries.
+Additionally, modern open science practices encourage publicly sharing research code and data so that others may explore, reproduce, learn from, and build upon existing work.
+Much of the benefit afforded by freely available research code depends on users' ability to execute it and achieve the same result as its original author.
 
-Python has become one of the most widely used and fastest-growing scientific programming languages by combining an accessible, high-level syntax with the availability of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
-The Python ecosystem offers an extensive data science toolkit, with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
-However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code: different versions of the same library may behave differently, adopting different syntax, adding or dropping support for specific functions or other libraries, addressing (or introducing) bugs, and so on.
-While these issues are present to some extent in any language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages. 
-Ensuring Python code behaves consistently over time and across users therefore typically requires making sure it is always run with the same specific set of versions for each package used.
+Python \cite{vanR95} has become one of the most widely used and fastest-growing scientific programming languages, in part by combining an accessible, high-level syntax with a rich ecosystem of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
+The Python ecosystem offers an extensive data science toolkit with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
+However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code:
+different versions of the same library may behave differently, adopt changes in syntax, expose different functions and interfaces, add or drop support for specific hardware or software, write (or expect to read) files in different formats, fix (or introduce) bugs, and so on.
+While these issues exist to some extent in any software language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
+Ensuring Python code behaves consistently over time and across users therefore typically requires ensuring it is always run with the same specific set of versions for each third-party package used.
+%Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
 

### 2022-09-20 paper/main.tex
updtes to par 3

@@
 
-One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Researchers can then share these environments alongside their code as configuration files that explicitly list required package versions, enabling other users to build identical copies for themselves.
-While often effective, this approach comes with two notable drawbacks:
-First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest.
-For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it is used to manage.
+One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using Docker \cite{Merk14}, Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to individual applications.
+A researcher may build such an environment around a specific experiment or analysis pipeline, and exclusively run their code from inside it, ``entering" and ``exiting" the environment before and after each time they do so.
+They can also share their custom environment alongside their code as a configuration file that explicitly lists required package versions, enabling others to build identical copies for themselves.
+While often effective, this approach bears two notable drawbacks.
+First, it can add substantially to the technical knowledge, computing resources, and initial setup needed to run or share the actual code of interest.
+%For example, sharing an analysis or tutorial that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires both the original author and anyone with whom the code is shared to first install and navigate additional software that is likely more complex and resource-intensive than the actual code it facilitates running.
+%For example, sharing an analysis or tutorial that relies on a particular Docker image to run properly not only necessitates writing and distributing extra configuration files and setup instructions, but more significantly, requires both the original author and anyone else who may want to run their code to first be able to install and be able to use additional software that is likely more complex and resource-intensive than the actual code it facilitates running.
+For example, sharing an analysis or tutorial that relies on a particular Docker image to run properly would, of course, necessitate writing and distributing extra configuration files and setup instructions.
+While this may seem like merely a minor inconvenience to a seasoned user of such tooling,
+
+But far more significantly, it would also require both the original author and anyone else who may want to run their code to first be able to install and be able to use additional software that is likely more complex and resource-intensive than the actual code it facilitates running.
 These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.

### 2022-09-30 paper/main.tex
WIP abstract updates

--- 2022-09-19 paper/main.tex
@@
 % 100-word limit (though many published articles don't seem to conform to this?)
+% \texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly in their code, and install them
+% \texttt{davos} is a Python package that enables creating and sharing reproducible workflows as a single, ready-to-run IPython notebook.
+
+%davos is a python package for creating, sharing, and running reproducible code without the need for
+
+TODO: clean up after writing body
+
+Reproducible code plays many important roles in modern scientific research: it enables scientists to collaborate on projects,\comment{parallelize data collection across multiple sites or machines} replicate and extend prior work, and teach students new concepts and techniques via hands-on, interactive tutorials.
+However, existing tools that facilitate creating, sharing, and running reproducible code are often highly complex and resource-intensive, creating barriers to both contributing to and benefitting from open science resources.
+Here, we introduce \texttt{davos}, a Python package that allows users to create and share reproducible workflows...
+
+%Many important parts of modern scientific research depend on writing, sharing, and running reproducible code.
+It enables scientists to collaborate on projects, replicate and extend prior work, and teach students new ideas and techniques through hands-on, interactive tutorials.
+
+%The ability to write, share, and run reproducible code plays many important roles in modern scientific research:
+
+%Writing and sharing reproducible code plays an important role in modern scientific research, enabling scientists to collaborate on projects, replicate and extend previous work, and teach students concepts and techniques through
+
+%\texttt{davos} is a Python package that provides a simple, accessible, and effective way to manage and share reproducible code.
+
+%\texttt{davos} provides the \texttt{smuggle} statement
+
+%\texttt{davos} is a Python package that allows users to write, run, and share reproducible Python code without the need for containers or virtual environments.
+
+%davos is a Python package that allows users to manage and share reproducible code without the need for containers or virtual environments.
+
+%\texttt{davos} is a Python package for creating, running, and sharing reproducible workflows without the need for external containerized or virtualized environments.
+
+%\texttt{davos} is a Python package that makes writing, running, and sharing reproducible code easy.
+Importing \texttt{davos} in an IPython notebook enables the \textit{smuggle} statement: a drop-in replacement for the built-in \textit{import} statement that can install missing packages as needed at runtime, and may be
+
+%\texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly within their code and install packages as needed at runtime.
+
+%\texttt{davos} works by providing the \textit{smuggle} statement: a drop-in replacement for the built-in \texttt{import} statement that  \_\_\_, and the
+
 \end{abstract}
@@
 \section{Motivation and significance}
-Modern scientific research often entails writing software code for a wide variety of purposes throughout the scientific process.
+Modern scientific research frequently entails writing software code for a wide variety of purposes throughout the scientific process.
 Researchers across disciplines may design and implement complex experiments; collect, store, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
-However, one requirement common to virtually all forms of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
-This stability can be crucial to ensuring, for example, that data are collected under the same conditions (e.g., across recordings, trials, or subjects)
+However, one fundamental requirement of virtually any form of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
+This stability can be crucial, for example, to ensuring that data are collected under the same conditions (e.g., across recordings, subjects, or physical locations)
 %^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
@@
 
-One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using \href{https://www.docker.com/}{Docker}, \href{https://sylabs.io/singularity/}{Singularity}, or \href{https://docs.conda.io/en/latest/}{conda}) tailored to individual applications.
-Researchers can then share these environments alongside their code as configuration files that explicitly list required package versions, enabling other users to build identical copies for themselves.
-While often effective, this approach comes with two notable drawbacks:
-First, it can add significantly to the technical knowledge, system resources, and initial setup required to share and run the actual code of interest.
-For example, sharing research code that relies on a particular Docker image to run properly not only necessitates distributing extra configuration files and setup instructions, but also requires that both the original author and anyone with whom the code may be shared install and navigate additional software that is likely more complex and resource-intensive than the Python code it is used to manage.
+One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using Docker \cite{Merk14}, Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to individual applications.
+A researcher may build such an environment around a particular experiment or analysis pipeline, and exclusively run their code from inside it, ``entering" and ``exiting" the environment before and after each time they do so.
+They can also share this custom environment alongside their code as a configuration file that explicitly lists required package versions, enabling others to build identical copies for themselves.
+
+While often effective, this approach bears two notable drawbacks.
+First, it can add substantially to the technical knowledge, computing resources, and initial setup needed to run or share the actual code of interest.
+For example, sharing code for an analysis or tutorial that relies on a particular Docker image to run properly naturally requires writing and distributing extra configuration files and setup instructions.
+But much more significantly, it also requires anyone hoping to run code to first be able to install and navigate additional software that is usually far more complex and resource-intensive than the actual analysis or tutorial code it facilitates running.
 These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.

### 2022-09-30 paper/main.tex
add PyPI to metadata C6
additional cleanup and tweaks to opening

@@
 \hline
-C6 & Software code languages, tools, and services used & Python, JavaScript, pip, IPython, Jupyter, Ipykernel, PyZMQ.
+C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, Ipykernel, PyZMQ.
 Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
@@
 A researcher may build such an environment around a particular experiment or analysis pipeline, and exclusively run their code from inside it, ``entering" and ``exiting" the environment before and after each time they do so.
-They can also share this custom environment alongside their code as a configuration file that explicitly lists required package versions, enabling others to build identical copies for themselves.
+They can also distribute their custom environment alongside their code as a configuration file that explicitly lists required package versions, enabling others to build identical copies for themselves.
+This allows research teams to deploy experiments on multiple machines for more efficient data collection, collaborate on analyses without introducing conflicts or inconsistencies, and publicly share their study designs and results for others to reproduce, replicate, or adapt to study new questions in the future.
 
@@
 First, it can add substantially to the technical knowledge, computing resources, and initial setup needed to run or share the actual code of interest.
-For example, sharing code for an analysis or tutorial that relies on a particular Docker image to run properly naturally requires writing and distributing extra configuration files and setup instructions.
-But much more significantly, it also requires anyone hoping to run code to first be able to install and navigate additional software that is usually far more complex and resource-intensive than the actual analysis or tutorial code it facilitates running.
+For example, sharing code for an analysis or tutorial that relies on a particular Docker image to run properly would of course necessitate writing and distributing extra configuration files and setup instructions.
+But far more burdensomely, it also requires that anyone who may want to run the code (in addition to the author seeking to share it!) first be able to install and navigate additional software that is likely far more complex and resource-intensive than the actual analysis or tutorial code it facilitates running.
+This can introduce a need for both a degree of computer literacy and computational resources that may not be universally accessible, particularly to students or other early-career scientists hoping to learn from publicly available tutorials.
 These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.
 
-%Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed.
-%This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them.
-%For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."
-%If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement, potentially altering or breaking the previous analyses in future runs, as well as for anyone with whom  analysis code.
-%Further, if earlier analyses require functionality
-
-Second, although many tools exist for installing Python packages in an isolated environment from a fixed set of required packages (e.g., in a \texttt{requirements.txt}, \texttt{pyproject.toml}, \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN} instruction, etc.), few if any enforce that the specified requirements \textit{remain} satisfied after this initial setup.
-The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software as needed); however, it also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them.
+Second, while many existing tools allow users to initially populate a Python environment with a fixed set of packages and package versions (e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml}, \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN} instruction, etc.), few, if any, ensure that these specified requirements \textit{remain} satisfied after they are first installed.
+The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software, when needed).
+However, this also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them.
 For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."

### 2022-09-30 paper/main.tex
add some more relevant keywords
rough version of software functionalities section

@@
 \begin{keyword}
-Python \sep Jupyter Notebook \sep Google Colaboratory \sep Reproducibility \sep Package management \sep Pip install
+Reproducibility \sep Open science \sep Python \sep Jupyter Notebook \sep Google Colaboratory \sep Package management
 \end{keyword}
@@
 
-\subsection{Software functionalities}\label{sec:functionalities}
+\subsection{Software functionalities}%\label{sec:functionalities}
 
-\subsection{The \texttt{smuggle} statement}
+\subsubsection{The \texttt{smuggle} statement}
+Importing \texttt{davos}\comment{in a Jupyter notebook} enables an additional Python keyword: ``\texttt{smuggle}".
+The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
+However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
+If a smuggled package does not exist in the local environment, \texttt{davos} will install it, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.
 
-\subsection{The onion comment}
+\subsubsection{The onion comment}
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}.
+An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
+Onion comments follow a simple syntax based on the ``type comment" syntax introduced in PEP 484 \cite{vanREtal14} and are designed to make managing packages via \texttt{davos} intuitive and familiar.
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
 
-\subsection{The \texttt{davos} config}
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
+\caption{\small \textbf{Figure 1}}
+\label{fig:snippet1}
+\end{figure}
 
-\subsection{Additional functionality}
+%\definecolor{backgroundgrey}{RGB}{244,246,249}
+%\definecolor{commentgrey}{RGB}{91,99,110}
+%\definecolor{keywordred}{RGB}{194,11,36}
+%
+%\lstset{
+%    backgroundcolor=\color{backgroundgrey},
+%    basicstyle=\footnotesize\fontfamily{qag}\selectfont, %\ttfamily,
+%    breaklines=true,
+%    commentstyle=\color{commentgrey},
+%    language=Python,
+%    emph={import, smuggle, from, as},
+%    emphstyle=\color{keywordred},
+%}
+%
+%\begin{lstlisting}
+%import davos
+%
+%# if numpy is not installed locally, pip-install it and display verbose output
+%smuggle numpy as np    # pip: numpy --verbose
+%
+%# pip-install pandas without using or writing to the package cache
+%smuggle pandas as pd    # pip: pandas --no-cache-dir
+%
+%# install scipy from a relative local path, in editable mode
+%from scipy.stats smuggle ttest_ind # pip: -e ../../pkgs/scipy
+%\end{lstlisting}
+
+\subsubsection{The \texttt{davos} config}
+
+\subsubsection{Additional functionality}
 

### 2022-09-30 paper/main.tex
final comments and cleanup for now

@@
 
+% ======== additional package not in SoftwareX template ========
 \usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
@@
 \usepackage[htt]{hyphenat}
+%\usepackage{listings}
+%\usepackage{xcolor}
+%\usepackage{todonotes}
+
+% \let\oldtodo\todo
+% \renewcommand{\todo}[1]{\oldtodo[tickmarkheight=0.5em]{#1}}
+
+\newcommand{\comment}[1]{}
+% =================================================
 
@@
 % 100-word limit (though many published articles don't seem to conform to this?)
-% \texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly in their code, and install them
-% \texttt{davos} is a Python package that enables creating and sharing reproducible workflows as a single, ready-to-run IPython notebook.
-
-%davos is a python package for creating, sharing, and running reproducible code without the need for
 
@@
 Here, we introduce \texttt{davos}, a Python package that allows users to create and share reproducible workflows...
-
-%Many important parts of modern scientific research depend on writing, sharing, and running reproducible code.
-It enables scientists to collaborate on projects, replicate and extend prior work, and teach students new ideas and techniques through hands-on, interactive tutorials.
-
-%The ability to write, share, and run reproducible code plays many important roles in modern scientific research:
-
-%Writing and sharing reproducible code plays an important role in modern scientific research, enabling scientists to collaborate on projects, replicate and extend previous work, and teach students concepts and techniques through
-
-%\texttt{davos} is a Python package that provides a simple, accessible, and effective way to manage and share reproducible code.
-
-%\texttt{davos} provides the \texttt{smuggle} statement
-
-%\texttt{davos} is a Python package that allows users to write, run, and share reproducible Python code without the need for containers or virtual environments.
-
-%davos is a Python package that allows users to manage and share reproducible code without the need for containers or virtual environments.
-
-%\texttt{davos} is a Python package for creating, running, and sharing reproducible workflows without the need for external containerized or virtualized environments.
-
-%\texttt{davos} is a Python package that makes writing, running, and sharing reproducible code easy.
-Importing \texttt{davos} in an IPython notebook enables the \textit{smuggle} statement: a drop-in replacement for the built-in \textit{import} statement that can install missing packages as needed at runtime, and may be
-
-%\texttt{davos} is a Python package for creating self-managing, reproducible workflows that specify dependencies directly within their code and install packages as needed at runtime.
-
-%\texttt{davos} works by providing the \textit{smuggle} statement: a drop-in replacement for the built-in \texttt{import} statement that  \_\_\_, and the
 
@@
 For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."
-If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking prior analyses for both the researcher and anyone with whom their code may be shared.
-Further, if certain analyses require Package \textit{Y} while others rely on a feature of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in the environment.
+If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking previous analyses when they are rerun later, either by the researcher or someone with whom they've shared their code.
+Further, if some analyses require Package \textit{Y} while others rely on features of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in their environment.
+
+%The \texttt{davos} package provides a novel, Python-native framework for creating, sharing, and running reproducible workflows that was designed to address each of these issues.
+The \texttt{davos} package provides a novel, Python-native framework for creating reproducible workflows that was designed to address each of these issues.
+\texttt{davos} allows users to specify dependencies directly within the code that...
+
+\comment {
+POINTS TO MAKE/THINGS TO SAY HERE TO WRAP UP (or maybe save some for impact section?):
+- davos simplifies the process of writing, sharing, and running reproducible code (eliminates need for additional complex env management tools, syntax is simple, packages are just installed at runtime without additional setup beforehand, etc.)...
+- ...it also provides stability/additional protections against accidental changes in ways other tools don't (i.e., addresses issue 2 above) by verifying (and installing if necessary) requirements each time code is run
+- ... while simultaneously enabling new package management patterns (using multiple versions versions of package in same notebook, etc.)
+- it's lightweight and intuitive (unlike big/complex env management tools like docker, etc.)
+- "davos was specifically designed for use with Jupyter notebook environments, and can be used either on its own or in tandem with another environment management tool"
+- "\texttt{davos} was designed specifically for use in Jupyter notebook (formerly called IPython notebook \cite{PereGran07}) environments, and supports Jupyter notebooks \cite{KluyEtal16}, JupyterLab \cite{GranGrou16}, Google Colaboratory, Binder \cite{RagaWill18}, and IDE-based notebook editors."
+
+- maybe don't mention smuggle statement \& onion comment explicitly in this paragraph since they haven't been defined/explained yet, or if we do, then add some sort of "see \_\_\_ below" with \\ref to relevant subsection
+}
 
@@
 
-\subsection{Software Architecture}
+\subsection{Software architecture}
+The \texttt{davos} package is structured as two subpackages: a set of ``core" modules that implement...
+
 % Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
@@
 \comment{
-- research domain-independent application
+- emphasize research domain-independent application (Journal's goals/values page says they prioritize this in submissions)
 - applicability not limited to research
     - regression (?) testing
+    - ***^^not sure this should be included -- hurts framing of davos as "research software"***
+- makes writing and running publicly available reproducible code more accessible (lowers required software comfort/familiarity level \& computing resources vs. installing docker/singularity/conda)
+    - also removes these requirements from other scenarios, e.g., easier for new/less experienced students/RAs to get involved with analyses
 - mention something about not having to teach environment management to teach day 1 python lesson, or spend hours debugging conda installation in order to share tutorial or demo with students
+    - e.g., "researchers who teach \_\_\_ may be familiar with the experience of running a lesson or workshop that requires students to use Docker (or similar...) to run their code, only to spend the majority of class time debugging students' computing environments rather than teaching the lesson itself."
 }
 
-Despite the short time since its conception and initial release, \texttt{davos} has already found use in a variety of applications.
+Since its initial release, \texttt{davos} has found use in a variety of applications.
 In addition to managing data analysis environments for multiple ongoing research studies, \texttt{davos} is being used by both students and instructors in programming courses such as \href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling with Data}} \cite{Mann21b} (an open course on data science, visualization, and communication) to simplify distributing lessons and submitting assignments, as well as in online demos such as {\texttt{abstract2paper}} \cite{Mann21a} (an example application of \href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share ready-to-run code that installs dependencies automatically.

### 2022-10-03 paper/main.tex
rewrote introduction, added shareable code figure

@@
 
-\title{\texttt{davos}: The Python package smuggler}
+\title{\texttt{davos}: a Python package ``smuggler'' for constructing
+  lightweight reproducible notebooks}
 \author{Paxton C. Fitzpatrick}
@@
 \begin{abstract}
-% 100-word limit (though many published articles don't seem to conform to this?)
+% 100-word limit (though many published articles don't seem to conform
+% to this?)
 
-TODO: clean up after writing body
-
-Reproducible code plays many important roles in modern scientific research: it enables scientists to collaborate on projects,\comment{parallelize data collection across multiple sites or machines} replicate and extend prior work, and teach students new concepts and techniques via hands-on, interactive tutorials.
-However, existing tools that facilitate creating, sharing, and running reproducible code are often highly complex and resource-intensive, creating barriers to both contributing to and benefitting from open science resources.
-Here, we introduce \texttt{davos}, a Python package that allows users to create and share reproducible workflows...
+A core requirement of modern scientific research is replicability.
+For computational research, replicability means that code should
+produce the same results, even when run on different systems.  The
+standard solution to improving replicability entails packaging a
+project's dependencies along with its primary code base.  Existing
+solutions vary in how deeply these dependencies are specified, ranging
+from virtual environments (which specify all Python package versions),
+to containers (which also specify the operating system), to
+virtual machines (which also specify hardware layers of the system).
+Each of these existing solutions requires installing or setting up a
+system for running the desired code that must be packaged alongside
+the primary code base.  Here we propose an even lighter-weight
+solution than virtual environments: the \texttt{davos} library.  When
+used in combination with a notebook-based Python project, \texttt{davos}
+library provides a mechanism for specifying (and automatically
+installing) the correct package versions of the project's.  This
+enables researchers to share a complete reproducible environment using
+a single iPython notebook file.
 
@@
 \hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Please fill in this column} \\
+\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Notes} \\
 \hline
@@
 \hline
-C8 & If available Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
+C8 & Link to developer documentation/manual & \url{https://github.com/ContextLab/davos\#readme} \\
 \hline
@@
 \section{Motivation and significance}
-Modern scientific research frequently entails writing software code for a wide variety of purposes throughout the scientific process.
-Researchers across disciplines may design and implement complex experiments; collect, store, and analyze large datasets; create visualizations for presentations and publications; and share their findings and techniques with peers, students, and the broader public through tutorials, demos, workshops, and classes.
-However, one fundamental requirement of virtually any form of research-related code is that its behavior and outputs remain consistent and predictable, no matter when, where, or by whom it is run.
-This stability can be crucial, for example, to ensuring that data are collected under the same conditions (e.g., across recordings, subjects, or physical locations)
+
+Jupyter (iPython) notebooks~\citep{KluyEtal16} have revolutionized
+code sharing by providing a single filetype that combines text, code,
+and figures.  For projects that depend on other software packages,
+however, additional work is often required to enable the code to run
+as its authors intended.  For example, a piece of software that
+depends on version 0.8 of package \textit{X} may behave differently
+(or may fail to run at all) if the user instead attempts to run the
+code in an environment with version 0.9 of package \textit{X}.
+
+% STOPPED HERE...
+
+Sharing a project's code base is most valuable when that code may be
+run on
+
+Modern scientific research frequently entails writing software code
+for a wide variety of purposes throughout the scientific process.
+Researchers across disciplines may design and implement complex
+experiments; collect, store, and analyze large datasets; create
+visualizations for presentations and publications; and share their
+findings and techniques with peers, students, and the broader public
+through tutorials, demos, workshops, and classes.  However, one
+fundamental requirement of virtually any form of research-related code
+is that its behavior and outputs remain consistent and predictable, no
+matter when, where, or by whom it is run.  This stability can be
+crucial, for example, to ensuring that data are collected under the
+same conditions (e.g., across recordings, subjects, or physical
+locations)
 %^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
-over multiple months or years, and that they can be accessed, processed, and analyzed consistently by a research team that may be spread across multiple institutions or countries.
-Additionally, modern open science practices encourage publicly sharing research code and data so that others may explore, reproduce, learn from, and build upon existing work.
-Much of the benefit afforded by freely available research code depends on users' ability to execute it and achieve the same result as its original author.
+over multiple months or years, and that they can be accessed,
+processed, and analyzed consistently by a research team that may be
+spread across multiple institutions or countries.  Additionally,
+modern open science practices encourage publicly sharing research code
+and data so that others may explore, reproduce, learn from, and build
+upon existing work.  Much of the benefit afforded by freely available
+research code depends on users' ability to execute it and achieve the
+same result as its original author.
 
-Python \cite{vanR95} has become one of the most widely used and fastest-growing scientific programming languages, in part by combining an accessible, high-level syntax with a rich ecosystem of powerful third-party tools that facilitate rapid development and collaboration \cite{MullEtal15}.
-The Python ecosystem offers an extensive data science toolkit with platforms for interactive programming (e.g., Project Jupyter \cite{KluyEtal16}, Google Colaboratory), community-maintained libraries for data manipulation (e.g., NumPy \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}), frameworks for training complex machine learning models (e.g., scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging Face \cite{WolfEtal20}), and myriad other resources.
-However, this heavy emphasis on third-party libraries also presents a challenge to writing and sharing stable, reproducible scientific Python code:
-different versions of the same library may behave differently, adopt changes in syntax, expose different functions and interfaces, add or drop support for specific hardware or software, write (or expect to read) files in different formats, fix (or introduce) bugs, and so on.
-While these issues exist to some extent in any software language or ecosystem, they have a particular impact on the Python community due to its unusually rapid growth relative to other languages.
-Ensuring Python code behaves consistently over time and across users therefore typically requires ensuring it is always run with the same specific set of versions for each third-party package used.
+Python \cite{vanR95} has become one of the most widely used and
+fastest-growing scientific programming languages, in part by combining
+an accessible, high-level syntax with a rich ecosystem of powerful
+third-party tools that facilitate rapid development and collaboration
+\cite{MullEtal15}.  The Python ecosystem offers an extensive data
+science toolkit with platforms for interactive programming (e.g.,
+Project Jupyter \cite{KluyEtal16}, Google Colaboratory),
+community-maintained libraries for data manipulation (e.g., NumPy
+\cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and
+visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}),
+frameworks for training complex machine learning models (e.g.,
+scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging
+Face \cite{WolfEtal20}), and myriad other resources.  However, this
+heavy emphasis on third-party libraries also presents a challenge to
+writing and sharing stable, reproducible scientific Python code:
+different versions of the same library may behave differently, adopt
+changes in syntax, expose different functions and interfaces, add or
+drop support for specific hardware or software, write (or expect to
+read) files in different formats, fix (or introduce) bugs, and so on.
+While these issues exist to some extent in any software language or
+ecosystem, they have a particular impact on the Python community due
+to its unusually rapid growth relative to other languages.  Ensuring
+Python code behaves consistently over time and across users therefore
+typically requires ensuring it is always run with the same specific
+set of versions for each third-party package used.
 %Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
 
-One common approach to solving this problem is to create containerized or virtualized Python environments (e.g., using Docker \cite{Merk14}, Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to individual applications.
-A researcher may build such an environment around a particular experiment or analysis pipeline, and exclusively run their code from inside it, ``entering" and ``exiting" the environment before and after each time they do so.
-They can also distribute their custom environment alongside their code as a configuration file that explicitly lists required package versions, enabling others to build identical copies for themselves.
-This allows research teams to deploy experiments on multiple machines for more efficient data collection, collaborate on analyses without introducing conflicts or inconsistencies, and publicly share their study designs and results for others to reproduce, replicate, or adapt to study new questions in the future.
+One common approach to solving this problem is to create containerized
+or virtualized Python environments (e.g., using Docker \cite{Merk14},
+Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to
+individual applications.  A researcher may build such an environment
+around a particular experiment or analysis pipeline, and exclusively
+run their code from inside it, ``entering" and ``exiting" the
+environment before and after each time they do so.  They can also
+distribute their custom environment alongside their code as a
+configuration file that explicitly lists required package versions,
+enabling others to build identical copies for themselves.  This allows
+research teams to deploy experiments on multiple machines for more
+efficient data collection, collaborate on analyses without introducing
+conflicts or inconsistencies, and publicly share their study designs
+and results for others to reproduce, replicate, or adapt to study new
+questions in the future.
 
 While often effective, this approach bears two notable drawbacks.
-First, it can add substantially to the technical knowledge, computing resources, and initial setup needed to run or share the actual code of interest.
-For example, sharing code for an analysis or tutorial that relies on a particular Docker image to run properly would of course necessitate writing and distributing extra configuration files and setup instructions.
-But far more burdensomely, it also requires that anyone who may want to run the code (in addition to the author seeking to share it!) first be able to install and navigate additional software that is likely far more complex and resource-intensive than the actual analysis or tutorial code it facilitates running.
-This can introduce a need for both a degree of computer literacy and computational resources that may not be universally accessible, particularly to students or other early-career scientists hoping to learn from publicly available tutorials.
-These added prerequisites clash with the simplicity and accessibility that have contributed to Python's popularity, and can create significant barriers to both contributing to and taking advantage of open science resources.
+First, it can add substantially to the technical knowledge, computing
+resources, and initial setup needed to run or share the actual code of
+interest.  For example, sharing code for an analysis or tutorial that
+relies on a particular Docker image to run properly would of course
+necessitate writing and distributing extra configuration files and
+setup instructions.  But far more burdensomely, it also requires that
+anyone who may want to run the code (in addition to the author seeking
+to share it!) first be able to install and navigate additional
+software that is likely far more complex and resource-intensive than
+the actual analysis or tutorial code it facilitates running.  This can
+introduce a need for both a degree of computer literacy and
+computational resources that may not be universally accessible,
+particularly to students or other early-career scientists hoping to
+learn from publicly available tutorials.  These added prerequisites
+clash with the simplicity and accessibility that have contributed to
+Python's popularity, and can create significant barriers to both
+contributing to and taking advantage of open science resources.
 
-Second, while many existing tools allow users to initially populate a Python environment with a fixed set of packages and package versions (e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml}, \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN} instruction, etc.), few, if any, ensure that these specified requirements \textit{remain} satisfied after they are first installed.
-The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software, when needed).
-However, this also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them.
-For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}."
-If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking previous analyses when they are rerun later, either by the researcher or someone with whom they've shared their code.
-Further, if some analyses require Package \textit{Y} while others rely on features of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in their environment.
+Second, while many existing tools allow users to initially populate a
+Python environment with a fixed set of packages and package versions
+(e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml},
+\texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN}
+instruction, etc.), few, if any, ensure that these specified
+requirements \textit{remain} satisfied after they are first installed.
+The ability to modify an environment after its creation is useful in
+many cases (e.g., to install additional software, when
+needed). However, this also makes it easy to inadvertently alter
+existing packages, potentially leading to subtle issues with code that
+relies on them.  For instance, suppose a researcher has implemented a
+series of analyses using version 1.0 of ``Package \textit{X}," and
+decides to perform an additional analysis that requires installing
+``Package \textit{Y}."  If Package \textit{Y} depends on version 0.9
+of Package \textit{X}, then Package \textit{X} will be downgraded to
+accommodate this new requirement, potentially altering or breaking
+previous analyses when they are rerun later, either by the researcher
+or someone with whom they've shared their code.  Further, if some
+analyses require Package \textit{Y} while others rely on features of
+Package \textit{X} not implemented until version 1.0, it's unclear
+which version the researcher should install in their environment.
 
 %The \texttt{davos} package provides a novel, Python-native framework for creating, sharing, and running reproducible workflows that was designed to address each of these issues.
-The \texttt{davos} package provides a novel, Python-native framework for creating reproducible workflows that was designed to address each of these issues.
-\texttt{davos} allows users to specify dependencies directly within the code that...
+The \texttt{davos} package provides a novel, Python-native framework
+for creating reproducible workflows that was designed to address each
+of these issues. \texttt{davos} allows users to specify dependencies
+directly within the code that...
 
@@
 
-Since its initial release, \texttt{davos} has found use in a variety of applications.
-In addition to managing data analysis environments for multiple ongoing research studies, \texttt{davos} is being used by both students and instructors in programming courses such as \href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling with Data}} \cite{Mann21b} (an open course on data science, visualization, and communication) to simplify distributing lessons and submitting assignments, as well as in online demos such as {\texttt{abstract2paper}} \cite{Mann21a} (an example application of \href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share ready-to-run code that installs dependencies automatically.
+Since its initial release, \texttt{davos} has found use in a variety
+of applications.  In addition to managing data analysis environments
+for multiple ongoing research studies, \texttt{davos} is being used by
+both students and instructors in programming courses such as
+\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
+    with Data}} \cite{Mann21b} (an open course on data science,
+visualization, and communication) to simplify distributing lessons and
+submitting assignments, as well as in online demos such as
+{\texttt{abstract2paper}} \cite{Mann21a} (an example application of
+\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
+ready-to-run code that installs dependencies automatically.
 

### 2022-10-03 paper/main.tex
working on intro...

@@
 
-Jupyter (iPython) notebooks~\citep{KluyEtal16} have revolutionized
-code sharing by providing a single filetype that combines text, code,
-and figures.  For projects that depend on other software packages,
-however, additional work is often required to enable the code to run
-as its authors intended.  For example, a piece of software that
-depends on version 0.8 of package \textit{X} may behave differently
-(or may fail to run at all) if the user instead attempts to run the
-code in an environment with version 0.9 of package \textit{X}.
+Code sharing is a core component of the open science movement
+that has inspired a full ecosystem of tools and packages.  However,
+sharing code, in and of itself, does not guarantee that others will be
+able to \textit{reproduce} the desired results.  For eample, research
+code often requires installing other software packages that extends
+the language's basic functionality.  Within the Python community,
+external packages that are published in the most popular 
+repositories~\citep{PIP, CONDA} are associated with version numbers
+and tags that enable users to guarantee that they are installing
+exactly the same code across different computing environments.
+Despire that it is \textit{possible} to manually install the intended version numbers of
+every dependency of a Python script or package, doing so may cause
+conflicts within the user's computing environment that interferes with
+the functionality of  \textit{other} code.
+
+To facilitate code sharing, the Python community has developed a broad
+set of approaches and tools (Fig.~\ref{fig:code-sharing}).  At one
+extreme, simply publishing a set of Python scripts (.py files) may
+enable others to use or gain insights into the relevant work.  Because
+Python is installed by default on most modern operating systems, for
+some projects this may be sufficient.  Another popular approach entails
+creating JSON files, called Jupyter notebooks~\citep{KluyEtal16} that
+comprise a mix of text, executable code, and embedded media.
+Notebooks may call or import external scripts or libraries in order to
+provide a more compact and readable experience for the users.  Each of
+these systems (Python scripts and notebooks) provides a convenient
+means of sharing code, with the caveat that they do not specify a
+complete computing environment.  Therefore the functionality of code
+shared using these systems cannot be guaranteed across different
+computing environments.
+
+At another extreme, virtual machines~citep{VM} provide a complete hardware-level
+simulation of the desired system.  Virtual machines are typically
+fully isolated from the user's system such that installing or running
+software on a virtual machine does not impact the user's primary
+operating system or computing environment.  Containers~\citep[e.g.,][]{Merk14,
+  SINGULARITY} provide a similar ``isolated'' experience.  Although
+containerized environments do not specify hardware-level operations,
+they are typically packaged with a complete operating system, in
+addition to a complete copy of Python and any relevant dependencies.
+Virtual environments~\citep[e.g.,][]{vanRoEtal14} also provide a
+computing environment that is largely separated from the user's main
+environment.  They incorporate a copy of Python and the target
+software's dependencies, but virtual environments do not specify or
+reproducee a complete copy of the original operating system.  Each of
+these systems (virtual machines, containers, and virtual environments)
+guarantees (to differing degrees-- at the hardware-level, operating system
+level, and Python environment, respectively) that the relevant code
+will run similarly for different users.  However, each of these
+systems also requires installing independent tools that
+can be resource intensive or burdensome to install or configure.
+
+We designed \texttt{davos} to occupy a ``sweet spot'' between these
+extremes.  \texttt{davos} is a notebook-installable package that adds
+functionality to the original.  Like standard Jupyter notebooks,
+\texttt{davos}-enhanced notebooks allows researchers to include text,
+executable code, and media within a single file.  No further setup or
+installation is required, beyond what is needed to run standard
+Jupyter notebooks.  And like virtual environments \texttt{davos}
+provides a convenient mechanism for fully specifying (and installing,
+as needed) a complete set of Python dependencies, including the
+relevant version numbers.
 

### 2022-10-04 paper/main.tex
refactoring intro

@@
 enables researchers to share a complete reproducible environment using
-a single iPython notebook file.
+a single Jupyter notebook file.
 
@@
 \hline
-\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Notes} \\
+\textbf{Nr.} & \textbf{Code metadata description} & \textbf{Metadata value} \\
 \hline
@@
 code often requires installing other software packages that extends
-the language's basic functionality.  Within the Python community,
+the language's basic functionality.  Within the Python community~\citep{vanR95},
 external packages that are published in the most popular 
-repositories~\citep{PIP, CONDA} are associated with version numbers
+repositories~\citep{pypi, Anac12} are associated with version numbers
 and tags that enable users to guarantee that they are installing
@@
 the functionality of  \textit{other} code.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=\textwidth]{figs/shareable_code}
+\caption{\small \textbf{Systems for sharing code within the Python ecosystem.}}
+\label{fig:code-sharing}
+\end{figure}
 
@@
 
-At another extreme, virtual machines~citep{VM} provide a complete hardware-level
+At another extreme, virtual machines~\citep{Gold74, AltiEtal05, vmware} provide a complete hardware-level
 simulation of the desired system.  Virtual machines are typically
@@
 operating system or computing environment.  Containers~\citep[e.g.,][]{Merk14,
-  SINGULARITY} provide a similar ``isolated'' experience.  Although
+  KurtEtal17} provide a similar ``isolated'' experience.  Although
 containerized environments do not specify hardware-level operations,
@@
 addition to a complete copy of Python and any relevant dependencies.
-Virtual environments~\citep[e.g.,][]{vanRoEtal14} also provide a
+Virtual environments~\citep[e.g.,][]{vanREtal14} also provide a
 computing environment that is largely separated from the user's main
@@
 
-% STOPPED HERE...
+% % STOPPED HERE...
 
-Sharing a project's code base is most valuable when that code may be
-run on
+% Sharing a project's code base is most valuable when that code may be
+% run on
 
-Modern scientific research frequently entails writing software code
-for a wide variety of purposes throughout the scientific process.
-Researchers across disciplines may design and implement complex
-experiments; collect, store, and analyze large datasets; create
-visualizations for presentations and publications; and share their
-findings and techniques with peers, students, and the broader public
-through tutorials, demos, workshops, and classes.  However, one
-fundamental requirement of virtually any form of research-related code
-is that its behavior and outputs remain consistent and predictable, no
-matter when, where, or by whom it is run.  This stability can be
-crucial, for example, to ensuring that data are collected under the
-same conditions (e.g., across recordings, subjects, or physical
-locations)
-%^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
-over multiple months or years, and that they can be accessed,
-processed, and analyzed consistently by a research team that may be
-spread across multiple institutions or countries.  Additionally,
-modern open science practices encourage publicly sharing research code
-and data so that others may explore, reproduce, learn from, and build
-upon existing work.  Much of the benefit afforded by freely available
-research code depends on users' ability to execute it and achieve the
-same result as its original author.
+% Modern scientific research frequently entails writing software code
+% for a wide variety of purposes throughout the scientific process.
+% Researchers across disciplines may design and implement complex
+% experiments; collect, store, and analyze large datasets; create
+% visualizations for presentations and publications; and share their
+% findings and techniques with peers, students, and the broader public
+% through tutorials, demos, workshops, and classes.  However, one
+% fundamental requirement of virtually any form of research-related code
+% is that its behavior and outputs remain consistent and predictable, no
+% matter when, where, or by whom it is run.  This stability can be
+% crucial, for example, to ensuring that data are collected under the
+% same conditions (e.g., across recordings, subjects, or physical
+% locations)
+% %^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
+% over multiple months or years, and that they can be accessed,
+% processed, and analyzed consistently by a research team that may be
+% spread across multiple institutions or countries.  Additionally,
+% modern open science practices encourage publicly sharing research code
+% and data so that others may explore, reproduce, learn from, and build
+% upon existing work.  Much of the benefit afforded by freely available
+% research code depends on users' ability to execute it and achieve the
+% same result as its original author.
 
-Python \cite{vanR95} has become one of the most widely used and
-fastest-growing scientific programming languages, in part by combining
-an accessible, high-level syntax with a rich ecosystem of powerful
-third-party tools that facilitate rapid development and collaboration
-\cite{MullEtal15}.  The Python ecosystem offers an extensive data
-science toolkit with platforms for interactive programming (e.g.,
-Project Jupyter \cite{KluyEtal16}, Google Colaboratory),
-community-maintained libraries for data manipulation (e.g., NumPy
-\cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and
-visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}),
-frameworks for training complex machine learning models (e.g.,
-scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging
-Face \cite{WolfEtal20}), and myriad other resources.  However, this
-heavy emphasis on third-party libraries also presents a challenge to
-writing and sharing stable, reproducible scientific Python code:
-different versions of the same library may behave differently, adopt
-changes in syntax, expose different functions and interfaces, add or
-drop support for specific hardware or software, write (or expect to
-read) files in different formats, fix (or introduce) bugs, and so on.
-While these issues exist to some extent in any software language or
-ecosystem, they have a particular impact on the Python community due
-to its unusually rapid growth relative to other languages.  Ensuring
-Python code behaves consistently over time and across users therefore
-typically requires ensuring it is always run with the same specific
-set of versions for each third-party package used.
-%Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
+% Python \cite{vanR95} has become one of the most widely used and
+% fastest-growing scientific programming languages, in part by combining
+% an accessible, high-level syntax with a rich ecosystem of powerful
+% third-party tools that facilitate rapid development and collaboration
+% \cite{MullEtal15}.  The Python ecosystem offers an extensive data
+% science toolkit with platforms for interactive programming (e.g.,
+% Project Jupyter \cite{KluyEtal16}, Google Colaboratory),
+% community-maintained libraries for data manipulation (e.g., NumPy
+% \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and
+% visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}),
+% frameworks for training complex machine learning models (e.g.,
+% scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging
+% Face~\cite{WolfEtal20}), and myriad other resources.  However, this
+% heavy emphasis on third-party libraries also presents a challenge to
+% writing and sharing stable, reproducible scientific Python code:
+% different versions of the same library may behave differently, adopt
+% changes in syntax, expose different functions and interfaces, add or
+% drop support for specific hardware or software, write (or expect to
+% read) files in different formats, fix (or introduce) bugs, and so on.
+% While these issues exist to some extent in any software language or
+% ecosystem, they have a particular impact on the Python community due
+% to its unusually rapid growth relative to other languages.  Ensuring
+% Python code behaves consistently over time and across users therefore
+% typically requires ensuring it is always run with the same specific
+% set of versions for each third-party package used.
+% %Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
 
-One common approach to solving this problem is to create containerized
-or virtualized Python environments (e.g., using Docker \cite{Merk14},
-Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to
-individual applications.  A researcher may build such an environment
-around a particular experiment or analysis pipeline, and exclusively
-run their code from inside it, ``entering" and ``exiting" the
-environment before and after each time they do so.  They can also
-distribute their custom environment alongside their code as a
-configuration file that explicitly lists required package versions,
-enabling others to build identical copies for themselves.  This allows
-research teams to deploy experiments on multiple machines for more
-efficient data collection, collaborate on analyses without introducing
-conflicts or inconsistencies, and publicly share their study designs
-and results for others to reproduce, replicate, or adapt to study new
-questions in the future.
+% One common approach to solving this problem is to create containerized
+% or virtualized Python environments (e.g., using Docker \cite{Merk14},
+% Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to
+% individual applications.  A researcher may build such an environment
+% around a particular experiment or analysis pipeline, and exclusively
+% run their code from inside it, ``entering" and ``exiting" the
+% environment before and after each time they do so.  They can also
+% distribute their custom environment alongside their code as a
+% configuration file that explicitly lists required package versions,
+% enabling others to build identical copies for themselves.  This allows
+% research teams to deploy experiments on multiple machines for more
+% efficient data collection, collaborate on analyses without introducing
+% conflicts or inconsistencies, and publicly share their study designs
+% and results for others to reproduce, replicate, or adapt to study new
+% questions in the future.
 
-While often effective, this approach bears two notable drawbacks.
-First, it can add substantially to the technical knowledge, computing
-resources, and initial setup needed to run or share the actual code of
-interest.  For example, sharing code for an analysis or tutorial that
-relies on a particular Docker image to run properly would of course
-necessitate writing and distributing extra configuration files and
-setup instructions.  But far more burdensomely, it also requires that
-anyone who may want to run the code (in addition to the author seeking
-to share it!) first be able to install and navigate additional
-software that is likely far more complex and resource-intensive than
-the actual analysis or tutorial code it facilitates running.  This can
-introduce a need for both a degree of computer literacy and
-computational resources that may not be universally accessible,
-particularly to students or other early-career scientists hoping to
-learn from publicly available tutorials.  These added prerequisites
-clash with the simplicity and accessibility that have contributed to
-Python's popularity, and can create significant barriers to both
-contributing to and taking advantage of open science resources.
+% While often effective, this approach bears two notable drawbacks.
+% First, it can add substantially to the technical knowledge, computing
+% resources, and initial setup needed to run or share the actual code of
+% interest.  For example, sharing code for an analysis or tutorial that
+% relies on a particular Docker image to run properly would of course
+% necessitate writing and distributing extra configuration files and
+% setup instructions.  But far more burdensomely, it also requires that
+% anyone who may want to run the code (in addition to the author seeking
+% to share it!) first be able to install and navigate additional
+% software that is likely far more complex and resource-intensive than
+% the actual analysis or tutorial code it facilitates running.  This can
+% introduce a need for both a degree of computer literacy and
+% computational resources that may not be universally accessible,
+% particularly to students or other early-career scientists hoping to
+% learn from publicly available tutorials.  These added prerequisites
+% clash with the simplicity and accessibility that have contributed to
+% Python's popularity, and can create significant barriers to both
+% contributing to and taking advantage of open science resources.
 
-Second, while many existing tools allow users to initially populate a
-Python environment with a fixed set of packages and package versions
-(e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml},
-\texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN}
-instruction, etc.), few, if any, ensure that these specified
-requirements \textit{remain} satisfied after they are first installed.
-The ability to modify an environment after its creation is useful in
-many cases (e.g., to install additional software, when
-needed). However, this also makes it easy to inadvertently alter
-existing packages, potentially leading to subtle issues with code that
-relies on them.  For instance, suppose a researcher has implemented a
-series of analyses using version 1.0 of ``Package \textit{X}," and
-decides to perform an additional analysis that requires installing
-``Package \textit{Y}."  If Package \textit{Y} depends on version 0.9
-of Package \textit{X}, then Package \textit{X} will be downgraded to
-accommodate this new requirement, potentially altering or breaking
-previous analyses when they are rerun later, either by the researcher
-or someone with whom they've shared their code.  Further, if some
-analyses require Package \textit{Y} while others rely on features of
-Package \textit{X} not implemented until version 1.0, it's unclear
-which version the researcher should install in their environment.
+% Second, while many existing tools allow users to initially populate a
+% Python environment with a fixed set of packages and package versions
+% (e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml},
+% \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN}
+% instruction, etc.), few, if any, ensure that these specified
+% requirements \textit{remain} satisfied after they are first installed.
+% The ability to modify an environment after its creation is useful in
+% many cases (e.g., to install additional software, when
+% needed). However, this also makes it easy to inadvertently alter
+% existing packages, potentially leading to subtle issues with code that
+% relies on them.  For instance, suppose a researcher has implemented a
+% series of analyses using version 1.0 of ``Package \textit{X}," and
+% decides to perform an additional analysis that requires installing
+% ``Package \textit{Y}."  If Package \textit{Y} depends on version 0.9
+% of Package \textit{X}, then Package \textit{X} will be downgraded to
+% accommodate this new requirement, potentially altering or breaking
+% previous analyses when they are rerun later, either by the researcher
+% or someone with whom they've shared their code.  Further, if some
+% analyses require Package \textit{Y} while others rely on features of
+% Package \textit{X} not implemented until version 1.0, it's unclear
+% which version the researcher should install in their environment.
 
-%The \texttt{davos} package provides a novel, Python-native framework for creating, sharing, and running reproducible workflows that was designed to address each of these issues.
-The \texttt{davos} package provides a novel, Python-native framework
-for creating reproducible workflows that was designed to address each
-of these issues. \texttt{davos} allows users to specify dependencies
-directly within the code that...
+% %The \texttt{davos} package provides a novel, Python-native framework for creating, sharing, and running reproducible workflows that was designed to address each of these issues.
+% The \texttt{davos} package provides a novel, Python-native framework
+% for creating reproducible workflows that was designed to address each
+% of these issues. \texttt{davos} allows users to specify dependencies
+% directly within the code that...
 
-\comment {
-POINTS TO MAKE/THINGS TO SAY HERE TO WRAP UP (or maybe save some for impact section?):
-- davos simplifies the process of writing, sharing, and running reproducible code (eliminates need for additional complex env management tools, syntax is simple, packages are just installed at runtime without additional setup beforehand, etc.)...
-- ...it also provides stability/additional protections against accidental changes in ways other tools don't (i.e., addresses issue 2 above) by verifying (and installing if necessary) requirements each time code is run
-- ... while simultaneously enabling new package management patterns (using multiple versions versions of package in same notebook, etc.)
-- it's lightweight and intuitive (unlike big/complex env management tools like docker, etc.)
-- "davos was specifically designed for use with Jupyter notebook environments, and can be used either on its own or in tandem with another environment management tool"
-- "\texttt{davos} was designed specifically for use in Jupyter notebook (formerly called IPython notebook \cite{PereGran07}) environments, and supports Jupyter notebooks \cite{KluyEtal16}, JupyterLab \cite{GranGrou16}, Google Colaboratory, Binder \cite{RagaWill18}, and IDE-based notebook editors."
+% \comment {
+% POINTS TO MAKE/THINGS TO SAY HERE TO WRAP UP (or maybe save some for impact section?):
+% - davos simplifies the process of writing, sharing, and running reproducible code (eliminates need for additional complex env management tools, syntax is simple, packages are just installed at runtime without additional setup beforehand, etc.)...
+% - ...it also provides stability/additional protections against accidental changes in ways other tools don't (i.e., addresses issue 2 above) by verifying (and installing if necessary) requirements each time code is run
+% - ... while simultaneously enabling new package management patterns (using multiple versions versions of package in same notebook, etc.)
+% - it's lightweight and intuitive (unlike big/complex env management tools like docker, etc.)
+% - "davos was specifically designed for use with Jupyter notebook environments, and can be used either on its own or in tandem with another environment management tool"
+% - "\texttt{davos} was designed specifically for use in Jupyter notebook (formerly called IPython notebook \cite{PereGran07}) environments, and supports Jupyter notebooks \cite{KluyEtal16}, JupyterLab \cite{GranGrou16}, Google Colaboratory, Binder \cite{RagaWill18}, and IDE-based notebook editors."
 
-- maybe don't mention smuggle statement \& onion comment explicitly in this paragraph since they haven't been defined/explained yet, or if we do, then add some sort of "see \_\_\_ below" with \\ref to relevant subsection
-}
+% - maybe don't mention smuggle statement \& onion comment explicitly in this paragraph since they haven't been defined/explained yet, or if we do, then add some sort of "see \_\_\_ below" with \\ref to relevant subsection
+% }
 
@@
 \includegraphics[width=\textwidth]{snippets/snippet1.pdf}
-\caption{\small \textbf{Figure 1}}
+\caption{\small \textbf{FILL THIS IN...}}
 \label{fig:snippet1}

### 2022-10-04 paper/main.tex
filled in impact and conclusions sections, updated figure, moved a bunch of old text to the boneyard

@@
 sharing code, in and of itself, does not guarantee that others will be
-able to \textit{reproduce} the desired results.  For eample, research
+able to \textit{reproduce} the desired results.  For example, research
 code often requires installing other software packages that extends
@@
 exactly the same code across different computing environments.
-Despire that it is \textit{possible} to manually install the intended version numbers of
+Despite that it is \textit{possible} to manually install the intended version numbers of
 every dependency of a Python script or package, doing so may cause
@@
 
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering
 \includegraphics[width=\textwidth]{figs/shareable_code}
-\caption{\small \textbf{Systems for sharing code within the Python ecosystem.}}
+\caption{\small \textbf{Systems for sharing code within the Python
+    ecosystem.}  From left to right: plain-text Python scripts (.py) provide the
+  most basic system for sharing raw code.  Scripts may reference
+  external libraries, but those libraries are not automatically
+  installed on other users' systems, nor is any version checking
+  performed by default.  Jupyter notebooks (.ipynb files) comprise embedded text,
+  executable code, and media (including rendered figures, code output,
+  etc.).  When the \texttt{davos} library is imported into a Jupyter
+  notebook, the notebook's functionality is extended to automatically
+  install the required external libraries (at their correct versions,
+  when specified).  Virtual environments install an isolated copy of
+  Python and all required dependencies.  This typically requires
+  defining a \texttt{requirements.txt} file that lists all
+  dependencies (including version numbers) along with an environment
+  (.yml) file that specifies how the virtual environment should be
+  configured.  Containers provide a means of defining an isolated
+  environment that includes a complete operating system (independent
+  of the user's operating system), in addition to a virtual
+  environment or other configurations needed to provide the necessary
+  computing environment.  Containers are typically defined using
+  specification files (e.g., a plain-text \texttt{dockerfile}) that
+  instruct the virtualization engine regarding how to build the
+  virtual environment.  Virtual machines provide a complete
+  hardware-level simulation of the computing environment.  In addition
+  to simulating specific hardware, virtual machines (typically
+  specified using binary images files) must also define operating
+  system-level properties of the computing environment.  Systems to
+  the left of the blue vertical line entail sharing using individual
+  files, with no additional installation or configuration needed to
+  run the target software.  Systems to the right of the red vertical
+  line provide high reproducibility by supporting precise control over
+  dependencies and versioning.}
 \label{fig:code-sharing}
@@
 software's dependencies, but virtual environments do not specify or
-reproducee a complete copy of the original operating system.  Each of
+reproduce a complete copy of the original operating system.  Each of
 these systems (virtual machines, containers, and virtual environments)
@@
 provides a convenient mechanism for fully specifying (and installing,
-as needed) a complete set of Python dependencies, including the
-relevant version numbers.
-
-% % STOPPED HERE...
-
-% Sharing a project's code base is most valuable when that code may be
-% run on
-
-% Modern scientific research frequently entails writing software code
-% for a wide variety of purposes throughout the scientific process.
-% Researchers across disciplines may design and implement complex
-% experiments; collect, store, and analyze large datasets; create
-% visualizations for presentations and publications; and share their
-% findings and techniques with peers, students, and the broader public
-% through tutorials, demos, workshops, and classes.  However, one
-% fundamental requirement of virtually any form of research-related code
-% is that its behavior and outputs remain consistent and predictable, no
-% matter when, where, or by whom it is run.  This stability can be
-% crucial, for example, to ensuring that data are collected under the
-% same conditions (e.g., across recordings, subjects, or physical
-% locations)
-% %^ or locations, e.g., in different test rooms, on different machines, at different sites, etc.
-% over multiple months or years, and that they can be accessed,
-% processed, and analyzed consistently by a research team that may be
-% spread across multiple institutions or countries.  Additionally,
-% modern open science practices encourage publicly sharing research code
-% and data so that others may explore, reproduce, learn from, and build
-% upon existing work.  Much of the benefit afforded by freely available
-% research code depends on users' ability to execute it and achieve the
-% same result as its original author.
-
-% Python \cite{vanR95} has become one of the most widely used and
-% fastest-growing scientific programming languages, in part by combining
-% an accessible, high-level syntax with a rich ecosystem of powerful
-% third-party tools that facilitate rapid development and collaboration
-% \cite{MullEtal15}.  The Python ecosystem offers an extensive data
-% science toolkit with platforms for interactive programming (e.g.,
-% Project Jupyter \cite{KluyEtal16}, Google Colaboratory),
-% community-maintained libraries for data manipulation (e.g., NumPy
-% \cite{HarrEtal20}, SciPy \cite{VirtEtal20}, Pandas \cite{McKi10}) and
-% visualization (e.g., Matplotlib \cite{Hunt07}, seaborn \cite{Wask21}),
-% frameworks for training complex machine learning models (e.g.,
-% scikit-learn \cite{PedrEtal11}, TensorFlow \cite{AbadEtal15}, Hugging
-% Face~\cite{WolfEtal20}), and myriad other resources.  However, this
-% heavy emphasis on third-party libraries also presents a challenge to
-% writing and sharing stable, reproducible scientific Python code:
-% different versions of the same library may behave differently, adopt
-% changes in syntax, expose different functions and interfaces, add or
-% drop support for specific hardware or software, write (or expect to
-% read) files in different formats, fix (or introduce) bugs, and so on.
-% While these issues exist to some extent in any software language or
-% ecosystem, they have a particular impact on the Python community due
-% to its unusually rapid growth relative to other languages.  Ensuring
-% Python code behaves consistently over time and across users therefore
-% typically requires ensuring it is always run with the same specific
-% set of versions for each third-party package used.
-% %Ensuring Python code behaves consistently over time and across users therefore typically requires guaranteeing that the same specific version of each required third-party package is used, every time it is run.
-
-% One common approach to solving this problem is to create containerized
-% or virtualized Python environments (e.g., using Docker \cite{Merk14},
-% Singularity \cite{KurtEtal17}, or conda \cite{Anac12}) tailored to
-% individual applications.  A researcher may build such an environment
-% around a particular experiment or analysis pipeline, and exclusively
-% run their code from inside it, ``entering" and ``exiting" the
-% environment before and after each time they do so.  They can also
-% distribute their custom environment alongside their code as a
-% configuration file that explicitly lists required package versions,
-% enabling others to build identical copies for themselves.  This allows
-% research teams to deploy experiments on multiple machines for more
-% efficient data collection, collaborate on analyses without introducing
-% conflicts or inconsistencies, and publicly share their study designs
-% and results for others to reproduce, replicate, or adapt to study new
-% questions in the future.
-
-% While often effective, this approach bears two notable drawbacks.
-% First, it can add substantially to the technical knowledge, computing
-% resources, and initial setup needed to run or share the actual code of
-% interest.  For example, sharing code for an analysis or tutorial that
-% relies on a particular Docker image to run properly would of course
-% necessitate writing and distributing extra configuration files and
-% setup instructions.  But far more burdensomely, it also requires that
-% anyone who may want to run the code (in addition to the author seeking
-% to share it!) first be able to install and navigate additional
-% software that is likely far more complex and resource-intensive than
-% the actual analysis or tutorial code it facilitates running.  This can
-% introduce a need for both a degree of computer literacy and
-% computational resources that may not be universally accessible,
-% particularly to students or other early-career scientists hoping to
-% learn from publicly available tutorials.  These added prerequisites
-% clash with the simplicity and accessibility that have contributed to
-% Python's popularity, and can create significant barriers to both
-% contributing to and taking advantage of open science resources.
-
-% Second, while many existing tools allow users to initially populate a
-% Python environment with a fixed set of packages and package versions
-% (e.g., from a \texttt{requirements.txt}, \texttt{pyproject.toml},
-% \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN}
-% instruction, etc.), few, if any, ensure that these specified
-% requirements \textit{remain} satisfied after they are first installed.
-% The ability to modify an environment after its creation is useful in
-% many cases (e.g., to install additional software, when
-% needed). However, this also makes it easy to inadvertently alter
-% existing packages, potentially leading to subtle issues with code that
-% relies on them.  For instance, suppose a researcher has implemented a
-% series of analyses using version 1.0 of ``Package \textit{X}," and
-% decides to perform an additional analysis that requires installing
-% ``Package \textit{Y}."  If Package \textit{Y} depends on version 0.9
-% of Package \textit{X}, then Package \textit{X} will be downgraded to
-% accommodate this new requirement, potentially altering or breaking
-% previous analyses when they are rerun later, either by the researcher
-% or someone with whom they've shared their code.  Further, if some
-% analyses require Package \textit{Y} while others rely on features of
-% Package \textit{X} not implemented until version 1.0, it's unclear
-% which version the researcher should install in their environment.
-
-% %The \texttt{davos} package provides a novel, Python-native framework for creating, sharing, and running reproducible workflows that was designed to address each of these issues.
-% The \texttt{davos} package provides a novel, Python-native framework
-% for creating reproducible workflows that was designed to address each
-% of these issues. \texttt{davos} allows users to specify dependencies
-% directly within the code that...
-
-% \comment {
-% POINTS TO MAKE/THINGS TO SAY HERE TO WRAP UP (or maybe save some for impact section?):
-% - davos simplifies the process of writing, sharing, and running reproducible code (eliminates need for additional complex env management tools, syntax is simple, packages are just installed at runtime without additional setup beforehand, etc.)...
-% - ...it also provides stability/additional protections against accidental changes in ways other tools don't (i.e., addresses issue 2 above) by verifying (and installing if necessary) requirements each time code is run
-% - ... while simultaneously enabling new package management patterns (using multiple versions versions of package in same notebook, etc.)
-% - it's lightweight and intuitive (unlike big/complex env management tools like docker, etc.)
-% - "davos was specifically designed for use with Jupyter notebook environments, and can be used either on its own or in tandem with another environment management tool"
-% - "\texttt{davos} was designed specifically for use in Jupyter notebook (formerly called IPython notebook \cite{PereGran07}) environments, and supports Jupyter notebooks \cite{KluyEtal16}, JupyterLab \cite{GranGrou16}, Google Colaboratory, Binder \cite{RagaWill18}, and IDE-based notebook editors."
-
-% - maybe don't mention smuggle statement \& onion comment explicitly in this paragraph since they haven't been defined/explained yet, or if we do, then add some sort of "see \_\_\_ below" with \\ref to relevant subsection
-% }
-
-%Introduce the scientific background and the motivation for developing the software.
-
-%Explain why the software is important, and describe the exact (scientific) problem(s) it solves.
-
-%Indicate in what way the software has contributed (or how it will contribute in the future) to the process of scientific discovery; if available, this is to be supported by citing a research paper using the software.
-
-%Provide a description of the experimental setting (how does the user use the software?).
-
-%Introduce related work in literature (cite or list algorithms used, other software etc.).
+as needed) a complete set of Python dependencies, including package versions.
 
@@
 \subsection{Software architecture}
-The \texttt{davos} package is structured as two subpackages: a set of ``core" modules that implement...
+The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
 
@@
 \section{Impact}
-\comment{
-- emphasize research domain-independent application (Journal's goals/values page says they prioritize this in submissions)
-- applicability not limited to research
-    - regression (?) testing
-    - ***^^not sure this should be included -- hurts framing of davos as "research software"***
-- makes writing and running publicly available reproducible code more accessible (lowers required software comfort/familiarity level \& computing resources vs. installing docker/singularity/conda)
-    - also removes these requirements from other scenarios, e.g., easier for new/less experienced students/RAs to get involved with analyses
-- mention something about not having to teach environment management to teach day 1 python lesson, or spend hours debugging conda installation in order to share tutorial or demo with students
-    - e.g., "researchers who teach \_\_\_ may be familiar with the experience of running a lesson or workshop that requires students to use Docker (or similar...) to run their code, only to spend the majority of class time debugging students' computing environments rather than teaching the lesson itself."
-}
 
-Since its initial release, \texttt{davos} has found use in a variety
-of applications.  In addition to managing data analysis environments
-for multiple ongoing research studies, \texttt{davos} is being used by
-both students and instructors in programming courses such as
-\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
-    with Data}} \cite{Mann21b} (an open course on data science,
-visualization, and communication) to simplify distributing lessons and
-submitting assignments, as well as in online demos such as
-{\texttt{abstract2paper}} \cite{Mann21a} (an example application of
-\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
-ready-to-run code that installs dependencies automatically.
+Like virtual environments, containers, and virtual machines, 
+the \texttt{davos} library (when used in conjunction with Jupyter
+notebook) provides a lightweight mechanism for sharing code and
+ensuring reproducibility across users and computing environments.
+Further,\texttt{davos} enables users to fully specify (and
+install, as needed) any project dependencies within the same
+notebook.  This provides a system whereby executable code (along with
+text and media) \textit{and} code for setting up and configuring the
+project dependencies, all within a single notebook file.
 
-%\textbf{This is the main section of the article and the reviewers weight the description here appropriately}
+We designed \texttt{davos} for use in research applications.  For
+example, in many cases \texttt{davos} may be used as a drop-in
+replacement for more-difficult-to-set-up virtual environments,
+containers, and/or virtual machines.  For researchers, this lowers barriers to sharing
+code.  And by eliminating most of the setup costs of reconstructing
+the researchers' computing environment, \texttt{davos} also serves to
+lower barriers to entry for members of the scientific community and of
+the public to \textit{benefiting} from shared code.
 
-%Indicate in what way new research questions can be pursued as a result of the software (if any).
+Beyond research applications, \texttt{davos} is also useful in
+pedagogical settings.  For example, in programming courses,
+instructors and students may choose to import the \texttt{davos}
+library into their notebooks to provide a simple means of ensuring
+their code will run on others' machines.  When combined with online
+notebook-based platforms like Google Colaboratory, \texttt{davos}
+provides a convenient means of managing dependencies within a
+notebook, without requiring any software (beyond a web browser) to be
+installed on the students' or instructors' systems.  For the same
+reasons, \texttt{davos} also provides an elegant means of sharing
+ready-to-run notebook-based demonstrations that install their
+dependencies automatically.
 
-%Indicate in what way, and to what extent, the pursuit of existing research questions is improved (if so).
+In addition to the above common uses of \texttt{davos}, our work also
+provides several more subtle ``advanced'' use cases.  
+Whereas Python's built-in \texttt{import} statement is agnostic to
+packages' version numbers, \texttt{smuggle} statements (when combined
+with onion comments) are version-sensitive.  This setup enables
+multiple versions of a single library to be imported within the same
+notebook.  This could be useful in cases where specific features were
+added or removed from a package across different versions, or in
+comparing the performance or functionality of particular features
+across different versions of the same package.
 
-%Indicate in what way the software has changed the daily practice of its users (if so).
-
-%Indicate how widespread the use of the software is within and outside the intended user group.
-
-%Indicate in what way the software is used in commercial settings and/or how it led to the creation of spin-off companies (if so).
+A second advanced use case is in providing a proof of concept of how
+one can add new ``keywords'' to the Python language by leveraging the
+error-handling mechanisms built into Jupyter notebooks.  This could
+lead to exciting new tools that, like \texttt{davos}, extend the
+Python language in useful ways.  We note that our approach to adding
+the \texttt{smuggle} keyword to Python when \texttt{davos} is imported
+into a notebook-based environment also carries some potential risk.
+For example, a malicious user could use a similar approach to
+substantially change a notebook's functionality, in
+difficult-to-predict ways when a particular library was imported into
+the current environment.  This highlights an important reason why
+security-conscious users would be well-served to only make use of
+libraries from trusted sources, or whose code is publicly available
+for review.
 
@@
 
+Perhaps the most exciting uses of the \texttt{davos} library are those
+that we have \textit{not} yet considered or imagined.  We hope that
+the Python community will find \texttt{davos} to provide a convenient
+means of managing project dependencies to facilitate code sharing.  We
+also hope that some of the more advanced applications of our library
+might lead to new insights or discoveries.
+
 \section*{Author Contributions}
-\textbf{Paxton C.
-Fitzpatrick}: Conceptualization, Methodology, Software, Validation, Writing - Original Draft, Visualization.
-\textbf{Jeremy R.
-Manning}: Conceptualization, Resources, Writing - Review \& Editing, Supervision, Funding acquisition.
+Conceptualization: PCF and JRM.  Methodology: PCF and JRM.
+Implementation: PCF.  Validation: PCF.  Testing: PCF and JRM.
+Writing: PCF and JRM.
 
 \section*{Funding}
-Our work was supported in part by NSF grant number 2145172 to J.R.M.
+Our work was supported in part by NSF grant number 2145172 to JRM.
 The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
@@
 \section*{Acknowledgements}
+We acknowledge useful feedback and discussion from the students of
+JRM's \textit{Storytelling with Data} course (Winter, 2022 offering)
+who used preliminary versions of our library in several assignments.
 

### 2022-10-04 paper/main.tex
minor edits, wording tweaks, other fixes

@@
 
-A core requirement of modern scientific research is replicability.
-For computational research, replicability means that code should
-produce the same results, even when run on different systems.  The
-standard solution to improving replicability entails packaging a
+  Reproducibility is a core requirement of modern scientific research.
+  For computational research, reproducibility means that code should
+  produce the same results, even when run on different systems.  A
+  standard approach to ensuring reproducibility entails packaging a
   project's dependencies along with its primary code base.  Existing
-solutions vary in how deeply these dependencies are specified, ranging
-from virtual environments (which specify all Python package versions),
-to containers (which also specify the operating system), to
-virtual machines (which also specify hardware layers of the system).
-Each of these existing solutions requires installing or setting up a
-system for running the desired code that must be packaged alongside
-the primary code base.  Here we propose an even lighter-weight
-solution than virtual environments: the \texttt{davos} library.  When
-used in combination with a notebook-based Python project, \texttt{davos}
-library provides a mechanism for specifying (and automatically
-installing) the correct package versions of the project's.  This
-enables researchers to share a complete reproducible environment using
-a single Jupyter notebook file.
+  solutions vary in how deeply these dependencies are specified,
+  ranging from virtual environments (which specify all Python package
+  versions), to containers (which also specify the operating system),
+  to virtual machines (which also specify hardware layers of the
+  system).  Each of these existing solutions requires installing or
+  setting up a system for running the desired code that must be
+  packaged alongside the primary code base.  Here we propose a
+  lighter-weight solution than virtual environments: the
+  \texttt{davos} library.  When used in combination with a
+  notebook-based Python project, the \texttt{davos} library provides a
+  mechanism for specifying (and automatically installing) the correct
+  package versions of the project's dependencies.  This enables researchers to
+  share a complete reproducible environment using a single Jupyter
+  notebook file.
 
@@
 \hline
-C7 & Compilation requirements, operating environments \& dependencies & Dependencies:~Python$>$=3.6, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+C7 & Compilation requirements, operating environments, and
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
 \\
@@
 
-Code sharing is a core component of the open science movement
-that has inspired a full ecosystem of tools and packages.  However,
-sharing code, in and of itself, does not guarantee that others will be
-able to \textit{reproduce} the desired results.  For example, research
-code often requires installing other software packages that extends
-the language's basic functionality.  Within the Python community~\citep{vanR95},
-external packages that are published in the most popular 
+Code sharing is a core component of the open science movement that has
+inspired the development of a full ecosystem of tools and packages.
+However, sharing code, in and of itself, does not guarantee that
+others will be able to \textit{reproduce} the desired results.  For
+example, research code often requires installing other software
+packages that extend the implementation language's basic
+functionality.  Within the Python community~\citep{vanR95}, external
+packages that are published in the most popular
 repositories~\citep{pypi, Anac12} are associated with version numbers
@@
 exactly the same code across different computing environments.
-Despite that it is \textit{possible} to manually install the intended version numbers of
-every dependency of a Python script or package, doing so may cause
-conflicts within the user's computing environment that interferes with
-the functionality of  \textit{other} code.
+Despite that it is \textit{possible} to manually install the intended
+version numbers of every dependency of a Python script or package,
+doing so may cause conflicts within the user's computing environment
+that interfere with the functionality of \textit{other} code.
 
@@
 \caption{\small \textbf{Systems for sharing code within the Python
-    ecosystem.}  From left to right: plain-text Python scripts (.py) provide the
-  most basic system for sharing raw code.  Scripts may reference
+    ecosystem.}  From left to right: plain-text \textbf{Python
+    scripts} (.py files) provide the
+  most basic ``system'' for sharing raw code.  Scripts may reference
   external libraries, but those libraries are not automatically
   installed on other users' systems, nor is any version checking
-  performed by default.  Jupyter notebooks (.ipynb files) comprise embedded text,
+  performed by default.  \textbf{Jupyter notebooks} (.ipynb files) comprise embedded text,
   executable code, and media (including rendered figures, code output,
-  etc.).  When the \texttt{davos} library is imported into a Jupyter
+  etc.).  When the \textbf{\texttt{davos} library} is imported into a Jupyter
   notebook, the notebook's functionality is extended to automatically
   install the required external libraries (at their correct versions,
-  when specified).  Virtual environments install an isolated copy of
+  when specified).  \textbf{Virtual environments} install an isolated copy of
   Python and all required dependencies.  This typically requires
@@
   (.yml) file that specifies how the virtual environment should be
-  configured.  Containers provide a means of defining an isolated
+  configured.  \textbf{Containers} provide a means of defining an isolated
   environment that includes a complete operating system (independent
@@
   instruct the virtualization engine regarding how to build the
-  virtual environment.  Virtual machines provide a complete
+  virtual environment.  \textbf{Virtual machines} provide a complete
   hardware-level simulation of the computing environment.  In addition
@@
   system-level properties of the computing environment.  Systems to
-  the left of the blue vertical line entail sharing using individual
+  the left of the blue vertical line entail sharing individual
   files, with no additional installation or configuration needed to
@@
   line provide high reproducibility by supporting precise control over
-  dependencies and versioning.}
+  dependencies and versioning.  Notebooks enhanced using the
+  \texttt{davos} library are easily shareable and require minimal
+  setup costs, while also facilitating high reproducibility by
+  enabling precise control over project dependencies.}
 \label{fig:code-sharing}
@@
 Python is installed by default on most modern operating systems, for
-some projects this may be sufficient.  Another popular approach entails
-creating JSON files, called Jupyter notebooks~\citep{KluyEtal16} that
-comprise a mix of text, executable code, and embedded media.
-Notebooks may call or import external scripts or libraries in order to
-provide a more compact and readable experience for the users.  Each of
-these systems (Python scripts and notebooks) provides a convenient
-means of sharing code, with the caveat that they do not specify a
-complete computing environment.  Therefore the functionality of code
-shared using these systems cannot be guaranteed across different
-computing environments.
+some projects this may be sufficient.  Another popular approach
+entails creating JSON files, called Jupyter
+notebooks~\citep{KluyEtal16}, that comprise a mix of text, executable
+code, and embedded media.  Notebooks may call or import external
+scripts or libraries in order to provide a more compact and readable
+experience for users.  Each of these systems (Python scripts and
+notebooks) provides a convenient means of sharing code, with the
+caveat that they do not specify the computing environment in which the
+code is executed.  Therefore the functionality of code shared using
+these systems cannot be guaranteed across different computing
+environments.
 
-At another extreme, virtual machines~\citep{Gold74, AltiEtal05, vmware} provide a complete hardware-level
-simulation of the desired system.  Virtual machines are typically
-fully isolated from the user's system such that installing or running
-software on a virtual machine does not impact the user's primary
-operating system or computing environment.  Containers~\citep[e.g.,][]{Merk14,
-  KurtEtal17} provide a similar ``isolated'' experience.  Although
-containerized environments do not specify hardware-level operations,
-they are typically packaged with a complete operating system, in
-addition to a complete copy of Python and any relevant dependencies.
-Virtual environments~\citep[e.g.,][]{vanREtal14} also provide a
-computing environment that is largely separated from the user's main
+At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
+  vmware} provide a hardware-level simulation of the desired system.
+Virtual machines are typically isolated from the user's system, such
+that installing or running software on a virtual machine does not
+impact the user's primary operating system or computing environment.
+Containers~\citep[e.g.,][]{Merk14, KurtEtal17} provide a similar
+``isolated'' experience.  Although containerized environments do not
+specify hardware-level operations, they are typically packaged with a
+complete operating system, in addition to a complete copy of Python
+and any relevant package dependencies.  Virtual
+environments~\citep[e.g.,][]{vanREtal14} also provide a computing
+environment that is largely separated from the user's main
 environment.  They incorporate a copy of Python and the target
 software's dependencies, but virtual environments do not specify or
-reproduce a complete copy of the original operating system.  Each of
+reproduce an operating system for the runtime environment.  Each of
 these systems (virtual machines, containers, and virtual environments)
-guarantees (to differing degrees-- at the hardware-level, operating system
-level, and Python environment, respectively) that the relevant code
-will run similarly for different users.  However, each of these
-systems also requires installing independent tools that
-can be resource intensive or burdensome to install or configure.
+guarantees (to differing degrees-- at the hardware level, operating
+system level, and Python environment level, respectively) that the
+relevant code will run similarly for different users.  However, each
+of these systems also relies on additional software that can be
+resource intensive or burdensome to install or configure.
 
@@
 extremes.  \texttt{davos} is a notebook-installable package that adds
-functionality to the original.  Like standard Jupyter notebooks,
-\texttt{davos}-enhanced notebooks allows researchers to include text,
-executable code, and media within a single file.  No further setup or
-installation is required, beyond what is needed to run standard
-Jupyter notebooks.  And like virtual environments \texttt{davos}
-provides a convenient mechanism for fully specifying (and installing,
-as needed) a complete set of Python dependencies, including package versions.
+functionality to the default notebook experience.  Like standard
+Jupyter notebooks, \texttt{davos}-enhanced notebooks allows
+researchers to include text, executable code, and media within a
+single file.  No further setup or installation is required, beyond
+what is needed to run standard Jupyter notebooks.  And like virtual
+environments \texttt{davos} provides a convenient mechanism for fully
+specifying (and installing, as needed) a complete set of Python
+dependencies, including package versions.
 
@@
 
-Like virtual environments, containers, and virtual machines, 
-the \texttt{davos} library (when used in conjunction with Jupyter
-notebook) provides a lightweight mechanism for sharing code and
-ensuring reproducibility across users and computing environments.
-Further,\texttt{davos} enables users to fully specify (and
-install, as needed) any project dependencies within the same
-notebook.  This provides a system whereby executable code (along with
-text and media) \textit{and} code for setting up and configuring the
-project dependencies, all within a single notebook file.
+Like virtual environments, containers, and virtual machines, the
+\texttt{davos} library (when used in conjunction with Jupyter
+notebooks) provides a lightweight mechanism for sharing code and
+ensuring reproducibility across users and computing environments
+(Fig.~\ref{fig:code-sharing}).  Further, \texttt{davos} enables users
+to fully specify (and install, as needed) any project dependencies
+within the same notebook.  This provides a system whereby executable
+code (along with text and media) \textit{and} code for setting up and
+configuring the project dependencies, may be combined within a single
+notebook file.
 
 We designed \texttt{davos} for use in research applications.  For
-example, in many cases \texttt{davos} may be used as a drop-in
+example, in many settings \texttt{davos} may be used as a drop-in
 replacement for more-difficult-to-set-up virtual environments,
-containers, and/or virtual machines.  For researchers, this lowers barriers to sharing
-code.  And by eliminating most of the setup costs of reconstructing
-the researchers' computing environment, \texttt{davos} also serves to
-lower barriers to entry for members of the scientific community and of
-the public to \textit{benefiting} from shared code.
+containers, and/or virtual machines.  For researchers, this lowers
+barriers to sharing code.  By eliminating most of the setup costs
+of reconstructing the original researchers' computing environment,
+\texttt{davos} also lowers barriers to entry for members of
+the scientific community and the public who seek to \textit{benefit}
+from shared code.
 
@@
 pedagogical settings.  For example, in programming courses,
-instructors and students may choose to import the \texttt{davos}
-library into their notebooks to provide a simple means of ensuring
-their code will run on others' machines.  When combined with online
-notebook-based platforms like Google Colaboratory, \texttt{davos}
-provides a convenient means of managing dependencies within a
-notebook, without requiring any software (beyond a web browser) to be
-installed on the students' or instructors' systems.  For the same
-reasons, \texttt{davos} also provides an elegant means of sharing
-ready-to-run notebook-based demonstrations that install their
-dependencies automatically.
+instructors and students may import the \texttt{davos} library into
+their notebooks to provide a simple means of ensuring their code will
+run on others' machines.  When combined with online notebook-based
+platforms like Google Colaboratory, \texttt{davos} provides a
+convenient way to manage dependencies within a notebook, without
+requiring any software (beyond a web browser) to be installed on the
+students' or instructors' systems.  For the same reasons,
+\texttt{davos} also provides an elegant means of sharing ready-to-run
+notebook-based demonstrations that install their dependencies
+automatically.
 
-In addition to the above common uses of \texttt{davos}, our work also
-provides several more subtle ``advanced'' use cases.  
-Whereas Python's built-in \texttt{import} statement is agnostic to
-packages' version numbers, \texttt{smuggle} statements (when combined
-with onion comments) are version-sensitive.  This setup enables
-multiple versions of a single library to be imported within the same
-notebook.  This could be useful in cases where specific features were
-added or removed from a package across different versions, or in
-comparing the performance or functionality of particular features
-across different versions of the same package.
+Our work also has several more subtle ``advanced'' use cases and
+potential impacts.  Whereas Python's built-in \texttt{import}
+statement is agnostic to packages' version numbers, \texttt{smuggle}
+statements (when combined with onion comments) are version-sensitive.
+This enables multiple versions of a single library to be
+imported within the same notebook.  This could be useful in cases
+where specific features were added or removed from a package across
+different versions, or in comparing the performance or functionality
+of particular features across different versions of the same package.
 
-A second advanced use case is in providing a proof of concept of how
+A second advanced use case is in providing a proof-of-concept of how
 one can add new ``keywords'' to the Python language by leveraging the
-error-handling mechanisms built into Jupyter notebooks.  This could
-lead to exciting new tools that, like \texttt{davos}, extend the
-Python language in useful ways.  We note that our approach to adding
-the \texttt{smuggle} keyword to Python when \texttt{davos} is imported
-into a notebook-based environment also carries some potential risk.
-For example, a malicious user could use a similar approach to
-substantially change a notebook's functionality, in
-difficult-to-predict ways when a particular library was imported into
-the current environment.  This highlights an important reason why
-security-conscious users would be well-served to only make use of
+error-handling mechanisms.  This could lead to exciting new tools
+that, like \texttt{davos}, extend the Python language in useful ways.
+We note that our approach to adding the \texttt{smuggle} keyword to
+Python when \texttt{davos} is imported into a notebook-based
+environment also has the potential to be exploited for more nefarious
+purposes.  For example, a malicious user could use a similar approach
+(e.g., in a different library) to substantially change a notebook's
+functionality by adding new \textit{unexpected} keyword-like objects
+(e.g., based around common typos).  This could lead to
+difficult-to-predict changes in a notebook's behavior once the
+malicious library was imported.  This highlights an important reason
+why security-conscious users would be well-served to only make use of
 libraries from trusted sources, or whose code is publicly available
@@
 
-Perhaps the most exciting uses of the \texttt{davos} library are those
+The \texttt{davos} library supports reproducible research by providing
+a novel lightweight system for sharing notebook-based code.  But
+perhaps the most exciting uses of the \texttt{davos} library are those
 that we have \textit{not} yet considered or imagined.  We hope that

### 2022-10-06 paper/main.tex
WIP software architecture section

@@
 \subsection{Software architecture}
-The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
+The \texttt{davos} package consists of two interdependent subpackages.
+The first comprises a set of ``core" modules that implement\comment{provide?} much of \texttt{davos}'s major functionality, including machinery for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
+However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementations depending on various properties of the notebook in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
+To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions", which are imported from the ``implementations" subpackage.
+This second subpackage defines multiple, interchangeable implementations of each helper function, organized into per-environment modules.
+At runtime, \texttt{davos}
 

### 2022-10-07 paper/main.tex
updates to software architecture section

--- 2022-10-04 paper/main.tex
@@
 
-\title{\texttt{davos}: a Python package ``smuggler'' for constructing
+\title{\texttt{davos}: a Python package ``smuggler" for constructing
   lightweight reproducible notebooks}
@@
 \subsection{Software architecture}
-The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
+The \texttt{davos} package consists of two interdependent subpackages.
+The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
+However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
+To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions" in the \texttt{davos.implementations} subpackage.
+This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
+At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
+An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants \texttt{davos} in the future relatively easy.
 
+\comment{
+- js_functions.py?
+- how parser is registered and deregistered?
+- stub files?
+- test suite?
+- packaged with new PEP \_\_\_ standard (pyproject.toml + setup.cfg; no setup.py)?
+}
 % Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.

### 2022-10-07 paper/main.tex
replace double quote with two single quotes

@@
 
-\title{\texttt{davos}: a Python package ``smuggler" for constructing
+\title{\texttt{davos}: a Python package ``smuggler'' for constructing
   lightweight reproducible notebooks}
@@
 However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
-To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions" in the \texttt{davos.implementations} subpackage.
+To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
 This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
@@
 
-\subsubsection{The \texttt{smuggle} statement}
-Importing \texttt{davos}\comment{in a Jupyter notebook} enables an additional Python keyword: ``\texttt{smuggle}".
+\subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
+Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}''.
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 
-\subsubsection{The onion comment}
+\subsubsection{The onion comment}\label{subsec:onion}
 For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}.
 An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
-Onion comments follow a simple syntax based on the ``type comment" syntax introduced in PEP 484 \cite{vanREtal14} and are designed to make managing packages via \texttt{davos} intuitive and familiar.
+Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages via \texttt{davos} intuitive and familiar.
 To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).

### 2022-10-07 paper/main.tex
working on adressing PF comments on section 1

--- 2022-10-06 paper/main.tex
@@
   solutions vary in how deeply these dependencies are specified,
-  ranging from virtual environments (which specify all Python package
-  versions), to containers (which also specify the operating system),
-  to virtual machines (which also specify hardware layers of the
-  system).  Each of these existing solutions requires installing or
+  ranging from virtual environments, to containers, to virtual
+  machines.  Each of these existing solutions requires installing or
   setting up a system for running the desired code that must be
@@
   mechanism for specifying (and automatically installing) the correct
-  package versions of the project's dependencies.  This enables researchers to
-  share a complete reproducible environment using a single Jupyter
-  notebook file.
+  package versions of the project's dependencies.  The \texttt{davos}
+  library also ensures that those versions are in use any time the
+  notebook's code is executed.  This enables researchers to share a complete
+  reproducible environment using a single Jupyter notebook file.
 
@@
 
+Modern research projects that rely on software are becoming
+increasingly complex.  Even when a particular function or script
+appears simple, the code may depend on external libraries (which in
+turn may depend on other libraries), particular CPU or GPU instruction sets, and
+so on.  Different versions of those external libraries (or processor
+instruction sets) may ....
+
+% IN-PROGRESS TEXT------
+
+The same code, executed on different systems or in different computing
+environments, may behave differently.  For example, when research code relies
+on external libraries, the code's functionality
+
+Reproducability and predictability are fundamental goals of nearly all
+scientific undertakings.  For projects that rely on software
+components, achieving these goals
+
+% --------
+
 Code sharing is a core component of the open science movement that has
-inspired the development of a full ecosystem of tools and packages.
+inspired the development of a large ecosystem of tools and packages.
 However, sharing code, in and of itself, does not guarantee that
@@
 \subsection{Software architecture}
-The \texttt{davos} package consists of two interdependent subpackages.
-The first comprises a set of ``core" modules that implement\comment{provide?} much of \texttt{davos}'s major functionality, including machinery for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
-However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementations depending on various properties of the notebook in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
-To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions", which are imported from the ``implementations" subpackage.
-This second subpackage defines multiple, interchangeable implementations of each helper function, organized into per-environment modules.
-At runtime, \texttt{davos}
+The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
 

### 2022-10-08 paper/main.tex
update in-text VMware reference
WIP updates to onion comment section

--- 2022-10-07 paper/main.tex
@@
 At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
-  vmware} provide a hardware-level simulation of the desired system.
+  Rose99} provide a hardware-level simulation of the desired system.
 Virtual machines are typically isolated from the user's system, such
@@
 
-\subsection{Software functionalities}%\label{sec:functionalities}
+\subsection{Software functionalities}
 
@@
 An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
-Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages via \texttt{davos} intuitive and familiar.
+Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
 To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
+%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by
 
@@
 \end{figure}
+
+Onion comments are also useful for smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
+However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
+If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will search for the smuggled package in the local environment (as usual), and if it is found, further check whether the existing version satisfies the given constraint(s).
+If either check fails, \texttt{davos} will install and use a suitable version of the package (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
 
@@
 
-\subsubsection{The \texttt{davos} config}
+\subsubsection{The \texttt{davos} config}\label{subsec:config}
 

### 2022-10-08 paper/main.tex
wrote onion comment functionalities section

@@
 \subsubsection{The onion comment}\label{subsec:onion}
-For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}.
-An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''.
+An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
 Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippet1})} (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
+%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippet1}.
 %Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by
+
+Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
+If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
+If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
+If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+
+%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
+If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead.
+This guarantees the notebook is always run with a specific (or constrained) version of a particular package.
+Similarly, \texttt{davos}
+%If the package exists locally, \texttt{davos} will extract its version from metadata before loading it to determine its version, and if it does not match the requested version (or if no local installation is found),
+%If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will check whether the smuggled package is installed locally (as usual), and if so, additionally parse its metadata to determine
+%Adding a version specifier \cite{CoghStuf13} to an onion comment guarantees the version loaded into the notebook will matches the version specified
+
+\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.
 
@@
 \includegraphics[width=\textwidth]{snippets/snippet1.pdf}
-\caption{\small \textbf{FILL THIS IN...}}
+\caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
 \label{fig:snippet1}
 \end{figure}
-
-Onion comments are also useful for smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
-However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will search for the smuggled package in the local environment (as usual), and if it is found, further check whether the existing version satisfies the given constraint(s).
-If either check fails, \texttt{davos} will install and use a suitable version of the package (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
 

### 2022-10-10 paper/main.tex
addressed PCF comments in abstract, motivation/significance, and impact sections

--- 2022-10-07 paper/main.tex
@@
 
-Modern research projects that rely on software are becoming
-increasingly complex.  Even when a particular function or script
-appears simple, the code may depend on external libraries (which in
-turn may depend on other libraries), particular CPU or GPU instruction sets, and
-so on.  Different versions of those external libraries (or processor
-instruction sets) may ....
+The same computer code may not behave identically under different
+circumstances.  For example, when code depends on external libraries,
+different versions of those libraries may function differently.  Or
+when CPU or GPU instruction sets differ across machines, the same
+high-level code may be compiled into different machine instructions.
+Because executing identical code does not guarantee identical
+outcomes, code sharing in and of itself is often insufficient for
+enabling researchers to reproduce each others' work.
 
-% IN-PROGRESS TEXT------
-
-The same code, executed on different systems or in different computing
-environments, may behave differently.  For example, when research code relies
-on external libraries, the code's functionality
-
-Reproducability and predictability are fundamental goals of nearly all
-scientific undertakings.  For projects that rely on software
-components, achieving these goals
-
-% --------
-
-Code sharing is a core component of the open science movement that has
-inspired the development of a large ecosystem of tools and packages.
-However, sharing code, in and of itself, does not guarantee that
-others will be able to \textit{reproduce} the desired results.  For
-example, research code often requires installing other software
-packages that extend the implementation language's basic
-functionality.  Within the Python community~\citep{vanR95}, external
+Within the Python~\citep{vanR95} community, external
 packages that are published in the most popular
@@
     ecosystem.}  From left to right: plain-text \textbf{Python
-    scripts} (.py files) provide the
-  most basic ``system'' for sharing raw code.  Scripts may reference
-  external libraries, but those libraries are not automatically
-  installed on other users' systems, nor is any version checking
-  performed by default.  \textbf{Jupyter notebooks} (.ipynb files) comprise embedded text,
-  executable code, and media (including rendered figures, code output,
-  etc.).  When the \textbf{\texttt{davos} library} is imported into a Jupyter
-  notebook, the notebook's functionality is extended to automatically
-  install the required external libraries (at their correct versions,
-  when specified).  \textbf{Virtual environments} install an isolated copy of
-  Python and all required dependencies.  This typically requires
-  defining a \texttt{requirements.txt} file that lists all
-  dependencies (including version numbers) along with an environment
-  (.yml) file that specifies how the virtual environment should be
-  configured.  \textbf{Containers} provide a means of defining an isolated
+    scripts} (\texttt{.py} files) provide the most basic ``system''
+  for sharing raw code.  Scripts may reference external libraries, but
+  those libraries must be manually installed on other users' systems.
+  Further, any checking needed to verify that the correct versions of
+  those libraries were installed must also be performed manually.
+  \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
+  text, executable code, and media (including rendered figures, code
+  output, etc.).  When the \textbf{\texttt{davos} library} is imported
+  into a Jupyter notebook, the notebook's functionality is extended to
+  automatically install the required external libraries (at their
+  correct versions, when specified).  \textbf{Virtual environments}
+  install an isolated copy of Python and all required dependencies.
+  This typically requires defining a \texttt{requirements.txt} file or
+  an environment (\texttt{.yml}) file that that specifies all project
+  dependencies (including version numbers of external libraries).
+  \textbf{Containers} provide a means of defining an isolated
   environment that includes a complete operating system (independent
-  of the user's operating system), in addition to a virtual
-  environment or other configurations needed to provide the necessary
-  computing environment.  Containers are typically defined using
-  specification files (e.g., a plain-text \texttt{dockerfile}) that
-  instruct the virtualization engine regarding how to build the
-  virtual environment.  \textbf{Virtual machines} provide a complete
-  hardware-level simulation of the computing environment.  In addition
-  to simulating specific hardware, virtual machines (typically
-  specified using binary images files) must also define operating
-  system-level properties of the computing environment.  Systems to
-  the left of the blue vertical line entail sharing individual
-  files, with no additional installation or configuration needed to
-  run the target software.  Systems to the right of the red vertical
-  line provide high reproducibility by supporting precise control over
-  dependencies and versioning.  Notebooks enhanced using the
-  \texttt{davos} library are easily shareable and require minimal
-  setup costs, while also facilitating high reproducibility by
-  enabling precise control over project dependencies.}
+  of the user's operating system), in addition to (optionally)
+  specifying a virtual environment or other configurations needed to
+  provide the necessary computing environment.  Containers are
+  typically defined using specification files (e.g., a plain-text
+  \texttt{Dockerfile}) that instruct the virtualization engine
+  regarding how to build the virtual environment.  \textbf{Virtual
+    machines} provide a complete hardware-level simulation of the
+  computing environment.  In addition to simulating specific hardware,
+  virtual machines (typically specified using binary images files)
+  must also define operating system-level properties of the computing
+  environment.  Systems to the left of the blue vertical line entail
+  sharing individual files, with no additional installation or
+  configuration needed to run the target code.  Systems to the right
+  of the red vertical line support precise control over dependencies
+  and versioning.  Notebooks enhanced using the \texttt{davos} library
+  are easily shareable and require minimal setup costs, while also
+  facilitating high reproducibility by enabling precise control over
+  project dependencies.}
 \label{fig:code-sharing}
@@
 
-To facilitate code sharing, the Python community has developed a broad
-set of approaches and tools (Fig.~\ref{fig:code-sharing}).  At one
+Researchers, programmers, and others have developed a broad
+set of approaches and tools to facilitate code sharing and
+reproducible outcomes (Fig.~\ref{fig:code-sharing}).  At one
 extreme, simply publishing a set of Python scripts (.py files) may
@@
 
+Since its initial release, \texttt{davos} has found use in a variety
+of applications.  In addition to managing computing environments
+for multiple ongoing research studies, \texttt{davos} is being used by
+both students and instructors in programming courses such as
+\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
+    with Data}} \cite{Mann21b} (an open course on data science,
+visualization, and communication) to simplify distributing lessons and
+submitting assignments, as well as in online demos such as
+{\texttt{abstract2paper}} \cite{Mann21a} (an example application of
+\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
+ready-to-run code that installs dependencies automatically.
+
 Our work also has several more subtle ``advanced'' use cases and
@@
 A second advanced use case is in providing a proof-of-concept of how
-one can add new ``keywords'' to the Python language by leveraging the
-error-handling mechanisms.  This could lead to exciting new tools
-that, like \texttt{davos}, extend the Python language in useful ways.
-We note that our approach to adding the \texttt{smuggle} keyword to
-Python when \texttt{davos} is imported into a notebook-based
-environment also has the potential to be exploited for more nefarious
-purposes.  For example, a malicious user could use a similar approach
-(e.g., in a different library) to substantially change a notebook's
-functionality by adding new \textit{unexpected} keyword-like objects
-(e.g., based around common typos).  This could lead to
-difficult-to-predict changes in a notebook's behavior once the
-malicious library was imported.  This highlights an important reason
-why security-conscious users would be well-served to only make use of
-libraries from trusted sources, or whose code is publicly available
-for review.
+one can add new ``keyword-like'' operators to the Python language by
+leveraging notebooks' error-handling mechanisms.  This could lead to
+exciting new tools that, like \texttt{davos}, extend the Python
+language in useful ways within notebook-based environments.  We note that
+our approach to adding the \texttt{smuggle} keyword to Python when
+\texttt{davos} is imported into a notebook-based environment also has
+the potential to be exploited for more nefarious purposes.  For
+example, a malicious user could use a similar approach (e.g., in a
+different library) to substantially change a notebook's functionality
+by adding new \textit{unexpected} keyword-like objects (e.g., based
+around common typos).  This could lead to difficult-to-predict changes
+in a notebook's behavior once the malicious library was imported.
+This highlights an important reason why security-conscious users would
+be well-served to only make use of libraries from trusted sources, or
+whose code is publicly available for review.
 
@@
 \section*{Author Contributions}
-Conceptualization: PCF and JRM.  Methodology: PCF and JRM.
-Implementation: PCF.  Validation: PCF.  Testing: PCF and JRM.
-Writing: PCF and JRM.
+\textbf{Paxton C. Fitzpatrick}: Conceptualization, Methodology,
+Software, Validation, Writing - Original Draft,
+Visualization. \textbf{Jeremy R. Manning}: Conceptualization,
+Resources, Validation, Writing - Review \& Editing, Supervision, Funding
+acquisition.
 

### 2022-10-11 paper/main.tex
fix typo in software architecture section

--- 2022-10-08 paper/main.tex
@@
 At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
-An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants \texttt{davos} in the future relatively easy.
+An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants to \texttt{davos} in the future relatively easy.
 

### 2022-10-11 paper/main.tex
reference new figure version

@@
 Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippet1})} (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
-%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippet1}.
-%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_ for examples).
+%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
+%Figure \ref{fig:snippets} provides a number of examples of \texttt{smuggle} statements accompanied by
 
-Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
 However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
+If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
 If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
 If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
 
-%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
+%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
 If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead.
@@
 \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
 For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.
@@
 \centering
-\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
+\includegraphics[width=\textwidth]{figs/snippets.pdf}
 \caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
-\label{fig:snippet1}
+\label{fig:snippets}
 \end{figure}

### 2022-10-11 paper/main.tex
fill in references to lines in Fig 2

@@
 Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_ for examples).
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines 3--10 for examples).
 %For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
@@
 
-Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
+Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines 12--13).
 However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
+If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
 If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
 If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines 21--22).
 
@@
 \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_).
-For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines 24--28).
+For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flag will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to the installer program's; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
 

### 2022-10-11 paper/main.tex

--- 2022-10-11 paper/main.tex
@@
   mechanism for specifying (and automatically installing) the correct
-  package versions of the project's dependencies.  This enables researchers to
-  share a complete reproducible environment using a single Jupyter
-  notebook file.
+  package versions of the project's dependencies.  The \texttt{davos}
+  library also ensures that those versions are in use any time the
+  notebook's code is executed.  This enables researchers to share a complete
+  reproducible copy of their code within a single Jupyter notebook file.
 
@@
 
-Code sharing is a core component of the open science movement that has
-inspired the development of a full ecosystem of tools and packages.
-However, sharing code, in and of itself, does not guarantee that
-others will be able to \textit{reproduce} the desired results.  For
-example, research code often requires installing other software
-packages that extend the implementation language's basic
-functionality.  Within the Python community~\citep{vanR95}, external
+The same computer code may not behave identically under different
+circumstances.  For example, when code depends on external libraries,
+different versions of those libraries may function differently.  Or
+when CPU or GPU instruction sets differ across machines, the same
+high-level code may be compiled into different machine instructions.
+Because executing identical code does not guarantee identical
+outcomes, code sharing in and of itself is often insufficient for
+enabling researchers to reproduce each others' work.
+
+Within the Python~\citep{vanR95} community, external
 packages that are published in the most popular
@@
 Despite that it is \textit{possible} to manually install the intended
-version numbers of every dependency of a Python script or package,
-doing so may cause conflicts within the user's computing environment
-that interfere with the functionality of \textit{other} code.
+version numbers of every dependency of a Python script or package, manually
+tracking down those dependencies can impose a substantial burden on
+the user.
 
@@
 At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
-  Rose99} provide a hardware-level simulation of the desired system.
+  vmware} provide a hardware-level simulation of the desired system.
 Virtual machines are typically isolated from the user's system, such
@@
 \subsection{Software architecture}
-The \texttt{davos} package consists of two interdependent subpackages.
-The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
-However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
-To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
-This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
-At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
-An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants to \texttt{davos} in the future relatively easy.
+The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
 
-\comment{
-- js_functions.py?
-- how parser is registered and deregistered?
-- stub files?
-- test suite?
-- packaged with new PEP \_\_\_ standard (pyproject.toml + setup.cfg; no setup.py)?
-}
 % Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
 
-\subsection{Software functionalities}
+\subsection{Software functionalities}%\label{sec:functionalities}
 
-\subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}''.
+\subsubsection{The \texttt{smuggle} statement}
+Importing \texttt{davos}\comment{in a Jupyter notebook} enables an additional Python keyword: ``\texttt{smuggle}".
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 
-\subsubsection{The onion comment}\label{subsec:onion}
-For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''.
-An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
-Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippet1})} (see Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_ for examples).
-%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippet1}.
-%Figure \ref{fig:snippet1} provides a number of examples of \texttt{smuggle} statements accompanied by
-
-Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
-However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
-If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
-If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
-
-%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
-If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead.
-This guarantees the notebook is always run with a specific (or constrained) version of a particular package.
-Similarly, \texttt{davos}
-%If the package exists locally, \texttt{davos} will extract its version from metadata before loading it to determine its version, and if it does not match the requested version (or if no local installation is found),
-%If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will check whether the smuggled package is installed locally (as usual), and if so, additionally parse its metadata to determine
-%Adding a version specifier \cite{CoghStuf13} to an onion comment guarantees the version loaded into the notebook will matches the version specified
-
-\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippet1}, lines \_\_\_-\_\_\_).
-For example, \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to \texttt{pip}'s; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to \texttt{sys.path}, if necessary, so the package can be imported.
+\subsubsection{The onion comment}
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}.
+An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
+Onion comments follow a simple syntax based on the ``type comment" syntax introduced in PEP 484 \cite{vanREtal14} and are designed to make managing packages via \texttt{davos} intuitive and familiar.
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
 
@@
 \includegraphics[width=\textwidth]{snippets/snippet1.pdf}
-\caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
+\caption{\small \textbf{FILL THIS IN...}}
 \label{fig:snippet1}
@@
 
-\subsubsection{The \texttt{davos} config}\label{subsec:config}
+\subsubsection{The \texttt{davos} config}
 

### 2022-10-11 paper/main.tex

@@
 \subsection{Software architecture}
-The \texttt{davos} package is structured as two sub-packages: a set of ``core" modules that implement...
+The \texttt{davos} package consists of two interdependent subpackages.
+The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
+However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
+To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
+This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
+At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
+An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants to \texttt{davos} in the future relatively easy.
 
+\comment{
+- js_functions.py?
+- how parser is registered and deregistered?
+- stub files?
+- test suite?
+- packaged with new PEP \_\_\_ standard (pyproject.toml + setup.cfg; no setup.py)?
+}
 % Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
 
-\subsection{Software functionalities}%\label{sec:functionalities}
+\subsection{Software functionalities}
 
-\subsubsection{The \texttt{smuggle} statement}
-Importing \texttt{davos}\comment{in a Jupyter notebook} enables an additional Python keyword: ``\texttt{smuggle}".
+\subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
+Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}''.
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 
-\subsubsection{The onion comment}
-For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the \textit{onion comment}.
-An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, how it should be installed.
-Onion comments follow a simple syntax based on the ``type comment" syntax introduced in PEP 484 \cite{vanREtal14} and are designed to make managing packages via \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to install the package as desired manually via the command line (see Fig.~\ref{fig:snippet1}).
+\subsubsection{The onion comment}\label{subsec:onion}
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''.
+An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
+Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines 3--10 for examples).
+%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
+%Figure \ref{fig:snippets} provides a number of examples of \texttt{smuggle} statements accompanied by
+
+Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines 12--13).
+However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
+If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
+If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
+If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines 21--22).
+
+%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
+If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead.
+This guarantees the notebook is always run with a specific (or constrained) version of a particular package.
+Similarly, \texttt{davos}
+%If the package exists locally, \texttt{davos} will extract its version from metadata before loading it to determine its version, and if it does not match the requested version (or if no local installation is found),
+%If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will check whether the smuggled package is installed locally (as usual), and if so, additionally parse its metadata to determine
+%Adding a version specifier \cite{CoghStuf13} to an onion comment guarantees the version loaded into the notebook will matches the version specified
+
+\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines 24--28).
+For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flag will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to the installer program's; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
 
@@
 \centering
-\includegraphics[width=\textwidth]{snippets/snippet1.pdf}
-\caption{\small \textbf{FILL THIS IN...}}
-\label{fig:snippet1}
+\includegraphics[width=\textwidth]{figs/snippets.pdf}
+\caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
+\label{fig:snippets}
 \end{figure}

### 2022-10-12 paper/main.tex
switched to using CDL bibliography, remove main.bib
switch conda citation for conda-forge

@@
 packages that are published in the most popular
-repositories~\citep{pypi, Anac12} are associated with version numbers
+repositories~\citep{pypi, cond15} are associated with version numbers
 and tags that enable users to guarantee that they are installing
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{main.bib}
+\bibliography{cdl}
 

### 2022-10-13 paper/main.tex
WIP implementation details section

@@
 At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
-An additional benefit of this design pattern is that it makes adding support for new or updated notebook variants to \texttt{davos} in the future relatively easy.
+An additional benefit of this design pattern is that it allows maintainers or contributors to extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.
+
+%The package also includes stub files (\texttt{.pyi} files) for each module for use with a static type checker, as well as a custom GitHub Actions-based CI test suite that uses
 
@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}''.
+Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}'' (also see Section \ref{subsec:implementation}).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 
-\subsection{Sample code snippets analysis (optional)}
+\subsection{Implementation details}\label{subsec:implementation}
+Functionally, importing \texttt{davos} appears to define ``\texttt{smuggle}'' as a Python keyword, similar to ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
+It also appears to cause Python to parse comments as potentially relevant to the code's behavior, which they normally are not.
+However, \texttt{davos} doesn't actually modify the rules used by Python's parser or lexical analyzer---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
+Instead, \texttt{davos} leverages the IPython notebook backend to implement the \texttt{smuggle} statement and onion comment via a combination of namespace injections and its own (far simpler) custom parser.
 

### 2022-10-16 paper/main.tex
fixed incorrect virtual environment citation
WIP implementation details section

@@
 and any relevant package dependencies.  Virtual
-environments~\citep[e.g.,][]{vanREtal14} also provide a computing
+environments~\citep[e.g.,][]{Anac12} also provide a computing
 environment that is largely separated from the user's main
@@
 Functionally, importing \texttt{davos} appears to define ``\texttt{smuggle}'' as a Python keyword, similar to ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
-It also appears to cause Python to parse comments as potentially relevant to the code's behavior, which they normally are not.
-However, \texttt{davos} doesn't actually modify the rules used by Python's parser or lexical analyzer---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
+It also appears to cause comments to be parsed and potentially able to affect the code's behavior, which they normally are not.
+However, \texttt{davos} doesn't actually modify the rules of Python's parser or lexical analyzer---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
 Instead, \texttt{davos} leverages the IPython notebook backend to implement the \texttt{smuggle} statement and onion comment via a combination of namespace injections and its own (far simpler) custom parser.
+
+%The \texttt{smuggle} keyword can be enabled and disabled at will by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above).
+When \texttt{davos} is imported, it is automatically activated by default.
+Activating \texttt{davos} triggers two things:
+%\begin{enumerate}
+%    \item The \texttt{smuggle()} function is injected into the IPython user namespace 
+%    \item The \texttt{davos} parser is registered as a custom IPython input transformer
+%\end{enumerate}
+
+The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above); when \texttt{davos} is first imported, it is activated automatically.
+Activating \texttt{davos} triggers two things: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
+IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands.
+\texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code.
+The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function.
+For example, if the code visible to the user reads
+\begin{verbatim}
+smuggle numpy as np    # pip: numpy>1.16,<=1.20 -vv,
+\end{verbatim} 
+the code that is actually executed by the Python interpreter would be 
+\begin{verbatim}
+smuggle(name="numpy", as_="np", installer="pip", args_str="""numpy>1.16,<=1.20 -vv""", installer_kwargs={`editable': False, `spec': `numpy>1.16,<=1.20', `verbosity': 2}).
+\end{verbatim}
+
+% talk about how exceptions have to inherit from SyntaxError since that's the only thing that can be raised during parsing
 

### 2022-10-16 paper/main.tex
add package structure figure
updates to implementation details section

@@
 
-\documentclass[preprint,12pt, a4paper]{elsarticle}
+\documentclass[preprint,12pt,a4paper]{elsarticle}
 
@@
 \subsection{Software architecture}
+% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
 The \texttt{davos} package consists of two interdependent subpackages.
@@
 }
-% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/package_structure}
+\caption{\small \textbf{Package structure.}}
+\label{fig:package-structure}
+\end{figure}
 
@@
 Functionally, importing \texttt{davos} appears to define ``\texttt{smuggle}'' as a Python keyword, similar to ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
-It also appears to cause comments to be parsed and potentially able to affect the code's behavior, which they normally are not.
+It also appears to cause comments to be parsed, and their contents potentially able to affect code behavior, which they normally are not.
 However, \texttt{davos} doesn't actually modify the rules of Python's parser or lexical analyzer---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
@@
 
-The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above); when \texttt{davos} is first imported, it is activated automatically.
+The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above).
+When \texttt{davos} is first imported, it is activated automatically.
 Activating \texttt{davos} triggers two things: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
@@
 The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function.
-For example, if the code visible to the user reads
+For example, if a user runs a notebook cell containing
 \begin{verbatim}
@@
 \end{verbatim}
+Because the \texttt{smuggle()} function is defined in the notebook namespace in order for this to work, it is also possible (though never necessary) to call it directly.
+Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless it has been overwritten and no longer refers to the \texttt{smuggle()} function, as well as deregister the \texttt{davos} parser from the set of input transformers that are run when each notebook cell is executed.
+While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.
 

### 2022-10-17 paper/main.tex
moved package structure fig to top of section 2
minor edits to software functionalities section

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/package_structure}
+\caption{\small \textbf{Package structure.}}
+\label{fig:package-structure}
+\end{figure}
+
 \subsection{Software architecture}
 % Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
-The \texttt{davos} package consists of two interdependent subpackages.
+The \texttt{davos} package consists of two interdependent subpackages (see Fig.~\ref{fig:package-structure}).
 The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
@@
 This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
-At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment from a single, constant location.
-An additional benefit of this design pattern is that it allows maintainers or contributors to extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.
+At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location.
+An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.
 
@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.}}
-\label{fig:package-structure}
-\end{figure}
-
 \subsection{Software functionalities}
-
+% Present the major functionalities of the software.
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}'' (also see Section \ref{subsec:implementation}).
+Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section \ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
 However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
-If a smuggled package does not exist in the local environment, \texttt{davos} will install it, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.
+If a smuggled package does not exist in the local environment, \texttt{davos} will install it automatically, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.
 
@@
 However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
+If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints.
 If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
@@
 \end{figure}
-
-%\definecolor{backgroundgrey}{RGB}{244,246,249}
-%\definecolor{commentgrey}{RGB}{91,99,110}
-%\definecolor{keywordred}{RGB}{194,11,36}
-%
-%\lstset{
-%    backgroundcolor=\color{backgroundgrey},
-%    basicstyle=\footnotesize\fontfamily{qag}\selectfont, %\ttfamily,
-%    breaklines=true,
-%    commentstyle=\color{commentgrey},
-%    language=Python,
-%    emph={import, smuggle, from, as},
-%    emphstyle=\color{keywordred},
-%}
-%
-%\begin{lstlisting}
-%import davos
-%
-%# if numpy is not installed locally, pip-install it and display verbose output
-%smuggle numpy as np    # pip: numpy --verbose
-%
-%# pip-install pandas without using or writing to the package cache
-%smuggle pandas as pd    # pip: pandas --no-cache-dir
-%
-%# install scipy from a relative local path, in editable mode
-%from scipy.stats smuggle ttest_ind # pip: -e ../../pkgs/scipy
-%\end{lstlisting}
 

### 2022-10-17 paper/main.tex
wrote section on davos config

@@
 \subsubsection{The \texttt{davos} config}\label{subsec:config}
+The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior.
+After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes.
+The config object exposes a mixture of writable and read-only fields.
+Writable fields include:
+\begin{itemize}
+\item \texttt{.active}: Whether or not \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) should be enabled for subsequent code.
+Defaults to \texttt{True} when \texttt{davos} is first imported.
+See Section \ref{subsec:implementation} for additional info.
+\item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code).
+If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement.
+Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart \& rerun the notebook or continue running with the imported package version.
+(Note: not configurable in Google Colaboratory).
+\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
+\item \texttt{.noninteractive}: Setting to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled.
+Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded.
+\item \texttt{.pip\_executable}: The path to the \texttt{pip} executable used to install smuggled packages.
+Default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if one can't be found.
+\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program.
+Useful when smuggling packages that need to install many dependencies and/or generate extensive output.
+If the installer program throws an error, both stdout and stderr will be shown with the traceback.
+\end{itemize}
+
+\noindent The top-level \texttt{davos} namespace additionally defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config fields at once.
 

### 2022-10-17 paper/main.tex
minor edits to additional functionalities section

@@
 \subsubsection{Additional functionality}
-
-% Present the major functionalities of the software.
+% - js functions
+% - complex use cases
 
@@
 
-%The \texttt{smuggle} keyword can be enabled and disabled at will by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above).
-When \texttt{davos} is imported, it is automatically activated by default.
-Activating \texttt{davos} triggers two things:
-%\begin{enumerate}
-%    \item The \texttt{smuggle()} function is injected into the IPython user namespace
-%    \item The \texttt{davos} parser is registered as a custom IPython input transformer
-%\end{enumerate}
-
 The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above).
 When \texttt{davos} is first imported, it is activated automatically.
-Activating \texttt{davos} triggers two things: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
+Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
 IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands.
@@
 \end{verbatim}
-Because the \texttt{smuggle()} function is defined in the notebook namespace in order for this to work, it is also possible (though never necessary) to call it directly.
-Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless it has been overwritten and no longer refers to the \texttt{smuggle()} function, as well as deregister the \texttt{davos} parser from the set of input transformers that are run when each notebook cell is executed.
+Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly.
+Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function.
+It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed.
 While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.

### 2022-10-18 paper/main.tex
minor wording changes in software functionalities section

@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in a Jupyter notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section \ref{subsec:implementation} for details on how this works).
+Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section \ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines 24--28).
-For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flag will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will disable \texttt{davos}'s input prompts in addition to the installer program's; and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
+For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
 

### 2022-10-18 paper/main.tex
updated paper with separated snippets

@@
 Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line\comment{(see Fig.~\ref{fig:snippets})} (see Fig.~\ref{fig:snippets}, lines 3--10 for examples).
-%For examples of \texttt{smuggle} statements and accompanying onion comments, see Figure \ref{fig:snippets}.
-%Figure \ref{fig:snippets} provides a number of examples of \texttt{smuggle} statements accompanied by
+To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
 
-Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it; e.g., Fig.~\ref{fig:snippets}, lines 12--13).
-However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13} (e.g., Fig.~\ref{fig:snippets}, lines 15--19), \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints.
+\begin{centering}
+\includegraphics[width=\textwidth]{figs/snippet1.pdf}
+\end{centering}
+
+\noindent Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
+
+\begin{centering}
+\includegraphics[width=\textwidth]{figs/snippet2.pdf}
+\end{centering}
+
+\noindent However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
+If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints.
 If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
-If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead.
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.; Fig.~\ref{fig:snippets}, lines 21--22).
+If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
 
-%If an onion comment includes a version specifier (\cite{CoghStuf13}; e.g., Fig.~\ref{fig:snippets}, lines \_\_\_-\_\_\_), \texttt{davos} will first check whether the smuggled package exists locally, and if so, extract its version info from its metadata to compare against the requested version.
-If the installed version doesn't satisfy the given constraint (or if no local version is found), \texttt{davos} will install and load a suitable version instead.
-This guarantees the notebook is always run with a specific (or constrained) version of a particular package.
-Similarly, \texttt{davos}
-%If the package exists locally, \texttt{davos} will extract its version from metadata before loading it to determine its version, and if it does not match the requested version (or if no local installation is found),
-%If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will check whether the smuggled package is installed locally (as usual), and if so, additionally parse its metadata to determine
-%Adding a version specifier \cite{CoghStuf13} to an onion comment guarantees the version loaded into the notebook will matches the version specified
+\begin{centering}
+\includegraphics[width=\textwidth]{figs/snippet3.pdf}
+\end{centering}
 
-\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed (e.g., Fig.~\ref{fig:snippets}, lines 24--28).
-For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported.
+\noindent Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
 
-\begin{figure}[h]
-\centering
-\includegraphics[width=\textwidth]{figs/snippets.pdf}
-\caption{\small Example \texttt{smuggle} statements and accompanying onion comments.}
-\label{fig:snippets}
-\end{figure}
+\begin{centering}
+\includegraphics[width=\textwidth]{figs/snippet4.pdf}
+\end{centering}
+
+\noindent \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed.
+For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
+
+\begin{centering}
+\includegraphics[width=\textwidth]{figs/snippet5.pdf}
+\end{centering}
 

### 2022-10-18 paper/main.tex
fixed blank line after snippets

@@
 To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
-
-\begin{centering}
+\begin{center}
 \includegraphics[width=\textwidth]{figs/snippet1.pdf}
-\end{centering}
-
-\noindent Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
-
-\begin{centering}
+\end{center}
+Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
+\begin{center}
 \includegraphics[width=\textwidth]{figs/snippet2.pdf}
-\end{centering}
-
-\noindent However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
+\end{center}
+However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
 If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints.
@@
 If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
-
-\begin{centering}
+\begin{center}
 \includegraphics[width=\textwidth]{figs/snippet3.pdf}
-\end{centering}
-
-\noindent Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
-
-\begin{centering}
+\end{center}
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
+\begin{center}
 \includegraphics[width=\textwidth]{figs/snippet4.pdf}
-\end{centering}
-
-\noindent \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
+\end{center}
+\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
 In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed.
 For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
-
-\begin{centering}
+\begin{center}
 \includegraphics[width=\textwidth]{figs/snippet5.pdf}
-\end{centering}
+\end{center}
 

### 2022-10-19 paper/main.tex
make snippets 90% of \textwidth
replaced in-text smuggle function example snippets with images

@@
 \begin{center}
-\includegraphics[width=\textwidth]{figs/snippet1.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet1.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figs/snippet2.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet2.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figs/snippet3.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet3.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figs/snippet4.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet4.pdf}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=\textwidth]{figs/snippet5.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet5.pdf}
 \end{center}
@@
 For example, if a user runs a notebook cell containing
-\begin{verbatim}
-smuggle numpy as np    # pip: numpy>1.16,<=1.20 -vv,
-\end{verbatim}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet6.pdf}
+\end{center}
 the code that is actually executed by the Python interpreter would be
-\begin{verbatim}
-smuggle(name="numpy", as_="np", installer="pip", args_str="""numpy>1.16,<=1.20 -vv""", installer_kwargs={`editable': False, `spec': `numpy>1.16,<=1.20', `verbosity': 2}).
-\end{verbatim}
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet7.pdf}
+\end{center}
 Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly.

### 2022-10-19 paper/main.tex
minor cleanup and grammatical fixes throughout

@@
 outcomes, code sharing in and of itself is often insufficient for
-enabling researchers to reproduce each others' work.
+enabling researchers to reproduce each other's work.
 
-Within the Python~\citep{vanR95} community, external
+Within the Python~\cite{vanR95} community, external
 packages that are published in the most popular
-repositories~\citep{pypi, cond15} are associated with version numbers
+repositories~\cite{pypi, cond15} are associated with version numbers
 and tags that enable users to guarantee that they are installing
@@
 reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
-extreme, simply publishing a set of Python scripts (.py files) may
+extreme, simply publishing a set of Python scripts (\texttt{.py} files) may
 enable others to use or gain insights into the relevant work. Because
@@
 some projects this may be sufficient. Another popular approach
-entails creating JSON files, called Jupyter
-notebooks~\citep{KluyEtal16}, that comprise a mix of text, executable
+entails creating JSON files called Jupyter
+notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
 code, and embedded media. Notebooks may call or import external
@@
 
-At another extreme, virtual machines~\citep{Gold74, AltiEtal05,
+At another extreme, virtual machines~\cite{Gold74, AltiEtal05,
  Rose99} provide a hardware-level simulation of the desired system.
@@
 impact the user's primary operating system or computing environment.
-Containers~\citep[e.g.,][]{Merk14, KurtEtal17} provide a similar
+Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
 ``isolated'' experience. Although containerized environments do not
@@
 and any relevant package dependencies. Virtual
-environments~\citep[e.g.,][]{Anac12} also provide a computing
+environments~\cite[e.g.,][]{Anac12} also provide a computing
 environment that is largely separated from the user's main
@@
 these systems (virtual machines, containers, and virtual environments)
-guarantees (to differing degrees-- at the hardware level, operating
+guarantees (to differing degrees---at the hardware level, operating
 system level, and Python environment level, respectively) that the
@@
 what is needed to run standard Jupyter notebooks. And like virtual
-environments \texttt{davos} provides a convenient mechanism for fully
+environments, \texttt{davos} provides a convenient mechanism for fully
 specifying (and installing, as needed) a complete set of Python
@@
 The \texttt{davos} package consists of two interdependent subpackages (see Fig.~\ref{fig:package-structure}).
-The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section \ref{subsec:smuggle}) and onion comment (see Section \ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section \ref{subsec:config}).
-However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython \cite{PereGran07} is used by the notebook kernel).
+The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section~\ref{subsec:smuggle}) and onion comment (see Section~\ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section~\ref{subsec:config}).
+However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython~\cite{PereGran07} is used by the notebook kernel).
 To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
-This second subpackage defines multiple, interchangeable versions of each helper function, organized into\comment{per-environment} modules by the conditions that trigger their use.
+This second subpackage defines multiple, interchangeable versions of each helper function, organized into modules by the conditions that trigger their use.
 At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location.
@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section \ref{subsec:implementation} for details on how this works).
+Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
-Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484 \cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
+Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
 To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet1.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet1}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet2.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet2}
 \end{center}
 However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier \cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook always matches the specific version requested, or satisfies the given version constraints.
+If an onion comment includes a version specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
 If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet3.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet3}
 \end{center}
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git \cite{TorvHama05}  branches, commits, tags, etc.):
+Onion comments can similarly be used to smuggle specific VCS references (e.g., Git~\cite{TorvHama05}  branches, commits, tags, etc.):
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet4.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet4}
 \end{center}
@@
 In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed.
-For example, the \texttt{--force-reinstall}, \texttt{-I}/\texttt{--ignore-installed}, and \texttt{-U}/\texttt{--upgrade} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy; \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section \ref{subsec:onion}); and installing a package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported:
+For example, the \texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet5.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet5}
 \end{center}
+Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:onion}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported
 
@@
 Defaults to \texttt{True} when \texttt{davos} is first imported.
-See Section \ref{subsec:implementation} for additional info.
+See Section~\ref{subsec:implementation} for additional info.
 \item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code).
@@
 
-The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section \ref{subsec:config}, above).
+The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section~\ref{subsec:config}, above).
 When \texttt{davos} is first imported, it is activated automatically.
@@
 \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code.
-The \texttt{davos} parser uses a complex regular expression \cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function.
+The \texttt{davos} parser uses a complex regular expression~\cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function.
 For example, if a user runs a notebook cell containing
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet6.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet6}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet7.pdf}
+\includegraphics[width=0.9\textwidth]{figs/snippet7}
 \end{center}
@@
 \href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
-    with Data}} \cite{Mann21b} (an open course on data science,
+    with Data}}~\cite{Mann21b} (an open course on data science,
 visualization, and communication) to simplify distributing lessons and
 submitting assignments, as well as in online demos such as
-{\texttt{abstract2paper}} \cite{Mann21a} (an example application of
+{\texttt{abstract2paper}}~\cite{Mann21a} (an example application of
 \href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share

### 2022-10-19 paper/main.tex
removed hyperlinks from impacts section and unitalicize course name

@@
 both students and instructors in programming courses such as
-\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
-    with Data}}~\cite{Mann21b} (an open course on data science,
+Storytelling with Data~\cite{Mann21b} (an open course on data science,
 visualization, and communication) to simplify distributing lessons and
 submitting assignments, as well as in online demos such as
-{\texttt{abstract2paper}}~\cite{Mann21a} (an example application of
-\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
-ready-to-run code that installs dependencies automatically.
+\texttt{abstract2paper}~\cite{Mann21a} (an example application of GPT-Neo)
+to share ready-to-run code that installs dependencies automatically.
 

### 2022-10-19 paper/main.tex
add refs for GPT-Neo

@@
 submitting assignments, as well as in online demos such as
-\texttt{abstract2paper}~\cite{Mann21a} (an example application of GPT-Neo)
-to share ready-to-run code that installs dependencies automatically.
+\texttt{abstract2paper}~\cite{Mann21a} (an example application of
+GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that
+installs dependencies automatically.
 

### 2022-10-19 paper/main.tex
add reference to PSYC11 in impact section

@@
 for multiple ongoing research studies, \texttt{davos} is being used by
-both students and instructors in programming courses such as
+both students and instructors in programming and methods courses such as
 Storytelling with Data~\cite{Mann21b} (an open course on data science,
-visualization, and communication) to simplify distributing lessons and
+visualization, and communication) and Laboratory in Psychological
+Science~\cite{Mann22} (an open course on experimental and statistical
+methods for psychology research) to simplify distributing lessons and
 submitting assignments, as well as in online demos such as

### 2022-10-19 paper/main.tex
remvoed advanced functionality section in favor of mention in impacts

@@
 
-\subsubsection{Additional functionality}
-% - js functions
-% - complex use cases
-
 \subsection{Implementation details}\label{subsec:implementation}
@@
 statements (when combined with onion comments) are version-sensitive.
-This enables multiple versions of a single library to be
-imported within the same notebook. This could be useful in cases
-where specific features were added or removed from a package across
-different versions, or in comparing the performance or functionality
-of particular features across different versions of the same package.
+And because onion comments are parsed at runtime, required package and
+their specified versions are installed in a just-in-time manner. Thus, it is possible
+in most cases to \texttt{smuggle} a specific package version or revision even if
+a different version has already been loaded. This enables more complex uses
+that take advantage of multiple versions of a package within a single interpreter
+session. This could be useful in cases where specific features are added or
+removed from a package across different versions, or in comparing the
+performance or functionality of particular features across different versions of
+the same package.
 

### 2022-10-19 paper/main.tex
BibTeX citation key changes from updating cdl.bib

@@
 packages that are published in the most popular
-repositories~\cite{pypi, cond15} are associated with version numbers
+repositories~\cite{Pyth03, cond15} are associated with version numbers
 and tags that enable users to guarantee that they are installing
@@
 both students and instructors in programming and methods courses such as
-Storytelling with Data~\cite{Mann21b} (an open course on data science,
+Storytelling with Data~\cite{Mann21d} (an open course on data science,
 visualization, and communication) and Laboratory in Psychological
@@
 submitting assignments, as well as in online demos such as
-\texttt{abstract2paper}~\cite{Mann21a} (an example application of
+\texttt{abstract2paper}~\cite{Mann21e} (an example application of
 GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that

### 2022-10-25 paper/main.tex
updates to abstract

@@
   machines.  Each of these existing solutions requires installing or
-  setting up a system for running the desired code that must be
-  packaged alongside the primary code base.  Here we propose a
-  lighter-weight solution than virtual environments: the
+  setting up a system for running the desired code, increasing the 
+  complexity and time cost of sharing or engaging with reproducible 
+  science. Here, we propose a lighter-weight solution:  the
   \texttt{davos} library.  When used in combination with a
@@
   mechanism for specifying (and automatically installing) the correct
-  package versions of the project's dependencies.  The \texttt{davos}
-  library also ensures that those versions are in use any time the
+  versions of the project's dependencies.  The \texttt{davos}
+  library further ensures that those packages and specific versions are used every time the
   notebook's code is executed.  This enables researchers to share a complete

### 2022-10-26 paper/main.tex
edits to paper through pg 3

@@
 Because executing identical code does not guarantee identical
-outcomes, code sharing in and of itself is often insufficient for
-enabling researchers to reproduce each other's work.
+outcomes, code sharing alone is often insufficient for
+enabling researchers to reproduce each other's work, or to collaborate on
+projects involving data collection or analysis.
 
@@
 repositories~\cite{Pyth03, cond15} are associated with version numbers
-and tags that enable users to guarantee that they are installing
-exactly the same code across different computing environments.
+and tags that allow users to guarantee they are installing
+exactly the same code across different computing environments \cite{CoghStuf13}.
 Despite that it is \textit{possible} to manually install the intended
-version numbers of every dependency of a Python script or package, manually
+version of every dependency of a Python script or package, manually
 tracking down those dependencies can impose a substantial burden on 
-the user.
+the user and make room for mistakes. Further, when dependency versions 
+are left unspecified, replicating the original computing environment 
+becomes difficult or impossible.
 
@@
 
-Researchers, programmers, and others have developed a broad
+Computational researchers and other programmers have developed a broad
 set of approaches and tools to facilitate code sharing and
 reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
-extreme, simply publishing a set of Python scripts (\texttt{.py} files) may
+extreme, simply distributing a set of Python scripts (\texttt{.py} files) may
 enable others to use or gain insights into the relevant work. Because
 Python is installed by default on most modern operating systems, for
-some projects this may be sufficient. Another popular approach
-entails creating JSON files called Jupyter
+some projects, this may be sufficient. Another popular approach
+entails creating Jupyter
 notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
 code, and embedded media. Notebooks may call or import external
-scripts or libraries in order to provide a more compact and readable
+scripts or libraries---even intersperse snippets of other programming 
+or markup languages---in order to provide a more compact and readable
 experience for users. Each of these systems (Python scripts and
@@
 code is executed. Therefore the functionality of code shared using
-these systems cannot be guaranteed across different computing
-environments.
+these systems cannot be guaranteed across different users or setups.
 
@@
  Rose99} provide a hardware-level simulation of the desired system.
-Virtual machines are typically isolated from the user's system, such
+Virtual machines are typically isolated such
 that installing or running software on a virtual machine does not

### 2022-10-26 paper/admin/cover_letter.tex

\title{cover letter}
%
% See http://texblog.org/2013/11/11/latexs-alternative-letter-class-newlfm/
% and http://www.ctan.org/tex-archive/macros/latex/contrib/newlfm
% for more information.
%
\documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{hyperref, pxfonts, geometry}

  \setlength{\voffset}{0in}

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

\newlfmP{Headlinewd=0pt,Footlinewd=0pt}

\namefrom{\vspace{-0.3in}Jeremy R. Manning}
\addrfrom{
	Dartmouth College\\
     Department of Psychological \& Brain Sciences\\
    HB 6207 Moore Hall\\
	Hanover, NH  03755}

\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{Software X}:}

\closeline{Sincerely,}
%\usepackage{setspace}
%\linespread{0.85}
% The cover letter should explain the importance of the work, and why you consider it appropriate for the diverse readership of . 
% OPTIONAL. Provide the name and institution of reviewers you would like to recommend and/or people you would like to be excluded from peer review (explaining why).

\begin{document}
\begin{newlfm}

  We have enclosed our manuscript entitled \textit{\texttt{davos}: a
    Python package ``smuggler'' for constructing lightweight
    reproducible notebooks} to be considered for publication as
  an \textit{Article}.

  Our manuscript describes a new Python package, \texttt{davos}.  When
  used in combination with a notebook-based Python project, the
  \texttt{davos} library provides tools for specifying and
  automatically installing the correct versions of the project's
  dependencies.  Our library also ensures that the correct versions of
  those dependencies are in use any time the notebook's code is
  executed.  This enables researchers to share a complete reproducible
  copy of their code within a single Jupyter notebook (.ipynb) file.

  Broadly, we designed the \texttt{davos} library to target a ``sweet
  spot'' along a continuum of existing approaches to facilitating reproducible
  code-based research.  At one end of this continuum, ``lightweight''
  approaches entail simply sharing raw code (e.g., plain-text python
  scripts) or Jupyter notebooks (e.g., JSON files that comprise a mix
  of text, code, and embedded media).  These lightweight solutions
  benefit from very low setup costs (which increase accessibility),
  but they typically do not make any attempt to manage or constrain
  the computing environment in which the shared code is executed.
  At best, when dependencies are missing on the end user's system, shared code
 may fail to run entirely.  And when the \textit{versions} of a
 project's dependencies differ across the original author's system and
 the end user's system, shared code may (at worst) behave in
 unexpected ways or even cause damage.

 At the other end of this continuum, ``heavyweight'' approaches entail
 simulating or replicating, to varying depths, the original computing
 environment that the shared code was developed for.  For example,
 virtual environments, containerized systems, and virtual machines
 reproduce (respectively) a complete Python environment, operating system, and/or
 full hardware simulation of the original environment.  Each of these
 systems guarantees, to varying degrees, that shared code will behave
 as expected for the end user.  A downside to these approaches is that
 they are often effort- and/or resource-intensive, since they require
 installing additional tools (e.g., Anaconda, Docker, machine
 emulators, etc.) and
 configuration files (e.g., environment configuration files,
 Dockerfiles, system images, etc.), alongside the to-be-shared code
 itself.

 The \texttt{davos} library is lightweight in the sense that it does
 not require any setup beyond that required to run standard Jupyter
 notebooks.  But \texttt{davos} also provides infrastructure for
 precisely controlling project dependencies in a way that can easily
 be embedded into standard notebooks.  This provides a complete system
 for sharing reproducible code inside of a standard notebook file.

 Beyond its intended primary role in facilitating reproducible
 research, \texttt{davos} is also useful in pedagogical settings
 (e.g., courses that involve programming in notebook-based
 environments), or when putting together lightweight notebook-based
 demonstrations.

 Thank you for considering our manuscript, and we
 hope you will find it suitable for publication in \textit{Software
   X}.

\end{newlfm}
\end{document}

### 2022-10-26 paper/main.tex
edits up through pg 4 (fig 1 caption)

@@
   \texttt{davos} library.  When used in combination with a
-  notebook-based Python project, the \texttt{davos} library provides a
+  notebook-based Python project, \texttt{davos} provides a
   mechanism for specifying (and automatically installing) the correct
@@
 exactly the same code across different computing environments \cite{CoghStuf13}.
-Despite that it is \textit{possible} to manually install the intended
+While it is \textit{possible} to manually install the intended
 version of every dependency of a Python script or package, manually
 tracking down those dependencies can impose a substantial burden on 
-the user and make room for mistakes. Further, when dependency versions 
+the user and create room for mistakes and inconsistencies. Further, when dependency versions 
 are left unspecified, replicating the original computing environment 
@@
   into a Jupyter notebook, the notebook's functionality is extended to
-  automatically install the required external libraries (at their
+  automatically install any required external libraries (at their
   correct versions, when specified).  \textbf{Virtual environments}
-  install an isolated copy of Python and all required dependencies.
-  This typically requires defining a \texttt{requirements.txt} file or
-  an environment (\texttt{.yml}) file that that specifies all project
-  dependencies (including version numbers of external libraries).
+  allow users to install an isolated copy of Python and all required 
+  dependencies. This typically entails distributing a configuration file
+  (e.g., a \texttt{pyproject.toml}~\cite{CannEtal16} or \texttt{environment.yml})
+  that specifies all project dependencies (including version numbers of 
+  external libraries) alongside the primary code base. Users can then install
+  a third-praty tool~\cite[e.g.,][]{Anac12, Eust19} to read the file and build the environment.
   \textbf{Containers} provide a means of defining an isolated
@@
   \texttt{Dockerfile}) that instruct the virtualization engine
-  regarding how to build the virtual environment.  \textbf{Virtual
+  regarding how to build the containerized environment.  \textbf{Virtual
     machines} provide a complete hardware-level simulation of the
@@
 scripts or libraries---even intersperse snippets of other programming 
-or markup languages---in order to provide a more compact and readable
-experience for users. Each of these systems (Python scripts and
-notebooks) provides a convenient means of sharing code, with the
+or markup lang\-uages---in order to provide a more compact and readable
+experience for users. Both of these systems (Python scripts and
+notebooks) provide a convenient means of sharing code, with the
 caveat that they do not specify the computing environment in which the
@@
 and any relevant package dependencies. Virtual
-environments~\cite[e.g.,][]{Anac12} also provide a computing
+environments~\cite[e.g.,][]{Anac12, Eust19} also provide a computing
 environment that is largely separated from the user's main
@@
 of these systems also relies on additional software that can be
-resource intensive or burdensome to install or configure.
+complex or resource-intensive to install and use, creating potential 
+barriers to both contributing to and taking advantage of open science 
+resources.
 
@@
 functionality to the default notebook experience. Like standard
-Jupyter notebooks, \texttt{davos}-enhanced notebooks allows
+Jupyter notebooks, \texttt{davos}-enhanced notebooks allow
 researchers to include text, executable code, and media within a

### 2022-10-26 paper/main.tex
text updates through pg 5 (excluding figs and captions)

@@
 % Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
+The \texttt{davos} package is named after Davos Seaworth, a smuggler often referred to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by George R. R. Martin.
 
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.}}
+\caption{\small \textbf{Package structure.} }
 \label{fig:package-structure}
@@
 The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section~\ref{subsec:smuggle}) and onion comment (see Section~\ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section~\ref{subsec:config}).
-However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementation approaches depending on various properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython~\cite{PereGran07} is used by the notebook kernel).
+However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementations depending on properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython~\cite{PereGran07} is used by the notebook kernel).
 To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
@@
 At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location.
-An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants simply by creating a new \texttt{davos.implementations} module with any necessary tweaks to existing helper functions.
+An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants by creating a new \texttt{davos.implementations} module with any necessary tweaks to the existing helper functions.
 
@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
+Importing \texttt{davos} in an IPython notebook appears to enable an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 \subsubsection{The onion comment}\label{subsec:onion}
-For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment''.
-An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
-Onion comments follow a simple syntax based on the ``type comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, simply provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment.'' An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
+Onion comments follow a simple format based on the ``type comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
+To construct an onion comment, users provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
 \begin{center}

### 2022-10-27 paper/main.tex
updates through line 149 (beginning of 2.2.3, davos config)

@@
 %\usepackage{listings}
-%\usepackage{xcolor}
+\usepackage{xcolor}
 %\usepackage{todonotes}
@@
 \end{center}
-Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) is different from its top-level module name (i.e., the name used when importing it):
+Occasionally, a package's distribution name (i.e., the name used when installing it) may differ from its top-level module name (i.e., the name used when importing it).
+In such cases, an onion comment can be used to ensure \texttt{davos} installs the proper distribution if the smuggled package can't be found locally:
+%Onion comments are useful in such cases for ensuring \texttt{davos} installs the proper distribution if the smuggled package isn't installed locally:
+%Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) differs from its top-level module name (i.e., the name used when importing it).
+Onion comments are useful in such cases for
 \begin{center}
@@
 \end{center}
-Onion comments can similarly be used to smuggle specific VCS references (e.g., Git~\cite{TorvHama05}  branches, commits, tags, etc.):
+Onion comments can also be used to smuggle specific VCS references (e.g., Git~\cite{TorvHama05}  branches, commits, tags, etc.):
 \begin{center}
@@
 \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} take certain logical actions when particular arguments are passed.
-For example, the \texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} to take certain logical actions when particular arguments are passed.
+For example, the \texttt{-I}/\newline\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
 \begin{center}
@@
 The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior.
-After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes.
+After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes (see Fig.~\textcolor{red}{REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
 The config object exposes a mixture of writable and read-only fields.

### 2022-10-27 davos/core/config.py
patched IPython environment check logic to account for colab IPython version upgrade (5.5.0 -> 7.9.0)

@@ -153,13 +153,13 @@ class DavosConfig(metaclass=SingletonConfig):
             self._environment = 'Python'
         else:
             import IPython
-            if IPython.version_info[0] < 7:
+            if IPython.version_info[0] >= 7:
                 if 'google.colab' in str(self._ipython_shell):
                     self._environment = 'Colaboratory'
                 else:
-                    self._environment = 'IPython<7.0'
+                    self._environment = 'IPython>=7.0'
             else:
-                self._environment = 'IPython>=7.0'
+                self._environment = 'IPython<7.0'
         self._conda_avail = None
         self._conda_envs_dirs = None
         self._ipy_showsyntaxerror_orig = None

### 2022-10-27 davos/implementations/__init__.py

@@ -70,8 +70,8 @@ else:
 
     _set_custom_showsyntaxerror()
 
-    if import_environment == 'IPython>=7.0':
-        from davos.implementations.ipython_post7 import (
+    if import_environment == 'IPython<7.0':
+        from davos.implementations.ipython_pre7 import (
             _activate_helper,
             _deactivate_helper,
             generate_parser_func
@@ -81,7 +81,7 @@ else:
             prompt_restart_rerun_buttons
         )
     else:
-        from davos.implementations.ipython_pre7 import (
+        from davos.implementations.ipython_post7 import (
             _activate_helper,
             _deactivate_helper,
             generate_parser_func

### 2022-10-28 tests/utils.py
assorted updates to tests and docstrings related to colab IPython version upgrade

@@ -44,7 +44,7 @@ _E = TypeVar('_E', bound=BaseException)
 _E1 = TypeVar('_E1', bound=BaseException)
 _F = TypeVar('_F', bound=Callable[..., None])
 _InstallerKwargVals = Union[bool, int, str]
-_IpyVersions = Literal['5.5.0', '7.3.0', '7.15', '7.16', 'latest']
+_IpyVersions = Literal['5.5.0', '7.3.0', '7.15', '7.16', '7.31', 'latest']
 _StrOrListStr = TypeVar('_StrOrListStr', str, List[str])
 _NbTypes = Literal['colab', 'jupyter']
 

### 2022-10-28 davos/core/config.py
removed duplicate entry in davos.config __repr__ display

@@ -219,7 +219,7 @@ class DavosConfig(metaclass=SingletonConfig):
     def __repr__(self):
         cls_name = self.__class__.__name__
         base_indent = len(cls_name) + 1
-        attrs_in_repr = ['active', 'auto_rerun', 'conda_avail']
+        attrs_in_repr = ['active', 'auto_rerun']
         if self._conda_avail is not None:
             attrs_in_repr.append('conda_avail')
             if self._conda_avail is True:

### 2022-10-28 paper/main.tex
updates to davos config section

@@
 \subsubsection{The \texttt{davos} config}\label{subsec:config}
-The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior.
+The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior.
+After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
+These include:
+%The \texttt{davos.config} object provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior.
+After importing \texttt{davos}, the config instance (a singleton) for the current session exposes a number of options that can be set by assigning values to the object's attributes (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
+These include:
+%The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior.
 After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes (see Fig.~\textcolor{red}{REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
@@
 \begin{itemize}
-\item \texttt{.active}: Whether or not \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) should be enabled for subsequent code.
-Defaults to \texttt{True} when \texttt{davos} is first imported.
+\item \texttt{.active}: This option allows users to disable \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) for subsequent notebook cells by setting its value to \texttt{False}.
+\texttt{davos} can be re-enabled at any time by setting this option to \texttt{True} (the default when \texttt{davos} is first imported).
 See Section~\ref{subsec:implementation} for additional info.
-\item \texttt{.auto\_rerun}: Controls behavior if \texttt{davos} is used to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded (i.e., it contains C-extensions that dynamically generate code).
+\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded.
+This can happen if the package includes extension modules that dynamically link C or C++ objects to the Python interpreter itself, and the code that generates those objects was changed between the old and new versions.
+If this option is set to \texttt{True}, \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement.
+If \texttt{False} (the deafult), \texttt{davos} will instead issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook, or continue running with the previously imported package version until the next time the kernel is restarted manually.
+(Note: not configurable in Google Colaboratory).
+%\item \texttt{.auto\_rerun}: Some packages (e.g., \texttt{numpy}, \texttt{pandas}) contain extension modules that dynamically link C or C++ objects to the Python interpreter when imported.
+If \texttt{davos} is used to \texttt{smuggle} a specific version of such a package after a different version of the same package was previously imported
+%\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported (at a different version) and cannot be reloaded (i.e., because it contains C-extensions that dynamically generate code).
 If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement.
-Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart \& rerun the notebook or continue running with the imported package version.
+Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook or continue running with the imported package version.
 (Note: not configurable in Google Colaboratory).
 \item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
-\item \texttt{.noninteractive}: Setting to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled.
-Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded.
-\item \texttt{.pip\_executable}: The path to the \texttt{pip} executable used to install smuggled packages.
-Default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if one can't be found.
+\item \texttt{.noninteractive}: Setting this option to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled.
+Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded, rather than prompting the user.
+\item \texttt{.pip\_executable}: This option's value specifies the path to the \texttt{pip} executable used to install smuggled packages.
+The default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if no executable can be found.
 \item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program.
-Useful when smuggling packages that need to install many dependencies and/or generate extensive output.
-If the installer program throws an error, both stdout and stderr will be shown with the traceback.
+This can be useful when smuggling packages that need to install many dependencies and/or generate extensive output.
+If the installer program throws an error, both the stdout and stderr streams will be displayed with the traceback.
 \end{itemize}
 
-\noindent The top-level \texttt{davos} namespace additionally defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config fields at once.
+%\noindent The \texttt{davos.config} object also provides a few informative read-only fields, including: 
+%\begin{itemize}
+%\item \texttt{.environment}: This field's value is a short string describing the notebook environment in which \texttt{davos} is currently running.
+This is used internally may be one of \texttt{IPython<7.0} (a notebook whose frontend uses the Jupyter JavaScript library and whose backend uses an IPython version older than v7.0), \texttt{IPython>=7.0} (, or \texttt{}
+%\end{itemize}
+\noindent The top-level \texttt{davos} namespace also defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config options at once.
 

### 2022-10-28 paper/main.tex
updates through section 2

@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in an IPython notebook appears to enable an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
+Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
@@
 \end{center}
-Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:onion}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported
+Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:config}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported
 
@@
 \subsection{Implementation details}\label{subsec:implementation}
-Functionally, importing \texttt{davos} appears to define ``\texttt{smuggle}'' as a Python keyword, similar to ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
-It also appears to cause comments to be parsed, and their contents potentially able to affect code behavior, which they normally are not.
-However, \texttt{davos} doesn't actually modify the rules of Python's parser or lexical analyzer---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
+Functionally, importing \texttt{davos} appears to make ``\texttt{smuggle}'' a valid Python keyword, similar to standard keywords like ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
+It also appears to fundamentally change how Python treats comments, suddenly allowing them to potentially influence code behavior at runtime if they conform to a particular syntax.
+However, \texttt{davos} doesn't actually modify the rules of Python's parser or lexical analyzer in order to accomplish this---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
 Instead, \texttt{davos} leverages the IPython notebook backend to implement the \texttt{smuggle} statement and onion comment via a combination of namespace injections and its own (far simpler) custom parser.
@@
 Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
-IPython preprocesses all executed code as plain text before it is sent to the Python parser, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands.
+IPython preprocesses all executed code as plain text before it is sent to the Python compiler, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands.
 \texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code.
@@
 \end{center}
+The call to the \texttt{smuggle()} function then carries out \texttt{davos}'s central logic of determining whether the smuggled package should be installed, doing so if necessary, and subsequently loading it into the namespace.
+This process is outlined in Figure \ref{fig:flow-chart}.
 Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly.
@@
 It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed.
-While the overhead added by the \texttt{davos} parser is de minimis, this may be useful, for example, when optimizing or precisely profiling code.
+While the overhead added by the \texttt{davos} parser is minimal, this may be useful, for example, when optimizing or precisely profiling code.
 

### 2022-10-29 davos/core/core.py
add --no-input arg to pip-install command in non-interactive mode

@@ -458,6 +458,8 @@ class Onion:
             args = self.args_str.replace("<", "'<'").replace(">", "'>'")
         if self.installer == 'pip':
             install_exe = config._pip_executable
+            if config.noninteractive:
+                args = f'{args} --no-input'
         else:
             install_exe = self.installer
 

### 2022-11-01 paper/main.tex
added flow chart figure
fixes and cleanup in impact section

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/flow_chart}
+\caption{\small \textbf{\texttt{smuggle()} function logic.} }
+\label{fig:flow-chart}
+\end{figure}
+
 % talk about how exceptions have to inherit from SyntaxError since that's the only thing that can be raised during parsing
@@
 \texttt{davos} library (when used in conjunction with Jupyter
-notebooks) provides a lightweight mechanism for sharing code and
+notebooks) provides a light\-weight mechanism for sharing code and
 ensuring reproducibility across users and computing environments
@@
 We designed \texttt{davos} for use in research applications. For
-example, in many settings \texttt{davos} may be used as a drop-in
+example, in many settings, \texttt{davos} may be used as a drop-in
 replacement for more-difficult-to-set-up virtual environments,
 containers, and/or virtual machines. For researchers, this lowers
-barriers to sharing code. By eliminating most of the setup costs
+barriers to both sharing code. By eliminating most of the setup costs
 of reconstructing the original researchers' computing environment,
 \texttt{davos} also lowers barriers to entry for members of
-the scientific community and the public who seek to \textit{benefit}
+the scientific community and the public who seek to benefit
 from shared code.
@@
 \texttt{davos} also provides an elegant means of sharing ready-to-run
-notebook-based demonstrations that install their dependencies
+notebook-based demonstrations or tutorials that install their dependencies
 automatically.
@@
 potential impacts. Whereas Python's built-in \texttt{import}
-statement is agnostic to packages' version numbers, \texttt{smuggle}
+statement is agnostic to packages' version information, \texttt{smuggle}
 statements (when combined with onion comments) are version-sensitive.
-And because onion comments are parsed at runtime, required package and
+And because onion comments are parsed at runtime, required packages and
 their specified versions are installed in a just-in-time manner. Thus, it is possible

### 2022-11-01 paper/main.tex
add illustrative example fig, recompile
section 3 intro paragraph, insert ref to illustrative example fig in section 2

@@
 The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior.
-After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
+After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\ref{fig:illustrative-example} for example usage).
 These include:
@@
 % Provide at least one illustrative example to demonstrate the major functions.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/illustrative_example}
+\caption{\small \textbf{Example use case for \texttt{davos}'s functionality.}}
+\label{fig:illustrative-example}
+\end{figure}
+
+Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses.
+In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in an IPython notebook.
+The hypothetical dataset (a \texttt{pandas} \cite{McKi10} \texttt{DataFrame}) and model (a \texttt{scikit-learn} \cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in December 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them.
+The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.
 

### 2022-11-03 paper/main.tex
tweaks to intro to section 3

@@
 Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses.
-In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in an IPython notebook.
-The hypothetical dataset (a \texttt{pandas} \cite{McKi10} \texttt{DataFrame}) and model (a \texttt{scikit-learn} \cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in December 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them.
+In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in a Jupyter notebook.
+The hypothetical dataset (a \texttt{pandas}~\cite{McKi10} \texttt{Panel}) and model (a \texttt{scikit-learn}~\cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in June 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them.
 The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.

### 2022-11-03 paper/main.tex
illustrative example walkthrough through line 4

@@
 
+After importing \texttt{davos} (line 1), the user first smuggles two utilities for checking and reading local files in the code below.
+The \texttt{smuggle} statement in line 3 loads the \texttt{is\_file()} function from the Python standard library's \texttt{os.path} module.
+Standard library modules are included with all Python distributions, so this line is functionally equivalent to an \texttt{import} statement and no onion comment is needed.
+Line 4 loads the \texttt{joblib} library~\cite{Varo10}, installing it first, if necessary.
+Since \texttt{joblib}'s I/O interface has historically remained stable and backwards-compatible across releases, requiring that users have a particular exact version installed would likely be unnecessarily restrictive.
+However, there's also no guarantee that a \textit{future} release won't introduce some breaking change, so to help ensure the analysis notebook continues to run properly in the future, the onion comment in line 4 limits allowable versions to those already released when the code was written.
+%After importing \texttt{davos} (line 1), the user first smuggles two utilities that will be used to help find and load local files in the code below: the \texttt{is\_file} function from the \texttt{os.path} module, and the \texttt{joblib} library~\cite{Varo10} (lines 3--4).
+The first \texttt{smuggle} statement needs no onion comment, as the \texttt{os.path} module is part of Python's standard library and is therefore guaranteed to be available.
+The second ensures \texttt{joblib} is installed before loading it Enforcing an exact version of \texttt{joblib} is likely unnecessary, since the package's I/O interface has historically remained generally stable across versions.
+However, there's no
+
 % Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.

### 2022-11-03 paper/main.tex
illustrative example walkthrough up through line 14

@@
 %\usepackage{listings}
-\usepackage{xcolor}
+%\usepackage{xcolor}
 %\usepackage{todonotes}
+\usepackage{placeins}
 
@@
 and tags that allow users to guarantee they are installing
-exactly the same code across different computing environments \cite{CoghStuf13}.
+exactly the same code across different computing environments~\cite{CoghStuf13}.
 While it is \textit{possible} to manually install the intended
@@
 
+Line 6 then uses the \texttt{davos.config} object to enable \texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next two packages, \texttt{NumPy}~\cite{HarrEtal20} and \texttt{pandas}.
+Because these packages rely heavily on custom C data types, loading them may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
+This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not implicitly imported when loading them).
+However, it's possible a future user could edit this notebook to add additional code before line 7, run the notebook's cells out of order, or even configure their IPython kernel to execute custom code on startup (e.g., as Google Colab notebooks do), any of which could potentially import a different, existing version of \texttt{NumPy} before \texttt{davos} smuggles the version specified in the onion comment.
+Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} would simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
+
+The dataset that the user wants to analyze was provided as a \texttt{pandas.Panel} object, serialized with Python's built-in \texttt{pickle} module.
+The \texttt{pickle} protocol is a popular choice for data persistence in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat: A ``pickled'' object's class definition must be importable from the same module as when it was saved in order to successfully ``unpickle'' (i.e., load and restore) it later.
+The \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the user's dataset can be loaded only if their notebook uses a \texttt{pandas} version released prior to that change.
+However, updates to the \texttt{pandas} library since then have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats (including in Jupyter notebooks).
+%Recent updates to the \texttt{pandas} library have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats (including in Jupyter notebooks).
+However, the \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the dataset they are working with can only be loaded by a version released prior to that change.
+\texttt{davos} makes it possible to do both within a single notebook, and with the \texttt{auto\_rerun} option, this process can be fully automated.
+The first time the notebook is run, lines 10--12 will install and load an older \texttt{pandas} version that defines the \texttt{Panel} class, read the dataset from its serialized format, convert it from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
+The \texttt{smuggle} statement on line 14 then installs a newer \texttt{pandas} version (v1.3.5) for use in the analyses themselves.
+Because an earlier version of \texttt{pandas} was previously loaded (by line 10), and because the package's C extension modules were updated between the old and new versions, switching to the new version will require restarting the notebook kernel.
+With the \texttt{auto\_rerun} option enabled, \texttt{davos} will handle this automatically, and once the kernel is restarted, will re-run the notebook up through the current cell (as well as re-queue any other cells that were queued before restarting).
+This second time the notebook is run (as well as any future times),
+
 % Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.

### 2022-11-03 paper/main.tex
wording tweaks to section 3

@@
 
-After importing \texttt{davos} (line 1), the user first smuggles two utilities for checking and reading local files in the code below.
+After importing \texttt{davos} (line 1), the user first smuggles two utilities for interacting with local files in the code below.
 The \texttt{smuggle} statement in line 3 loads the \texttt{is\_file()} function from the Python standard library's \texttt{os.path} module.
@@
 Because these packages rely heavily on custom C data types, loading them may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
-This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not implicitly imported when loading them).
+This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not implicitly imported while loading them).
 However, it's possible a future user could edit this notebook to add additional code before line 7, run the notebook's cells out of order, or even configure their IPython kernel to execute custom code on startup (e.g., as Google Colab notebooks do), any of which could potentially import a different, existing version of \texttt{NumPy} before \texttt{davos} smuggles the version specified in the onion comment.
-Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} would simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
+Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} helps to simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
 
@@
 \texttt{davos} makes it possible to do both within a single notebook, and with the \texttt{auto\_rerun} option, this process can be fully automated.
-The first time the notebook is run, lines 10--12 will install and load an older \texttt{pandas} version that defines the \texttt{Panel} class, read the dataset from its serialized format, convert it from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
-The \texttt{smuggle} statement on line 14 then installs a newer \texttt{pandas} version (v1.3.5) for use in the analyses themselves.
-Because an earlier version of \texttt{pandas} was previously loaded (by line 10), and because the package's C extension modules were updated between the old and new versions, switching to the new version will require restarting the notebook kernel.
-With the \texttt{auto\_rerun} option enabled, \texttt{davos} will handle this automatically, and once the kernel is restarted, will re-run the notebook up through the current cell (as well as re-queue any other cells that were queued before restarting).
-This second time the notebook is run (as well as any future times),
+The first time the notebook is run, lines 10--12 will install and load an older \texttt{pandas} version that defines the \texttt{Panel} class, use it to read the dataset from its serialized file format, convert the dataset from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
+The \texttt{smuggle} statement on line 14 then installs a newer version of \texttt{pandas} (v1.3.5) for use in the analyses themselves.
+Because an older \texttt{pandas} version was previously loaded (by line 10), and because the package's C extension modules were modified between the old and new versions, switching to the new version requires restarting the notebook kernel.
+With \texttt{auto\_rerun} enabled, \texttt{davos} takes care of this automatically and will restart the kernel, re-run the notebook up through the current cell, and also re-queue any other cells that the user had queued before the restart was triggered.
+This second time the code is run (as well as any future times), \texttt{smuggle} statements that have already been executed once before will run (virutlally) as quickly as import statements, since the specified package versions are already installed.
+Additionally,
 

### 2022-11-09 paper/main.tex
illustrative example walkthrough up to line 19, other minor text updates throughout

@@
 \newcommand{\comment}[1]{}
+%\let\oldtexttt\texttt
+%\renewcommand{\texttt}[1]{\mbox{\oldtexttt{#1}}}
 % =================================================
@@
 This second subpackage defines multiple, interchangeable versions of each helper function, organized into modules by the conditions that trigger their use.
-At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the correct implementations for the current notebook environment in a single, consistent location.
-An additional benefit of this design pattern is that it allows maintainers or users to easily extend \texttt{davos} to support new, updated, or custom notebook variants by creating a new \texttt{davos.implementations} module with any necessary tweaks to the existing helper functions.
-
+At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the proper implementations for the current notebook environment in a single, consistent location.
+An additional benefit of this design pattern is that it allows both maintainers and users to easily extend \texttt{davos} to support new, updated, or custom notebook variants by creating a new \texttt{davos.implementations} module that defines its own version of each helper function, modified as much or little as necessary.
 %The package also includes stub files (\texttt{.pyi} files) for each module for use with a static type checker, as well as a custom GitHub Actions-based CI test suite that uses
@@
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in \texttt{import} statement to load libraries, modules, and other objects into the current namespace.
+Functionally, importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
+The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in ``\texttt{import}'' to load libraries, modules, and other objects into the current namespace.
 However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
@@
 Occasionally, a package's distribution name (i.e., the name used when installing it) may differ from its top-level module name (i.e., the name used when importing it).
-In such cases, an onion comment can be used to ensure \texttt{davos} installs the proper distribution if the smuggled package can't be found locally:
+In such cases, an onion comment can be used to ensure that \texttt{davos} installs the proper distribution if the smuggled package can't be found locally:
 %Onion comments are useful in such cases for ensuring \texttt{davos} installs the proper distribution if the smuggled package isn't installed locally:
@@
 \texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this allows \texttt{davos} to take certain logical actions when particular arguments are passed.
-For example, the \texttt{-I}/\newline\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will all cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
+In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this enables \texttt{davos} to take certain logical actions when particular arguments are passed.
+For example, each of the \mbox{\texttt{-I}/\texttt{--ignore-installed}}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
 \begin{center}
@@
 \end{center}
-Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:config}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{dir} to be prepended to the module search path (\texttt{sys.path}), if necessary, so the package can be imported
+Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:config}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{davos} to prepend \texttt{dir} to the module search path (i.e., \texttt{sys.path}), if necessary, so the package can be imported.
 
@@
 
-Line 6 then uses the \texttt{davos.config} object to enable \texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next two packages, \texttt{NumPy}~\cite{HarrEtal20} and \texttt{pandas}.
-Because these packages rely heavily on custom C data types, loading them may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
+Line 6 then uses the \texttt{davos.config} object to enable \texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next two packages: \texttt{NumPy}~\cite{HarrEtal20} and \texttt{pandas}.
+Because these libraries rely heavily on custom C data types, loading the particular versions from the onion comments may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
 This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not implicitly imported while loading them).
@@
 The dataset that the user wants to analyze was provided as a \texttt{pandas.Panel} object, serialized with Python's built-in \texttt{pickle} module.
-The \texttt{pickle} protocol is a popular choice for data persistence in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat: A ``pickled'' object's class definition must be importable from the same module as when it was saved in order to successfully ``unpickle'' (i.e., load and restore) it later.
-The \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the user's dataset can be loaded only if their notebook uses a \texttt{pandas} version released prior to that change.
-However, updates to the \texttt{pandas} library since then have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats (including in Jupyter notebooks).
+The \texttt{pickle} protocol is a popular choice for persisting data in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat:
+In order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, its class must be defined in and importable from the same module as when it was saved.
+%A ``pickled'' object's class definition must be importable from the same module as when it was saved in order to successfully ``unpickle'' (i.e., load and restore) it later. 
+The \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the dataset can be loaded only if the user's notebook uses a \texttt{pandas} version released prior to that change.
+However, more recent updates to the \texttt{pandas} library since then have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats for data structures (including in Jupyter notebooks).
 %Recent updates to the \texttt{pandas} library have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats (including in Jupyter notebooks).
@@
 \texttt{davos} makes it possible to do both within a single notebook, and with the \texttt{auto\_rerun} option, this process can be fully automated.
-The first time the notebook is run, lines 10--12 will install and load an older \texttt{pandas} version that defines the \texttt{Panel} class, use it to read the dataset from its serialized file format, convert the dataset from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
-The \texttt{smuggle} statement on line 14 then installs a newer version of \texttt{pandas} (v1.3.5) for use in the analyses themselves.
-Because an older \texttt{pandas} version was previously loaded (by line 10), and because the package's C extension modules were modified between the old and new versions, switching to the new version requires restarting the notebook kernel.
-With \texttt{auto\_rerun} enabled, \texttt{davos} takes care of this automatically and will restart the kernel, re-run the notebook up through the current cell, and also re-queue any other cells that the user had queued before the restart was triggered.
-This second time the code is run (as well as any future times), \texttt{smuggle} statements that have already been executed once before will run (virutlally) as quickly as import statements, since the specified package versions are already installed.
-Additionally,
+The first time the notebook is run, lines 10--12 will install and load an older version of \texttt{pandas} that defines the \texttt{Panel} class, use it to read the dataset from its serialized file format, convert the dataset from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
+The \texttt{smuggle} statement on line 14 will then install a newer \texttt{pandas} version (v1.3.5) for use in the analyses themselves.
+Because an older \texttt{pandas} version was previously loaded (by line 10), and because the package's C extension modules were modified between the old and new versions, switching to the new version will require restarting the notebook kernel.
+When \texttt{davos} determines this, it will automatically restart the kernel, re-run the notebook up through the current cell, and also re-queue any subsequent cells that were queued before the restart was triggered.
+This second time the code is run (as well as any future times), lines 10--12 will be skipped since the CSV-formatted dataset has already been created, and the \texttt{smuggle} statements up through line 14 will execute (virtually) as fast as regular \texttt{import} statements since the required package versions have already been installed.
+%This second time the code is run (as well as any future times), the \texttt{smuggle} statements that have already been run once will execute (virtually) as fast as \texttt{import} statements since the required package versions are now installed, and lines 10--12 will be skipped altogether since the CSV-formatted dataset has already been created.
+It's worth noting that one could instead save the converted \texttt{DataFrame} as a pickle file
+
+Line 16 then uses the \texttt{davos.configure()} function to disable the \texttt{auto\_rerun} option and simultaneously enable two other options: \texttt{suppress\_stdout} and \texttt{noninteractive}.
+With these options enabled, lines 17--18 \texttt{smuggle} \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful end-to-end platform for building and working with machine learning models, and \texttt{UMAP}~\cite{McInEtal18b}, a library that implements a family of related manifold learning techniques.
+The onion comment in line 18 also specifies that \texttt{UMAP} should be installed with the optional requirements needed for its ``plot'' and ``parametric\_umap'' features.
+Together, these two packages depend on 36 other unique packages, most of which have dependencies of their own.
+And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run.
+Enabling the \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+Additionally, installing more than three dozen packages could result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
+Enabling \texttt{suppress\_stdout} hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
+Importantly, if either line fails for any reason, both the stdout and stderr streams will be shown alongside the regular Python traceback.
+
+%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run and result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
+Enabling the \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+Enabling the \texttt{suppress\_stdout} option hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
+Importantly, if either line fails for any reason, both the stdout and stderr streams will be shown alongside the regular Python traceback.
+
+%a large amount of standard output text generated by the installer program.
+The \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+
+%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run.
+The \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+Additionally, in the process
+
+%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run, and generate a large amount of standard output text while doing so.
+The \texttt{suppress\_stdout} option hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
+Importantly, if either line fails for any reason, both the stdout and stderr streams from the installer program will be shown alongside the regular Python traceback.
+
+% The \texttt{suppress\_stdout} option hides the output from the installer program for these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
+Importantly, if either line fails for any reason, both its stdout and stderr streams will be shown along with the
+
+% have 36 unique dependencies, most of which require other packages, in turn.
+
+% and \texttt{UMAP}~\cite{McInEtal18b}.
+\texttt{TensorFlow} provides an end-to-end platform for building and working with machine learning models, and \texttt{UMAP} is a library for non-linear dimensionality reduction.
+the onion comment in line 18 also specifies that
+
+%These options are enabled while smuggling the following two libraries \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful, heavyweight machine learning
+
+%The next two packages smuggled, \texttt{TensorFlow}~\cite{AbadEtal15} and \texttt{UMAP}~\cite{McInEtal18b} (lines 17--18), are machine learning libraries that depend on a relatively large number of heavyweight packages.
+The onion comment on line 18 also specifies that \texttt{UMAP} should be installed with
+
+% The following two lines then \texttt{smuggle} \texttt{TensorFlow}~\cite{AbadEtal15}, a large library
+
+Next, the user installs a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets.
 

### 2022-11-14 paper/main.tex
illustrative example walkthrough up to line 24

@@
 The \texttt{smuggle} statement in line 3 loads the \texttt{is\_file()} function from the Python standard library's \texttt{os.path} module.
-Standard library modules are included with all Python distributions, so this line is functionally equivalent to an \texttt{import} statement and no onion comment is needed.
+Standard library modules are included with all Python distributions, so this line is functionally equivalent to an \texttt{import} statement and does not need or benefit from an onion comment.
 Line 4 loads the \texttt{joblib} library~\cite{Varo10}, installing it first, if necessary.
@@
 Because these libraries rely heavily on custom C data types, loading the particular versions from the onion comments may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
-This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not implicitly imported while loading them).
+This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not imported and cached while loading them).
 However, it's possible a future user could edit this notebook to add additional code before line 7, run the notebook's cells out of order, or even configure their IPython kernel to execute custom code on startup (e.g., as Google Colab notebooks do), any of which could potentially import a different, existing version of \texttt{NumPy} before \texttt{davos} smuggles the version specified in the onion comment.
-Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} helps to simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
+Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} will help to simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
 
@@
 When \texttt{davos} determines this, it will automatically restart the kernel, re-run the notebook up through the current cell, and also re-queue any subsequent cells that were queued before the restart was triggered.
-This second time the code is run (as well as any future times), lines 10--12 will be skipped since the CSV-formatted dataset has already been created, and the \texttt{smuggle} statements up through line 14 will execute (virtually) as fast as regular \texttt{import} statements since the required package versions have already been installed.
+This second time the code is run (as well as in any future runs), lines 10--12 will be skipped since the CSV-formatted dataset has already been created, and the \texttt{smuggle} statements up through line 14 will execute (virtually) as fast as regular \texttt{import} statements since the required package versions have already been installed.
 %This second time the code is run (as well as any future times), the \texttt{smuggle} statements that have already been run once will execute (virtually) as fast as \texttt{import} statements since the required package versions are now installed, and lines 10--12 will be skipped altogether since the CSV-formatted dataset has already been created.
@@
 And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run.
-Enabling the \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+Enabling the \texttt{noninteractive} option ensures the installation process won't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
 Additionally, installing more than three dozen packages could result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
@@
 Importantly, if either line fails for any reason, both the stdout and stderr streams will be shown alongside the regular Python traceback.
-
 %And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run and result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
@@
 
-%a large amount of standard output text generated by the installer program.
-The \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
+After re-enabling these two options (line 19), the user next smuggles specific versions of three plotting libraries: \texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and \texttt{Quail}~\cite{HeusEtal17} (lines 21--23).
+Because the first two are requirements of \texttt{UMAP}'s optional ``plot'' feature, they will have already been installed by line 18, though possibly as different versions than those specified in the onion comments on lines 21 and 22.
+If the installed and specified versions are the same, these \texttt{smuggle} statements will function like regular \texttt{import} statements to load the libraries into the notebook namespace.
+If they differ, \texttt{davos} will download the requested versions in place of the installed versions before doing so.
+It's also worth noting that while loading \texttt{UMAP} in line 18 will not result in either \texttt{Matplotlib} or \texttt{seaborn} being imported internally due to the specific layout of the \texttt{UMAP} package, if it had, \texttt{davos} would also gracefully replace the cached versions of the two packages so that the smuggled versions are loaded properly.
+And (as with all other \texttt{smuggle} statements in Figure~\ref{fig:illustrative-example}), if for any reason the specified package versions are incompatible with any other packages (e.g., \texttt{UMAP}), the installer program would display a warning to this effect in the notebook.
 
-%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run.
-The \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
-Additionally, in the process
-
-%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run, and generate a large amount of standard output text while doing so.
-The \texttt{suppress\_stdout} option hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
-Importantly, if either line fails for any reason, both the stdout and stderr streams from the installer program will be shown alongside the regular Python traceback.
-
-% The \texttt{suppress\_stdout} option hides the output from the installer program for these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
-Importantly, if either line fails for any reason, both its stdout and stderr streams will be shown along with the
-
-% have 36 unique dependencies, most of which require other packages, in turn.
-
-% and \texttt{UMAP}~\cite{McInEtal18b}.
-\texttt{TensorFlow} provides an end-to-end platform for building and working with machine learning models, and \texttt{UMAP} is a library for non-linear dimensionality reduction.
-the onion comment in line 18 also specifies that
-
-%These options are enabled while smuggling the following two libraries \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful, heavyweight machine learning
-
-%The next two packages smuggled, \texttt{TensorFlow}~\cite{AbadEtal15} and \texttt{UMAP}~\cite{McInEtal18b} (lines 17--18), are machine learning libraries that depend on a relatively large number of heavyweight packages.
-The onion comment on line 18 also specifies that \texttt{UMAP} should be installed with
-
-% The following two lines then \texttt{smuggle} \texttt{TensorFlow}~\cite{AbadEtal15}, a large library
-
-Next, the user installs a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets.
+The third plotting library smuggled, \texttt{Quail}, is also pinned to a precise version with an onion comment, though in a slightly different manner than other packages in Figure~\ref{fig:illustrative-example}.
+Line 23 installs and loads \texttt{Quail} from the user's fork (``myfork'') of the package's GitHub repository, at a specific point in its revision history (i.e., the commit whose short hash is ``6c847a4'').
+This can serve as a useful way to access a version of a package the user has customized, patched, or somehow modified for this specific use case, while still allowing them to further modify their fork of the package in the future without affecting the version used in these analyses.
 

### 2022-11-15 paper/main.tex
WIP illustrative example section, saving to branch off and implement davos dir

@@
 
+Next, the user smuggles a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets.
+The \texttt{ipywidgets}~\cite{GrouEtal15} package provides an API for creating these widgets with Python code, and the \texttt{widgetsnbextension} package provides the machinery for the notebook frontend to display them.
+Thus, \texttt{ipywidgets} must be installed in the same environment as the IPython kernel, and \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server.
+In the simplest case, these two environments are the same; however, a common approach to using Jupyter notebooks with multiple different Python environments (e.g., for different tasks or projects) is to run the notebook server from a ``base environment,'' with additional environments each providing their own separate, interchangeable IPython kernels.
+(While possible to detect programmatically, Figure~\ref{fig:illustrative-example} assumes this setup to simplify the example code.) To handle this multi-environment installation, line 25 temporarily changes the \texttt{pip} executable used to install smuggled packages to that of the notebook server's environment before smuggling \texttt{widgetsnbextension} (line 26).
+Since there is no need to actually load this package for later use in the analysis code, it is aliased as a single underscore---by convention, a ``throwaway'' variable in Python.
+In line 27, the user changes the \texttt{pip} executable back to that of the notebook kernel environment (its original value) before installing \texttt{ipywidgets} and subsequent packages.
+With these two packages installed, line 30 smuggles \texttt{tqdm}~\cite{CaspEtal22}, which provides convenient progress bars for long-running code.
+In Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported to enable prettier progress bars displayed via \texttt{ipywidgets}, if that package is installed and importable.
+Therefore, in this case, it was important to \texttt{smuggle}
+
+% In Jupyter notebooks, \texttt{tqdm} will attempt to display these progress bars using \texttt{ipywidgets} if the package is installed and available.
+
+%managing multiple, interchangeable IPython kernels is to run the notebook server from a ``base environment,'' with additional Python environments each providing its own separate kernel (e.g.,
+
+Finally, the user loads in the ... but in order to successfully ... they must deal with a similar problem to ...
+
 % Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.

### 2022-11-16 davos/core/config.py
handle importing packages installed in alternate environment when pip-executable is set

@@ -215,6 +215,7 @@ class DavosConfig(metaclass=SingletonConfig):
                     self._pip_executable = f'{sys.executable} -m pip'
             else:
                 self._pip_executable = pip_exe
+        self._pip_executable_orig = self._pip_executable
 
     def __repr__(self):
         cls_name = self.__class__.__name__

### 2022-11-16 paper/main.tex
finished illustrative example section

@@
 In the simplest case, these two environments are the same; however, a common approach to using Jupyter notebooks with multiple different Python environments (e.g., for different tasks or projects) is to run the notebook server from a ``base environment,'' with additional environments each providing their own separate, interchangeable IPython kernels.
-(While possible to detect programmatically, Figure~\ref{fig:illustrative-example} assumes this setup to simplify the example code.) To handle this multi-environment installation, line 25 temporarily changes the \texttt{pip} executable used to install smuggled packages to that of the notebook server's environment before smuggling \texttt{widgetsnbextension} (line 26).
+(While possible to detect programmatically, Figure~\ref{fig:illustrative-example} assumes this setup to simplify the example code.) To handle this multi-environment installation, line 25 temporarily sets the \texttt{pip} executable used to install smuggled packages to that of the notebook server's environment before smuggling \texttt{widgetsnbextension} (line 26).
 Since there is no need to actually load this package for later use in the analysis code, it is aliased as a single underscore---by convention, a ``throwaway'' variable in Python.
@@
 In Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported to enable prettier progress bars displayed via \texttt{ipywidgets}, if that package is installed and importable.
-Therefore, in this case, it was important to \texttt{smuggle}
+Therefore, to take advantage of this feature, it was important to \texttt{smuggle} \texttt{tqdm} after ensuring the \texttt{ipywidgets} package was available.
 
-% In Jupyter notebooks, \texttt{tqdm} will attempt to display these progress bars using \texttt{ipywidgets} if the package is installed and available.
-
-%managing multiple, interchangeable IPython kernels is to run the notebook server from a ``base environment,'' with additional Python environments each providing its own separate kernel (e.g.,
-
-Finally, the user loads in the ... but in order to successfully ... they must deal with a similar problem to ...
+Finally, the user loads in the re-formatted dataset (line 32) and pre-trained model (line 34) they'll use in their analyses.
+But in accessing the latter, the user encounters an issue similar to the one they initially faced with the dataset.
+This hypothetical semantic model was provided as a \texttt{scikit-learn} ``\texttt{Pipeline}'' object that allows the user to pass text data through two pre-trained transformers, in series: a \texttt{CountVectorizer} instance and a \texttt{LatentDirichletAllocation} instance (i.e., a topic model \cite{BleiEtal03}).
+The model was saved by its original creator using the \texttt{joblib} library, as \texttt{scikit-learn}'s documentation recommends, with the caveat that because \texttt{joblib} uses the \texttt{pickle} protocol internally, the ability to save and load pre-trained models is not guaranteed across versions due to \texttt{pickle}'s requirement that referenced classes be importable from the same location when saved and loaded.
+This issue affects the user's model by way of the \texttt{LatentDirichletAllocation} class---when the \texttt{Pipeline} object was created (again, in June, 2019, using \texttt{scikit-learn} v0.21.3), the class's definition lived in the \texttt{sklearn.decomposition.online\_lda} module.
+However, in version 0.22.0 (released November, 2019), that module was renamed to ``\texttt{\_online\_lda},'' and in v0.22.1 (January, 2020) it was again renamed to ``\texttt{\_lda}'' (which has remained its name since then).
+Thus, in order to successfully load the model that includes the pre-trained \texttt{LatentDirichletAllocation} instance, in line 33, the user first smuggles a version of \texttt{scikit-learn} prior to v0.22.0 (i.e., before the first time the module's name was changed).
+Once the model is loaded and reconstructed in memory  from a compatible package version (line 34), the user then upgrades to a newer version of \texttt{scikit-learn} for use elsewhere in their analyses.
+When
+line 35 is run, \texttt{davos} will replace the existing \texttt{scikit-learn} version with v1.1.3 in both the user's local package environment and in memory without interruption, such that ``\texttt{sklearn}'' will reference the new version in any code below.
+However, this will not affect the already compiled code object stored in the ``\texttt{transformer}'' variable, meaning that the pre-trained model will be usable simultaneously.
+% It's possible that in some cases, a version mismatch like this could introduce certain compatibility issues, depending on the specific package and the differences between the two versions being used.
+For example, a function from a newer package version could fail to handle an object from an older version passed to it as an argument, if it expects the object to have certain attributes that had not yet been added in the older version.
+Fortunately, with \texttt{davos}, this scenario is relatively easy to handle, as \texttt{smuggle} statements can be used to temporarily switch between package versions as needed (e.g., for a single line, in order to call an older version of the function).
+And because the installer program caches previously installed package versions, switching between package versions in this way can be done fairly quickly.
 

### 2022-11-16 paper/main.tex

@@
 % ----------------------------------------------- ILLUSTRATIVE EXAMPLES ------------------------------------------------
-\section{Illustrative Examples}
+\section{Illustrative Example}\label{sec:illustrative-example}
 % Provide at least one illustrative example to demonstrate the major functions.
@@
 that take advantage of multiple versions of a package within a single interpreter
-session. This could be useful in cases where specific features are added or
+session (e.g., see Section~\ref{sec:illustrative-example}). This could be useful in cases where specific features are added or
 removed from a package across different versions, or in comparing the
@@
 
-A second advanced use case is in providing a proof-of-concept of how
-one can add new ``keyword-like'' operators to the Python language by
-leveraging notebooks' error-handling mechanisms. This could lead to
-exciting new tools that, like \texttt{davos}, extend the Python
-language in useful ways within notebook-based environments. We note that
-our approach to adding the \texttt{smuggle} keyword to Python when
-\texttt{davos} is imported into a notebook-based environment also has
-the potential to be exploited for more nefarious purposes. For
-example, a malicious user could use a similar approach (e.g., in a
-different library) to substantially change a notebook's functionality
-by adding new \textit{unexpected} keyword-like objects (e.g., based
-around common typos). This could lead to difficult-to-predict changes
-in a notebook's behavior once the malicious library was imported.
-This highlights an important reason why security-conscious users would
-be well-served to only make use of libraries from trusted sources, or
-whose code is publicly available for review.
+A second more subtle impact of our work is in providing a proof-of-concept of how the ability to add new ``keyword-like'' operators to the Python language could be specifically useful to researchers.
+With \texttt{davos}, we accomplish this by leveraging IPython notebooks' internal code parsing and execution machinery.
+We note that, while other popular packages similarly use these mechanisms to providing notebook-specific functionality (e.g., \cite{Hunt07,HeusEtal18a}), this approach also has the potential to be exploited for more nefarious purposes.
+For example, a malicious user could design a Python library that, when imported, substantially changes the notebook's functionality by adding new \textit{unexpected} keyword-like objects (e.g., based around common typos).
+We also note that this implementation approach means \texttt{davos}'s functionality is currently restricted to IPython notebook environments, as would be that of any potential similar tools that enable user-defined keywords.
+However, there has been early-stage discussion of providing this sort of syntactic customizability as a core feature of the Python language, including a draft proposal \cite{Shan20}.
+In addition to enabling \texttt{davos} to be extended for use outside of notebooks, this could lead to exciting new tools that, like \texttt{davos}, extend the Python language in useful and more secure ways.
 

### 2022-11-16 paper/main.tex

@@
 Next, the user smuggles a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets.
-The \texttt{ipywidgets}~\cite{GrouEtal15} package provides an API for creating these widgets with Python code, and the \texttt{widgetsnbextension} package provides the machinery for the notebook frontend to display them.
+The \texttt{ipywidgets}~\cite{FredEtal15} package provides an API for creating these widgets with Python code, and the \texttt{widgetsnbextension} package provides the machinery for the notebook frontend to display them.
 Thus, \texttt{ipywidgets} must be installed in the same environment as the IPython kernel, and \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server.
@@
 In line 27, the user changes the \texttt{pip} executable back to that of the notebook kernel environment (its original value) before installing \texttt{ipywidgets} and subsequent packages.
-With these two packages installed, line 30 smuggles \texttt{tqdm}~\cite{CaspEtal22}, which provides convenient progress bars for long-running code.
+With these two packages installed, line 30 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which provides convenient progress bars for long-running code.
 In Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported to enable prettier progress bars displayed via \texttt{ipywidgets}, if that package is installed and importable.

### 2022-11-17 paper/main.tex
added CDL bibliography as a submodule

@@
 
-Computational researchers and other programmers have developed a broad
+Computational researchers and other programmers have de\-vel\-oped a broad
 set of approaches and tools to facilitate code sharing and
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{cdl}
+\bibliography{CDL-bibliography/cdl}
 

### 2022-11-17 paper/main.tex
JRM edits (next pass)

@@
-%%
-%% Copyright 2007, 2008, 2009 Elsevier Ltd
-%%
-%% This file is part of the 'Elsarticle Bundle'.
-%% ---------------------------------------------
-%%
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%%
-%% The list of all files belonging to the 'Elsarticle Bundle' is
-%% given in the file `manifest.txt'.
-%%
-
-%% Template article for Elsevier's document class `elsarticle'
-%% with numbered style bibliographic references
-%% SP 2008/03/01
-
 \documentclass[preprint,12pt,a4paper]{elsarticle}
-
-%% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
-
-%% For including figures, graphicx.sty has been loaded in
-%% elsarticle.cls. If you prefer to use the old commands
-%% please give \usepackage{epsfig}
-
-%% The amssymb package provides various useful mathematical symbols
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
 \usepackage{lineno}
-
 \usepackage{float}
 \restylefloat{table}
-
-% ======== additional package not in SoftwareX template ========
 \usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
@@
 \usepackage[htt]{hyphenat}
-%\usepackage{listings}
-%\usepackage{xcolor}
-%\usepackage{todonotes}
 \usepackage{placeins}
-
-% \let\oldtodo\todo
-% \renewcommand{\todo}[1]{\oldtodo[tickmarkheight=0.5em]{#1}}
-
 \newcommand{\comment}[1]{}
-%\let\oldtexttt\texttt
-%\renewcommand{\texttt}[1]{\mbox{\oldtexttt{#1}}}
-% =================================================
 
@@
 
-% ------------------------------------------------------ ABSTRACT ------------------------------------------------------
-
 \begin{abstract}
-% 100-word limit (though many published articles don't seem to conform
-% to this?)
-
   Reproducibility is a core requirement of modern scientific research.
@@
   \texttt{davos} library.  When used in combination with a
-  notebook-based Python project, \texttt{davos} provides a
-  mechanism for specifying (and automatically installing) the correct
-  versions of the project's dependencies.  The \texttt{davos}
-  library further ensures that those packages and specific versions are used every time the
-  notebook's code is executed.  This enables researchers to share a complete
-  reproducible copy of their code within a single Jupyter notebook file.
-
+  notebook-based Python project, \texttt{davos} provides a mechanism
+  for specifying (and automatically installing) the correct versions
+  of the project's dependencies.  The \texttt{davos} library further
+  ensures that those packages and specific versions are used every
+  time the notebook's code is executed.  This enables researchers to
+  share a complete reproducible copy of their code within a single
+  Jupyter notebook file.
 \end{abstract}
@@
 \begin{keyword}
-Reproducibility \sep Open science \sep Python \sep Jupyter Notebook \sep Google Colaboratory \sep Package management
+  Reproducibility \sep Open science \sep Python \sep Jupyter Notebook
+  \sep Google Colaboratory \sep Package management
 \end{keyword}
@@
 
-% ------------------------------------------------------ METADATA ------------------------------------------------------
-\section*{Required Metadata}
+\section*{Metadata}
 
@@
 
-% --------------------------------------------- MOTIVATION & SIGNIFICANCE ----------------------------------------------
 \section{Motivation and significance}
@@
 Because executing identical code does not guarantee identical
-outcomes, code sharing alone is often insufficient for
-enabling researchers to reproduce each other's work, or to collaborate on
+outcomes, code sharing alone is often insufficient for enabling
+researchers to reproduce each other's work, or to collaborate on
 projects involving data collection or analysis.
 
-Within the Python~\cite{vanR95} community, external
-packages that are published in the most popular
-repositories~\cite{Pyth03, cond15} are associated with version numbers
-and tags that allow users to guarantee they are installing
-exactly the same code across different computing environments~\cite{CoghStuf13}.
-While it is \textit{possible} to manually install the intended
-version of every dependency of a Python script or package, manually
-tracking down those dependencies can impose a substantial burden on
-the user and create room for mistakes and inconsistencies. Further, when dependency versions
-are left unspecified, replicating the original computing environment
-becomes difficult or impossible.
+Within the Python~\cite{vanR95} community, external packages that are
+published in the most popular repositories~\cite{Pyth03, cond15} are
+associated with version numbers and tags that allow users to guarantee
+they are installing exactly the same code across different computing
+environments~\cite{CoghStuf13}.  While it is \textit{possible} to
+manually install the intended version of every dependency of a Python
+script or package, manually tracking down those dependencies can
+impose a substantial burden on the user and create room for mistakes
+and inconsistencies. Further, when dependency versions are left
+unspecified, replicating the original computing environment becomes
+difficult or impossible.
 
@@
   allow users to install an isolated copy of Python and all required
-  dependencies. This typically entails distributing a configuration file
-  (e.g., a \texttt{pyproject.toml}~\cite{CannEtal16} or \texttt{environment.yml})
-  that specifies all project dependencies (including version numbers of
-  external libraries) alongside the primary code base. Users can then install
-  a third-praty tool~\cite[e.g.,][]{Anac12, Eust19} to read the file and build the environment.
-  \textbf{Containers} provide a means of defining an isolated
-  environment that includes a complete operating system (independent
-  of the user's operating system), in addition to (optionally)
-  specifying a virtual environment or other configurations needed to
-  provide the necessary computing environment.  Containers are
-  typically defined using specification files (e.g., a plain-text
-  \texttt{Dockerfile}) that instruct the virtualization engine
-  regarding how to build the containerized environment.  \textbf{Virtual
-    machines} provide a complete hardware-level simulation of the
-  computing environment.  In addition to simulating specific hardware,
-  virtual machines (typically specified using binary images files)
-  must also define operating system-level properties of the computing
-  environment.  Systems to the left of the blue vertical line entail
-  sharing individual files, with no additional installation or
-  configuration needed to run the target code.  Systems to the right
-  of the red vertical line support precise control over dependencies
-  and versioning.  Notebooks enhanced using the \texttt{davos} library
-  are easily shareable and require minimal setup costs, while also
-  facilitating high reproducibility by enabling precise control over
-  project dependencies.}
+  dependencies. This typically entails distributing a configuration
+  file (e.g., a \texttt{pyproject.toml}~\cite{CannEtal16} or
+  \texttt{environment.yml} file) that specifies all project
+  dependencies (including version numbers of external libraries)
+  alongside the primary code base. Users can then install a
+  third-party tool~\cite[e.g.,][]{Anac12, Eust19} to read the file and
+  build the environment.  \textbf{Containers} provide a means of
+  defining an isolated environment that includes a complete operating
+  system (independent of the user's operating system), in addition to
+  (optionally) specifying a virtual environment or other
+  configurations needed to provide the necessary computing
+  environment.  Containers are typically defined using specification
+  files (e.g., a plain-text \texttt{Dockerfile}) that instruct the
+  virtualization engine regarding how to build the containerized
+  environment.  \textbf{Virtual machines} provide a complete
+  hardware-level simulation of the computing environment.  In addition
+  to simulating specific hardware, virtual machines (typically
+  specified using binary image files) must also define operating
+  system-level properties of the computing environment.  Systems to
+  the left of the blue vertical line entail sharing individual files,
+  with no additional installation or configuration needed to run the
+  target code.  Systems to the right of the red vertical line support
+  precise control over dependencies and versioning.  Notebooks
+  enhanced using the \texttt{davos} library are easily shareable and
+  require minimal setup costs, while also facilitating high
+  reproducibility by enabling precise control over project
+  dependencies.}
 \label{fig:code-sharing}
@@
 
-Computational researchers and other programmers have de\-vel\-oped a broad
-set of approaches and tools to facilitate code sharing and
-reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one
-extreme, simply distributing a set of Python scripts (\texttt{.py} files) may
+Computational researchers and other programmers have de\-vel\-oped a
+broad set of approaches and tools to facilitate code sharing and
+reproducible outcomes (Fig.~\ref{fig:code-sharing}). At one extreme,
+simply distributing a set of Python scripts (\texttt{.py} files) may
 enable others to use or gain insights into the relevant work. Because
@@
 some projects, this may be sufficient. Another popular approach
-entails creating Jupyter
-notebooks~\cite{KluyEtal16} that comprise a mix of text, executable
-code, and embedded media. Notebooks may call or import external
-scripts or libraries---even intersperse snippets of other programming
-or markup lang\-uages---in order to provide a more compact and readable
-experience for users. Both of these systems (Python scripts and
-notebooks) provide a convenient means of sharing code, with the
-caveat that they do not specify the computing environment in which the
-code is executed. Therefore the functionality of code shared using
-these systems cannot be guaranteed across different users or setups.
+entails creating Jupyter notebooks~\cite{KluyEtal16} that comprise a
+mix of text, executable code, and embedded media. Notebooks may call
+or import external scripts or libraries---or even intersperse snippets
+of other programming or markup lang\-uages---in order to provide a
+more compact and readable experience for users. Both of these systems
+(Python scripts and notebooks) provide a convenient means of sharing
+code, with the caveat that they do not specify the computing
+environment in which the code is executed. Therefore the functionality
+of code shared using these systems cannot be guaranteed across
+different users or setups.
 
-At another extreme, virtual machines~\cite{Gold74, AltiEtal05,
- Rose99} provide a hardware-level simulation of the desired system.
-Virtual machines are typically isolated such
-that installing or running software on a virtual machine does not
-impact the user's primary operating system or computing environment.
+At another extreme, virtual machines~\cite{Gold74, AltiEtal05, Rose99}
+provide a hardware-level simulation of the desired system.  Virtual
+machines are typically isolated, such that installing or running
+software on a virtual machine does not impact the user's primary
+operating system or computing environment.
 Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
@@
 system level, and Python environment level, respectively) that the
-relevant code will run similarly for different users. However, each
-of these systems also relies on additional software that can be
-complex or resource-intensive to install and use, creating potential
-barriers to both contributing to and taking advantage of open science
+relevant code will run similarly for different users. However, each of
+these systems also relies on additional software that can be complex
+or resource-intensive to install and use, creating potential barriers
+to both contributing to and taking advantage of open science
 resources.
@@
 functionality to the default notebook experience. Like standard
-Jupyter notebooks, \texttt{davos}-enhanced notebooks allow
-researchers to include text, executable code, and media within a
-single file. No further setup or installation is required, beyond
-what is needed to run standard Jupyter notebooks. And like virtual
-environments, \texttt{davos} provides a convenient mechanism for fully
-specifying (and installing, as needed) a complete set of Python
-dependencies, including package versions.
+Jupyter notebooks, \texttt{davos}-enhanced notebooks allow researchers
+to include text, executable code, and media within a single file. No
+further setup or installation is required, beyond what is needed to
+run standard Jupyter notebooks. And like virtual environments,
+\texttt{davos} provides a convenient mechanism for fully specifying
+(and installing, as needed) a complete set of Python dependencies,
+including package versions.
 
-% ------------------------------------------------ SOFTWARE DESCRIPTION ------------------------------------------------
 \section{Software description}
-% Describe the software in as much as is necessary to establish a vocabulary needed to explain its impact.
-The \texttt{davos} package is named after Davos Seaworth, a smuggler often referred to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by George R. R. Martin.
+
+The \texttt{davos} package is named after Davos Seaworth, a smuggler
+referred to as ``the Onion Knight" from the series \textit{A Song of
+  Ice and Fire} by George R. R. Martin~\citep{Mart12}.  The
+\texttt{smuggle} keyword-like operator implemented in \texttt{davos}
+is a play on Python's \texttt{import} keyword: whereas importing can
+bring a package into the Python workspace within the existing rules
+and frameworks provided by the Python language, ``smuggling'' provides
+an alternative that expands the scope and reach of ``importing.''
+Like the character Davos Seaworth (who became famous for smuggling
+onions through a blockade on his homeland), we use ``onion'' comments
+to precisely control how packages are smuggled into the Python
+workspace.
 
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} }
+\caption{\small \textbf{Package structure.} The \texttt{davos} library
+  comprises two interdependent subpackages.  The \texttt{davos.core}
+  subpackage includes modules for parsing \texttt{smuggle} statements
+  and onion comments, installing and validating packages, and
+  configuring \texttt{davos}'s behavior.  The
+  \texttt{davos.implementations} subpackage includes
+  environment-specific modifications and features that are needed to
+  support the core functionality across different notebook-based
+  environments.  Individual \texttt{.py} files are represented by lime
+  rounded rectangles, and arrows denote dependencies (each arrow
+  points to a file that import objects defined or specified at the
+  arrow's source).}
 \label{fig:package-structure}
@@
 \subsection{Software architecture}
-% Give a short overview of the overall software architecture; provide a pictorial component overview or similar (if possible). If necessary provide implementation details.
-The \texttt{davos} package consists of two interdependent subpackages (see Fig.~\ref{fig:package-structure}).
-The first, \texttt{davos.core}, comprises a set of modules that implement\comment{provide?} the bulk of the package's core functionality, including pipelines for installing and validating packages, custom parsers for the \texttt{smuggle} statement (see Section~\ref{subsec:smuggle}) and onion comment (see Section~\ref{subsec:onion}), and a runtime interface for configuring \texttt{davos}'s behavior (see Section~\ref{subsec:config}).
-However, certain critical\comment{other important} aspects of this functionality require (often substantially) different implementations depending on properties of the notebook environment in which \texttt{davos} is used (e.g., whether the frontend is provided by Jupyter or Google Colaboratory, or which version of IPython~\cite{PereGran07} is used by the notebook kernel).
-To deal with this, environment-dependent parts of core features and behaviors are isolated and abstracted to ``helper functions'' in the \texttt{davos.implementations} subpackage.
-This second subpackage defines multiple, interchangeable versions of each helper function, organized into modules by the conditions that trigger their use.
-At runtime, \texttt{davos} detects various features in the notebook environment and selectively imports a single version of each helper function into the top-level \texttt{davos.implementations} namespace, allowing \texttt{davos.core} modules to access the proper implementations for the current notebook environment in a single, consistent location.
-An additional benefit of this design pattern is that it allows both maintainers and users to easily extend \texttt{davos} to support new, updated, or custom notebook variants by creating a new \texttt{davos.implementations} module that defines its own version of each helper function, modified as much or little as necessary.
-%The package also includes stub files (\texttt{.pyi} files) for each module for use with a static type checker, as well as a custom GitHub Actions-based CI test suite that uses
 
-\comment{
-- js_functions.py?
-- how parser is registered and deregistered?
-- stub files?
-- test suite?
-- packaged with new PEP \_\_\_ standard (pyproject.toml + setup.cfg; no setup.py)?
-}
+The \texttt{davos} package consists of two interdependent subpackages
+(see Fig.~\ref{fig:package-structure}). The first,
+\texttt{davos.core}, comprises a set of modules that
+implement\comment{provide?} the bulk of the package's core
+functionality, including pipelines for installing and validating
+packages, custom parsers for the \texttt{smuggle} statement (see
+Section~\ref{subsec:smuggle}) and onion comment (see
+Section~\ref{subsec:onion}), and a runtime interface for configuring
+\texttt{davos}'s behavior (see Section~\ref{subsec:config}). However,
+certain critical\comment{other important} aspects of this
+functionality require (often substantially) different implementations
+depending on properties of the notebook environment in which
+\texttt{davos} is used (e.g., whether the frontend is provided by
+Jupyter or Google Colaboratory, or which version of
+IPython~\cite{PereGran07} is used by the notebook kernel). To deal
+with this, environment-dependent parts of core features and behaviors
+are isolated and abstracted to ``helper functions'' in the
+\texttt{davos.implementations} subpackage. This second subpackage
+defines multiple, interchangeable versions of each helper function,
+organized into modules by the conditions that trigger their use. At
+runtime, \texttt{davos} detects various features in the notebook
+environment and selectively imports a single version of each helper
+function into the top-level \texttt{davos.implementations} namespace,
+allowing \texttt{davos.core} modules to access the proper
+implementations for the current notebook environment in a single,
+consistent location. An additional benefit of this design is that it
+allows maintainers, developers, and users to extend \texttt{davos} to
+support new, updated, or custom notebook variants by creating new
+\texttt{davos.implementations} modules that define their own versions
+of each helper function, modified from existing implementations as
+needed.
 
 \subsection{Software functionalities}
-% Present the major functionalities of the software.
+
 \subsubsection{The \texttt{smuggle} statement}\label{subsec:smuggle}
-Functionally, importing \texttt{davos} in an IPython notebook enables an additional Python keyword: ``\texttt{smuggle}'' (see Section~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} statement can be used as a drop-in replacement for Python's built-in ``\texttt{import}'' to load libraries, modules, and other objects into the current namespace.
-However, whereas \texttt{import} will fail if the requested package is not installed locally, \texttt{smuggle} statements can handle missing packages on the fly.
-If a smuggled package does not exist in the local environment, \texttt{davos} will install it automatically, expose its contents to Python's \texttt{import} machinery, and load it into the namespace for immediate use.
+
+Functionally, importing \texttt{davos} in an IPython notebook enables
+an additional Python keyword: ``\texttt{smuggle}'' (see
+Section~\ref{subsec:implementation} for details on how this works).
+The \texttt{smuggle} keyword-like object can be used as a drop-in
+replacement for Python's built-in \texttt{import} keyword to load
+libraries, modules, and other objects into the current namespace.
+However, whereas \texttt{import} will fail if the requested package is
+not installed locally, \texttt{smuggle} statements can handle missing
+packages on the fly.  If a smuggled package does not exist in the
+local environment, \texttt{davos} will install it automatically,
+expose its contents to Python's \texttt{import} machinery, and load it
+into the namespace for immediate use.
 
 \subsubsection{The onion comment}\label{subsec:onion}
-For greater control over the behavior of \texttt{smuggle} statements, \texttt{davos} defines an additional construct called the ``onion comment.'' An onion comment is a special type of inline comment that may be placed on a line containing a \texttt{smuggle} statement to customize how \texttt{davos} searches for the smuggled package locally and, if necessary, downloads and installs it.
-Onion comments follow a simple format based on the ``type comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{davos} intuitive and familiar.
-To construct an onion comment, users provide the name of the installer program (e.g., \texttt{pip}) and the same arguments one would use to manually install the package as desired via the command line:
+
+For greater control over the behavior of \texttt{smuggle} statements,
+\texttt{davos} defines an additional construct called the ``onion
+comment.'' An onion comment is a special type of inline comment that
+may be placed on a line containing a \texttt{smuggle} statement to
+customize how \texttt{davos} searches for the smuggled package locally
+and, if necessary, downloads and installs it. Onion comments follow a
+simple format based on the ``type comment'' syntax introduced in PEP
+484~\cite{vanREtal14}, and are designed to make managing packages with
+\texttt{davos} intuitive and familiar. To construct an onion comment,
+users provide the name of the installer program (e.g., \texttt{pip})
+and the same arguments one would use to manually install the package
+as desired via the command line:
 \begin{center}
@@
 \end{center}
-Occasionally, a package's distribution name (i.e., the name used when installing it) may differ from its top-level module name (i.e., the name used when importing it).
-In such cases, an onion comment can be used to ensure that \texttt{davos} installs the proper distribution if the smuggled package can't be found locally:
-%Onion comments are useful in such cases for ensuring \texttt{davos} installs the proper distribution if the smuggled package isn't installed locally:
-%Onion comments are useful when smuggling a package whose distribution name (i.e., the name used when installing it) differs from its top-level module name (i.e., the name used when importing it).
-Onion comments are useful in such cases for
+Occasionally, a package's distribution name (i.e., the name used when
+installing it) may differ from its top-level module name (i.e., the
+name used when importing it). In such cases, an onion comment can be
+used to ensure that \texttt{davos} installs the proper distribution if
+the smuggled package cannot be found locally:
 \begin{center}
@@
 \end{center}
-However, the most powerful use of the onion comment is making \texttt{smuggle} statements \textit{version-sensitive}.
-If an onion comment includes a version specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the version of the package loaded into the notebook matches the specific version requested, or satisfies the given version constraints.
-If the smuggled package exists locally, \texttt{davos} will extract its version info from its metadata and compare it to the specifier provided.
-If the two are incompatible (or no local installation is found), \texttt{davos} will install and load a suitable version of the package instead:
+Because onion comments may be constructed to specify any aspect of the
+installer's behavior, they provide a mechanism for precisely
+controlling how, where, and when smuggled packages are installed.
+Critically, if an onion comment includes a version
+specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the
+version of the package loaded into the notebook matches the specific
+version requested, or satisfies the given version constraints. If the
+smuggled package exists locally, \texttt{davos} will extract its
+version information from its metadata and compare it to the specifier
+provided. If the two are incompatible (or no local installation is
+found), \texttt{davos} will install and load a suitable version of the
+package instead:
 \begin{center}
@@
 \end{center}
-Onion comments can also be used to smuggle specific VCS references (e.g., Git~\cite{TorvHama05}  branches, commits, tags, etc.):
+Onion comments can also be used to smuggle specific VCS references
+(e.g., Git~\cite{TorvHama05} branches, commits, tags, etc.):
 \begin{center}
@@
 \end{center}
-\texttt{davos} processes onion comments internally before forwarding arguments to the installer program.
-In addition to preventing onion comments from being used as a vehicle for shell injection attacks, this enables \texttt{davos} to take certain logical actions when particular arguments are passed.
-For example, each of the \mbox{\texttt{-I}/\texttt{--ignore-installed}}, \texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags will cause \texttt{davos} to skip searching for a smuggled package locally before installing a new copy:
+\texttt{davos} processes onion comments internally before forwarding
+arguments to the installer program. In addition to preventing onion
+comments from being used as a vehicle for shell injection attacks,
+this design provides the user with additional control over which
+packages are imported. For example, each of the
+\mbox{\texttt{-I}/\texttt{--ignore-installed}},
+\texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags
+will cause \texttt{davos} to skip searching for a smuggled package
+locally before installing a new copy:
 \begin{center}
@@
 \end{center}
-Similarly, passing \texttt{--no-input} will temporarily enable \texttt{davos}'s non-interactive mode (see Section~\ref{subsec:config}), and installing a smuggled package into \texttt{<dir>} with \texttt{--target <dir>} will cause \texttt{davos} to prepend \texttt{dir} to the module search path (i.e., \texttt{sys.path}), if necessary, so the package can be imported.
+Similarly, passing \texttt{--no-input} will temporarily enable
+\texttt{davos}'s non-interactive mode (see
+Section~\ref{subsec:config}), and installing a smuggled package into a
+custom directory (\texttt{<dir>}) using the \texttt{--target <dir>}
+flag will cause \texttt{davos} to prepend \texttt{<dir>} to the module
+search path (i.e., \texttt{sys.path}), if necessary, so the package
+can be imported.
 
-\subsubsection{The \texttt{davos} config}\label{subsec:config}
-The \texttt{davos} config provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior.
-After importing \texttt{davos}, the \texttt{davos.config} object (a singleton) exposes a number of configurable options as attributes that can be assigned different values, checked at runtime, and displayed in the notebook cell output (see Fig.~\ref{fig:illustrative-example} for example usage).
-These include:
-%The \texttt{davos.config} object provides a simple, high-level interface for controlling various aspects of \texttt{davos}'s behavior.
-After importing \texttt{davos}, the config instance (a singleton) for the current session exposes a number of options that can be set by assigning values to the object's attributes (see Fig.~\textcolor{red}{INSERT REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
-These include:
-%The \texttt{davos} config object provides a simple, high-level interface that allows users to view and set various options that affect \texttt{davos}'s behavior.
-After importing \texttt{davos}, the config instance (a singleton) for the current session is available as \texttt{davos.config}, and its various fields are accessible as attributes (see Fig.~\textcolor{red}{REF TO ILLUSTRATIVE EXAMPLE FIG} for example usage).
-The config object exposes a mixture of writable and read-only fields.
-Writable fields include:
+\subsubsection{The \texttt{davos} config object}\label{subsec:config}
+
+The \texttt{davos} config object provides a high-level interface for
+controlling various aspects of \texttt{davos}'s behavior. After
+importing \texttt{davos}, the \texttt{davos.con\-fig} object (a
+singleton) exposes configurable options as attributes that can be
+modified, checked at runtime, or displayed (see
+Sec.~\ref{sec:illustrative-example} for an illustrative example or
+Sec.~\ref{subsec:implementation} for implementation details and
+additional information). These include:
+
 \begin{itemize}
-\item \texttt{.active}: This option allows users to disable \texttt{davos} functionality (i.e., support for \texttt{smuggle} statements and onion comments) for subsequent notebook cells by setting its value to \texttt{False}.
-\texttt{davos} can be re-enabled at any time by setting this option to \texttt{True} (the default when \texttt{davos} is first imported).
-See Section~\ref{subsec:implementation} for additional info.
-\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported and cannot be reloaded.
-This can happen if the package includes extension modules that dynamically link C or C++ objects to the Python interpreter itself, and the code that generates those objects was changed between the old and new versions.
-If this option is set to \texttt{True}, \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement.
-If \texttt{False} (the deafult), \texttt{davos} will instead issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook, or continue running with the previously imported package version until the next time the kernel is restarted manually.
-(Note: not configurable in Google Colaboratory).
-%\item \texttt{.auto\_rerun}: Some packages (e.g., \texttt{numpy}, \texttt{pandas}) contain extension modules that dynamically link C or C++ objects to the Python interpreter when imported.
-If \texttt{davos} is used to \texttt{smuggle} a specific version of such a package after a different version of the same package was previously imported
-%\item \texttt{.auto\_rerun}: This option controls how \texttt{davos} behaves when attempting to \texttt{smuggle} a new version of a package that was previously imported (at a different version) and cannot be reloaded (i.e., because it contains C-extensions that dynamically generate code).
-If \texttt{True} (default: \texttt{False}), \texttt{davos} will automatically restart the notebook kernel and rerun all code up to (and including) the current \texttt{smuggle} statement.
-Otherwise, \texttt{davos} will issue a warning, pause execution, and prompt the user with buttons to either restart and rerun the notebook or continue running with the imported package version.
-(Note: not configurable in Google Colaboratory).
-\item \texttt{.confirm\_install}: If \texttt{True} (default: \texttt{False}), \texttt{davos} will require user confirmation (\texttt{[y]es/[n]o} input) before installing a smuggled package.
-\item \texttt{.noninteractive}: Setting this option to \texttt{True} (default: \texttt{False}) enables non-interactive mode, in which all user input and confirmation is disabled.
-Note that in non-interactive mode, the \texttt{confirm\_install} option is set to \texttt{False}, and if \texttt{auto\_rerun} is \texttt{False}, \texttt{davos} will throw an error if a smuggled package cannot be reloaded, rather than prompting the user.
-\item \texttt{.pip\_executable}: This option's value specifies the path to the \texttt{pip} executable used to install smuggled packages.
-The default is programmatically determined from the Python environment and falls back to \texttt{sys.executable -m pip} if no executable can be found.
-\item \texttt{.suppress\_stdout}: If \texttt{True} (default: \texttt{False}), suppress all unnecessary output issued by both \texttt{davos} and the installer program.
-This can be useful when smuggling packages that need to install many dependencies and/or generate extensive output.
-If the installer program throws an error, both the stdout and stderr streams will be displayed with the traceback.
+\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
+  statements and onion comments) is enabled (\texttt{True}) or
+  disabled (\texttt{False}).  When \texttt{davos} is first imported),
+  the \texttt{.active} attribute is set to \texttt{True}.
+
+\item \texttt{.auto\_rerun}: This attribute controls how
+  \texttt{davos} behaves when attempting to \texttt{smuggle} a new
+  version of a package that was previously imported and cannot be
+  reloaded. This can happen if the package includes extension modules
+  that dynamically link C or C++ objects to the Python interpreter
+  itself, and if the code that generates those objects was changed
+  between the previously imported and to-be-smuggled versions.  If
+  this attribute is set to \texttt{True}, \texttt{davos} will
+  automatically restart the notebook kernel and rerun all code up to
+  (and including) the current \texttt{smuggle} statement. If
+  \texttt{False} (the default), \texttt{davos} will instead issue a
+  warning, pause execution, and prompt the user to either restart and
+  rerun the notebook, or continue running with the previously imported
+  package version until the next time the kernel is restarted
+  manually.  Note that, as of this writing, the \texttt{.auto\_rerun} attribute
+  is not supported in Google Colaboratory notebooks.
+
+\item \texttt{.confirm\_install}: If \texttt{True} (default:
+  \texttt{False}), \texttt{davos} will require user confirmation
+  before installing a smuggled package that do not yet exist in the
+  user's environment.
+
+\item \texttt{.noninteractive}: Setting this attribute to
+  \texttt{True} (default: \texttt{False}) enables non-interactive
+  mode, in which all user interactions (prompts and dialogues) are
+  disabled. Note that in non-interactive mode, the
+  \texttt{confirm\_install} option is set to \texttt{False}.  If
+  \texttt{auto\_rerun} is \texttt{False} while in non-interactive
+  mode, \texttt{davos} will raise an exception if a smuggled package
+  cannot be reloaded, rather than prompting the user.
+
+\item \texttt{.pip\_executable}: This attribute's value specifies the
+  path to the \texttt{pip} executable used to install smuggled
+  packages. The default is programmatically determined from the Python
+  environment and falls back to \texttt{sys.executable -m pip} if no
+  executable can be found.
+
+\item \texttt{.suppress\_stdout}: If this attribute is set to
+  \texttt{True} (default: \texttt{False}), \texttt{davos} suppresses
+  printed (console) outputs from itself and the installer program.
+  This can be useful when smuggling packages that need to install many
+  dependencies and/or generate extensive output. However, if the installer
+  program throws an error, both the stdout and stderr streams will still be
+  displayed along with a stack trace.
 \end{itemize}
 
-%\noindent The \texttt{davos.config} object also provides a few informative read-only fields, including:
-%\begin{itemize}
-%\item \texttt{.environment}: This field's value is a short string describing the notebook environment in which \texttt{davos} is currently running.
-This is used internally may be one of \texttt{IPython<7.0} (a notebook whose frontend uses the Jupyter JavaScript library and whose backend uses an IPython version older than v7.0), \texttt{IPython>=7.0} (, or \texttt{}
-%\end{itemize}
-\noindent The top-level \texttt{davos} namespace also defines a handful of convenience functions for setting and checking \texttt{davos}'s active/inactive state (\texttt{davos.activate()}; \texttt{davos.deactivate()}; \texttt{davos.is\_active()}) as well as the \texttt{davos.configure()} function, which allows setting multiple config options at once.
+\noindent The top-level \texttt{davos} namespace also defines
+convenience functions for setting and checking whether \texttt{davos}
+is active (\texttt{davos.activate()}; \texttt{davos.deactivate()};
+\texttt{davos.is\_active()}) as well as the \texttt{davos.configure()}
+function, which allows setting multiple configuration options
+simultaneously.
 
 \subsection{Implementation details}\label{subsec:implementation}
-Functionally, importing \texttt{davos} appears to make ``\texttt{smuggle}'' a valid Python keyword, similar to standard keywords like ``\texttt{import}'', ``\texttt{def}'', or ``\texttt{return}''.
-It also appears to fundamentally change how Python treats comments, suddenly allowing them to potentially influence code behavior at runtime if they conform to a particular syntax.
-However, \texttt{davos} doesn't actually modify the rules of Python's parser or lexical analyzer in order to accomplish this---in fact, modifying the Python grammar isn't possible at runtime, as doing so would require rebuilding the interpreter.
-Instead, \texttt{davos} leverages the IPython notebook backend to implement the \texttt{smuggle} statement and onion comment via a combination of namespace injections and its own (far simpler) custom parser.
 
-The \texttt{smuggle} keyword can be enabled and disabled at any time by ``activating'' and ``deactivating'' \texttt{davos} (see Section~\ref{subsec:config}, above).
-When \texttt{davos} is first imported, it is activated automatically.
-Activating \texttt{davos} triggers two actions: (1) the \texttt{smuggle()} function is injected into the IPython user namespace, and (2) the \texttt{davos} parser is registered as a custom IPython input transformer.
-IPython preprocesses all executed code as plain text before it is sent to the Python compiler, in order to handle special constructs like \texttt{\%magic} and \texttt{!shell} commands.
-\texttt{davos} hooks into this process to transform \texttt{smuggle} statements into syntactically valid Python code.
-The \texttt{davos} parser uses a complex regular expression~\cite{Thom68} to match lines of code containing \texttt{smuggle} statements (and, optionally, onion comments), extract relevant information from their text, and replace them with equivalent calls to the \texttt{smuggle()} function.
-For example, if a user runs a notebook cell containing
+Although \texttt{davos} is designed to \texttt{appear} to add a new
+Python keyword to a notebook's vocabulary, this illusion is actually a
+consequence of several ``hacks'' that make use of the IPython backend
+for processing and executing notebook code.  Specifically, when
+\texttt{davos} is first imported, or when it activated after being set
+to an inactive state, two actions are triggered.  First, the
+\texttt{smuggle()} function is injected into the IPython user
+namespace.  Second, the \texttt{davos} parser is registered as a
+custom IPython input transformer.
+
+IPython preprocesses all executed code as plain text before it is sent
+to the Python compiler, in order to handle special constructs like
+\texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} uses
+this process to transform \texttt{smuggle} statements into
+syntactically valid Python code. The \texttt{davos} parser uses a
+regular expression to match lines of code containing \texttt{smuggle}
+statements (and, optionally, onion comments), extract relevant
+information from their text, and replace them with equivalent calls to
+the \texttt{smuggle()} function. For example, if a user runs a
+notebook cell containing
 \begin{center}
@@
 \end{center}
-The call to the \texttt{smuggle()} function then carries out \texttt{davos}'s central logic of determining whether the smuggled package should be installed, doing so if necessary, and subsequently loading it into the namespace.
-This process is outlined in Figure \ref{fig:flow-chart}.
-Because the \texttt{smuggle()} function is defined in the notebook namespace, it is also possible (though never necessary) to call it directly.
-Deactivating \texttt{davos} will delete the name ``\texttt{smuggle}'' from the namespace, unless its value has been overwritten and no longer refers to the \texttt{smuggle()} function.
-It will also deregister the \texttt{davos} parser from the set of input transformers run when each notebook cell is executed.
-While the overhead added by the \texttt{davos} parser is minimal, this may be useful, for example, when optimizing or precisely profiling code.
+The call to the \texttt{smuggle()} function carries out
+\texttt{davos}'s central logic by determining whether the smuggled
+package must be installed, carrying out the installation if necessary,
+and subsequently loading it into the namespace. This process is
+outlined in Figure \ref{fig:flow-chart}. Because the
+\texttt{smuggle()} function is defined in the notebook namespace, it
+is also possible (though never necessary) to call it
+directly. Deactivating \texttt{davos} will delete the name
+``\texttt{smuggle}'' from the namespace, unless its value has been
+overwritten and no longer refers to the \texttt{smuggle()}
+function. It will also deregister the \texttt{davos} parser from the
+set of input transformers run when each notebook cell is
+executed. While the overhead added by the \texttt{davos} parser is
+minimal, this may be useful, for example, when optimizing or precisely
+profiling code.
 
@@
 \includegraphics[width=\textwidth]{figs/flow_chart}
-\caption{\small \textbf{\texttt{smuggle()} function logic.} }
+\caption{\small \textbf{\texttt{smuggle()} function algorithm.}  At a
+  high level, the \texttt{smuggle()} function may be conceptualized as
+following two basic steps.  First (left), \texttt{davos} ensures that the
+correct version of the desired package has been installed, carrying
+out the installation automatically if needed.  Second (right),
+\texttt{davos} imports the package and updates the current runtime environment.}
 \label{fig:flow-chart}
@@
 
-% talk about how exceptions have to inherit from SyntaxError since that's the only thing that can be raised during parsing
+\section{Illustrative Example}\label{sec:illustrative-example}
 
-% ----------------------------------------------- ILLUSTRATIVE EXAMPLES ------------------------------------------------
-\section{Illustrative Example}\label{sec:illustrative-example}
-% Provide at least one illustrative example to demonstrate the major functions.
+Across different versions of a given package, functions may be
+changed, depreciated, added, or renamed.  In addition to changing the
+behaviors of active computations, saved objects created using one
+version of a package may be incompatible with another version of the
+same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
+library prior to version 0.25.0 included the \texttt{Panel} datatype
+for storing 3-dimensional arrays.  Since version 0.20.0,
+however, the \texttt{Panel} datatype has been depreciated, and the
+datatype was removed entirely in version 0.25.0.  If one had saved a dataset in a
+\texttt{Panel} object (created using an older version of
+\texttt{pandas}), e.g., by serializing the \texttt{Panel} and saving
+it to disk using, \texttt{pickle}, that dataset could not be read by
+any version of \texttt{pandas} from 0.25.0 or beyond.  These
+incompatibilities are not limited solely to traditional forms of data.
+For example, saved model states and other objects may reference
+functions, attributes, classes, and other objects that are not present
+across all versions of their associated library.
 
@@
 \includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for \texttt{davos}'s functionality.}}
+\caption{\small \textbf{Example use case for \texttt{davos}'s
+    functionality.}  Snippets from the example are also excerpted in
+  the main text of Section~\ref{sec:illustrative-example}.}
 \label{fig:illustrative-example}
@@
 
-Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses.
-In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in a Jupyter notebook.
-The hypothetical dataset (a \texttt{pandas}~\cite{McKi10} \texttt{Panel}) and model (a \texttt{scikit-learn}~\cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in June 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them.
-The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.
+The example provided in Figure~\ref{fig:illustrative-example}
+demonstrates how the \texttt{davos} library can be used to circumvent
+these incompatibilities by carefully controlling which versions of
+each package are used in different parts of the notebook.  The example
+shows how a data and model saved using since-depreciated functionality
+in the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
+packages may be loaded in (using older versions of each package) and
+manipulated or analyzed (using more recent versions of each package).
 
-After importing \texttt{davos} (line 1), the user first smuggles two utilities for interacting with local files in the code below.
-The \texttt{smuggle} statement in line 3 loads the \texttt{is\_file()} function from the Python standard library's \texttt{os.path} module.
-Standard library modules are included with all Python distributions, so this line is functionally equivalent to an \texttt{import} statement and does not need or benefit from an onion comment.
-Line 4 loads the \texttt{joblib} library~\cite{Varo10}, installing it first, if necessary.
-Since \texttt{joblib}'s I/O interface has historically remained stable and backwards-compatible across releases, requiring that users have a particular exact version installed would likely be unnecessarily restrictive.
-However, there's also no guarantee that a \textit{future} release won't introduce some breaking change, so to help ensure the analysis notebook continues to run properly in the future, the onion comment in line 4 limits allowable versions to those already released when the code was written.
-%After importing \texttt{davos} (line 1), the user first smuggles two utilities that will be used to help find and load local files in the code below: the \texttt{is\_file} function from the \texttt{os.path} module, and the \texttt{joblib} library~\cite{Varo10} (lines 3--4).
-The first \texttt{smuggle} statement needs no onion comment, as the \texttt{os.path} module is part of Python's standard library and is therefore guaranteed to be available.
-The second ensures \texttt{joblib} is installed before loading it Enforcing an exact version of \texttt{joblib} is likely unnecessary, since the package's I/O interface has historically remained generally stable across versions.
-However, there's no
+After importing \texttt{davos} (line 1), the user first smuggles two
+utilities for interacting with local files in the code below. The
+\texttt{smuggle} statement in line 3 loads the \texttt{is\_file()}
+function from the Python standard library's \texttt{os.path}
+module. Standard library modules are included with all Python
+distributions, so this line is functionally equivalent to an
+\texttt{import} statement and does not need or benefit from an onion
+comment. Line 4 loads the \texttt{joblib} library~\cite{Varo10},
+installing it first, if necessary. Since \texttt{joblib}'s I/O
+interface has historically remained stable and backwards-compatible
+across releases, requiring that users have a particular exact version
+installed would likely be unnecessarily restrictive. However, a
+\textit{future} release might introduce some breaking change.  The
+onion comment in line 4 helps ensure the analysis notebook continues
+to run properly in the future, by limiting allowable versions to those
+already released when the code was written:
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example1}
+\end{center}
+Line 6 then uses the \texttt{davos.config} object to enable
+\texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next
+two packages: \texttt{NumPy}~\cite{HarrEtal20} and
+\texttt{pandas}. Because these libraries rely heavily on custom C data
+types, loading the particular versions from the onion comments may
+require restarting the notebook kernel if different versions had been previously
+imported during the same interpreter session (see
+Section~\ref{subsec:config}).
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example2}
+\end{center}
+Setting the \texttt{auto\_rerun} attribute to \texttt{True} also
+benefits the (potential) installation of \texttt{pandas} on the next
+lines:
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example3}
+\end{center}
+If we suppose that the data contained in \texttt{data-old.pkl} is
+stored in a \texttt{Panel} object (i.e., created in a version of
+\texttt{pandas} prior to 0.25.0), then we would not be able to load in
+that object with newer versions of \texttt{pandas}.  Line 10 ensures
+that an older version of \texttt{pandas} will be imported, enabling
+the data to be read in (and saved out to a \texttt{.csv} file, which
+is compatible with newer versions of \texttt{pandas}).
 
-Line 6 then uses the \texttt{davos.config} object to enable \texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next two packages: \texttt{NumPy}~\cite{HarrEtal20} and \texttt{pandas}.
-Because these libraries rely heavily on custom C data types, loading the particular versions from the onion comments may require restarting the notebook kernel if different versions were already imported during the same interpreter session (see Section~\ref{subsec:config}).
-This is unlikely to happen with \texttt{NumPy}, as it is loaded explicitly only once (by line 7) and is not required by any packages loaded before it (and therefore not imported and cached while loading them).
-However, it's possible a future user could edit this notebook to add additional code before line 7, run the notebook's cells out of order, or even configure their IPython kernel to execute custom code on startup (e.g., as Google Colab notebooks do), any of which could potentially import a different, existing version of \texttt{NumPy} before \texttt{davos} smuggles the version specified in the onion comment.
-Enabling the \texttt{auto\_rerun} option before smuggling \texttt{NumPy} will help to simplify running the notebook in these scenarios, but the main benefit it affords comes when smuggling the \texttt{pandas} library.
+Newer versions of \texttt{pandas} have brought substantial
+performance improvements, added new functionality, fixed bugs, etc.
+Although the original dataset had to be read in using an older version
+of the package, we can take advantage of those newer changes using a
+new \texttt{smuggle} statement and onion comment on line 14 (which
+specifies that version 1.3.5 should be imported).  Since
+\texttt{pandas} had already been imported into the current workspace
+(on line 10), the runtime must be restarted in order to gain access to
+the newer version of \texttt{pandas}.  The \texttt{.auto\_rerun} flag
+set on line 6 enables this process to happen automatically, and saving
+out the dataset to a \texttt{.csv} file in lines 9--12 ensures that
+the older version of \texttt{pandas} does not need to be reinstalled.
 
-The dataset that the user wants to analyze was provided as a \texttt{pandas.Panel} object, serialized with Python's built-in \texttt{pickle} module.
-The \texttt{pickle} protocol is a popular choice for persisting data in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat:
-In order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, its class must be defined in and importable from the same module as when it was saved.
-%A ``pickled'' object's class definition must be importable from the same module as when it was saved in order to successfully ``unpickle'' (i.e., load and restore) it later.
-The \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the dataset can be loaded only if the user's notebook uses a \texttt{pandas} version released prior to that change.
-However, more recent updates to the \texttt{pandas} library since then have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats for data structures (including in Jupyter notebooks).
-%Recent updates to the \texttt{pandas} library have brought substantial improvements that the user would like to take advantage of in their analysis code, including faster performance, more memory-efficient data types, new functions and methods, compatibility with newer versions of Python and popular plotting libraries, and better display formats (including in Jupyter notebooks).
-However, the \texttt{Panel} class was removed from \texttt{pandas} in July, 2019 (v0.25.0), meaning that the dataset they are working with can only be loaded by a version released prior to that change.
-\texttt{davos} makes it possible to do both within a single notebook, and with the \texttt{auto\_rerun} option, this process can be fully automated.
-The first time the notebook is run, lines 10--12 will install and load an older version of \texttt{pandas} that defines the \texttt{Panel} class, use it to read the dataset from its serialized file format, convert the dataset from a \texttt{Panel} to a multi-index \texttt{DataFrame}, and write its contents to a CSV file.
-The \texttt{smuggle} statement on line 14 will then install a newer \texttt{pandas} version (v1.3.5) for use in the analyses themselves.
-Because an older \texttt{pandas} version was previously loaded (by line 10), and because the package's C extension modules were modified between the old and new versions, switching to the new version will require restarting the notebook kernel.
-When \texttt{davos} determines this, it will automatically restart the kernel, re-run the notebook up through the current cell, and also re-queue any subsequent cells that were queued before the restart was triggered.
-This second time the code is run (as well as in any future runs), lines 10--12 will be skipped since the CSV-formatted dataset has already been created, and the \texttt{smuggle} statements up through line 14 will execute (virtually) as fast as regular \texttt{import} statements since the required package versions have already been installed.
-%This second time the code is run (as well as any future times), the \texttt{smuggle} statements that have already been run once will execute (virtually) as fast as \texttt{import} statements since the required package versions are now installed, and lines 10--12 will be skipped altogether since the CSV-formatted dataset has already been created.
-It's worth noting that one could instead save the converted \texttt{DataFrame} as a pickle file
+Next, line 16 uses the \texttt{davos.configure()} function to disable
+the \texttt{auto\_rerun} option and simultaneously enable two other
+options: \texttt{suppress\_stdout} and \texttt{noninteractive}. With
+these options enabled, lines 17--18 \texttt{smuggle}
+\texttt{TensorFlow}~\cite{AbadEtal15}, a powerful end-to-end platform
+for building and working with machine learning models, and
+\texttt{UMAP}~\cite{McInEtal18b}, a library that implements a family
+of related manifold learning techniques. The onion comment in line 18
+also specifies that \texttt{UMAP} should be installed with the
+optional requirements needed for its ``plot'' and ``parametric\_umap''
+features. Together, these two packages depend on 36 other unique
+packages, most of which have dependencies of their own. And if many of
+these are not already installed in the user's environment, lines
+17--18 could take several minutes to run.  Enabling the
+\texttt{noninteractive} option ensures that the installation will
+continue automatically without user input during that time.  Enabling
+\texttt{suppress\_stdout} also suppresses console outputs from the
+installer that might otherwise distract from other more important outputs.
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example4}
+\end{center}
 
-Line 16 then uses the \texttt{davos.configure()} function to disable the \texttt{auto\_rerun} option and simultaneously enable two other options: \texttt{suppress\_stdout} and \texttt{noninteractive}.
-With these options enabled, lines 17--18 \texttt{smuggle} \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful end-to-end platform for building and working with machine learning models, and \texttt{UMAP}~\cite{McInEtal18b}, a library that implements a family of related manifold learning techniques.
-The onion comment in line 18 also specifies that \texttt{UMAP} should be installed with the optional requirements needed for its ``plot'' and ``parametric\_umap'' features.
-Together, these two packages depend on 36 other unique packages, most of which have dependencies of their own.
-And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run.
-Enabling the \texttt{noninteractive} option ensures the installation process won't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
-Additionally, installing more than three dozen packages could result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
-Enabling \texttt{suppress\_stdout} hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
-Importantly, if either line fails for any reason, both the stdout and stderr streams will be shown alongside the regular Python traceback.
-%And if many of these are not already installed in the user's environment, lines 17--18 could take multiple minutes to run and result in the installer program writing an extremely large amount of standard output text to the notebook cell's output area.
-Enabling the \texttt{noninteractive} option ensures the installation process doesn't require any input from the user to finish successfully, allowing them to simply ignore the notebook during this time and either work in another browser tab or application, or step away from their computer entirely.
-Enabling the \texttt{suppress\_stdout} option hides the output from these two \texttt{smuggle} statements so that other potentially important output (e.g., from previous \texttt{smuggle} statements) isn't buried and lost.
-Importantly, if either line fails for any reason, both the stdout and stderr streams will be shown alongside the regular Python traceback.
+After re-enabling these two options (line 19), the user next smuggles
+specific versions of three plotting libraries:
+\texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and
+\texttt{Quail}~\cite{HeusEtal17} (lines 21--23). Because the first two
+are requirements of \texttt{UMAP}'s optional ``plot'' feature, they
+will have already been installed by line 18, though possibly as
+different versions than those specified in the onion comments on lines
+21 and 22. If the installed and specified versions are the same, these
+\texttt{smuggle} statements will function like standard \texttt{import}
+statements to load the libraries into the notebook namespace. If they
+differ, \texttt{davos} will download the requested versions in place
+of the installed versions before doing so.
 
-After re-enabling these two options (line 19), the user next smuggles specific versions of three plotting libraries: \texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and \texttt{Quail}~\cite{HeusEtal17} (lines 21--23).
-Because the first two are requirements of \texttt{UMAP}'s optional ``plot'' feature, they will have already been installed by line 18, though possibly as different versions than those specified in the onion comments on lines 21 and 22.
-If the installed and specified versions are the same, these \texttt{smuggle} statements will function like regular \texttt{import} statements to load the libraries into the notebook namespace.
-If they differ, \texttt{davos} will download the requested versions in place of the installed versions before doing so.
-It's also worth noting that while loading \texttt{UMAP} in line 18 will not result in either \texttt{Matplotlib} or \texttt{seaborn} being imported internally due to the specific layout of the \texttt{UMAP} package, if it had, \texttt{davos} would also gracefully replace the cached versions of the two packages so that the smuggled versions are loaded properly.
-And (as with all other \texttt{smuggle} statements in Figure~\ref{fig:illustrative-example}), if for any reason the specified package versions are incompatible with any other packages (e.g., \texttt{UMAP}), the installer program would display a warning to this effect in the notebook.
+Line 23 uses an onion comment to specify that \texttt{Quail} should be
+installed directly from a specific GitHub commit (\texttt{6c847a4}).
+This ability to install packages directly from GitHub repositories can
+enable developers to use forked or modified versions of other
+libraries in their notebooks, even if those versions have not been
+officially released.
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example5}
+\end{center}
 
-The third plotting library smuggled, \texttt{Quail}, is also pinned to a precise version with an onion comment, though in a slightly different manner than other packages in Figure~\ref{fig:illustrative-example}.
-Line 23 installs and loads \texttt{Quail} from the user's fork (``myfork'') of the package's GitHub repository, at a specific point in its revision history (i.e., the commit whose short hash is ``6c847a4'').
-This can serve as a useful way to access a version of a package the user has customized, patched, or somehow modified for this specific use case, while still allowing them to further modify their fork of the package in the future without affecting the version used in these analyses.
+In lines 25--28, we demonstrate another aspect of \texttt{davos}'s
+functionality that supports more advanced installation scenarios.  The
+\texttt{ipywidgets}~\cite{FredEtal15} package provides an API for
+creating these widgets with Python code, and the
+\texttt{widgetsnbextension} package provides the machinery for the
+notebook frontend to display them.
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example6}
+\end{center}
+A complication is that \texttt{ipywidgets} must be installed in the
+same environment as the IPython kernel, whereas
+\texttt{widgetsnbextension} must be installed in the environment that
+houses the Jupyter notebook server. In standard setups, these two
+environments are the same.  However, a common ``advanced'' approach is
+to run the notebook server from a base environment, with additional
+environments each providing their own separate, interchangeable
+IPython kernels.  To accomodate this multi-environment scenario, on
+lines 25 and 27 we control which environments each package should be
+installed to.  Once these two packages are installed and imported, line 30 smuggles
+\texttt{tqdm}~\cite{daCoEtal22}, which display progress
+bars to provide status updates for running code. In Jupyter notebooks, the
+\texttt{tqdm.notebook} module can be imported to enable aesthetically pleasing
+progress bars that are displayed via \texttt{ipywidgets}, if that package is
+installed and importable. Therefore, to take advantage of this
+feature, it was important to \texttt{smuggle} \texttt{tqdm} after
+ensuring the \texttt{ipywidgets} package was available.
 
-Next, the user smuggles a pair of packages that extend the Jupyter notebook interface with various interactive JavaScript widgets.
-The \texttt{ipywidgets}~\cite{FredEtal15} package provides an API for creating these widgets with Python code, and the \texttt{widgetsnbextension} package provides the machinery for the notebook frontend to display them.
-Thus, \texttt{ipywidgets} must be installed in the same environment as the IPython kernel, and \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server.
-In the simplest case, these two environments are the same; however, a common approach to using Jupyter notebooks with multiple different Python environments (e.g., for different tasks or projects) is to run the notebook server from a ``base environment,'' with additional environments each providing their own separate, interchangeable IPython kernels.
-(While possible to detect programmatically, Figure~\ref{fig:illustrative-example} assumes this setup to simplify the example code.) To handle this multi-environment installation, line 25 temporarily sets the \texttt{pip} executable used to install smuggled packages to that of the notebook server's environment before smuggling \texttt{widgetsnbextension} (line 26).
-Since there is no need to actually load this package for later use in the analysis code, it is aliased as a single underscore---by convention, a ``throwaway'' variable in Python.
-In line 27, the user changes the \texttt{pip} executable back to that of the notebook kernel environment (its original value) before installing \texttt{ipywidgets} and subsequent packages.
-With these two packages installed, line 30 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which provides convenient progress bars for long-running code.
-In Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported to enable prettier progress bars displayed via \texttt{ipywidgets}, if that package is installed and importable.
-Therefore, to take advantage of this feature, it was important to \texttt{smuggle} \texttt{tqdm} after ensuring the \texttt{ipywidgets} package was available.
+Next, we load in the reformatted dataset (line 32) and pre-trained
+model (line 34) that we wish to use in our analysis.  In our
+hypothetical example, we can suppose that the model was provided as a
+\texttt{scikit-learn} \texttt{Pipeline} object that passes data
+through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
+instance converts text data to an array of word counts.  Second, the
+word counts are passed to a topic model~\citep{BleiEtal03} using a
+pretrained \texttt{LatentDirichletAllocation} instance.
 
-Finally, the user loads in the re-formatted dataset (line 32) and pre-trained model (line 34) they'll use in their analyses.
-But in accessing the latter, the user encounters an issue similar to the one they initially faced with the dataset.
-This hypothetical semantic model was provided as a \texttt{scikit-learn} ``\texttt{Pipeline}'' object that allows the user to pass text data through two pre-trained transformers, in series: a \texttt{CountVectorizer} instance and a \texttt{LatentDirichletAllocation} instance (i.e., a topic model \cite{BleiEtal03}).
-The model was saved by its original creator using the \texttt{joblib} library, as \texttt{scikit-learn}'s documentation recommends, with the caveat that because \texttt{joblib} uses the \texttt{pickle} protocol internally, the ability to save and load pre-trained models is not guaranteed across versions due to \texttt{pickle}'s requirement that referenced classes be importable from the same location when saved and loaded.
-This issue affects the user's model by way of the \texttt{LatentDirichletAllocation} class---when the \texttt{Pipeline} object was created (again, in June, 2019, using \texttt{scikit-learn} v0.21.3), the class's definition lived in the \texttt{sklearn.decomposition.online\_lda} module.
-However, in version 0.22.0 (released November, 2019), that module was renamed to ``\texttt{\_online\_lda},'' and in v0.22.1 (January, 2020) it was again renamed to ``\texttt{\_lda}'' (which has remained its name since then).
-Thus, in order to successfully load the model that includes the pre-trained \texttt{LatentDirichletAllocation} instance, in line 33, the user first smuggles a version of \texttt{scikit-learn} prior to v0.22.0 (i.e., before the first time the module's name was changed).
-Once the model is loaded and reconstructed in memory  from a compatible package version (line 34), the user then upgrades to a newer version of \texttt{scikit-learn} for use elsewhere in their analyses.
-When
-line 35 is run, \texttt{davos} will replace the existing \texttt{scikit-learn} version with v1.1.3 in both the user's local package environment and in memory without interruption, such that ``\texttt{sklearn}'' will reference the new version in any code below.
-However, this will not affect the already compiled code object stored in the ``\texttt{transformer}'' variable, meaning that the pre-trained model will be usable simultaneously.
-% It's possible that in some cases, a version mismatch like this could introduce certain compatibility issues, depending on the specific package and the differences between the two versions being used.
-For example, a function from a newer package version could fail to handle an object from an older version passed to it as an argument, if it expects the object to have certain attributes that had not yet been added in the older version.
-Fortunately, with \texttt{davos}, this scenario is relatively easy to handle, as \texttt{smuggle} statements can be used to temporarily switch between package versions as needed (e.g., for a single line, in order to call an older version of the function).
-And because the installer program caches previously installed package versions, switching between package versions in this way can be done fairly quickly.
+Let us suppose that the \texttt{Pipeline} object had been saved by its
+original creator using the \texttt{joblib} library, as
+\texttt{scikit-learn}'s documentation recommends.  Because
+\texttt{joblib} uses the \texttt{pickle} protocol internally, the
+ability to save and load pre-trained models is not guaranteed across
+different \texttt{scikit-learn} versions.  For example, suppose that
+the \texttt{Pipeline} object was created using \texttt{scikit-learn}
+v0.21.3).  In that version of \texttt{scikit-learn}, the
+\texttt{LatentDirichletAllocation} class is defined in
+\texttt{sklearn.decomposition.online\_lda}.  However, in version
+0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
+versions 0.22.1 and higher, the name has been reverted back to
+\texttt{\_lda}.
 
-% Optional: you may include one explanatory video that will appear next to your article, in the right hand side panel.
-(Please upload any video as a single supplementary file with your article.
-Only one MP4 formatted, with 50MB maximum size, video is possible per article.
-Recommended video dimensions are 640 x 480 at a maximum of 30 frames/second.
-Prior to submission please test and validate your .mp4 file at $ http://elsevier-apps.sciverse.com/GadgetVideoPodcastPlayerWeb/verification$.
-This tool will display your video exactly in the same way as it will appear on ScienceDirect.).
+In order to correctly load the model that
+includes the pretrained \texttt{LatentDirichletAllocation} instance,
+in line 33, the user first smuggles a version of \texttt{scikit-learn}
+prior to v0.22.0 (i.e., before the first time the relevant module's name was
+changed).  Once the model is loaded and reconstructed in memory from a
+compatible package version (line 34), we upgrade to a
+newer version of \texttt{scikit-learn} in line 35.  Taken together,
+the code in Figure~\ref{fig:illustrative-example} shows how
+\texttt{davos} can enable users to load in data and models that are
+incompatible with newer versions of \texttt{pandas} and
+\texttt{scikit-learn}, but still \textit{analyze} and the data and
+model output using the latest approaches and implementations.
 
-% ------------------------------------------------------- IMPACT -------------------------------------------------------
 \section{Impact}
@@
 Beyond research applications, \texttt{davos} is also useful in
-pedagogical settings. For example, in programming courses,
-instructors and students may import the \texttt{davos} library into
-their notebooks to provide a simple means of ensuring their code will
-run on others' machines. When combined with online notebook-based
-platforms like Google Colaboratory, \texttt{davos} provides a
-convenient way to manage dependencies within a notebook, without
-requiring any software (beyond a web browser) to be installed on the
-students' or instructors' systems. For the same reasons,
-\texttt{davos} also provides an elegant means of sharing ready-to-run
-notebook-based demonstrations or tutorials that install their dependencies
-automatically.
+pedagogical settings. For example, in programming courses, instructors
+and students may use the \texttt{davos} library to ensure their
+notebooks will run correctly on others' machines. When combined with
+online notebook-based platforms like Google Colaboratory,
+\texttt{davos} provides a convenient way to manage dependencies within
+a notebook, without requiring any software (beyond a web browser) to
+be installed on the students' or instructors' systems. For the same
+reasons, \texttt{davos} also provides an elegant means of sharing
+ready-to-run notebook-based demonstrations or tutorials that install
+their dependencies automatically.
 
 Since its initial release, \texttt{davos} has found use in a variety
-of applications. In addition to managing computing environments
-for multiple ongoing research studies, \texttt{davos} is being used by
-both students and instructors in programming and methods courses such as
-Storytelling with Data~\cite{Mann21d} (an open course on data science,
-visualization, and communication) and Laboratory in Psychological
-Science~\cite{Mann22} (an open course on experimental and statistical
-methods for psychology research) to simplify distributing lessons and
-submitting assignments, as well as in online demos such as
-\texttt{abstract2paper}~\cite{Mann21e} (an example application of
-GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that
-installs dependencies automatically.
+of applications. In addition to managing computing environments for
+multiple ongoing research studies, \texttt{davos} is being used by
+both students and instructors in programming and methods courses such
+as Storytelling with Data~\cite{Mann21d} (an open course on data
+science, visualization, and communication) and Laboratory in
+Psychological Science~\cite{Mann22} (an open course on experimental
+and statistical methods for psychology research) to simplify
+distributing lessons and submitting assignments, as well as in online
+demos such as \texttt{abstract2paper}~\cite{Mann21e} (an example
+application of GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share
+ready-to-run code that installs dependencies automatically.
 
 Our work also has several more subtle ``advanced'' use cases and
-potential impacts. Whereas Python's built-in \texttt{import}
-statement is agnostic to packages' version information, \texttt{smuggle}
+potential impacts. Whereas Python's built-in \texttt{import} statement
+is agnostic to packages' version information, \texttt{smuggle}
 statements (when combined with onion comments) are version-sensitive.
-And because onion comments are parsed at runtime, required packages and
-their specified versions are installed in a just-in-time manner. Thus, it is possible
-in most cases to \texttt{smuggle} a specific package version or revision even if
-a different version has already been loaded. This enables more complex uses
-that take advantage of multiple versions of a package within a single interpreter
-session (e.g., see Section~\ref{sec:illustrative-example}). This could be useful in cases where specific features are added or
-removed from a package across different versions, or in comparing the
-performance or functionality of particular features across different versions of
-the same package.
+And because onion comments are parsed at runtime, required packages
+and their specified versions are installed in a just-in-time
+manner. Thus, it is possible in most cases to \texttt{smuggle} a
+specific package version or revision even if a different version has
+already been loaded. This enables more complex uses that take
+advantage of multiple versions of a package within a single
+interpreter session (e.g., see
+Section~\ref{sec:illustrative-example}). This could be useful in cases
+where specific features are added or removed from a package across
+different versions, or in comparing the performance or functionality
+of particular features across different versions of the same package.
 
-A second more subtle impact of our work is in providing a proof-of-concept of how the ability to add new ``keyword-like'' operators to the Python language could be specifically useful to researchers.
-With \texttt{davos}, we accomplish this by leveraging IPython notebooks' internal code parsing and execution machinery.
-We note that, while other popular packages similarly use these mechanisms to providing notebook-specific functionality (e.g., \cite{Hunt07,HeusEtal18a}), this approach also has the potential to be exploited for more nefarious purposes.
-For example, a malicious user could design a Python library that, when imported, substantially changes the notebook's functionality by adding new \textit{unexpected} keyword-like objects (e.g., based around common typos).
-We also note that this implementation approach means \texttt{davos}'s functionality is currently restricted to IPython notebook environments, as would be that of any potential similar tools that enable user-defined keywords.
-However, there has been early-stage discussion of providing this sort of syntactic customizability as a core feature of the Python language, including a draft proposal \cite{Shan20}.
-In addition to enabling \texttt{davos} to be extended for use outside of notebooks, this could lead to exciting new tools that, like \texttt{davos}, extend the Python language in useful and more secure ways.
+A second more subtle impact of our work is in providing a
+proof-of-concept of how the ability to add new ``keyword-like''
+operators to the Python language could be specifically useful to
+researchers. With \texttt{davos}, we accomplish this by leveraging
+IPython notebooks' internal code parsing and execution machinery. We
+note that, while other popular packages similarly use these mechanisms
+to providing notebook-specific functionality (e.g.,
+\cite{Hunt07,HeusEtal18a}), this approach also has the potential to be
+exploited for more nefarious purposes. For example, a malicious user
+could design a Python library that, when imported, substantially
+changes the notebook's functionality by adding new \textit{unexpected}
+keyword-like objects (e.g., based around common typos). We also note
+that this implementation approach means \texttt{davos}'s functionality
+is currently restricted to IPython notebook environments, as would be
+that of any potential similar tools that enable user-defined
+keywords. However, there has been early-stage discussion of providing
+this sort of syntactic customizability as a core feature of the Python
+language, including a draft proposal \cite{Shan20}. In addition to
+enabling \texttt{davos} to be extended for use outside of notebooks,
+this could lead to exciting new tools that, like \texttt{davos},
+extend the Python language in useful and more secure ways.
 
-% ---------------------------------------------------- CONCLUSIONS -----------------------------------------------------
 \section{Conclusions}
-% Set out the conclusion of this original software publication.
 
@@
 perhaps the most exciting uses of the \texttt{davos} library are those
-that we have \textit{not} yet considered or imagined. We hope that
-the Python community will find \texttt{davos} to provide a convenient
+that we have \textit{not} yet considered or imagined. We hope that the
+Python community will find \texttt{davos} to provide a convenient
 means of managing project dependencies to facilitate code sharing. We
@@
 \section*{Author Contributions}
+
 \textbf{Paxton C. Fitzpatrick}: Conceptualization, Methodology,
@@
 Visualization. \textbf{Jeremy R. Manning}: Conceptualization,
-Resources, Validation, Writing - Review \& Editing, Supervision, Funding
-acquisition.
+Resources, Validation, Writing - Review \& Editing, Supervision,
+Funding acquisition.
 
 \section*{Funding}
+
 Our work was supported in part by NSF grant number 2145172 to JRM.
-The content is solely the responsibility of the authors and does not necessarily represent the official views of our supporting organizations.
+The content is solely the responsibility of the authors and does not
+necessarily represent the official views of our supporting
+organizations.
 
 \section*{Declaration of Competing Interest}
-We wish to confirm that there are no known conflicts of interest associated with this publication and there has been no significant financial support for this work that could have influenced its outcome.
+
+We wish to confirm that there are no known conflicts of interest
+associated with this publication and there has been no significant
+financial support for this work that could have influenced its
+outcome.
 
 \section*{Acknowledgements}
+
 We acknowledge useful feedback and discussion from the students of
@@
 
-%---------------------------------------------------- BIBLIOGRAPHY -----------------------------------------------------
 \bibliographystyle{elsarticle-num}

### 2022-11-17 paper/main.tex
finished next round of edits

@@
 \newcommand{\comment}[1]{}
+\usepackage{geometry}
+\geometry{letterpaper,left=1in,right=1in,top=1in,bottom=1in,headsep=0pt,footskip=0pt}
 
@@
   science. Here, we propose a lighter-weight solution: the
-  \texttt{davos} library.  When used in combination with a
+  \texttt{davos} package.  When used in combination with a
   notebook-based Python project, \texttt{davos} provides a mechanism
   for specifying (and automatically installing) the correct versions
-  of the project's dependencies.  The \texttt{davos} library further
+  of the project's dependencies.  The \texttt{davos} package further
   ensures that those packages and specific versions are used every
@@
 The same computer code may not behave identically under different
-circumstances.  For example, when code depends on external libraries,
-different versions of those libraries may function differently.  Or
+circumstances.  For example, when code depends on external packages,
+different versions of those packages may function differently.  Or
 when CPU or GPU instruction sets differ across machines, the same
@@
 script or package, manually tracking down those dependencies can
-impose a substantial burden on the user and create room for mistakes
+impose a substantial burden on the user and creates room for mistakes
 and inconsistencies. Further, when dependency versions are left
@@
     scripts} (\texttt{.py} files) provide the most basic ``system''
-  for sharing raw code.  Scripts may reference external libraries, but
-  those libraries must be manually installed on other users' systems.
+  for sharing raw code.  Scripts may reference external packages, but
+  those packages must be manually installed on other users' systems.
   Further, any checking needed to verify that the correct versions of
-  those libraries were installed must also be performed manually.
+  those packages were installed must also be performed manually.
   \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
   text, executable code, and media (including rendered figures, code
-  output, etc.).  When the \textbf{\texttt{davos} library} is imported
+  output, etc.).  When the \textbf{\texttt{davos} package} is imported
   into a Jupyter notebook, the notebook's functionality is extended to
-  automatically install any required external libraries (at their
+  automatically install any required external packages (at their
   correct versions, when specified).  \textbf{Virtual environments}
@@
   \texttt{environment.yml} file) that specifies all project
-  dependencies (including version numbers of external libraries)
+  dependencies (including version numbers of external packages)
   alongside the primary code base. Users can then install a
@@
   precise control over dependencies and versioning.  Notebooks
-  enhanced using the \texttt{davos} library are easily shareable and
+  enhanced using the \texttt{davos} package are easily shareable and
   require minimal setup costs, while also facilitating high
@@
 mix of text, executable code, and embedded media. Notebooks may call
-or import external scripts or libraries---or even intersperse snippets
+or import external scripts or packages---or even intersperse snippets
 of other programming or markup lang\-uages---in order to provide a
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The \texttt{davos} library
+\caption{\small \textbf{Package structure.} The \texttt{davos} package
   comprises two interdependent subpackages.  The \texttt{davos.core}
@@
   rounded rectangles, and arrows denote dependencies (each arrow
-  points to a file that import objects defined or specified at the
+  points to a file that imports objects defined or specified at the
   arrow's source).}
@@
 replacement for Python's built-in \texttt{import} keyword to load
-libraries, modules, and other objects into the current namespace.
+packages, modules, and other objects into the current namespace.
 However, whereas \texttt{import} will fail if the requested package is
@@
 packages on the fly.  If a smuggled package does not exist in the
-local environment, \texttt{davos} will install it automatically,
+local environment, \texttt{davos} will download and install it automatically,
 expose its contents to Python's \texttt{import} machinery, and load it
@@
 installing it) may differ from its top-level module name (i.e., the
-name used when importing it). In such cases, an onion comment can be
-used to ensure that \texttt{davos} installs the proper distribution if
-the smuggled package cannot be found locally:
+name used when importing it). In such cases, an onion comment may be
+used to ensure that \texttt{davos} installs the proper package if it
+cannot be found locally:
 \begin{center}
@@
 provided. If the two are incompatible (or no local installation is
-found), \texttt{davos} will install and load a suitable version of the
-package instead:
+found), \texttt{davos} will download, install, and load a suitable
+version of the package instead:
 \begin{center}
@@
 \end{center}
-Similarly, passing \texttt{--no-input} will temporarily enable
+Similarly, the \texttt{--no-input} flag will temporarily enable
 \texttt{davos}'s non-interactive mode (see
@@
   reloaded. This can happen if the package includes extension modules
-  that dynamically link C or C++ objects to the Python interpreter
-  itself, and if the code that generates those objects was changed
-  between the previously imported and to-be-smuggled versions.  If
-  this attribute is set to \texttt{True}, \texttt{davos} will
-  automatically restart the notebook kernel and rerun all code up to
-  (and including) the current \texttt{smuggle} statement. If
-  \texttt{False} (the default), \texttt{davos} will instead issue a
-  warning, pause execution, and prompt the user to either restart and
-  rerun the notebook, or continue running with the previously imported
-  package version until the next time the kernel is restarted
-  manually.  Note that, as of this writing, the \texttt{.auto\_rerun} attribute
-  is not supported in Google Colaboratory notebooks.
+  that dynamically link C or C++ objects to the Python interpreter,
+  and if the code that generates those objects was changed between the
+  previously imported and to-be-smuggled versions.  If this attribute
+  is set to \texttt{True}, \texttt{davos} will automatically restart
+  the notebook kernel and rerun all code up to (and including) the
+  current \texttt{smuggle} statement. If \texttt{False} (the default),
+  \texttt{davos} will instead issue a warning, pause execution, and
+  prompt the user to either restart and rerun the notebook, or
+  continue running with the previously imported package version until
+  the next time the kernel is restarted manually.  Note that, as of
+  this writing, the \texttt{.auto\_rerun} attribute is not supported
+  in Google Colaboratory notebooks.
 
@@
   \texttt{False}), \texttt{davos} will require user confirmation
-  before installing a smuggled package that do not yet exist in the
+  before installing a smuggled package that does not yet exist in the
   user's environment.
@@
 \item \texttt{.noninteractive}: Setting this attribute to
-  \texttt{True} (default: \texttt{False}) enables non-interactive
+  \texttt{True} (default: \texttt{False}) enables non-in\-ter\-act\-ive
   mode, in which all user interactions (prompts and dialogues) are
@@
 
-Although \texttt{davos} is designed to \texttt{appear} to add a new
+Although \texttt{davos} is designed to \textit{appear} to add a new
 Python keyword to a notebook's vocabulary, this illusion is actually a
@@
 for processing and executing notebook code.  Specifically, when
-\texttt{davos} is first imported, or when it activated after being set
-to an inactive state, two actions are triggered.  First, the
+\texttt{davos} is first imported, or when it is activated after being
+set to an inactive state, two actions are triggered.  First, the
 \texttt{smuggle()} function is injected into the IPython user
@@
 same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
-library prior to version 0.25.0 included the \texttt{Panel} datatype
+package prior to version 0.25.0 included the \texttt{Panel} datatype
 for storing 3-dimensional arrays.  Since version 0.20.0,
@@
 \texttt{pandas}), e.g., by serializing the \texttt{Panel} and saving
-it to disk using, \texttt{pickle}, that dataset could not be read by
+it to disk using \texttt{pickle}, that dataset could not be read by
 any version of \texttt{pandas} from 0.25.0 or beyond.  These
@@
 functions, attributes, classes, and other objects that are not present
-across all versions of their associated library.
+across all versions of their associated package.
 
@@
 \includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for \texttt{davos}'s
-    functionality.}  Snippets from the example are also excerpted in
-  the main text of Section~\ref{sec:illustrative-example}.}
+\caption{\small \textbf{Example use case for \texttt{davos}.}
+  Snippets from this example are also excerpted in the main text of
+  Section~\ref{sec:illustrative-example}.}
 \label{fig:illustrative-example}
@@
 The example provided in Figure~\ref{fig:illustrative-example}
-demonstrates how the \texttt{davos} library can be used to circumvent
+demonstrates how the \texttt{davos} package can be used to circumvent
 these incompatibilities by carefully controlling which versions of
 each package are used in different parts of the notebook.  The example
-shows how a data and model saved using since-depreciated functionality
-in the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
+shows how data and a model saved using since-depreciated components of
+the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
 packages may be loaded in (using older versions of each package) and
@@
 
-After importing \texttt{davos} (line 1), the user first smuggles two
+After importing \texttt{davos} (line 1), we first smuggle two
 utilities for interacting with local files in the code below. The
@@
 \texttt{import} statement and does not need or benefit from an onion
-comment. Line 4 loads the \texttt{joblib} library~\cite{Varo10},
+comment. Line 4 loads the \texttt{joblib} package~\cite{Varo10},
 installing it first, if necessary. Since \texttt{joblib}'s I/O
@@
 two packages: \texttt{NumPy}~\cite{HarrEtal20} and
-\texttt{pandas}. Because these libraries rely heavily on custom C data
+\texttt{pandas}. Because these packages rely heavily on custom C data
 types, loading the particular versions from the onion comments may
@@
 that an older version of \texttt{pandas} will be imported, enabling
-the data to be read in (and saved out to a \texttt{.csv} file, which
-is compatible with newer versions of \texttt{pandas}).
+the data to be read in (and, in line 12, saved out to a \texttt{.csv}
+file, which is compatible with newer versions of \texttt{pandas}).
 
@@
 for building and working with machine learning models, and
-\texttt{UMAP}~\cite{McInEtal18b}, a library that implements a family
+\texttt{UMAP}~\cite{McInEtal18b}, a package that implements a family
 of related manifold learning techniques. The onion comment in line 18
@@
 
-After re-enabling these two options (line 19), the user next smuggles
-specific versions of three plotting libraries:
+After re-enabling these two options (line 19), we next smuggle
+specific versions of three plotting packages:
 \texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and
@@
 \texttt{smuggle} statements will function like standard \texttt{import}
-statements to load the libraries into the notebook namespace. If they
+statements to load the packages into the notebook namespace. If they
 differ, \texttt{davos} will download the requested versions in place
 of the installed versions before doing so.
-
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example5}
+\end{center}
 Line 23 uses an onion comment to specify that \texttt{Quail} should be
@@
 enable developers to use forked or modified versions of other
-libraries in their notebooks, even if those versions have not been
+packages in their notebooks, even if those versions have not been
 officially released.
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example5}
-\end{center}
 
@@
 \texttt{ipywidgets}~\cite{FredEtal15} package provides an API for
-creating these widgets with Python code, and the
-\texttt{widgetsnbextension} package provides the machinery for the
-notebook frontend to display them.
+creating widgets, and the \texttt{widgetsnbextension} package provides
+the machinery needed by the notebook frontend to display them.
 \begin{center}
@@
 houses the Jupyter notebook server. In standard setups, these two
-environments are the same.  However, a common ``advanced'' approach is
-to run the notebook server from a base environment, with additional
-environments each providing their own separate, interchangeable
-IPython kernels.  To accomodate this multi-environment scenario, on
-lines 25 and 27 we control which environments each package should be
-installed to.  Once these two packages are installed and imported, line 30 smuggles
-\texttt{tqdm}~\cite{daCoEtal22}, which display progress
-bars to provide status updates for running code. In Jupyter notebooks, the
-\texttt{tqdm.notebook} module can be imported to enable aesthetically pleasing
-progress bars that are displayed via \texttt{ipywidgets}, if that package is
-installed and importable. Therefore, to take advantage of this
-feature, it was important to \texttt{smuggle} \texttt{tqdm} after
-ensuring the \texttt{ipywidgets} package was available.
+environments are the same.  However, a common ``advanced'' approach
+entails running the notebook server from a base environment, with
+additional environments each providing their own separate,
+interchangeable IPython kernels.  To accomodate this multi-environment
+scenario, on lines 25 and 27 we control which environments each
+package should be installed to.  Once these two packages are installed
+and imported, line 30 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which
+display progress bars to provide status updates for running code. In
+Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported
+to enable aesthetically pleasing progress bars that are displayed via
+\texttt{ipywidgets}, if that package is installed and
+importable. Therefore, to take advantage of this feature, it was
+important to \texttt{smuggle} \texttt{tqdm} after ensuring the
+\texttt{ipywidgets} package was available.
 
@@
 pretrained \texttt{LatentDirichletAllocation} instance.
-
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example7}
+\end{center}
 Let us suppose that the \texttt{Pipeline} object had been saved by its
-original creator using the \texttt{joblib} library, as
+original creator using the \texttt{joblib} package, as
 \texttt{scikit-learn}'s documentation recommends.  Because
@@
 \texttt{LatentDirichletAllocation} class is defined in
-\texttt{sklearn.decomposition.online\_lda}.  However, in version
+\texttt{sklearn.decomposition.\_lda}.  However, in version
 0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
-versions 0.22.1 and higher, the name has been reverted back to
+versions 0.22.1 and higher, the name was reverted back to
 \texttt{\_lda}.
 
-In order to correctly load the model that
-includes the pretrained \texttt{LatentDirichletAllocation} instance,
-in line 33, the user first smuggles a version of \texttt{scikit-learn}
-prior to v0.22.0 (i.e., before the first time the relevant module's name was
-changed).  Once the model is loaded and reconstructed in memory from a
-compatible package version (line 34), we upgrade to a
-newer version of \texttt{scikit-learn} in line 35.  Taken together,
-the code in Figure~\ref{fig:illustrative-example} shows how
-\texttt{davos} can enable users to load in data and models that are
-incompatible with newer versions of \texttt{pandas} and
-\texttt{scikit-learn}, but still \textit{analyze} and the data and
-model output using the latest approaches and implementations.
+In order to correctly load the model that includes the pretrained
+\texttt{LatentDirichletAllocation} instance, in line 33, we first
+smuggle a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
+before the first time the relevant module's name was changed).  Once
+the model is loaded and reconstructed in memory from a compatible
+package version (line 34), we upgrade to a newer version of
+\texttt{scikit-learn} in line 35.  Taken together, the code in
+Figure~\ref{fig:illustrative-example} shows how \texttt{davos} can
+enable users to load in data and models that are incompatible with
+newer versions of \texttt{pandas} and \texttt{scikit-learn}, but still
+\textit{analyze} and manipulate the data and model output using the
+latest approaches and implementations.
 
@@
 Like virtual environments, containers, and virtual machines, the
-\texttt{davos} library (when used in conjunction with Jupyter
+\texttt{davos} package (when used in conjunction with Jupyter
 notebooks) provides a light\-weight mechanism for sharing code and
@@
 containers, and/or virtual machines. For researchers, this lowers
-barriers to both sharing code. By eliminating most of the setup costs
-of reconstructing the original researchers' computing environment,
-\texttt{davos} also lowers barriers to entry for members of
-the scientific community and the public who seek to benefit
-from shared code.
+barriers to sharing code. By eliminating most of the setup costs of
+reconstructing the original researchers' computing environment,
+\texttt{davos} also lowers barriers to entry for members of the
+scientific community and the public who seek to run shared code.
 
@@
 pedagogical settings. For example, in programming courses, instructors
-and students may use the \texttt{davos} library to ensure their
+and students may use the \texttt{davos} package to ensure their
 notebooks will run correctly on others' machines. When combined with
@@
 exploited for more nefarious purposes. For example, a malicious user
-could design a Python library that, when imported, substantially
+could design a Python package that, when imported, substantially
 changes the notebook's functionality by adding new \textit{unexpected}
@@
 that this implementation approach means \texttt{davos}'s functionality
-is currently restricted to IPython notebook environments, as would be
-that of any potential similar tools that enable user-defined
-keywords. However, there has been early-stage discussion of providing
-this sort of syntactic customizability as a core feature of the Python
-language, including a draft proposal \cite{Shan20}. In addition to
-enabling \texttt{davos} to be extended for use outside of notebooks,
-this could lead to exciting new tools that, like \texttt{davos},
-extend the Python language in useful and more secure ways.
+is currently restricted to IPython notebook environments. However,
+there have been early-stage discussions of providing this sort of
+syntactic customizability as a core feature of the Python language,
+including a draft proposal \cite{Shan20}. In addition to enabling
+\texttt{davos} to be extended for use outside of notebooks, this could
+lead to exciting new tools that, like \texttt{davos}, extend the
+Python language in useful and more secure ways.
 
@@
 
-The \texttt{davos} library supports reproducible research by providing
+The \texttt{davos} package supports reproducible research by providing
 a novel lightweight system for sharing notebook-based code. But
-perhaps the most exciting uses of the \texttt{davos} library are those
+perhaps the most exciting uses of the \texttt{davos} package are those
 that we have \textit{not} yet considered or imagined. We hope that the
@@
 means of managing project dependencies to facilitate code sharing. We
-also hope that some of the more advanced applications of our library
+also hope that some of the more advanced applications of our package
 might lead to new insights or discoveries.
@@
 JRM's \textit{Storytelling with Data} course (Winter, 2022 offering)
-who used preliminary versions of our library in several assignments.
+who used preliminary versions of our package in several assignments.
 

### 2022-11-18 paper/admin/cover_letter.tex
minor updates to cover letter

@@
 \documentclass[11pt,stdletter,orderfromtodate,sigleft]{newlfm}
+\let\geometry\relax
 \usepackage{hyperref, pxfonts, geometry}
@@
 
-\greetto{To the editors of \textit{Software X}:}
+\greetto{To the editors of \textit{SoftwareX}:}
 
@@
     reproducible notebooks} to be considered for publication as
-  an \textit{Article}.
+  an \textit{Original Software Publication}.
 
@@
   executed.  This enables researchers to share a complete reproducible
-  copy of their code within a single Jupyter notebook (.ipynb) file.
+  copy of their code within a single Jupyter notebook (\texttt{.ipynb}) file.
 
@@
   code-based research.  At one end of this continuum, ``lightweight''
-  approaches entail simply sharing raw code (e.g., plain-text python
-  scripts) or Jupyter notebooks (e.g., JSON files that comprise a mix
+  approaches entail simply sharing raw code (i.e., plain-text Python
+  scripts) or Jupyter notebooks (which can contain a mix
   of text, code, and embedded media).  These lightweight solutions
@@
  may fail to run entirely.  And when the \textit{versions} of a
- project's dependencies differ across the original author's system and
+ project's dependencies differ between the original author's system and
  the end user's system, shared code may (at worst) behave in
@@
  simulating or replicating, to varying depths, the original computing
- environment that the shared code was developed for.  For example,
+ environment in which the shared code was developed.  For example,
  virtual environments, containerized systems, and virtual machines
@@
  they are often effort- and/or resource-intensive, since they require
- installing additional tools (e.g., Anaconda, Docker, machine
- emulators, etc.) and
+ installing and mastering additional tools (e.g., Anaconda, Docker, machine
+ emulators, etc.), as well as writing and distributing additional
  configuration files (e.g., environment configuration files,
- Dockerfiles, system images, etc.), alongside the to-be-shared code
- itself.
+ Dockerfiles, system images, etc.), in order to share and run reproducible code.
 
@@
  Thank you for considering our manuscript, and we
- hope you will find it suitable for publication in \textit{Software
-   X}.
+ hope you will find it suitable for publication in \textit{SoftwareX}.
 

### 2022-11-18 paper/main.tex
fixed GRRM citation, updated Fig 2 caption, \citep -> \cite, add non-breaking spaces before \cite and \ref

@@
 referred to as ``the Onion Knight" from the series \textit{A Song of
-  Ice and Fire} by George R. R. Martin~\citep{Mart12}.  The
+  Ice and Fire} by George R. R. Martin~\cite{Mart98}.  The
 \texttt{smuggle} keyword-like operator implemented in \texttt{davos}
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The \texttt{davos} package
-  comprises two interdependent subpackages.  The \texttt{davos.core}
+\caption{\small \textbf{Package structure.} The \texttt{davos} package (orange)
+  comprises two interdependent subpackages (purple).  The \texttt{davos.core}
   subpackage includes modules for parsing \texttt{smuggle} statements
@@
   support the core functionality across different notebook-based
-  environments.  Individual \texttt{.py} files are represented by lime
+  environments.  Individual modules (i.e., \texttt{.py} files) are represented by lime
   rounded rectangles, and arrows denote dependencies (each arrow
-  points to a file that imports objects defined or specified at the
+  points to a module that imports objects defined in the module at the
   arrow's source).}
@@
 and subsequently loading it into the namespace. This process is
-outlined in Figure \ref{fig:flow-chart}. Because the
+outlined in Figure~\ref{fig:flow-chart}. Because the
 \texttt{smuggle()} function is defined in the notebook namespace, it
@@
 instance converts text data to an array of word counts.  Second, the
-word counts are passed to a topic model~\citep{BleiEtal03} using a
+word counts are passed to a topic model~\cite{BleiEtal03} using a
 pretrained \texttt{LatentDirichletAllocation} instance.
@@
 syntactic customizability as a core feature of the Python language,
-including a draft proposal \cite{Shan20}. In addition to enabling
+including a draft proposal~\cite{Shan20}. In addition to enabling
 \texttt{davos} to be extended for use outside of notebooks, this could

### 2022-11-18 paper/main.tex
add %pip install davos to beginning of Fig 4, update line numbers throughout text

@@
 
-After importing \texttt{davos} (line 1), we first smuggle two
+After installing and importing \texttt{davos} (lines 1--2), we first smuggle two
 utilities for interacting with local files in the code below. The
-\texttt{smuggle} statement in line 3 loads the \texttt{is\_file()}
+\texttt{smuggle} statement in line 4 loads the \texttt{is\_file()}
 function from the Python standard library's \texttt{os.path}
@@
 \texttt{import} statement and does not need or benefit from an onion
-comment. Line 4 loads the \texttt{joblib} package~\cite{Varo10},
+comment. Line 5 loads the \texttt{joblib} package~\cite{Varo10},
 installing it first, if necessary. Since \texttt{joblib}'s I/O
@@
 \textit{future} release might introduce some breaking change.  The
-onion comment in line 4 helps ensure the analysis notebook continues
+onion comment in line 5 helps ensure the analysis notebook continues
 to run properly in the future, by limiting allowable versions to those
@@
 \end{center}
-Line 6 then uses the \texttt{davos.config} object to enable
+Line 7 then uses the \texttt{davos.config} object to enable
 \texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next
@@
 \texttt{pandas} prior to 0.25.0), then we would not be able to load in
-that object with newer versions of \texttt{pandas}.  Line 10 ensures
+that object with newer versions of \texttt{pandas}.  Line 11 ensures
 that an older version of \texttt{pandas} will be imported, enabling
-the data to be read in (and, in line 12, saved out to a \texttt{.csv}
+the data to be read in (and, in line 13, saved out to a \texttt{.csv}
 file, which is compatible with newer versions of \texttt{pandas}).
@@
 of the package, we can take advantage of those newer changes using a
-new \texttt{smuggle} statement and onion comment on line 14 (which
+new \texttt{smuggle} statement and onion comment on line 15 (which
 specifies that version 1.3.5 should be imported).  Since
 \texttt{pandas} had already been imported into the current workspace
-(on line 10), the runtime must be restarted in order to gain access to
+(on line 11), the runtime must be restarted in order to gain access to
 the newer version of \texttt{pandas}.  The \texttt{.auto\_rerun} flag
-set on line 6 enables this process to happen automatically, and saving
-out the dataset to a \texttt{.csv} file in lines 9--12 ensures that
+set on line 7 enables this process to happen automatically, and saving
+out the dataset to a \texttt{.csv} file in lines 10--13 ensures that
 the older version of \texttt{pandas} does not need to be reinstalled.
 
-Next, line 16 uses the \texttt{davos.configure()} function to disable
+Next, line 17 uses the \texttt{davos.configure()} function to disable
 the \texttt{auto\_rerun} option and simultaneously enable two other
 options: \texttt{suppress\_stdout} and \texttt{noninteractive}. With
-these options enabled, lines 17--18 \texttt{smuggle}
+these options enabled, lines 18--19 \texttt{smuggle}
 \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful end-to-end platform
@@
 \texttt{UMAP}~\cite{McInEtal18b}, a package that implements a family
-of related manifold learning techniques. The onion comment in line 18
+of related manifold learning techniques. The onion comment in line 19
 also specifies that \texttt{UMAP} should be installed with the
@@
 these are not already installed in the user's environment, lines
-17--18 could take several minutes to run.  Enabling the
+18--19 could take several minutes to run.  Enabling the
 \texttt{noninteractive} option ensures that the installation will
@@
 
-After re-enabling these two options (line 19), we next smuggle
+After re-enabling these two options (line 20), we next smuggle
 specific versions of three plotting packages:
 \texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and
-\texttt{Quail}~\cite{HeusEtal17} (lines 21--23). Because the first two
+\texttt{Quail}~\cite{HeusEtal17} (lines 22--24). Because the first two
 are requirements of \texttt{UMAP}'s optional ``plot'' feature, they
-will have already been installed by line 18, though possibly as
+will have already been installed by line 19, though possibly as
 different versions than those specified in the onion comments on lines
-21 and 22. If the installed and specified versions are the same, these
+22 and 23. If the installed and specified versions are the same, these
 \texttt{smuggle} statements will function like standard \texttt{import}
@@
 \end{center}
-Line 23 uses an onion comment to specify that \texttt{Quail} should be
+Line 24 uses an onion comment to specify that \texttt{Quail} should be
 installed directly from a specific GitHub commit (\texttt{6c847a4}).
@@
 
-In lines 25--28, we demonstrate another aspect of \texttt{davos}'s
+In lines 26--29, we demonstrate another aspect of \texttt{davos}'s
 functionality that supports more advanced installation scenarios.  The
@@
 interchangeable IPython kernels.  To accomodate this multi-environment
-scenario, on lines 25 and 27 we control which environments each
+scenario, on lines 26 and 28 we control which environments each
 package should be installed to.  Once these two packages are installed
@@
 
-Next, we load in the reformatted dataset (line 32) and pre-trained
-model (line 34) that we wish to use in our analysis.  In our
+Next, we load in the reformatted dataset (line 33) and pre-trained
+model (line 35) that we wish to use in our analysis.  In our
 hypothetical example, we can suppose that the model was provided as a
@@
 \texttt{LatentDirichletAllocation} class is defined in
-\texttt{sklearn.decomposition.\_lda}.  However, in version
+\texttt{sklearn.decomposition.online\_lda}.  However, in version
 0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
-versions 0.22.1 and higher, the name was reverted back to
-\texttt{\_lda}.
+version 0.22.1, it was again renamed to \texttt{\_lda}.
 
-In order to correctly load the model that includes the pretrained
-\texttt{LatentDirichletAllocation} instance, in line 33, we first
+In order to correctly load the model that includes the pre-trained
+\texttt{LatentDirichletAllocation} instance, in line 34, we first
 smuggle a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
@@
 the model is loaded and reconstructed in memory from a compatible
-package version (line 34), we upgrade to a newer version of
-\texttt{scikit-learn} in line 35.  Taken together, the code in
+package version (line 35), we upgrade to a newer version of
+\texttt{scikit-learn} in line 36.  Taken together, the code in
 Figure~\ref{fig:illustrative-example} shows how \texttt{davos} can

### 2022-11-20 paper/main.tex
edits through section 2

@@
 \usepackage{breakurl}
-\usepackage[htt]{hyphenat}
 \usepackage{placeins}
-\newcommand{\comment}[1]{}
 \usepackage{geometry}
-\geometry{letterpaper,left=1in,right=1in,top=1in,bottom=1in,headsep=0pt,footskip=0pt}
+\geometry{left=1in,right=1in,top=1in,bottom=1in,headsep=0pt}
 
@@
 script or package, manually tracking down those dependencies can
-impose a substantial burden on the user and creates room for mistakes
+impose a substantial burden on the user and create room for mistakes
 and inconsistencies. Further, when dependency versions are left
@@
 (and installing, as needed) a complete set of Python dependencies,
-including package versions.
+including specific package versions.
 
@@
   Ice and Fire} by George R. R. Martin~\cite{Mart98}.  The
-\texttt{smuggle} keyword-like operator implemented in \texttt{davos}
+\texttt{smuggle} keyword provided by \texttt{davos}
 is a play on Python's \texttt{import} keyword: whereas importing can
-bring a package into the Python workspace within the existing rules
+load a package into the Python workspace within the existing rules
 and frameworks provided by the Python language, ``smuggling'' provides
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The \texttt{davos} package (orange)
-  comprises two interdependent subpackages (purple).  The \texttt{davos.core}
+\caption{\small \textbf{Package structure.} The \texttt{davos} package
+  comprises two interdependent subpackages.  The \texttt{davos.core}
   subpackage includes modules for parsing \texttt{smuggle} statements
@@
 \texttt{davos.core}, comprises a set of modules that
-implement\comment{provide?} the bulk of the package's core
+implement the bulk of the package's core
 functionality, including pipelines for installing and validating
@@
 \texttt{davos}'s behavior (see Section~\ref{subsec:config}). However,
-certain critical\comment{other important} aspects of this
+certain critical aspects of this
 functionality require (often substantially) different implementations
@@
 comments from being used as a vehicle for shell injection attacks,
-this design provides the user with additional control over which
-packages are imported. For example, each of the
-\mbox{\texttt{-I}/\texttt{--ignore-installed}},
-\texttt{-U}/\texttt{--upgrade}, and \texttt{--force-reinstall} flags
-will cause \texttt{davos} to skip searching for a smuggled package
-locally before installing a new copy:
+this enables \texttt{davos} to adapt its behavior based on how particular
+flags will affect the behavior of the installer program. For example, if an
+onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
+\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag,
+\texttt{davos} will not bother checking for a local copy of the smuggled
+package before installing a new one:
 \begin{center}
@@
 singleton) exposes configurable options as attributes that can be
-modified, checked at runtime, or displayed (see
-Sec.~\ref{sec:illustrative-example} for an illustrative example or
+modified, displayed in the notebook, or checked programmatically at runtime
+(see Sec.~\ref{sec:illustrative-example} for an illustrative example or
 Sec.~\ref{subsec:implementation} for implementation details and
@@
   that dynamically link C or C++ objects to the Python interpreter,
-  and if the code that generates those objects was changed between the
+  and the code that generates those objects was changed between the
   previously imported and to-be-smuggled versions.  If this attribute
@@
   \texttt{True} (default: \texttt{False}), \texttt{davos} suppresses
-  printed (console) outputs from itself and the installer program.
+  printed (console) outputs from both itself and the installer program.
   This can be useful when smuggling packages that need to install many
   dependencies and/or generate extensive output. However, if the installer
-  program throws an error, both the stdout and stderr streams will still be
-  displayed along with a stack trace.
+  program throws an error, both its stdout and stderr streams will be
+  displayed alongside the Python traceback to allow for debugging.
 \end{itemize}
@@
 Although \texttt{davos} is designed to \textit{appear} to add a new
-Python keyword to a notebook's vocabulary, this illusion is actually a
-consequence of several ``hacks'' that make use of the IPython backend
-for processing and executing notebook code.  Specifically, when
-\texttt{davos} is first imported, or when it is activated after being
-set to an inactive state, two actions are triggered.  First, the
+keyword to Python's vocabulary, this illusion is actually created through
+several ``hacks'' that make use of the notebook's IPython backend
+for processing and executing users' code.  Specifically, when
+\texttt{davos} is first imported, or when it is activated after having been
+set to an inactive state, two actions are triggered:  First, the
 \texttt{smuggle()} function is injected into the IPython user

### 2022-11-20 paper/main.tex
Section -> Sec. in parens

@@
 packages, custom parsers for the \texttt{smuggle} statement (see
-Section~\ref{subsec:smuggle}) and onion comment (see
-Section~\ref{subsec:onion}), and a runtime interface for configuring
-\texttt{davos}'s behavior (see Section~\ref{subsec:config}). However,
+Sec.~\ref{subsec:smuggle}) and onion comment (see
+Sec.~\ref{subsec:onion}), and a runtime interface for configuring
+\texttt{davos}'s behavior (see Sec.~\ref{subsec:config}). However,
 certain critical aspects of this
@@
 an additional Python keyword: ``\texttt{smuggle}'' (see
-Section~\ref{subsec:implementation} for details on how this works).
+Sec.~\ref{subsec:implementation} for details on how this works).
 The \texttt{smuggle} keyword-like object can be used as a drop-in
@@
 \texttt{davos}'s non-interactive mode (see
-Section~\ref{subsec:config}), and installing a smuggled package into a
+Sec.~\ref{subsec:config}), and installing a smuggled package into a
 custom directory (\texttt{<dir>}) using the \texttt{--target <dir>}
@@
 imported during the same interpreter session (see
-Section~\ref{subsec:config}).
+Sec.~\ref{subsec:config}).
 \begin{center}
@@
 interpreter session (e.g., see
-Section~\ref{sec:illustrative-example}). This could be useful in cases
+Sec.~\ref{sec:illustrative-example} and Fig.~\ref{fig:illustrative-example}). This could be useful in cases
 where specific features are added or removed from a package across

### 2022-11-21 paper/main.tex
WIP fixes to section 3

@@
 
-Across different versions of a given package, functions may be
-changed, depreciated, added, or renamed.  In addition to changing the
-behaviors of active computations, saved objects created using one
-version of a package may be incompatible with another version of the
+Across different versions of a given package, particular modules, functions, and other objects 
+may be updated, removed, renamed, or otherwise altered in some manner.  In addition to changing the
+behaviors of active computations, these changes can render saved objects created using one
+version of a package incompatible with other versions of the
 same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
-package prior to version 0.25.0 included the \texttt{Panel} datatype
-for storing 3-dimensional arrays.  Since version 0.20.0,
-however, the \texttt{Panel} datatype has been depreciated, and the
-datatype was removed entirely in version 0.25.0.  If one had saved a dataset in a
-\texttt{Panel} object (created using an older version of
-\texttt{pandas}), e.g., by serializing the \texttt{Panel} and saving
-it to disk using \texttt{pickle}, that dataset could not be read by
-any version of \texttt{pandas} from 0.25.0 or beyond.  These
-incompatibilities are not limited solely to traditional forms of data.
+library used to include the \texttt{Panel} data structure for storing 3-dimensional arrays.  
+Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in 
+version 0.25.0, it was removed entirely. If a user had a dataset stored in a \texttt{Panel} object
+(created using an older version of \texttt{pandas}) and saved it to their disk (e.g., for later reuse
+or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol, 
+that dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
+incompatibilities are also not limited solely to traditional forms of data.
 For example, saved model states and other objects may reference
-functions, attributes, classes, and other objects that are not present
+modules, functions, attributes, classes, or other objects that may not be identical (or even present)
 across all versions of their associated package.
@@
 each package are used in different parts of the notebook.  The example
-shows how data and a model saved using since-depreciated components of
+shows how a dataset and model that require now-incompatible components of
 the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
-packages may be loaded in (using older versions of each package) and
-manipulated or analyzed (using more recent versions of each package).
+packages may be loaded in (using older versions of each package) and used
+alongside more recent versions of each package that provide new and improved functionality.
+When included at the top of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
+ensures that these objects will be loaded successfully and analyzed using the same set
+of package versions, no matter when or by whom the notebook is run.
 
@@
 onion comment in line 5 helps ensure the analysis notebook continues
-to run properly in the future, by limiting allowable versions to those
+to run properly in the future by limiting allowable versions to those
 already released when the code was written:
@@
 \end{center}
-Setting the \texttt{auto\_rerun} attribute to \texttt{True} also
-benefits the (potential) installation of \texttt{pandas} on the next
+Setting the \texttt{auto\_rerun} attribute to \texttt{True} is particularly useful
+for the installation of \texttt{pandas} in the next
 lines:
@@
 If we suppose that the data contained in \texttt{data-old.pkl} is
-stored in a \texttt{Panel} object (i.e., created in a version of
-\texttt{pandas} prior to 0.25.0), then we would not be able to load in
-that object with newer versions of \texttt{pandas}.  Line 11 ensures
+stored in a \texttt{Panel} object, then we must use a version of 
+\texttt{pandas} prior to 0.25.0 (i.e., the version in which the \texttt{Panel} 
+class was removed) to be able to load it in. Line 11 ensures
 that an older version of \texttt{pandas} will be imported, enabling

### 2022-11-21 paper/main.tex
edits and fixes up through line 315

@@
 Setting the \texttt{auto\_rerun} attribute to \texttt{True} is particularly useful
-for the installation of \texttt{pandas} in the next
+for managing the installation of \texttt{pandas} in the next
 lines:
@@
 that an older version of \texttt{pandas} will be imported, enabling
-the data to be read in (and, in line 13, saved out to a \texttt{.csv}
+the data to be read in (and, in line 13, written to a CSV
 file, which is compatible with newer versions of \texttt{pandas}).
@@
 Newer versions of \texttt{pandas} have brought substantial
-performance improvements, added new functionality, fixed bugs, etc.
+improvements including better performance, bug fixes, and additional functionality.
 Although the original dataset had to be read in using an older version
-of the package, we can take advantage of those newer changes using a
-new \texttt{smuggle} statement and onion comment on line 15 (which
-specifies that version 1.3.5 should be imported).  Since
-\texttt{pandas} had already been imported into the current workspace
-(on line 11), the runtime must be restarted in order to gain access to
-the newer version of \texttt{pandas}.  The \texttt{.auto\_rerun} flag
-set on line 7 enables this process to happen automatically, and saving
-out the dataset to a \texttt{.csv} file in lines 10--13 ensures that
+of the package, we can take advantage of these more recent updates 
+by smuggling \texttt{pandas} a second time on line 15 (whose onion comment
+specifies that version 1.3.5 should be installed and loaded).  Since
+a different version of \texttt{pandas} had already been loaded by the Python interpreter
+(on line 11), the notebook kernel must be restarted in order to replace the old 
+version's custom C extensions with those from the new version.  The \texttt{auto\_rerun} flag
+set on line 7 enables \texttt{davos} to trigger this process automatically so that
+the code can continue running without user intervention, and converting
+the dataset to a CSV file in lines 10--13 ensures that
 the older version of \texttt{pandas} does not need to be reinstalled.
@@
 continue automatically without user input during that time.  Enabling
-\texttt{suppress\_stdout} also suppresses console outputs from the
-installer that might otherwise distract from other more important outputs.
+\texttt{suppress\_stdout} also suppresses console outputs while installing 
+these packages and their many dependencies to prevent other potentially important outputs from being buried.
 \begin{center}
@@
 installed directly from a specific GitHub commit (\texttt{6c847a4}).
-This ability to install packages directly from GitHub repositories can
-enable developers to use forked or modified versions of other
+This ability to load packages directly from GitHub repositories can
+enable developers to more easily use forked or modified versions of other
 packages in their notebooks, even if those versions have not been
@@
 \texttt{ipywidgets}~\cite{FredEtal15} package provides an API for
-creating widgets, and the \texttt{widgetsnbextension} package provides
+creating various JavaScript widgets with Python code, and the \texttt{widgetsnbextension} package provides
 the machinery needed by the notebook frontend to display them.
@@
 \texttt{widgetsnbextension} must be installed in the environment that
-houses the Jupyter notebook server. In standard setups, these two
+houses the Jupyter notebook server. In many basic setups, these two
 environments are the same.  However, a common ``advanced'' approach
@@
 interchangeable IPython kernels.  To accomodate this multi-environment
-scenario, on lines 26 and 28 we control which environments each
+scenario, on lines 26 and 28, we use the \texttt{pip\_executable} option to control which environments each
 package should be installed to.  Once these two packages are installed
@@
 Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported
-to enable aesthetically pleasing progress bars that are displayed via
+to enable more aesthetically pleasing progress bars that are displayed via
 \texttt{ipywidgets}, if that package is installed and
@@
 the \texttt{Pipeline} object was created using \texttt{scikit-learn}
-v0.21.3).  In that version of \texttt{scikit-learn}, the
-\texttt{LatentDirichletAllocation} class is defined in
+v0.21.3.  In that version of \texttt{scikit-learn}, the
+\texttt{LatentDirichletAllocation} class was defined in
 \texttt{sklearn.decomposition.online\_lda}.  However, in version
@@
 In order to correctly load the model that includes the pre-trained
-\texttt{LatentDirichletAllocation} instance, in line 34, we first
-smuggle a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
+\texttt{LatentDirichlet\-Allocation} instance, in line 34, we first
+\texttt{smuggle} a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
 before the first time the relevant module's name was changed).  Once

### 2022-11-21 paper/main.tex
tiny syntax update to main.tex

@@
 \texttt{davos} is first imported, or when it is activated after having been
-set to an inactive state, two actions are triggered:  First, the
+set to an inactive state, two actions are triggered.  First, the
 \texttt{smuggle()} function is injected into the IPython user
@@
 instance converts text data to an array of word counts.  Second, the
-word counts are passed to a topic model~\cite{BleiEtal03} using a
+word counts are passed to a topic model~\citep{BleiEtal03} using a
 pretrained \texttt{LatentDirichletAllocation} instance.

### 2022-11-22 paper/admin/cover_letter.tex

@@
  they are often effort- and/or resource-intensive, since they require
- installing and mastering additional tools (e.g., Anaconda, Docker, machine
+ installing and learning additional tools (e.g., Anaconda, Docker, machine
  emulators, etc.), as well as writing and distributing additional

### 2022-11-22 paper/main.tex
revert citep --> cite
re-added pickle incompatibility explanation to beginning of section 3

@@
 Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in 
-version 0.25.0, it was removed entirely. If a user had a dataset stored in a \texttt{Panel} object
-(created using an older version of \texttt{pandas}) and saved it to their disk (e.g., for later reuse
-or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol, 
-that dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
+version 0.25.0, it was removed entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
+(created using an older version of \texttt{pandas}) and had saved it to their disk (e.g., for later reuse
+or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
+The \texttt{pickle} protocol is a popular choice for persisting data in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat:
+In order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, its class must be defined in and importable from the same module as when it was saved.
+Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
 incompatibilities are also not limited solely to traditional forms of data.

### 2022-11-22 paper/main.tex
ensure fig 4 comes before partial snippets
minor wording changes

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{figs/illustrative_example}
+\caption{\small \textbf{Example use case for \texttt{davos}.}
+  Snippets from this example are also excerpted in the main text of
+  Section~\ref{sec:illustrative-example}.}
+\label{fig:illustrative-example}
+\end{figure}
+
 Across different versions of a given package, particular modules, functions, and other objects
@@
 or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
-The \texttt{pickle} protocol is a popular choice for persisting data in Python, allowing users to save, share, and load arbitrary objects, though with an important caveat:
-In order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, its class must be defined in and importable from the same module as when it was saved.
+The \texttt{pickle} protocol is a popular, built-in method of persisting data in Python, allowing users to save, share, and load arbitrary objects.
+However, in order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, the object's class must be defined in and importable from the same module as when it was saved.
 Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
@@
 across all versions of their associated package.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for \texttt{davos}.}
-  Snippets from this example are also excerpted in the main text of
-  Section~\ref{sec:illustrative-example}.}
-\label{fig:illustrative-example}
-\end{figure}
 
@@
 If we suppose that the data contained in \texttt{data-old.pkl} is
-stored in a \texttt{Panel} object, then we must use a version of 
+stored in a pickled \texttt{Panel} object, then we must use a version of
 \texttt{pandas} prior to 0.25.0 (i.e., the version in which the \texttt{Panel}
@@
 the data to be read in (and, in line 13, written to a CSV
-file, which is compatible with newer versions of \texttt{pandas}).
+file, which is compatible with newer \texttt{pandas} versions).
 

### 2022-11-22 paper/main.tex
minor tweaks to conclusion and contributions

@@
 The \texttt{davos} package supports reproducible research by providing
-a novel lightweight system for sharing notebook-based code. But
+a novel, lightweight system for sharing notebook-based code. But
 perhaps the most exciting uses of the \texttt{davos} package are those
 that we have \textit{not} yet considered or imagined. We hope that the
-Python community will find \texttt{davos} to provide a convenient
-means of managing project dependencies to facilitate code sharing. We
+research and scientific Python communities will find \texttt{davos} to provide a convenient
+means of managing project dependencies to facilitate code sharing and collaboration. We
 also hope that some of the more advanced applications of our package
@@
 Visualization. \textbf{Jeremy R. Manning}: Conceptualization,
-Resources, Validation, Writing - Review \& Editing, Supervision,
+Resources, Validation, Writing - Review \& Editing, Visualization, Supervision,
 Funding acquisition.

### 2022-11-22 paper/main.tex
minor tweaks to metadata table

@@
 \hline
-C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, Ipykernel, PyZMQ.
-Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
+C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.
+Additional tools used for tests: pytest, Selenium, Requests, Mypy, GitHub Actions \\
 \hline
 C7 & Compilation requirements, operating environments, and
-     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
 \\

### 2022-11-23 paper/main.tex
minor typo fixes to 2.2.3

@@
 \item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
-  statements and onion comments) is enabled (\texttt{True}) or
-  disabled (\texttt{False}).  When \texttt{davos} is first imported),
+  statements and onion comments is enabled (\texttt{True}) or
+  disabled (\texttt{False}).  When \texttt{davos} is first imported,
   the \texttt{.active} attribute is set to \texttt{True}.
@@
 \bibliographystyle{elsarticle-num}
-\bibliography{CDL-bibliography/cdl}
+\bibliography{main}
 

### 2022-11-23 paper/main.tex

@@
 \end{center}
-Onion comments can also be used to smuggle specific VCS references
+Onion comments can also be used to \texttt{smuggle} specific VCS references
 (e.g., Git~\cite{TorvHama05} branches, commits, tags, etc.):
@@
   the notebook kernel and rerun all code up to (and including) the
-  current \texttt{smuggle} statement. If \texttt{False} (the default),
+  current \texttt{smuggle} statement. If set to \texttt{False} (the default),
   \texttt{davos} will instead issue a warning, pause execution, and
@@
 
-\item \texttt{.confirm\_install}: If \texttt{True} (default:
+\item \texttt{.confirm\_install}: If set to \texttt{True} (default:
   \texttt{False}), \texttt{davos} will require user confirmation
@@
   \texttt{confirm\_install} option is set to \texttt{False}.  If
-  \texttt{auto\_rerun} is \texttt{False} while in non-interactive
+  \texttt{auto\_rerun} is set to \texttt{False} while in non-interactive
   mode, \texttt{davos} will raise an exception if a smuggled package
@@
 Across different versions of a given package, particular modules, functions, and other objects
-may be updated, removed, renamed, or otherwise altered in some manner.  In addition to changing the
+may be updated, removed, renamed, or otherwise altered.  In addition to changing the
 behaviors of active computations, these changes can render saved objects created using one
@@
 or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
-The \texttt{pickle} protocol is a popular, built-in method of persisting data in Python, allowing users to save, share, and load arbitrary objects.
-However, in order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' object, the object's class must be defined in and importable from the same module as when it was saved.
+The \texttt{pickle} protocol is a popular built-in method of persisting data in Python, allowing users to save, share, and load arbitrary objects.
+However, in order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved) object, the object's class must be defined in and importable from the same module as when it was saved.
 Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
@@
 
-After installing and importing \texttt{davos} (lines 1--2), we first smuggle two
+After installing and importing \texttt{davos} (lines 1--2), we first \texttt{smuggle} two
 utilities for interacting with local files in the code below. The
@@
 
-After re-enabling these two options (line 20), we next smuggle
+After re-enabling these two options (line 20), we next \texttt{smuggle}
 specific versions of three plotting packages:
@@
 package should be installed to.  Once these two packages are installed
-and imported, line 30 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which
+and imported, line 31 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which
 display progress bars to provide status updates for running code. In

### 2023-04-14 paper/main.tex
working on text edits to address reviewer comments

@@
 unspecified, replicating the original computing environment becomes
-difficult or impossible.
+difficult or impossible~\citep{PimeEtal19}.
 
@@
 
-We designed \texttt{davos} to occupy a ``sweet spot'' between these
-extremes.  \texttt{davos} is a notebook-installable package that adds
-functionality to the default notebook experience. Like standard
-Jupyter notebooks, \texttt{davos}-enhanced notebooks allow researchers
-to include text, executable code, and media within a single file. No
-further setup or installation is required, beyond what is needed to
-run standard Jupyter notebooks. And like virtual environments,
-\texttt{davos} provides a convenient mechanism for fully specifying
-(and installing, as needed) a complete set of Python dependencies,
-including specific package versions.
+We designed \texttt{davos} to occupy a ``sweet spot'' between these extremes.
+\texttt{davos} is a notebook-installable package that adds functionality to the
+default notebook experience. Like standard Jupyter notebooks,
+\texttt{davos}-enhanced notebooks allow researchers to include text, executable
+code, and media within a single file. No further setup or installation is
+required from the user, beyond what is needed to run standard Jupyter
+notebooks. And like virtual environments, \texttt{davos} provides a convenient
+mechanism for fully specifying (and installing, as needed) a complete set of
+Python dependencies, including specific package versions, which are contained
+and isolated from the rest of the user's system.
 
@@
 
+Installing new packages in a notebook using standard approaches (e.g., system
+commmands) affect the runtime environment. This could lead to undesired
+behaviors. For example, running a notebook that installs new packages in the
+user's primary system environment might alter their main system installation
+and/or containerized environment in unexpected ways (e.g., changing package
+versions, causing conflicts with other packages, etc.). To protect against
+undesired changes to the runtime environment, \texttt{davos} incorporates its
+own virtual environment for managing packages it installs. When \texttt{davos}
+is imported, a new virtual environment (folder) is created automatically. The
+folder's name may be customized to support multi-notebook projects. Any
+\texttt{smuggle}d packages that were not available in the notebook's runtime
+environment are installed to the current project folder. The runtime
+environment remains unaffected by \texttt{davos}'s behavior (see
+Sec.~\ref{subsec:project}).
+
 \subsubsection{The onion comment}\label{subsec:onion}
@@
 For greater control over the behavior of \texttt{smuggle} statements,
-\texttt{davos} defines an additional construct called the ``onion
-comment.'' An onion comment is a special type of inline comment that
-may be placed on a line containing a \texttt{smuggle} statement to
-customize how \texttt{davos} searches for the smuggled package locally
-and, if necessary, downloads and installs it. Onion comments follow a
-simple format based on the ``type comment'' syntax introduced in PEP
-484~\cite{vanREtal14}, and are designed to make managing packages with
-\texttt{davos} intuitive and familiar. To construct an onion comment,
-users provide the name of the installer program (e.g., \texttt{pip})
-and the same arguments one would use to manually install the package
-as desired via the command line:
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet1}
-\end{center}
-Occasionally, a package's distribution name (i.e., the name used when
-installing it) may differ from its top-level module name (i.e., the
-name used when importing it). In such cases, an onion comment may be
-used to ensure that \texttt{davos} installs the proper package if it
-cannot be found locally:
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet2}
-\end{center}
-Because onion comments may be constructed to specify any aspect of the
-installer's behavior, they provide a mechanism for precisely
-controlling how, where, and when smuggled packages are installed.
-Critically, if an onion comment includes a version
-specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the
-version of the package loaded into the notebook matches the specific
-version requested, or satisfies the given version constraints. If the
-smuggled package exists locally, \texttt{davos} will extract its
-version information from its metadata and compare it to the specifier
-provided. If the two are incompatible (or no local installation is
-found), \texttt{davos} will download, install, and load a suitable
-version of the package instead:
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet3}
-\end{center}
-Onion comments can also be used to \texttt{smuggle} specific VCS references
-(e.g., Git~\cite{TorvHama05} branches, commits, tags, etc.):
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet4}
-\end{center}
-\texttt{davos} processes onion comments internally before forwarding
-arguments to the installer program. In addition to preventing onion
-comments from being used as a vehicle for shell injection attacks,
-this enables \texttt{davos} to adapt its behavior based on how particular
-flags will affect the behavior of the installer program. For example, if an
-onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
-\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag,
-\texttt{davos} will not bother checking for a local copy of the smuggled
-package before installing a new one:
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet5}
-\end{center}
-Similarly, the \texttt{--no-input} flag will temporarily enable
-\texttt{davos}'s non-interactive mode (see
-Sec.~\ref{subsec:config}), and installing a smuggled package into a
+\texttt{davos} defines an additional construct called the ``onion comment.'' An
+onion comment is a special type of inline comment that may be placed on a line
+containing a \texttt{smuggle} statement to customize how \texttt{davos}
+searches for the smuggled package locally and, if necessary, downloads and
+installs it. Onion comments follow a simple format based on the ``type
+comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to
+make managing packages with \texttt{davos} intuitive and familiar. To construct
+an onion comment, users provide the name of the installer program (e.g.,
+\texttt{pip}) and the same arguments one would use to manually install the
+package as desired via the command line: \begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet1} \end{center} Occasionally,
+a package's distribution name (i.e., the name used when installing it) may
+differ from its top-level module name (i.e., the name used when importing it).
+In such cases, an onion comment may be used to ensure that \texttt{davos}
+installs the proper package if it cannot be found locally: \begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet2} \end{center} Because onion
+comments may be constructed to specify any aspect of the installer's behavior,
+they provide a mechanism for precisely controlling how, where, and when
+smuggled packages are installed. Critically, if an onion comment includes a
+version specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the
+version of the package loaded into the notebook matches the specific version
+requested, or satisfies the given version constraints. If the smuggled package
+exists locally, \texttt{davos} will extract its version information from its
+metadata and compare it to the specifier provided. If the two are incompatible
+(or no local installation is found), \texttt{davos} will download, install, and
+load a suitable version of the package instead: \begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet3} \end{center} Onion
+comments can also be used to \texttt{smuggle} specific VCS references (e.g.,
+Git~\cite{TorvHama05} branches, commits, tags, etc.): \begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet4} \end{center}
+\texttt{davos} processes onion comments internally before forwarding arguments
+to the installer program. In addition to preventing onion comments from being
+used as a vehicle for shell injection attacks, this enables \texttt{davos} to
+adapt its behavior based on how particular flags will affect the behavior of
+the installer program. For example, if an onion comment contains either the
+\texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, or
+\texttt{--force-reinstall} flag, \texttt{davos} will not bother checking for a
+local copy of the smuggled package before installing a new one: \begin{center}
+\includegraphics[width=0.9\textwidth]{figs/snippet5} \end{center} Similarly,
+the \texttt{--no-input} flag will temporarily enable \texttt{davos}'s
+non-interactive mode (see Sec.~\ref{subsec:config}). Installation flags that
+affect the user's system outside of the current notebook are disabled by
+default (see Sec.~\ref{subsec:projects}).
+
+, and installing a smuggled package into a
 custom directory (\texttt{<dir>}) using the \texttt{--target <dir>}
@@
 
+\subsubsection{Projects}\label{subsec:projects}
+
+Because \texttt{davos} can install new packages, running the code in a
+\texttt{davos}-enhanced notebook might (in principle) affect the behavior of
+\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
+altering which packages are installed in the runtime environment. This could
+lead to undesired consequences. For example, suppose Person A develops a
+notebook (Notebook A) for their research project. We will assume that Notebook
+A does not use \texttt{davos} to manage project dependencies.  If Person A
+runs a \texttt{davos}-enhanced Notebook B, e.g., sent by another developer,
+might this unexpectedly affect the behavior of Notebook A?
+
+We implemented a ``project'' system in \texttt{davos} to protect against the
+above scenario. By default, importing \texttt{davos} creates a new project
+folder in the user's home directory (contained within a hidden \texttt{.davos}
+folder). The default project name is computed to uniquely identify each
+notebook according to its filename and path. Any packages that were not
+originally available in the notebook's runtime environment are installed to the
+notebook's project directory. When external libraries are \texttt{smuggle}d,
+\texttt{davos} temporally appends the current project directory to the search
+path. Because the user's system path remains unchanged, and because none of the
+runtime environment's packages are altered, the user's system and runtime
+environment remain unaffected (aside from installing the \texttt{davos} package
+itself to the runtime environment).
+
+Each notebook's project may be customized by setting \texttt{davos.project} to
+any string that can be used as a valid folder name in the user's operating
+system. By customizing the project name, users can build multi-notebook
+projects that share the same core set of dependencies without needing to
+duplicate each package for each notebook in the project.
+
+Finally, if the user \textit{does} wish to modify their runtime environment,
+this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
+will cause any packages installed by \texttt{davos} to affect the user's
+runtime environment.  This is generally not recommended, as it can lead to
+unintended consequences for other code that shares the runtime environment.
+
 \subsection{Implementation details}\label{subsec:implementation}
@@
 
-Across different versions of a given package, particular modules, functions, and other objects
-may be updated, removed, renamed, or otherwise altered.  In addition to changing the
-behaviors of active computations, these changes can render saved objects created using one
-version of a package incompatible with other versions of the
-same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
-library used to include the \texttt{Panel} data structure for storing 3-dimensional arrays.
-Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in
-version 0.25.0, it was removed entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
-(created using an older version of \texttt{pandas}) and had saved it to their disk (e.g., for later reuse
-or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
-The \texttt{pickle} protocol is a popular built-in method of persisting data in Python, allowing users to save, share, and load arbitrary objects.
-However, in order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved) object, the object's class must be defined in and importable from the same module as when it was saved.
-Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
-incompatibilities are also not limited solely to traditional forms of data.
-For example, saved model states and other objects may reference
-modules, functions, attributes, classes, or other objects that may not be identical (or even present)
-across all versions of their associated package.
+Across different versions of a given package, particular modules, functions,
+and other objects may be updated, removed, renamed, or otherwise altered. In
+addition to changing the behaviors of active computations, these changes can
+render saved objects created using one version of a package incompatible with
+other versions of the same package. For example, the popular
+\texttt{pandas}~\cite{McKi10} library used to include the \texttt{Panel} data
+structure for storing 3-dimensional arrays. Since version 0.20.0, however, the
+\texttt{Panel} class has been deprecated, and in version 0.25.0, it was removed
+entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
+(created using an older version of \texttt{pandas}) and had saved it to their
+disk (e.g., for later reuse or to share with other users) by serializing the
+\texttt{Panel} with Python's \texttt{pickle} protocol. The \texttt{pickle}
+protocol is a popular built-in method of persisting data in Python, allowing
+users to save, share, and load arbitrary objects. However, in order to
+successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved)
+object, the object's class must be defined in and importable from the same
+module as when it was saved. Thus, because of the \texttt{Panel} class's
+removal, the user's dataset could not be read by any version of \texttt{pandas}
+from 0.25.0 or beyond. These incompatibilities are also not limited solely to
+traditional forms of data. For example, saved model states and other objects
+may reference modules, functions, attributes, classes, or other objects that
+may not be identical (or even present) across all versions of their associated
+package.
 
-The example provided in Figure~\ref{fig:illustrative-example}
-demonstrates how the \texttt{davos} package can be used to circumvent
-these incompatibilities by carefully controlling which versions of
-each package are used in different parts of the notebook.  The example
-shows how a dataset and model that require now-incompatible components of
-the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
-packages may be loaded in (using older versions of each package) and used
-alongside more recent versions of each package that provide new and improved functionality.
-When included at the top of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
-ensures that these objects will be loaded successfully and analyzed using the same set
-of package versions, no matter when or by whom the notebook is run.
+The example provided in Figure~\ref{fig:illustrative-example} demonstrates how
+the \texttt{davos} package can be used to circumvent these incompatibilities by
+carefully controlling which versions of each package are used in different
+parts of the notebook. The example shows how a dataset and model that require
+now-incompatible components of the \texttt{pandas} and
+\texttt{scikit-learn}~\cite{PedrEtal11} packages may be loaded in (using older
+versions of each package) and used alongside more recent versions of each
+package that provide new and improved functionality. When included at the top
+of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
+ensures that these objects will be loaded successfully and analyzed using the
+same set of package versions, no matter when or by whom the notebook is run.
 
@@
 
-Newer versions of \texttt{pandas} have brought substantial
-improvements including better performance, bug fixes, and additional functionality.
-Although the original dataset had to be read in using an older version
-of the package, we can take advantage of these more recent updates
-by smuggling \texttt{pandas} a second time on line 15 (whose onion comment
-specifies that version 1.3.5 should be installed and loaded).  Since
-a different version of \texttt{pandas} had already been loaded by the Python interpreter
-(on line 11), the notebook kernel must be restarted in order to replace the old
-version's custom C extensions with those from the new version.  The \texttt{auto\_rerun} flag
-set on line 7 enables \texttt{davos} to trigger this process automatically so that
-the code can continue running without user intervention, and converting
-the dataset to a CSV file in lines 10--13 ensures that
-the older version of \texttt{pandas} does not need to be reinstalled.
+Newer versions of \texttt{pandas} have brought substantial improvements
+including better performance, bug fixes, and additional functionality. Although
+the original dataset had to be read in using an older version of the package,
+we can take advantage of these more recent updates by smuggling \texttt{pandas}
+a second time on line 15 (whose onion comment specifies that version 1.3.5
+should be installed and loaded). Since a different version of \texttt{pandas}
+had already been loaded by the Python interpreter (on line 11), the notebook
+kernel must be restarted in order to replace the old version's custom C
+extensions with those from the new version. The \texttt{auto\_rerun} flag set
+on line 7 enables \texttt{davos} to trigger this process automatically so that
+the code can continue running without user intervention, and converting the
+dataset to a CSV file in lines 10--13 ensures that the older version of
+\texttt{pandas} does not need to be reinstalled.
 
@@
 
-Since its initial release, \texttt{davos} has found use in a variety
-of applications. In addition to managing computing environments for
-multiple ongoing research studies, \texttt{davos} is being used by
-both students and instructors in programming and methods courses such
-as Storytelling with Data~\cite{Mann21d} (an open course on data
-science, visualization, and communication) and Laboratory in
-Psychological Science~\cite{Mann22} (an open course on experimental
-and statistical methods for psychology research) to simplify
-distributing lessons and submitting assignments, as well as in online
-demos such as \texttt{abstract2paper}~\cite{Mann21e} (an example
-application of GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share
-ready-to-run code that installs dependencies automatically.
+Since its initial release, \texttt{davos} has found use in a variety of
+applications. In addition to managing computing environments for multiple prior
+and ongoing research studies~\citep{MannEtal23, OwenMann23, ZimaEtal23},
+\texttt{davos} is being used by both students and instructors in programming
+and methods courses such as Storytelling with Data~\cite{Mann21d} (an open
+course on data science, visualization, and communication) and Laboratory in
+Psychological Science~\cite{Mann22} (an open course on experimental and
+statistical methods for psychology research) to simplify distributing lessons
+and submitting assignments, as well as in online demos such as
+\texttt{abstract2paper}~\cite{Mann21e} (an example application of
+GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
+dependencies automatically.
 
-Our work also has several more subtle ``advanced'' use cases and
-potential impacts. Whereas Python's built-in \texttt{import} statement
-is agnostic to packages' version information, \texttt{smuggle}
-statements (when combined with onion comments) are version-sensitive.
-And because onion comments are parsed at runtime, required packages
-and their specified versions are installed in a just-in-time
-manner. Thus, it is possible in most cases to \texttt{smuggle} a
-specific package version or revision even if a different version has
-already been loaded. This enables more complex uses that take
-advantage of multiple versions of a package within a single
-interpreter session (e.g., see
-Sec.~\ref{sec:illustrative-example} and Fig.~\ref{fig:illustrative-example}). This could be useful in cases
-where specific features are added or removed from a package across
-different versions, or in comparing the performance or functionality
-of particular features across different versions of the same package.
+Our work also has several more subtle ``advanced'' use cases and potential
+impacts. Whereas Python's built-in \texttt{import} statement is agnostic to
+packages' version information, \texttt{smuggle} statements (when combined with
+onion comments) are version-sensitive. And because onion comments are parsed at
+runtime, required packages and their specified versions are installed in a
+just-in-time manner. Thus, it is possible in most cases to \texttt{smuggle} a
+specific package version or revision even if a different version has already
+been loaded. This enables more complex uses that take advantage of multiple
+versions of a package within a single interpreter session (e.g., see
+Sec.~\ref{sec:illustrative-example} and Fig.~\ref{fig:illustrative-example}).
+This could be useful in cases where specific features are added or removed from
+a package across different versions, or in comparing the performance or
+functionality of particular features across different versions of the same
+package.
 

### 2023-04-17 paper/main.tex
added pitfalls and limitations section

@@
 
+Although existing notebooks \textit{can} incorporate system calls that install
+project requirements, handling project requirements in the general case is
+non-trivial (e.g., see Fig.~\ref{fig:flow-chart}). Further, \texttt{davos}
+incorporates its own virtual environment system that isolates
+notebook-installed packages from the runtime environment
+(Sec.~\ref{subsec:projects}). In many setups this feature can eliminate the
+need to set up a seperate virtual environment or container (e.g., in
+conjunction with a \texttt{requirements.txt}, \texttt{project.toml}, or
+\texttt{environment.yml} file specifying the project's dependencies).
+
 We designed \texttt{davos} for use in research applications. For
@@
 
+\subsection{Pitfalls and limitations}
+
+While \texttt{davos} enables developers to conveniently specify all project
+dependencies, there are some edge cases and limitations that are worth
+considering. Many Python packages include (in their \texttt{setup} options)
+additional dependencies that often carry their own version specifications.
+Although \texttt{davos} will check that the correct version of the requested
+top-level package is installed and imported into the workspace, the version
+numbers of any \textit{dependencies} of the request package are \textit{not}
+checked. In principle, this could lead to unexpected behavior, for example if a
+given package's dependencies (or dependencies of those dependencies, etc.) were
+left under-specified. A developer could mitigate this by explicitly smuggling
+exact version numbers of \textit{every} project dependency (e.g., obtained via
+\texttt{pip freeze}). However, for projects where the versions of dependencies
+of \texttt{smuggle}d packages also need to be precisely controlled, a lockfile
+or a \texttt{requirements.txt} file produced by \texttt{pip freeze} (i.e.,
+explicitly specifying \textit{all} package's version numbers) may provide a
+more comprehensive alternative to \texttt{davos}.
+
+Reproducibility is not solely about dependency management. In addition to
+ensuring that project dependencies are satisfied, the user running a given
+notebook must also execute the code in the indicated order. For example, the
+cells in a notebook may be manually run out of order. If different cells in a
+\texttt{davos}-enhanced notebook made use of different versions of the same
+package, this could result in \textit{more} confusion or \textit{greater}
+replication failure rates relative to standard Jupyter notebooks. Therefore an
+important consideration when using \texttt{davos} is that it is perhaps even more
+important to execute notebook cells in order than would be the case in the
+standard (non-\texttt{davos}) setup.  We suggest that developers who wish to use
+\texttt{davos} include notes regarding which cells must be executed in sequence.
+
+As of this writing, \texttt{davos} can install packages using \textt{pip}, but
+not other standard Python package management systems such as \texttt{conda}.
+Therefore packages that are not installable via \texttt{pip} are currently
+unsupported by \texttt{davos}.  We anticipate adding support for other
+package management systems, including \texttt{conda} in a future release.
+
 \section{Conclusions}

### 2023-06-13 davos/core/project.py
handle removing project dirs that are empty but contain a .DS_Store file from having been opened in Finder on a Mac

@@ -332,12 +332,18 @@ def cleanup_project_dir_atexit(dirpath):
     if dirpath.is_dir() and _dir_is_empty(dirpath):
         try:
             dirpath.rmdir()
-        except OSError:
-            pass
-
-
-def prune_projects():
-    """delete (auto-named) projects for which a notebook doesn't exist"""
+        except OSError as e:
+            if e.errno == errno.ENOTEMPTY:
+                # dirpath is empty except for a .DS_Store file
+                try:
+                    dirpath.joinpath('.DS_Store').unlink()
+                except FileNotFoundError:
+                    # shouldn't be possible to get here, but silently
+                    # handle errors just in case so we don't interfere
+                    # with shutdown
+                    pass
+                else:
+                    dirpath.rmdir()
 
 
 def use_default_project():

### 2023-06-13 davos/core/project.py
more efficient check for empty directory (excluding potential .DS_Store)

@@ -235,8 +235,10 @@ class ConcreteProject(Project):
 
 
 def _dir_is_empty(path):
-    return next((f for f in path.iterdir() if f.name != '.DS_Store'), None) is None
-
+    for p in path.iterdir():
+        if p.name != '.DS_Store':
+            return False
+    return True
 
 def _get_project_name_type(name):
     """TODO: add docstring"""

### 2023-06-14 davos/core/project.py
rewrote _get_project_name_type function to handle relative path to notebook in CWD, also added more helpful error messages & conditions

@@ -240,44 +240,80 @@ def _dir_is_empty(path):
             return False
     return True
 
-def _get_project_name_type(name):
-    """TODO: add docstring"""
+
+def _get_project_name_type(project_name):
+    if isinstance(project_name, Path):
+        # if user passed a pathlib.Path, convert it to a str so it can
+        # be properly expanded, substituted, resolved, etc. below
+        project_name = str(project_name)
+    elif not isinstance(project_name, str):
+        raise TypeError(
+            "Project name must be either a str or pathlib.Path, not "
+            f"{type(project_name)}"
+        )
+
+    if (
+            project_name == '' or
+            ':' in project_name or
+            # disallow backslash on non-Windows systems only
+            ('\\' in project_name and os.name != 'nt')
+    ):
+        raise DavosProjectError(
+            f"Invalid project name: '{project_name}'. Names for both Jupyter "
+            "notebooks and davos Projects must be at least one character and "
+            "may not contain ':' or '\\'."
+        )
+
     project_type = ConcreteProject
-    # if user passed a pathlib.Path, convert it to a str so it can
-    # be properly expanded, substituted, resolved, etc. below
-    project_name = str(name)
-    if PATHSEP in project_name:
-        # `name` is a path to a notebook file, either the default
-        # project (path to the current notebook) or user-specified.
-        # File doesn't *have* to exist at this point (will be an
-        # AbstractProject, if not), but must at least point to what
+    if project_name.endswith('.ipynb'):
+        # `project_name` is a path to a notebook file, either the
+        # default (absolute path to the current notebook) or
+        # user-specified (can be absolute or relative). File doesn't
+        # strictly have to exist at this point (and will be an
+        # `AbstractProject`, if not), but must at least point to what
         # could eventually be a notebook
-        # TODO: carve this off into some sort of "resolve path" utility
-        #  function?
-        name_path = Path(expandvars(project_name)).expanduser().resolve(strict=False)
-        if name_path.suffix != '.ipynb' or name_path.is_dir():
+        nb_path = Path(expandvars(project_name)).expanduser().resolve()
+        if nb_path.is_dir():
             raise DavosProjectError(
-                f"Invalid project name: {name!r} (which resolves to "
-                f"'{name_path}'). Project names may be either a simple "
-                f"name (without {PATHSEP!r}) or a path to a Jupyter "
-                f"notebook file (ending in '.ipynb')."
[…]

### 2023-06-14 davos/__init__.py
top-level module property for getting all local projects

@@ -46,6 +46,15 @@ class ConfigProxyModule(ModuleType):
         else:
             super().__setattr__(name, value)
 
+    @property
+    def all_projects(self):
+        """TODO: add docstring"""
+        projects_list = []
+        for path in DAVOS_PROJECT_DIR.iterdir():
+            if path.is_dir():
+                projects_list.append(Project(path.name))
+        return projects_list
+
 
 # pylint: disable=unused-argument
 def configure(

### 2023-06-14 davos/core/project.py
require explicitly passing 'yes=True' to remove project in noninteractive mode

@@ -160,6 +160,11 @@ class Project(metaclass=ProjectChecker):
          to bypass
         """
         if not yes:
+            if config.noninteractive:
+                raise DavosProjectError(
+                    "To remove a project when noninteractive mode is "
+                    "enabled, you must explicitly pass 'yes=True'."
+                )
             prompt = f"Remove project {self.name!r} and all installed packages?"
             confirmed = prompt_input(prompt, default='n')
             if not confirmed:

### 2023-06-14 davos/core/exceptions.py
add new project-related exception classes to __all__

@@ -10,6 +10,8 @@ __all__ = [
     'OnionParserError',
     'OnionArgumentError',
     'ParserNotImplementedError',
+    'DavosProjectError',
+    'ProjectNotebookNotFoundError',
     'SmugglerError',
     'InstallerError'
 ]

### 2023-06-15 davos/__init__.py
added & updated docstrings

@@ -1,7 +1,15 @@
 """
-Top-level `davos` module. Initializes the global `davos` config object
-and defines some convenience functions for accessing/setting
-`davos.config` values.
+Top-level `davos` module. When imported, the code in this module:
+
+    - initializes the global `davos.config` object
+    - enables `davos` functionality in the importing notebook
+    - configures the default Project for the session
+
+This module also provides some high-level convenience functions for
+managing local Projects and `davos.config` options. Note that at
+runtime, this module's object (i.e., "`davos`", given "`import davos`")
+will be an instance of the `ConfigProxyModule` class. See that class's
+docstring for more info.
 """
 
 
@@ -25,13 +33,38 @@ config = DavosConfig()
 
 import davos.implementations
 from davos.core.core import smuggle
-# TODO: refactor to find a cleaner way of setting this during __init__,
-#  also possibly defer lazily? Or if run at import, maybe async?
 from davos.core.project import DAVOS_PROJECT_DIR, Project, use_default_project
 
 
 class ConfigProxyModule(ModuleType):
-    """TODO: add docstring"""
+    """
+    Subclass of Python's built-in `module` type that enables accessing
+    `davos.config` fields via the top-level `davos` namespace.
+
+    When imported, the top-level `davos` module object is "converted"
+    to an instance of this class (by overwriting its `__class__`
+    attribute). The `ConfigProxyModule` class tweaks the built-in
+    `module` type's attribute access behavior to:
+
+        1. forward attribute lookups that fail on the module object to
+           the `davos.config` object
+        2. preferentially forward attribute assignments to the
+           `davos.config` object if it defines the given attribute name
+        3. support dynamically computed (*and settable*) module-level
+           attributes via properties defined by the class.
+
+        This makes it possible to get and set all `davos` configuration
+        options directly from the module object itself. For example:
+    ```python
+    print(davos.config.pip_executable)
+    davos.config.project = "myproject"
+    ```
+    is equivalent to:
+    ```python
+    print(davos.pip_executable)
+    davos.project = "myproject"
+    ```
+    """
     def __getattr__(self, name):
         try:
             return getattr(config, name)
@@ -48,7 +81,14 @@ class ConfigProxyModule(ModuleType):
 
     @property
     def all_projects(self):
-        """TODO: add docstring"""
+        """
+        Get a list of all local projects.
+
+        Returns
+        -------
+        list of AbstractProject or ConcreteProject
[…]

### 2023-06-15 davos/core/core.py
suppress pip warning about installing scripts outside of PATH

@@ -539,7 +539,7 @@ class Onion:
                 args = f'{args} --no-input'
             if config.project is not None:
                 install_exe = f'PYTHONUSERBASE="{config.project.project_dir}" {install_exe}'
-                args = f'--user {args}'
+                args = f'--no-warn-script-location --user {args}'
         else:
             install_exe = self.installer
         return f'{install_exe} install {args}'

### 2023-06-15 davos/core/config.py
improved error message when setting davos.config.project to a notebook path that is syntactically valid but doesn't exist

@@ -356,8 +356,10 @@ class DavosConfig(metaclass=SingletonConfig):
             proj = Project(proj)
             if isinstance(proj, AbstractProject):
                 raise ProjectNotebookNotFoundError(
-                    "Cannot associate a Project with a notebook that does not "
-                    f"exist (no such notebook: {proj.name!r})."
+                    "To use a project associated with a specific notebook, "
+                    "the specified path must point to an existing Jupyter "
+                    f"notebook ('.ipynb') file. {proj.name!r} could not be "
+                    f"found)."
                 )
             self._project = proj
         else:

### 2023-06-15 davos/core/project.py
folded _set_names method into __init__ since it's only called once

@@ -58,7 +58,10 @@ class Project(metaclass=ProjectChecker):
         TODO: add docstring, note difference between what name can be
          passed as vs what it is when __init__ is run due to metaclass
         """
-        self._set_names(name)
+        self.name = name
+        self.safe_name = name.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
+        self.project_dir = DAVOS_PROJECT_DIR.joinpath(self.safe_name)
+        self.site_packages_dir = self.project_dir.joinpath(SITE_PACKAGES_SUFFIX)
         # eagerly create project dir since it's low-cost
         self.project_dir.mkdir(parents=False, exist_ok=True)
         # register atexit hook to remove project dir if empty
@@ -129,13 +132,6 @@ class Project(metaclass=ProjectChecker):
             else:
                 self._installed_packages = [tuple(pkg.values()) for pkg in pip_list_json]
             self._site_packages_mtime = site_pkgs_mtime
-
-    def _set_names(self, name):
-        """set various name-related attributes given the project name"""
-        self.name = name
-        self.safe_name = name.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
-        self.project_dir = DAVOS_PROJECT_DIR.joinpath(self.safe_name)
-        self.site_packages_dir = self.project_dir.joinpath(SITE_PACKAGES_SUFFIX)
 
     def freeze(self):
         """pip-freeze-like output for the Project"""

### 2023-06-15 davos/core/project.py
remove .reload() method since it's now redundant with code in .rename()

@@ -137,18 +137,6 @@ class Project(metaclass=ProjectChecker):
         """pip-freeze-like output for the Project"""
         return '\n'.join('=='.join(pkg) for pkg in self.installed_packages)
 
-    def reload(self):
-        """TODO: add docstring"""
-        # NOTE: this currently busts cache of installed packages
-        template_instance = Project(self.name)
-        self.__class__ = template_instance.__class__
-        self.__dict__ = template_instance.__dict__
-        # explicitly delete the temporary new Project instance so its
-        # __del__ method is called before this method returns and we
-        # can ensure the project directory exists after reload
-        del template_instance
-        self.project_dir.mkdir(parents=False, exist_ok=True)
-
     def remove(self, yes=False):
         """
         TODO: add docstring -- remove the project and all installed

### 2023-06-16 davos/core/project.py
only recreate the project directory after removing if it's the currently active project

@@ -156,7 +156,8 @@ class Project(metaclass=ProjectChecker):
                 return
         print(f"Removing {self.project_dir}...")
         shutil.rmtree(self.project_dir)
-        self.project_dir.mkdir()
+        if self == config.project:
+            self.project_dir.mkdir()
 
     def rename(self, new_name):
         """

### 2023-06-16 paper/main.tex
addressed PCF suggestions from slack message (6/15/23 pinned item)

--- 2023-04-14 paper/main.tex
@@
 \usepackage{geometry}
-\geometry{left=1in,right=1in,top=1in,bottom=1in,headsep=0pt}
+
+\geometry{left=1in, right=1in, top=1in, bottom=1in, headsep=0pt}
 
@@
 
-\title{\texttt{davos}: a Python package ``smuggler'' for constructing
+\title{Davos: a Python package ``smuggler'' for constructing
   lightweight reproducible notebooks}
@@
   science. Here, we propose a lighter-weight solution: the
-  \texttt{davos} package.  When used in combination with a
-  notebook-based Python project, \texttt{davos} provides a mechanism
+  Davos package.  When used in combination with a
+  notebook-based Python project, Davos provides a mechanism
   for specifying (and automatically installing) the correct versions
-  of the project's dependencies.  The \texttt{davos} package further
+  of the project's dependencies.  The Davos package further
   ensures that those packages and specific versions are used every
@@
   text, executable code, and media (including rendered figures, code
-  output, etc.).  When the \textbf{\texttt{davos} package} is imported
+  output, etc.).  When the \textbf{Davos package} is imported
   into a Jupyter notebook, the notebook's functionality is extended to
@@
   precise control over dependencies and versioning.  Notebooks
-  enhanced using the \texttt{davos} package are easily shareable and
+  enhanced using the Davos package are easily shareable and
   require minimal setup costs, while also facilitating high
@@
 
-We designed \texttt{davos} to occupy a ``sweet spot'' between these extremes.
-\texttt{davos} is a notebook-installable package that adds functionality to the
+We designed Davos to occupy a ``sweet spot'' between these extremes.
+Davos is a notebook-installable package that adds functionality to the
 default notebook experience. Like standard Jupyter notebooks,
-\texttt{davos}-enhanced notebooks allow researchers to include text, executable
+Davos-enhanced notebooks allow researchers to include text, executable
 code, and media within a single file. No further setup or installation is
 required from the user, beyond what is needed to run standard Jupyter
-notebooks. And like virtual environments, \texttt{davos} provides a convenient
+notebooks. And like virtual environments, Davos provides a convenient
 mechanism for fully specifying (and installing, as needed) a complete set of
@@
 
-The \texttt{davos} package is named after Davos Seaworth, a smuggler
-referred to as ``the Onion Knight" from the series \textit{A Song of
-  Ice and Fire} by George R. R. Martin~\cite{Mart98}.  The
-\texttt{smuggle} keyword provided by \texttt{davos}
-is a play on Python's \texttt{import} keyword: whereas importing can
-load a package into the Python workspace within the existing rules
-and frameworks provided by the Python language, ``smuggling'' provides
-an alternative that expands the scope and reach of ``importing.''
-Like the character Davos Seaworth (who became famous for smuggling
-onions through a blockade on his homeland), we use ``onion'' comments
-to precisely control how packages are smuggled into the Python
-workspace.
+The Davos package is named after Davos Seaworth, a smuggler referred
+to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by
+George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by
+Davos is a play on Python's \texttt{import} keyword: whereas importing
+can load a package into the Python workspace within the existing rules and
+frameworks provided by the Python language, ``smuggling'' provides an
+alternative that expands the scope and reach of ``importing.'' Like the
+character Davos Seaworth (who became famous for smuggling onions through a
+blockade on his homeland), we use ``onion'' comments to precisely control how
+packages are smuggled into the Python workspace.
 
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The \texttt{davos} package
+\caption{\small \textbf{Package structure.} The Davos package
   comprises two interdependent subpackages.  The \texttt{davos.core}
@@
   and onion comments, installing and validating packages, and
-  configuring \texttt{davos}'s behavior.  The
+  configuring Davos's behavior.  The
   \texttt{davos.implementations} subpackage includes
@@
 
-The \texttt{davos} package consists of two interdependent subpackages
+The Davos package consists of two interdependent subpackages
 (see Fig.~\ref{fig:package-structure}). The first,
@@
 Sec.~\ref{subsec:onion}), and a runtime interface for configuring
-\texttt{davos}'s behavior (see Sec.~\ref{subsec:config}). However,
+Davos's behavior (see Sec.~\ref{subsec:config}). However,
 certain critical aspects of this
@@
 depending on properties of the notebook environment in which
-\texttt{davos} is used (e.g., whether the frontend is provided by
+Davos is used (e.g., whether the frontend is provided by
 Jupyter or Google Colaboratory, or which version of
@@
 organized into modules by the conditions that trigger their use. At
-runtime, \texttt{davos} detects various features in the notebook
+runtime, Davos detects various features in the notebook
 environment and selectively imports a single version of each helper
@@
 consistent location. An additional benefit of this design is that it
-allows maintainers, developers, and users to extend \texttt{davos} to
+allows maintainers, developers, and users to extend Davos to
 support new, updated, or custom notebook variants by creating new
@@
 
-Functionally, importing \texttt{davos} in an IPython notebook enables
+Functionally, importing Davos in an IPython notebook enables
 an additional Python keyword: ``\texttt{smuggle}'' (see
@@
 packages on the fly.  If a smuggled package does not exist in the
-local environment, \texttt{davos} will download and install it automatically,
+local environment, Davos will download and install it automatically,
 expose its contents to Python's \texttt{import} machinery, and load it
@@
 versions, causing conflicts with other packages, etc.). To protect against
-undesired changes to the runtime environment, \texttt{davos} incorporates its
-own virtual environment for managing packages it installs. When \texttt{davos}
+undesired changes to the runtime environment, Davos incorporates its
+own virtual environment for managing packages it installs. When Davos
 is imported, a new virtual environment (folder) is created automatically. The
@@
 environment are installed to the current project folder. The runtime
-environment remains unaffected by \texttt{davos}'s behavior (see
-Sec.~\ref{subsec:project}).
+environment remains unaffected by Davos's behavior (see
+Sec.~\ref{subsec:projects}).
 
@@
 
-For greater control over the behavior of \texttt{smuggle} statements,
-\texttt{davos} defines an additional construct called the ``onion comment.'' An
-onion comment is a special type of inline comment that may be placed on a line
-containing a \texttt{smuggle} statement to customize how \texttt{davos}
-searches for the smuggled package locally and, if necessary, downloads and
-installs it. Onion comments follow a simple format based on the ``type
-comment'' syntax introduced in PEP 484~\cite{vanREtal14}, and are designed to
-make managing packages with \texttt{davos} intuitive and familiar. To construct
-an onion comment, users provide the name of the installer program (e.g.,
-\texttt{pip}) and the same arguments one would use to manually install the
-package as desired via the command line: \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet1} \end{center} Occasionally,
-a package's distribution name (i.e., the name used when installing it) may
-differ from its top-level module name (i.e., the name used when importing it).
-In such cases, an onion comment may be used to ensure that \texttt{davos}
-installs the proper package if it cannot be found locally: \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet2} \end{center} Because onion
-comments may be constructed to specify any aspect of the installer's behavior,
-they provide a mechanism for precisely controlling how, where, and when
-smuggled packages are installed. Critically, if an onion comment includes a
-version specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the
-version of the package loaded into the notebook matches the specific version
-requested, or satisfies the given version constraints. If the smuggled package
-exists locally, \texttt{davos} will extract its version information from its
+For greater control over the behavior of \texttt{smuggle} statements, Davos
+defines an additional construct called the ``onion comment.'' An onion comment
+is a special type of inline comment that may be placed on a line containing a
+\texttt{smuggle} statement to customize how Davos searches for the smuggled
+package locally and, if necessary, downloads and installs it. Onion comments
+follow a simple format based on the ``type comment'' syntax introduced in PEP
+484~\cite{vanREtal14}, and are designed to make managing packages with Davos
+intuitive and familiar. To construct an onion comment, users provide the name
+of the installer program (e.g., \texttt{pip}) and the same arguments one would
+use to manually install the package as desired via the command line:
+\begin{center} \includegraphics[width=0.9\textwidth]{figs/snippet1}
+\end{center} Occasionally, a package's distribution name (i.e., the name used
+when installing it) may differ from its top-level module name (i.e., the name
+used when importing it). In such cases, an onion comment may be used to ensure
+that Davos installs the proper package if it cannot be found locally:
+\begin{center} \includegraphics[width=0.9\textwidth]{figs/snippet2}
+\end{center} Because onion comments may be constructed to specify any aspect of
+the installer's behavior, they provide a mechanism for precisely controlling
+how, where, and when smuggled packages are installed. Critically, if an onion
+comment includes a version specifier~\cite{CoghStuf13}, Davos will ensure that
+the version of the package loaded into the notebook matches the specific
+version requested, or satisfies the given version constraints. If the smuggled
+package exists locally, Davos will extract its version information from its
 metadata and compare it to the specifier provided. If the two are incompatible
-(or no local installation is found), \texttt{davos} will download, install, and
-load a suitable version of the package instead: \begin{center}
+(or no local installation is found), Davos will download, install, and load a
+suitable version of the package instead: \begin{center}
 \includegraphics[width=0.9\textwidth]{figs/snippet3} \end{center} Onion
@@
 Git~\cite{TorvHama05} branches, commits, tags, etc.): \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet4} \end{center}
-\texttt{davos} processes onion comments internally before forwarding arguments
-to the installer program. In addition to preventing onion comments from being
-used as a vehicle for shell injection attacks, this enables \texttt{davos} to
-adapt its behavior based on how particular flags will affect the behavior of
-the installer program. For example, if an onion comment contains either the
+\includegraphics[width=0.9\textwidth]{figs/snippet4} \end{center} Davos
+processes onion comments internally before forwarding arguments to the
+installer program. In addition to preventing onion comments from being used as
+a vehicle for shell injection attacks, this enables Davos to adapt its behavior
+based on how particular flags will affect the behavior of the installer
+program. For example, if an onion comment contains either the
 \texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, or
-\texttt{--force-reinstall} flag, \texttt{davos} will not bother checking for a
-local copy of the smuggled package before installing a new one: \begin{center}
+\texttt{--force-reinstall} flag, Davos will not bother checking for a local
+copy of the smuggled package before installing a new one: \begin{center}
 \includegraphics[width=0.9\textwidth]{figs/snippet5} \end{center} Similarly,
-the \texttt{--no-input} flag will temporarily enable \texttt{davos}'s
-non-interactive mode (see Sec.~\ref{subsec:config}). Installation flags that
-affect the user's system outside of the current notebook are disabled by
-default (see Sec.~\ref{subsec:projects}).
-
-, and installing a smuggled package into a
-custom directory (\texttt{<dir>}) using the \texttt{--target <dir>}
-flag will cause \texttt{davos} to prepend \texttt{<dir>} to the module
-search path (i.e., \texttt{sys.path}), if necessary, so the package
-can be imported.
-
-\subsubsection{The \texttt{davos} config object}\label{subsec:config}
-
-The \texttt{davos} config object provides a high-level interface for
-controlling various aspects of \texttt{davos}'s behavior. After
-importing \texttt{davos}, the \texttt{davos.con\-fig} object (a
-singleton) exposes configurable options as attributes that can be
-modified, displayed in the notebook, or checked programmatically at runtime
-(see Sec.~\ref{sec:illustrative-example} for an illustrative example or
-Sec.~\ref{subsec:implementation} for implementation details and
-additional information). These include:
-
-\begin{itemize}
-\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
-  statements and onion comments is enabled (\texttt{True}) or
-  disabled (\texttt{False}).  When \texttt{davos} is first imported,
-  the \texttt{.active} attribute is set to \texttt{True}.
-
-\item \texttt{.auto\_rerun}: This attribute controls how
-  \texttt{davos} behaves when attempting to \texttt{smuggle} a new
-  version of a package that was previously imported and cannot be
-  reloaded. This can happen if the package includes extension modules
-  that dynamically link C or C++ objects to the Python interpreter,
-  and the code that generates those objects was changed between the
-  previously imported and to-be-smuggled versions.  If this attribute
-  is set to \texttt{True}, \texttt{davos} will automatically restart
-  the notebook kernel and rerun all code up to (and including) the
-  current \texttt{smuggle} statement. If set to \texttt{False} (the default),
-  \texttt{davos} will instead issue a warning, pause execution, and
-  prompt the user to either restart and rerun the notebook, or
-  continue running with the previously imported package version until
-  the next time the kernel is restarted manually.  Note that, as of
-  this writing, the \texttt{.auto\_rerun} attribute is not supported
-  in Google Colaboratory notebooks.
-
-\item \texttt{.confirm\_install}: If set to \texttt{True} (default:
-  \texttt{False}), \texttt{davos} will require user confirmation
-  before installing a smuggled package that does not yet exist in the
-  user's environment.
-
-\item \texttt{.noninteractive}: Setting this attribute to
-  \texttt{True} (default: \texttt{False}) enables non-in\-ter\-act\-ive
-  mode, in which all user interactions (prompts and dialogues) are
-  disabled. Note that in non-interactive mode, the
-  \texttt{confirm\_install} option is set to \texttt{False}.  If
-  \texttt{auto\_rerun} is set to \texttt{False} while in non-interactive
-  mode, \texttt{davos} will raise an exception if a smuggled package
-  cannot be reloaded, rather than prompting the user.
-
-\item \texttt{.pip\_executable}: This attribute's value specifies the
-  path to the \texttt{pip} executable used to install smuggled
-  packages. The default is programmatically determined from the Python
-  environment and falls back to \texttt{sys.executable -m pip} if no
-  executable can be found.
-
-\item \texttt{.suppress\_stdout}: If this attribute is set to
-  \texttt{True} (default: \texttt{False}), \texttt{davos} suppresses
-  printed (console) outputs from both itself and the installer program.
-  This can be useful when smuggling packages that need to install many
-  dependencies and/or generate extensive output. However, if the installer
-  program throws an error, both its stdout and stderr streams will be
-  displayed alongside the Python traceback to allow for debugging.
-\end{itemize}
-
-\noindent The top-level \texttt{davos} namespace also defines
-convenience functions for setting and checking whether \texttt{davos}
-is active (\texttt{davos.activate()}; \texttt{davos.deactivate()};
-\texttt{davos.is\_active()}) as well as the \texttt{davos.configure()}
-function, which allows setting multiple configuration options
-simultaneously.
+the \texttt{--no-input} flag will temporarily enable Davos's non-interactive
+mode (see Sec.~\ref{subsec:config}). Installation flags that affect the user's
+system outside of the current notebook are disabled by default (see
+Sec.~\ref{subsec:projects}), and installing a smuggled package into a custom
+directory (\texttt{<dir>}) using the \texttt{--target <dir>} flag will cause
+Davos to prepend \texttt{<dir>} to the module search path (i.e.,
+\texttt{sys.path}), if necessary, so the package can be imported.
 
@@
 
-Because \texttt{davos} can install new packages, running the code in a
-\texttt{davos}-enhanced notebook might (in principle) affect the behavior of
+Because Davos can install new packages, running the code in a
+Davos-enhanced notebook might (in principle) affect the behavior of
 \textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
@@
 notebook (Notebook A) for their research project. We will assume that Notebook
-A does not use \texttt{davos} to manage project dependencies.  If Person A
-runs a \texttt{davos}-enhanced Notebook B, e.g., sent by another developer,
+A does not use Davos to manage project dependencies.  If Person A
+runs a Davos-enhanced Notebook B, e.g., sent by another developer,
 might this unexpectedly affect the behavior of Notebook A?
 
-We implemented a ``project'' system in \texttt{davos} to protect against the
-above scenario. By default, importing \texttt{davos} creates a new project
+We implemented a ``project'' system in Davos to protect against the
+above scenario. By default, importing Davos creates a new project
 folder in the user's home directory (contained within a hidden \texttt{.davos}
@@
 notebook's project directory. When external libraries are \texttt{smuggle}d,
-\texttt{davos} temporally appends the current project directory to the search
+Davos temporally appends the current project directory to the search
 path. Because the user's system path remains unchanged, and because none of the
 runtime environment's packages are altered, the user's system and runtime
-environment remain unaffected (aside from installing the \texttt{davos} package
+environment remain unaffected (aside from installing the Davos package
 itself to the runtime environment).
@@
 this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
-will cause any packages installed by \texttt{davos} to affect the user's
+will cause any packages installed by Davos to affect the user's
 runtime environment.  This is generally not recommended, as it can lead to
@@
 
+\subsubsection{Configuring and querying Davos}\label{subsec:config}
+
+Davos's behavior may be customized by modifying a set of attributes attached to
+the \texttt{davos} module object that is added to the workspace when Davos is
+imported. These attributes may be modified, displayed, or checked
+programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
+illustrative example or Sec.~\ref{subsec:implementation} for implementation
+details and additional information). These include:
+
+\begin{itemize}
+\item \texttt{.active}: This attribute controls whether support for \texttt{smuggle}
+  statements and onion comments is enabled (\texttt{True}) or
+  disabled (\texttt{False}).  When Davos is first imported,
+  the \texttt{.active} attribute is set to \texttt{True}.
+
+\item \texttt{.auto\_rerun}: This attribute controls how
+  Davos behaves when attempting to \texttt{smuggle} a new
+  version of a package that was previously imported and cannot be
+  reloaded. This can happen if the package includes extension modules
+  that dynamically link C or C++ objects to the Python interpreter,
+  and the code that generates those objects was changed between the
+  previously imported and to-be-smuggled versions.  If this attribute
+  is set to \texttt{True}, Davos will automatically restart
+  the notebook kernel and rerun all code up to (and including) the
+  current \texttt{smuggle} statement. If set to \texttt{False} (the default),
+  Davos will instead issue a warning, pause execution, and
+  prompt the user to either restart and rerun the notebook, or
+  continue running with the previously imported package version until
+  the next time the kernel is restarted manually.  Note that, as of
+  this writing, the \texttt{.auto\_rerun} attribute is not supported
+  in Google Colaboratory notebooks.
+
+\item \texttt{.confirm\_install}: If set to \texttt{True} (default:
+  \texttt{False}), Davos will require user confirmation
+  before installing a smuggled package that does not yet exist in the
+  user's environment.
+
+\item \texttt{.noninteractive}: Setting this attribute to
+  \texttt{True} (default: \texttt{False}) enables non-in\-ter\-act\-ive
+  mode, in which all user interactions (prompts and dialogues) are
+  disabled. Note that in non-interactive mode, the
+  \texttt{confirm\_install} option is set to \texttt{False}.  If
+  \texttt{auto\_rerun} is set to \texttt{False} while in non-interactive
+  mode, Davos will raise an exception if a smuggled package
+  cannot be reloaded, rather than prompting the user.
+
+\item \texttt{.pip\_executable}: This attribute's value specifies the
+  path to the \texttt{pip} executable used to install smuggled
+  packages. The default is programmatically determined from the Python
+  environment and falls back to \texttt{sys.executable -m pip} if no
+  executable can be found.
+
+\item \texttt{.suppress\_stdout}: If this attribute is set to
+  \texttt{True} (default: \texttt{False}), Davos suppresses
+  printed (console) outputs from both itself and the installer program.
+  This can be useful when smuggling packages that need to install many
+  dependencies and/or generate extensive output. However, if the installer
+  program throws an error, both its stdout and stderr streams will be
+  displayed alongside the Python traceback to allow for debugging.
+
+\item \texttt{.project}: This attribute is a string that specifies the name of
+the ``project'' associated with the current notebook. As described in
+Section~\ref{subsec:projects}, a notebook's project determines where and how
+any \textttt{smuggle}d dependencies are installed if they are not available in
+the current runtime environment. By default, this attribute is named according
+to the current notebook's absolute file path. However, the project name may be
+customized to enable shared dependency installations across notebooks (see
+Sec.~\ref{subsec:projects}).
+
+\end{itemize}
+
+\noindent Davos namespace also defines the \texttt{davos.configure()} function,
+which allows setting multiple configuration options simultaneously. In addition
+to the above configurable attributes, the \texttt{davos} object also includes
+several read-only attributes that contain potentially useful information about
+the current environment or Davos's behavior:
+
+\begin{itemize}
+
+\item \texttt{.environment}: This attribute's value is a string describing the notebook
+environment Davos was imported into. As of the current version (0.2.0), this
+attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”}.
+
+  \item \texttt{.ipython\_shell}: This attribute contains the global IPython \texttt{InteractiveShell} instance underlying the notebook kernel session.
+
+  \item \texttt{.smuggled}: This attribute is set to a Python dictionary that functions as a cache of any \texttt{smuggle} commands run during the current
+session.  The dictionary's keys are package names and the values are arguments passed via the corresponding smuggle statement's onion comment.
+
+  \item \texttt{.all\_projects}: This attribute contains a list of all local projects (i.e., projects with virtual environment directories located in \texttt{\$HOME/.davos/projects}).
+See Section~\ref{subsec:projects} for additional information about Davos projects.
+
+\end{itemize}
+
 \subsection{Implementation details}\label{subsec:implementation}
 
-Although \texttt{davos} is designed to \textit{appear} to add a new
+Although Davos is designed to \textit{appear} to add a new
 keyword to Python's vocabulary, this illusion is actually created through
@@
 for processing and executing users' code.  Specifically, when
-\texttt{davos} is first imported, or when it is activated after having been
+Davos is first imported, or when it is activated after having been
 set to an inactive state, two actions are triggered.  First, the
 \texttt{smuggle()} function is injected into the IPython user
-namespace.  Second, the \texttt{davos} parser is registered as a
+namespace.  Second, the Davos parser is registered as a
 custom IPython input transformer.
@@
 to the Python compiler, in order to handle special constructs like
-\texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} uses
+\texttt{\%magic} and \texttt{!shell} commands. Davos uses
 this process to transform \texttt{smuggle} statements into
-syntactically valid Python code. The \texttt{davos} parser uses a
+syntactically valid Python code. The Davos parser uses a
 regular expression to match lines of code containing \texttt{smuggle}
@@
 The call to the \texttt{smuggle()} function carries out
-\texttt{davos}'s central logic by determining whether the smuggled
+Davos's central logic by determining whether the smuggled
 package must be installed, carrying out the installation if necessary,
@@
 is also possible (though never necessary) to call it
-directly. Deactivating \texttt{davos} will delete the name
+directly. Deactivating Davos will delete the name
 ``\texttt{smuggle}'' from the namespace, unless its value has been
 overwritten and no longer refers to the \texttt{smuggle()}
-function. It will also deregister the \texttt{davos} parser from the
+function. It will also deregister the Davos parser from the
 set of input transformers run when each notebook cell is
-executed. While the overhead added by the \texttt{davos} parser is
+executed. While the overhead added by the Davos parser is
 minimal, this may be useful, for example, when optimizing or precisely
@@
   high level, the \texttt{smuggle()} function may be conceptualized as
-following two basic steps.  First (left), \texttt{davos} ensures that the
+following two basic steps.  First (left), Davos ensures that the
 correct version of the desired package has been installed, carrying
 out the installation automatically if needed.  Second (right),
-\texttt{davos} imports the package and updates the current runtime environment.}
+Davos imports the package and updates the current runtime environment.}
 \label{fig:flow-chart}
@@
 \includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for \texttt{davos}.}
+\caption{\small \textbf{Example use case for Davos.}
   Snippets from this example are also excerpted in the main text of
@@
 The example provided in Figure~\ref{fig:illustrative-example} demonstrates how
-the \texttt{davos} package can be used to circumvent these incompatibilities by
+the Davos package can be used to circumvent these incompatibilities by
 carefully controlling which versions of each package are used in different
@@
 
-After installing and importing \texttt{davos} (lines 1--2), we first \texttt{smuggle} two
+After installing and importing Davos (lines 1--2), we first \texttt{smuggle} two
 utilities for interacting with local files in the code below. The
@@
 Line 7 then uses the \texttt{davos.config} object to enable
-\texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next
+Davos's \texttt{auto\_rerun} option before smuggling the next
 two packages: \texttt{NumPy}~\cite{HarrEtal20} and
@@
 extensions with those from the new version. The \texttt{auto\_rerun} flag set
-on line 7 enables \texttt{davos} to trigger this process automatically so that
+on line 7 enables Davos to trigger this process automatically so that
 the code can continue running without user intervention, and converting the
@@
 statements to load the packages into the notebook namespace. If they
-differ, \texttt{davos} will download the requested versions in place
+differ, Davos will download the requested versions in place
 of the installed versions before doing so.
@@
 
-In lines 26--29, we demonstrate another aspect of \texttt{davos}'s
+In lines 26--29, we demonstrate another aspect of Davos's
 functionality that supports more advanced installation scenarios.  The
@@
 \texttt{scikit-learn} in line 36.  Taken together, the code in
-Figure~\ref{fig:illustrative-example} shows how \texttt{davos} can
+Figure~\ref{fig:illustrative-example} shows how Davos can
 enable users to load in data and models that are incompatible with
@@
 Like virtual environments, containers, and virtual machines, the
-\texttt{davos} package (when used in conjunction with Jupyter
+Davos package (when used in conjunction with Jupyter
 notebooks) provides a light\-weight mechanism for sharing code and
 ensuring reproducibility across users and computing environments
-(Fig.~\ref{fig:code-sharing}). Further, \texttt{davos} enables users
+(Fig.~\ref{fig:code-sharing}). Further, Davos enables users
 to fully specify (and install, as needed) any project dependencies
@@
 
-We designed \texttt{davos} for use in research applications. For
-example, in many settings, \texttt{davos} may be used as a drop-in
+Although existing notebooks \textit{can} incorporate system calls that install
+project requirements, handling project requirements in the general case is
+non-trivial (e.g., see Fig.~\ref{fig:flow-chart}). Further, Davos
+incorporates its own virtual environment system that isolates
+notebook-installed packages from the runtime environment
+(Sec.~\ref{subsec:projects}). In many setups this feature can eliminate the
+need to set up a seperate virtual environment or container (e.g., in
+conjunction with a \texttt{requirements.txt}, \texttt{project.toml}, or
+\texttt{environment.yml} file specifying the project's dependencies).
+
+We designed Davos for use in research applications. For
+example, in many settings, Davos may be used as a drop-in
 replacement for more-difficult-to-set-up virtual environments,
@@
 reconstructing the original researchers' computing environment,
-\texttt{davos} also lowers barriers to entry for members of the
+Davos also lowers barriers to entry for members of the
 scientific community and the public who seek to run shared code.
 
-Beyond research applications, \texttt{davos} is also useful in
+Beyond research applications, Davos is also useful in
 pedagogical settings. For example, in programming courses, instructors
-and students may use the \texttt{davos} package to ensure their
+and students may use the Davos package to ensure their
 notebooks will run correctly on others' machines. When combined with
 online notebook-based platforms like Google Colaboratory,
-\texttt{davos} provides a convenient way to manage dependencies within
+Davos provides a convenient way to manage dependencies within
 a notebook, without requiring any software (beyond a web browser) to
 be installed on the students' or instructors' systems. For the same
-reasons, \texttt{davos} also provides an elegant means of sharing
+reasons, Davos also provides an elegant means of sharing
 ready-to-run notebook-based demonstrations or tutorials that install
@@
 
-Since its initial release, \texttt{davos} has found use in a variety of
+Since its initial release, Davos has found use in a variety of
 applications. In addition to managing computing environments for multiple prior
 and ongoing research studies~\citep{MannEtal23, OwenMann23, ZimaEtal23},
-\texttt{davos} is being used by both students and instructors in programming
+Davos is being used by both students and instructors in programming
 and methods courses such as Storytelling with Data~\cite{Mann21d} (an open
@@
 operators to the Python language could be specifically useful to
-researchers. With \texttt{davos}, we accomplish this by leveraging
+researchers. With Davos, we accomplish this by leveraging
 IPython notebooks' internal code parsing and execution machinery. We
@@
 keyword-like objects (e.g., based around common typos). We also note
-that this implementation approach means \texttt{davos}'s functionality
+that this implementation approach means Davos's functionality
 is currently restricted to IPython notebook environments. However,
@@
 including a draft proposal~\cite{Shan20}. In addition to enabling
-\texttt{davos} to be extended for use outside of notebooks, this could
-lead to exciting new tools that, like \texttt{davos}, extend the
+Davos to be extended for use outside of notebooks, this could
+lead to exciting new tools that, like Davos, extend the
 Python language in useful and more secure ways.
+
+\subsection{Pitfalls and limitations}
+
+While Davos enables developers to conveniently specify all project
+dependencies, there are some edge cases and limitations that are worth
+considering. Many Python packages include (in their \texttt{setup} options)
+additional dependencies that often carry their own version specifications.
+Although Davos will check that the correct version of the requested
+top-level package is installed and imported into the workspace, the version
+numbers of any \textit{dependencies} of the request package are \textit{not}
+checked. In principle, this could lead to unexpected behavior, for example if a
+given package's dependencies (or dependencies of those dependencies, etc.) were
+left under-specified. A developer could mitigate this by explicitly smuggling
+exact version numbers of \textit{every} project dependency (e.g., obtained via
+\texttt{pip freeze}). However, for projects where the versions of dependencies
+of \texttt{smuggle}d packages also need to be precisely controlled, a lockfile
+or a \texttt{requirements.txt} file produced by \texttt{pip freeze} (i.e.,
+explicitly specifying \textit{all} package's version numbers) may provide a
+more comprehensive alternative to Davos.
+
+Reproducibility is not solely about dependency management. In addition to
+ensuring that project dependencies are satisfied, the user running a given
+notebook must also execute the code in the indicated order. For example, the
+cells in a notebook may be manually run out of order. If different cells in a
+Davos-enhanced notebook made use of different versions of the same
+package, this could result in \textit{more} confusion or \textit{greater}
+replication failure rates relative to standard Jupyter notebooks. Therefore an
+important consideration when using Davos is that it is perhaps even more
+important to execute notebook cells in order than would be the case in the
+standard (non-Davos) setup.  We suggest that developers who wish to use
+Davos include notes regarding which cells must be executed in sequence.
+
+As of this writing, Davos can install packages using \textt{pip}, but
+not other standard Python package management systems such as \texttt{conda}.
+Therefore packages that are not installable via \texttt{pip} are currently
+unsupported by Davos.  We anticipate adding support for other
+package management systems, including \texttt{conda} in a future release.
 
@@
 
-The \texttt{davos} package supports reproducible research by providing
+The Davos package supports reproducible research by providing
 a novel, lightweight system for sharing notebook-based code. But
-perhaps the most exciting uses of the \texttt{davos} package are those
+perhaps the most exciting uses of the Davos package are those
 that we have \textit{not} yet considered or imagined. We hope that the
-research and scientific Python communities will find \texttt{davos} to provide a convenient
+research and scientific Python communities will find Davos to provide a convenient
 means of managing project dependencies to facilitate code sharing and collaboration. We

### 2023-06-19 davos/core/core.py
disallow pip-install arguments that change the package's install location (-t/--target, --user, --root, --prefix) when using a davos Project

@@ -467,6 +467,33 @@ class Onion:
             self.install_name = package_name
             self.version_spec = ''
             return
+        if config._project is not None and (
+            # for this few checks, `or` is ~3x faster than `any()` and
+            # ~2x faster than `set.intersection()`
+            'target' in installer_kwargs or
+            'user' in installer_kwargs or
+            'root' in installer_kwargs or
+            'prefix' in installer_kwargs
+        ):
+            # when using a davos Project, pip-install arguments that
+            # install the package into a different location are
+            # disallowed. This check needs to happen at runtime rather
+            # than during the parsing stage in case `davos.project` is
+            # set/changed in the same cell as the `smuggle` statement.
+            msg = (
+                "When using a davos Project to isolate smuggled packages, "
+                "pip-install arguments that change the package's install "
+                "location (`-t/--target`, `--user`, `--root`, `--prefix`) "
+                "are disallowed. To disable davos project isolation, set "
+                "`davos.project = None`."
+            )
+            bad_arg = next(arg for arg in ('target', 'user', 'root', 'prefix')
+                           if arg in installer_kwargs)
+            if bad_arg == 'target':
+                bad_arg = '-t/--target'
+            else:
+                bad_arg = f'--{bad_arg}'
+            raise OnionArgumentError(msg, argument=bad_arg)
         full_spec = installer_kwargs.pop('spec').strip("'\"")
         self.is_editable = installer_kwargs.pop('editable')
         self.verbosity = installer_kwargs.pop('verbosity', 0)

### 2023-06-20 davos/__init__.py
make constants from davos.core.project available from top-level namespace

@@ -13,7 +13,15 @@ docstring for more info.
 """
 
 
-__all__ = ['config', 'configure', 'smuggle', 'use_default_project']
+__all__ = [
+    'DAVOS_CONFIG_DIR',
+    'DAVOS_PROJECT_DIR',
+    'config',
+    'configure',
+    'Project',
+    'smuggle',
+    'use_default_project'
+]
 
 
 import sys
@@ -33,7 +41,12 @@ config = DavosConfig()
 
 import davos.implementations
 from davos.core.core import smuggle
-from davos.core.project import DAVOS_PROJECT_DIR, Project, use_default_project
+from davos.core.project import (
+    DAVOS_CONFIG_DIR,
+    DAVOS_PROJECT_DIR,
+    Project,
+    use_default_project
+)
 
 
 class ConfigProxyModule(ModuleType):

### 2023-06-20 davos/__init__.py
support importing and setting project in IPython shell, issue warning

@@ -182,6 +182,4 @@ config.active = True
 
 DAVOS_PROJECT_DIR.mkdir(parents=True, exist_ok=True)
 
-# TODO: throws error when importing in IPython shell -- add informative
-#  error message saying not supported
 use_default_project()

### 2023-06-20 davos/core/config.py

@@ -162,6 +162,13 @@ class DavosConfig(metaclass=SingletonConfig):
             self._environment = 'Python'
         else:
             import IPython
+            if isinstance(
+                    self._ipython_shell,
+                    IPython.terminal.interactiveshell.TerminalInteractiveShell
+            ):
+                _msg = ("davos does not officially support IPython terminal "
+                        "shells. Some features may not work as expected.")
+                warnings.warn(_msg, category=RuntimeWarning)
             if IPython.version_info[0] >= 7:
                 if 'google.colab' in str(self._ipython_shell):
                     self._environment = 'Colaboratory'

### 2023-06-20 davos/core/project.py

@@ -376,9 +376,18 @@ def cleanup_project_dir_atexit(dirpath):
 
 def use_default_project():
     """
-    TODO: add docstring -- use the default project for the current
-     notebook
+    Switch (back) to using the default project.
+
+    Determine the default davos Project from the environment and set
+    `davos.config.project` to it. In IPython notebooks, this is a
+    notebook-specific project named for the notebook's filepath. In an
+    IPython shell, this is a project named "ipython-shell", which is
+    shared by all IPython shell instances.
     """
-    nb_path = get_notebook_path()
-    default_project = Project(nb_path)
+    if isinstance(config._ipython_shell, TerminalInteractiveShell):
+        proj_name = "ipython-shell"
+    else:
+        proj_name = get_notebook_path()
+
+    default_project = Project(proj_name)
     config.project = default_project

### 2023-06-20 davos/__init__.py
get __version__ using importlib.metadata instead of pkg_resources

@@ -27,13 +27,15 @@ __all__ = [
 import sys
 from types import ModuleType
 
-import pkg_resources
+if sys.version_info >= (3, 8):
+    from importlib import metadata
+else:
+    import importlib_metadata as metadata
 
 from davos.core.config import DavosConfig
 
 
-__version__ = pkg_resources.get_distribution('davos').version
-
+__version__ = metadata.version('davos')
 
 # config must be instantiated before importing implementations module
 config = DavosConfig()

### 2023-06-20 davos/core/project.py
separate functions for converting between filepaths and "safe" project names

@@ -59,7 +59,7 @@ class Project(metaclass=ProjectChecker):
          passed as vs what it is when __init__ is run due to metaclass
         """
         self.name = name
-        self.safe_name = name.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
+        self.safe_name = _filepath_to_safename(name)
         self.project_dir = DAVOS_PROJECT_DIR.joinpath(self.safe_name)
         self.site_packages_dir = self.project_dir.joinpath(SITE_PACKAGES_SUFFIX)
         # eagerly create project dir since it's low-cost
@@ -169,7 +169,7 @@ class Project(metaclass=ProjectChecker):
         if new_project_name == self.name:
             # no change
             return
-        new_safe_name = new_project_name.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
+        new_safe_name = _filepath_to_safename(new_project_name)
         new_project_dir = DAVOS_PROJECT_DIR.joinpath(new_safe_name)
         if new_project_dir.is_dir() and not _dir_is_empty(new_project_dir):
             # new project dir exists and is non-empty
@@ -296,7 +296,7 @@ def _get_project_name_type(project_name):
         # directory name, since that could cause impassable errors until
         # manually fixed. Instead, just make it an AbstractProject and
         # let the user rename or delete it via the davos interface.
-        nb_path = Path(f"{project_name.replace(PATHSEP_REPLACEMENT, PATHSEP)}.ipynb")
+        nb_path = Path(_safename_to_filepath(project_name))
         if not nb_path.is_file():
             project_type = AbstractProject
         project_name = str(nb_path)
@@ -305,6 +305,51 @@ def _get_project_name_type(project_name):
     # formatting or validation (beyond type and valid character checks
     # above) is needed
     return project_name, project_type
+
+
+def _filepath_to_safename(filepath):
+    """
+    Convert a filepath to a project name in "safe" format.
+
+    Takes an absolute path to a notebook file and returns it in a format
+    that can be used as a valid directory name. This is the format used
+    to name notebook-specific projects directories in
+    `davos.DAVOS_PROJECT_DIR`.
+
+    Parameters
+    ----------
+    filepath : str
+        An absolute path to a Jupyter notebook (.ipynb) file.
+
+    Returns
+    -------
+    str
+        The filepath in "safe" format.
+    """
[…]

### 2023-06-21 davos/core/project.py
prune_projects function for cleaning up old unused projects and installed packages

@@ -419,6 +419,115 @@ def cleanup_project_dir_atexit(dirpath):
                     dirpath.rmdir()
 
 
+def prune_projects(yes=False):
+    """
+    Remove unused local projects.
+
+    Delete any notebook-specific projects from `davos.DAVOS_PROJECT_DIR`
+    whose corresponding notebooks no longer exist (i.e., any
+    `AbstractProject`s). See "Notes" section below for more info.
+
+    Parameters
+    ----------
+    yes : bool, optional
+        If `True` (default: `False`), don't prompt for confirmation
+        before removing each unused project.
+
+    Notes
+    -----
+    1. By default, user confirmation (y/n input) is required before
+       deleting each project, but this can be bypassed by passing
+       `yes=True`. Note that if davos's non-interactive mode is enabled
+       (i.e., `davos.noninteractive` has been set to `True`), `yes=True`
+       *must* be explicitly passed to prune projects. This serves as a
+       safeguard against unintentionally deleting projects, since
+       non-interactive mode disables all user input and confirmation.
+    2. The function will also remove any project directories (other than
+       the currently active project's) that contain no installed
+       packages. However, this is done silently since the intended
+       behavior is for empty projects to be removed automatically when
+       the interpreter is shut down -- they're only checked for and
+       dealt with here as a fallback in case one somehow sneaks through.
+    """
+    # dict of projects to remove -- keys: "safe"-formatted project
+    # directory names; values: corresponding notebook filepaths
+    to_remove = {}
+    # iterate through project directory and do checks manually rather
+    # than checking `davos.all_projects` to avoid creating a bunch of
+    # Project instances and registering duplicate `atexit` callbacks
+    # unnecessarily
+    for project_dir in DAVOS_PROJECT_DIR.iterdir():
+        if (
+                not project_dir.is_dir()
+                or project_dir.name == config._project.safe_name
+        ):
+            # skip .DS_Store files and the project currently in use
+            continue
+
+        project_dirname = project_dir.name
+        if PATHSEP_REPLACEMENT in project_dirname:
+            # if the project is notebook-specific...
+            as_filepath = _safename_to_filepath(project_dirname)
+            if not Path(as_filepath).is_file():
[…]

### 2023-06-21 davos/__init__.py
make prune_projects function accessible from top-level namespace

@@ -19,6 +19,7 @@ __all__ = [
     'config',
     'configure',
     'Project',
+    'prune_projects',
     'smuggle',
     'use_default_project'
 ]
@@ -47,6 +48,7 @@ from davos.core.project import (
     DAVOS_CONFIG_DIR,
     DAVOS_PROJECT_DIR,
     Project,
+    prune_projects,
     use_default_project
 )
 

### 2023-06-21 davos/__init__.py
"get_project" function for getting a project's object by its name

@@ -18,6 +18,7 @@ __all__ = [
     'DAVOS_PROJECT_DIR',
     'config',
     'configure',
+    'get_project',
     'Project',
     'prune_projects',
     'smuggle',
@@ -47,6 +48,7 @@ from davos.core.core import smuggle
 from davos.core.project import (
     DAVOS_CONFIG_DIR,
     DAVOS_PROJECT_DIR,
+    get_project,
     Project,
     prune_projects,
     use_default_project

### 2023-06-21 davos/core/project.py

@@ -12,6 +12,8 @@ from urllib.parse import unquote, urljoin, urlparse
 
 import ipykernel
 import requests
+from IPython.display import clear_output
+from IPython.terminal.interactiveshell import TerminalInteractiveShell
 
 from davos import config
 from davos.core.core import prompt_input, run_shell_command
@@ -350,6 +352,57 @@ def _safename_to_filepath(safename):
         associated with the project.
     """
     return f'{safename.replace(PATHSEP_REPLACEMENT, PATHSEP)}.ipynb'
+
+
+def get_project(project_name, create=False):
+    """
+    Get a Project by its name.
+
+    Return the `Project` instance for the project named `project_name`,
+    optionally creating it if it doesn't already exist. If the project
+    does not exist and `create` is `False`, return `None`
+    (mirrors behavior of built-in `dict.get()`)
+
+    Parameters
+    ----------
+    project_name : str or pathlib.Path
+        The name of the project to get. As is the case when creating a
+        new `Project` or setting the `davos.project` field, project
+        names that represent notebook filepaths may be provided as an
+        absolute or relative path, or in the "safe" name format used for
+        directories in `DAVOS_PROJECT_DIR`.
+    create : bool, optional
+        Whether to create the project if it doesn't already exist
+        (default: `False`).
+
+    Returns
+    -------
+    davos.core.project.Project or None
+        The `Project` instance for the project named `project_name`, or
+        `None` if the project does not exist and `create` is `False`.
+
+    """
+    if create:
+        # if we're going to create a Project instance whether the
+        # project directory exists or not, no need to check for it first
+        return Project(project_name)
+
+    # rather than creating `Project(project_name)` and checking for it
+    # in `davos.all_projects`, determine what the project's directory
+    # *would* be named and check whether it exists. This avoids creating
+    # a bunch of `Project` instances and registering duplicate `atexit`
+    # callbacks unnecessarily
+    cleaned_name, project_cls = _get_project_name_type(project_name)
+    safe_name = _filepath_to_safename(cleaned_name)
+    project_dir = DAVOS_PROJECT_DIR.joinpath(safe_name)
+    if project_dir.is_dir():
+        # since we already got the project's name and type above, we can
+        # call `type.__call__` directly and bypass the `ProjectChecker`
+        # metaclass's `__call__` method.
+        return type.__call__(project_cls, cleaned_name)
+
+    # else, the project doesn't exist
+    return None
 
 
 def get_notebook_path():

### 2023-06-21 davos/core/project.py
add some missing objects to __all__

@@ -20,7 +20,15 @@ from davos.core.core import prompt_input, run_shell_command
 from davos.core.exceptions import DavosProjectError
 
 
-__all__ = ['Project', 'get_notebook_path', 'use_default_project']
+__all__ = [
+    'DAVOS_CONFIG_DIR',
+    'DAVOS_PROJECT_DIR',
+    'Project',
+    'get_notebook_path',
+    'get_project',
+    'prune_projects',
+    'use_default_project'
+]
 
 
 DAVOS_CONFIG_DIR = Path.home().joinpath('.davos')

### 2023-06-21 davos/core/project.py
all docstring updates

@@ -1,4 +1,47 @@
-"""TODO: add module docstring"""
+"""
+"Project" system for isolating smuggled dependencies.
+
+This module implements davos's "Project" scheme for isolating packages
+smuggled in a davos-enhanced notebook from the main Python environment,
+as well as from those smuggled in other davos-enhanced notebooks.
+Functionally, a davos project is similar to Python virtual environment,
+with a few main differences:
+    - davos projects do not need to be set up, activated, or deactivated
+      manually; they are automatically created and used when
+      davos-enhanced notebooks are run.
+    - davos projects *extend*, rather than replace, the main Python
+      environment; they contain only the dependencies of davos-enhanced
+      notebooks that are not already satisfied by the packages available
+      in those notebooks' "normal" Python environments.
+    - davos projects do not contain their own Python or pip executables;
+      packages are installed into them using the pip executable from the
+      Python environment used to run the notebook kernel.
+All davos projects are stored in `davos.DAVOS_PROJECT_DIR`
+(`~/.davos/projects/`). By default, each davos-enhanced notebook will
+create and use a notebook-specific project named for the path to the
+notebook file. Any packages (or specific package versions) smuggled in
+that notebook that are not already available in the main Python
+environment will be installed into and loaded from the project's
+isolated package directory (along with any dependencies of those
+packages not already available in the main environment). This way, davos
+automatically ensures all smuggled packages and specific package
+versions are available at runtime without altering the main Python
+environment.
+
+davos projects can also be shared by multiple notebooks. The project
+used by the current notebook can be accessed and set via the
+`davos.project` (or `davos.config.project`) attribute. When accessed,
+the value of `davos.project` will always be a
+`davos.core.project.ConcreteProject` instance, but the attribute can
+also be assigned either a `str` or `pathlib.Path`, which will be
+converted to a `ConcreteProject` internally on assignment. The same
+project can be used by multiple notebooks simply by setting
+`davos.project` to the same value at the top of each one. While
+notebook-specific projects are typically (and by default) named for the
+notebook's path, notebook-agnostic projects can be given arbitrary names
+(that are not file paths), e.g., `davos.project = "my-project"`.
+"""
+
 
 import atexit
 import errno
@@ -46,10 +89,9 @@ class ProjectChecker(type):
     """
     Metaclass that determines whether the object returned by the
     `Project` constructor will be a `ConcreteProject` or an
-    `AbstractProject`
+    `AbstractProject`.
     """
     def __call__(cls, name):
[…]

### 2023-06-21 davos/core/project.py
add stubs for new functions, reorganize in module

@@ -409,6 +409,28 @@ def _dir_is_empty(path):
     return True
 
 
+def _filepath_to_safename(filepath):
+    """
+    Convert a filepath to a project name in "safe" format.
+
+    Takes an absolute path to a notebook file and returns it in a format
+    that can be used as a valid directory name. This is the format used
+    to name notebook-specific projects directories in
+    `davos.DAVOS_PROJECT_DIR`.
+
+    Parameters
+    ----------
+    filepath : str
+        An absolute path to a Jupyter notebook (.ipynb) file.
+
+    Returns
+    -------
+    str
+        The filepath in "safe" format.
+    """
+    return filepath.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
+
+
 def _get_project_name_type(project_name):
     """
     Normalize the project name and determine the project type.
@@ -515,28 +537,6 @@ def _get_project_name_type(project_name):
     return project_name, project_type
 
 
-def _filepath_to_safename(filepath):
-    """
-    Convert a filepath to a project name in "safe" format.
-
-    Takes an absolute path to a notebook file and returns it in a format
-    that can be used as a valid directory name. This is the format used
-    to name notebook-specific projects directories in
-    `davos.DAVOS_PROJECT_DIR`.
-
-    Parameters
-    ----------
-    filepath : str
-        An absolute path to a Jupyter notebook (.ipynb) file.
-
-    Returns
-    -------
-    str
-        The filepath in "safe" format.
-    """
-    return filepath.replace(PATHSEP, PATHSEP_REPLACEMENT).replace('.ipynb', '')
-
-
 def _safename_to_filepath(safename):
     """
     Convert a project name in "safe" format to a filepath.
@@ -560,55 +560,49 @@ def _safename_to_filepath(safename):
     return f'{safename.replace(PATHSEP_REPLACEMENT, PATHSEP)}.ipynb'
 
 
-def get_project(project_name, create=False):
+def cleanup_project_dir_atexit(dirpath):
     """
-    Get a Project by its name.
+    Remove project directory on interpreter termination, if empty.
 
-    Return the `Project` instance for the project named `project_name`,
-    optionally creating it if it doesn't already exist. If the project
-    does not exist and `create` is `False`, return `None`
-    (mirrors behavior of built-in `dict.get()`)
+    Each Project instance eagerly creates its `.project_dir` on
+    instantiation so it's available for use, then if it isn't used,
[…]

### 2023-06-21 davos/core/core.py
change "TheNightIsDarkAndFullOfTerrors" -> "TheNightIsDarkAndFullOfTErrors"

@@ -38,7 +38,7 @@ from davos.core.exceptions import (
     OnionParserError,
     ParserNotImplementedError,
     SmugglerError,
-    TheNightIsDarkAndFullOfTerrors
+    TheNightIsDarkAndFullOfTErrors
 )
 from davos.core.parsers import pip_parser
 from davos.core.regexps import (
@@ -974,7 +974,7 @@ def smuggle(
     pkg_name = name.split('.')[0]
 
     if pkg_name == 'davos':
-        raise TheNightIsDarkAndFullOfTerrors("Don't do that.")
+        raise TheNightIsDarkAndFullOfTErrors("Don't do that.")
 
     onion = Onion(pkg_name, installer=installer,
                   args_str=args_str, **installer_kwargs)

### 2023-06-21 davos/core/exceptions.py

@@ -203,7 +203,7 @@ class SmugglerError(DavosError):
     """Base class for errors raised during the smuggle phase"""
 
 
-class TheNightIsDarkAndFullOfTerrors(SmugglerError):
+class TheNightIsDarkAndFullOfTErrors(SmugglerError):
     """A little Easter egg for anyone who tries to `smuggle davos`"""
 
 

### 2023-06-21 davos/__init__.py
docstring updates throughout

@@ -84,6 +84,7 @@ class ConfigProxyModule(ModuleType):
     davos.project = "myproject"
     ```
     """
+
     def __getattr__(self, name):
         try:
             return getattr(config, name)

### 2023-06-21 davos/core/config.py

@@ -1,9 +1,17 @@
 """
-This module defines the global `davos.config` object. The `davos`
-config consists of public fields that may be set by the user to affect
-`davos`'s behavior, as well as private (internal use only) fields that
-store information about the context into which the package was imported
-and available functionality.
+Davos's global configuration object.
+
+The `DavosConfig` class is a singleton whose instance is accessible as
+`davos.config`. The config object defines attributes whose values
+determine various aspects of the package's behavior. Most of these
+attributes can be set by the user to control how, where, and when
+smuggled packages are installed. Others are read-only fields that store
+information about the notebook environment into which `davos` was
+imported and whether or not it supports various `davos` functionality.
+The config object's repr displays the current values of all fields, and
+multiple fields can be set simultaneously via the `davos.configure()`
+function. As of v0.2, `davos.config` fields can also be accessed and set
+via attributes of the top-level `davos` module.
 """
 # TODO: standardize single vs double quotes (just for style consistency)
 # TODO: standardize line breaks in function calls -- first arg on same
@@ -61,6 +69,7 @@ class DavosConfig(metaclass=SingletonConfig):
                 reloaded (Note: currently implemented for Jupyter
                 notebooks only)
             conda_env: str or None
+                NOTE: NOT CURRENTLY SUPPORTED.
                 The name of the resident conda environment of the
                 current Python interpreter, if running within a `conda`
                 environment. Otherwise, `None`.
@@ -79,8 +88,19 @@ class DavosConfig(metaclass=SingletonConfig):
                 The path to the `pip` executable that should be used.
                 Must be a path to a real file. Defaults to automatically
                 discovered executable, if available.
-            project : davos.core.project.Project
-                # TODO: document new attribute
+            project : davos.core.project.ConcreteProject
+                The "Project" environment into which smuggled packages
+                should be installed. The default is a notebook-specific
+                Project whose name is the path to the current notebook.
+                This field may also be specified as a `str` or
+                `pathlib.Path`, which will be converted to a
+                `ConcreteProject` instance on assignment. If set to
+                `None`, smuggled packages will be installed into the
+                regular Python environment rather than isolated in a
+                Project. Projects are a virtual environment-like
+                construct specific to `davos`. For additional info, see
+                https://github.com/ContextLab/davos#readme and
[…]

### 2023-06-21 davos/core/core.py

@@ -1,9 +1,16 @@
 """
-This module implements core functionality and common utilities used
-across the environment-specific `davos` implementations.
+Davos core functionality and utilities.
+
+This module implements core elements of davos's functionality and
+various utilities that are common across the various
+environment-specific implementations. This includes parsing user code to
+extract `smuggle` statements and Onion comments, parsing their contents,
+searching the local package environment, installing missing packages,
+loading them into the user's namespace, and more.
 """
 
 
+# pylint: disable=too-many-lines
 __all__ = [
     'capture_stdout',
     'check_conda',
@@ -35,6 +42,7 @@ from davos import config
 from davos.core.exceptions import (
     DavosError,
     InstallerError,
+    OnionArgumentError,
     OnionParserError,
     ParserNotImplementedError,
     SmugglerError,
@@ -261,9 +269,14 @@ def get_previously_imported_pkgs(install_cmd_stdout, installer):
 @contextmanager
 def handle_alternate_pip_executable(installed_name):
     """
+    Load packages installed outside of the typical module search path.
+
     Context manager that makes it possible to load packages installed
     into a different Python environment by changing the `pip` executable
-    (`davos.config.pip_executable`).
+    (`davos.config.pip_executable`). This is done by using the `pip`
+    executable with which the package was installed to determine its
+    location, and then temporarily prepending that location to the
+    module search path.
 
     Parameters
     ----------
@@ -274,7 +287,7 @@ def handle_alternate_pip_executable(installed_name):
 
     Notes
     -----
-    super-duper edge case not handled by this: user has used alternate
+    Super-duper edge case not handled by this: user has used alternate
     pip_executable to smuggle local package from CWD and supplies
     relative path in onion comment (i.e., "# pip: . <args>").
     """
@@ -371,34 +384,37 @@ class Onion:
     """
     Class representing a single package to be smuggled.
 
-    Naturally, "`davos`" smuggles "`Onion`s". Internally, each `smuggle`
-    statement (with or without an "onion comment") creates an `Onion`
-    instance, which contains all the information necessary to import
-    and, if necessary, install it.
+    Naturally, "`davos`" smuggles "`Onion`s" [1]. Internally, each
+    `smuggle` statement (with or without an "onion comment") creates an
+    `Onion` instance, which contains all the information necessary to
+    import and, if necessary, install it.
 
-    # TODO: document attributes
+    See Also
+    --------
[…]

### 2023-06-21 davos/core/exceptions.py

@@ -1,6 +1,4 @@
-"""
-This module defines the set of `davos`-related exception classes.
-"""
+"""davos-specific exception classes."""
 
 
 __all__ = [
@@ -196,20 +194,20 @@ class DavosProjectError(DavosError):
 
 
 class ProjectNotebookNotFoundError(DavosProjectError, FileNotFoundError):
-    """Class for errors related to projects missing associated notebooks"""
+    """Class for errors related to projects missing associated notebooks."""
 
 
 class SmugglerError(DavosError):
-    """Base class for errors raised during the smuggle phase"""
+    """Base class for errors raised during the smuggle phase."""
 
 
 class TheNightIsDarkAndFullOfTErrors(SmugglerError):
-    """A little Easter egg for anyone who tries to `smuggle davos`"""
+    """A little Easter egg for anyone who tries to `smuggle davos`."""
 
 
 class InstallerError(SmugglerError, CalledProcessError):
     """
-    Class for errors related to the installer program
+    Class for errors related to the installer program.
 
     This exception is raised when the installer program itself (rather
     than `davos`) encounters an error (e.g., failure to connect to
@@ -220,7 +218,7 @@ class InstallerError(SmugglerError, CalledProcessError):
     @classmethod
     def from_error(cls, cpe, show_output=None):
         """
-        Create a class instance from a `subprocess.CalledProcessError`
+        Create a class instance from a `subprocess.CalledProcessError`.
 
         Parameters
         ----------

### 2023-06-21 davos/core/parsers.py

@@ -1,7 +1,9 @@
 """
-This module defines reimplementations of the command line parsers for
-installer programs supported by `davos`, slightly modified to parse
-arguments supplied via an Onion comment.
+Command line parser reimplementations for Onion comments.
+
+This module reimplements the command line parsers for installer programs
+supported by `davos` (currently, just `pip`). The reimplementations are
+slightly modified to parse arguments supplied via Onion comments.
 """
 # TODO: update with new pip install arguments as of v23
 
@@ -101,14 +103,14 @@ class OnionParser(ArgumentParser):
         """
         Raise an OnionArgumentError with a given message.
 
-        This is needed to override `argparse.ArgumentParser.error()`.
-        `argparse` is  which exits the program when called (in response
-        to an exception being raised) because it is generally intended
-        for command line interfaces. The generally idea is to affect the
-        stack trace displayed for the user as little as possible, while
-        also ensuring all exceptions raised inherit from `SyntaxError`
-        so they can be successfully raised during the notebook cell
-        pre-execution step.
+        This is needed to override `argparse.ArgumentParser.error()`,
+        which exits the program when called (in response to an exception
+        being raised) because `argparse.ArgumentParser` is generally
+        intended for command line interfaces. This version attempts to
+        affect the stack trace displayed for the user as little as
+        possible, while also ensuring all exceptions raised inherit from
+        `SyntaxError` so they can be successfully raised during the
+        notebook cell pre-execution step.
 
         Parameters
         ----------

### 2023-06-21 davos/core/project.py

@@ -91,6 +91,7 @@ class ProjectChecker(type):
     `Project` constructor will be a `ConcreteProject` or an
     `AbstractProject`.
     """
+
     def __call__(cls, name):
         cleaned_name, cls_to_init = _get_project_name_type(name)
         # `name` passed to __init__ is now a str: either a simple name
@@ -103,6 +104,7 @@ class Project(metaclass=ProjectChecker):
     A pseudo-environment associated with a particular (set of)
     davos-enhanced notebook(s).
     """
+
     def __init__(self, name):
         """
         Parameters
@@ -355,6 +357,7 @@ class AbstractProject(Project):
     renamed/moved notebook to continue using it to manage smuggled
     packages.
     """
+
     def __getattr__(self, item):
         if hasattr(ConcreteProject, item):
             msg = f"{item!r} is not supported for abstract projects"

### 2023-06-21 davos/implementations/__init__.py

@@ -1,24 +1,24 @@
 """
-This module dynamically imports and defines functions based on the
-environment into which `davos` is imported.
+Environment-specific implementations of `davos` functionality.
 
-Some `davos` functionality requires (often quite drastically) different
-implementations depending on certain properties of the importing
-environment (e.g., "regular" Python vs IPython, the IPython notebook
-front-end, etc.). To deal with this, environment-dependent parts of core
-features and behaviors (in the `davos.core` subpackage) are isolated and
-abstracted as "helper functions". Multiple, interchangeable
-implementations of each helper function are organized into
-per-environment modules within the `davos.implementations` subpackage.
-At runtime, this module selectively imports a single version of each
-helper function based on the global Python environment. `davos.core`
-modules can then access the correct implementation of each helper
-function regardless of the environment by importing it from the
-top-level `davos.implementations` module. This also allows individual
-`davos.implementations` modules to import packages that aren't
-guaranteed to be installed outside certain environments (e.g., `google`,
-`ipykernel`) without requiring them as dependencies of the overall
-`davos` package.
+This module dynamically imports and defines functions based on the
+environment into which `davos` is imported. Some `davos` functionality
+requires (often quite drastically) different implementations depending
+on certain properties of the importing environment (e.g., "regular"
+Python vs IPython, the IPython notebook front-end, etc.). To deal with
+this, environment-dependent parts of core features and behaviors (in the
+`davos.core` subpackage) are isolated and abstracted as "helper
+functions". Multiple, interchangeable implementations of each helper
+function are organized into per-environment modules within the
+`davos.implementations` subpackage. At runtime, this module selectively
+imports a single version of each helper function based on the global
+Python environment. `davos.core` modules can then access the correct
+implementation of each helper function regardless of the environment by
+importing it from the top-level `davos.implementations` module. This
+also allows individual `davos.implementations` modules to import
+packages that aren't guaranteed to be installed outside certain
+environments (e.g., `google`, `ipykernel`) without requiring them as
+dependencies of the overall `davos` package.
 
 The importing environment is determined by the value of the
 `environment` field of the global `DavosConfig` instance, so it's

### 2023-06-21 davos/implementations/colab.py

@@ -1,7 +1,4 @@
-"""
-This module contains implementations of helper functions specific to
-Google Colaboratory notebooks.
-"""
+"""Helper function implementations specific to Google Colab notebooks."""
 
 
 __all__ = ['auto_restart_rerun', 'prompt_restart_rerun_buttons']

### 2023-06-21 davos/implementations/ipython_common.py

@@ -1,6 +1,6 @@
 """
-This module contains implementations of helper functions common across
-all IPython versions and front-end interfaces.
+Helper function implementations common across all IPython versions and
+front-end interfaces.
 """
 
 __all__ = []
@@ -176,7 +176,6 @@ def _showsyntaxerror_davos(
     """
     Show `davos` library `SyntaxError` subclasses with full tracebacks.
 
-
     Replaces global IPython interactive shell object's
     `.showsyntaxerror()` method during initialization as a way to hook
     into `IPython`'s exception handling machinery for errors raised
@@ -216,7 +215,6 @@ def _showsyntaxerror_davos(
         Generates unique names for each cell used in `linecache.cache`.
     IPython.core.interactiveshell.InteractiveShell.showsyntaxerror :
         The original `.showsyntaxerror()` method this function replaces.
-
 
     Notes
     -----

### 2023-06-21 davos/implementations/ipython_post7.py

@@ -1,7 +1,4 @@
-"""
-This module contains implementations of helper functions specific to
-newer versions of `IPython`, starting with v7.0.0.
-"""
+"""Helper functions specific to IPython versions >= 7.0.0."""
 
 
 __all__ = ['generate_parser_func']

### 2023-06-21 davos/implementations/ipython_pre7.py

@@ -1,7 +1,11 @@
 """
-This module contains implementations of helper functions specific to
-versions of `IPython` before v7.0.0 (the oldest officially supported
-version is v5.5.0).
+Helper function implementations specific to IPython>=5.5.0,<7.0.0.
+
+Many of the IPython internals relevant to davos functionality were
+overhauled in IPython v7.0.0, so this module contains implementations of
+helper functions that allow davos to interface with IPython versions
+before that. The oldest IPython version officially supported by davos is
+v5.5.0.
 """
 
 

### 2023-06-21 davos/implementations/js_functions.py

@@ -1,26 +1,32 @@
 """
-This module contains JavaScript code for various `davos` features that
-require manipulating the notebook JS object in the browser.
+JavaScript code for interacting with the Jupyter notebook frontend.
 
-**Note**: currently, these features are implemented for Jupyter
+This module contains JavaScript code for various `davos` features that
+require manipulating with the `Jupyter.notebook` JS object in the
+browser. Note that these features are implemented for Jupyter
 notebooks only, as Colaboratory heavily restricts communication between
-the Python kernel and notebook frontend. However, within Jupyter, they
-are implemented for all `IPython` versions supported by `davos`.
+the IPython kernel and notebook frontend. However, they are implemented
+for Jupyter notebooks running all `IPython` versions supported by
+`davos`.
 
 JavaScript functions in this module are organized in a `DotDict`
 instance (see class docstring below) whose keys are function names and
 whose values are function definitions.  Two functions are currently
 implemented:
 
-`JS_FUNCTIONS.jupyter.restartRunCellsAbove`
-    Restarts the notebook kernel and queues all cells above for
-    execution, including the current (highlighted) cell. In `davos`,
-    this is generally useful when a smuggled package that was previously
-    imported cannot be reloaded by the current interpreter.
+- `JS_FUNCTIONS.jupyter.restartRunCellsAbove`
+    Restarts the notebook kernel, and queues all cells above and
+    including the current (highlighted) cell for execution upon restart.
+    When using `davos`, this is generally useful when a different
+    version of a smuggled package was previously imported during the
+    current interpreter session and cannot be reloaded -- this can
+    happen when the package includes extension modules that dynamically
+    link C or C++ objects to the interpreter, and those modules were
+    changed between the previously-loaded and just-smuggled versions.
 
-`JS_FUNCTIONS.jupyter.displayButtonPrompt`
+- `JS_FUNCTIONS.jupyter.displayButtonPrompt`
     Displays any number of buttons in the output area of the current
-    cell for user selection and (together with
+    cell for user selection and (in tandem with
     `davos.implementations.jupyter.prompt_restart_rerun_buttons`) blocks
     further code execution until one is clicked. Each button can
     optionally trigger a JavaScript-based callback when clicked, and/or
@@ -43,6 +49,7 @@ from textwrap import dedent
 
 class DotDict(dict):
     """Simple `dict` subclass that can be accessed like a JS object"""
+
     __delattr__ = dict.__delitem__
[…]

### 2023-06-21 davos/implementations/jupyter.py

@@ -1,7 +1,4 @@
-"""
-This module contains implementations of helper functions specific to
-Jupyter notebooks.
-"""
+"""Helper function implementations specific to Jupyter notebooks."""
 
 
 __all__ = ['auto_restart_rerun', 'prompt_restart_rerun_buttons']
@@ -34,7 +31,7 @@ def auto_restart_rerun(pkgs):
 
     Parameters
     ----------
-    pkgs : list of str
+    pkgs : iterable of str
         Packages that could not be reloaded without restarting the
         kernel.
 
@@ -106,7 +103,7 @@ def prompt_restart_rerun_buttons(pkgs):
 
     Parameters
     ----------
-    pkgs : list of str
+    pkgs : iterable of str
         Packages that could not be reloaded without restarting the
         kernel.
 
@@ -126,10 +123,9 @@ def prompt_restart_rerun_buttons(pkgs):
 
     Notes
     -----
-    1. This method of blocking and waiting for user input is based on
-       `ipykernel`'s replacement for the built-in `input` function used
-       in notebook environments.
-
+    This method of blocking and waiting for user input is based on
+    `ipykernel`'s replacement for the built-in `input` function used in
+    notebook environments.
     """
     # UI: could remove warning message when "continue" button is clicked
     msg = (

### 2023-06-21 davos/implementations/python.py

@@ -1,9 +1,9 @@
 """
-This module contains implementations of helper functions specific to
-"pure" (i.e., non-interactive) Python scripts.
+Helper function implementations specific to "plain" Python environments.
 
-**Note**: `davos` does not currently support pure Python, but will begin
-to do so in a near-future version.
+NOTE: `davos` does not currently support "plain" (i.e., non-interactive)
+Python environments (scripts, the IDLE, etc.), but aims to do so in a
+future version.
 """
 
 __all__ = [

### 2023-06-21 davos/implementations/ipython_post7.py
update references to now-removed top-level davos.activate(), davos.deactivate(), davos.is_active() functions

@@ -13,8 +13,8 @@ def _activate_helper(smuggle_func, parser_func):
     """
     `IPython>=7.0.0`-specific implementation of `_activate_helper`.
 
-    Helper function called when setting `davos.config.active = True` or
-    running `davos.activate()`. Registers the `davos` parser
+    Helper function called when setting `davos.active = True` (or
+    `davos.config.active = True`). Registers the `davos` parser
     (`parser_func`) as an `IPython` input transformer (in the
     `input_transformers_post` group) if it isn't one already. Injects
     `smuggle_func` into the `IPython` user namespace as `"smuggle"`.
@@ -47,8 +47,8 @@ def _deactivate_helper(smuggle_func, parser_func):
     """
     `IPython>=7.0.0`-specific implementation of `_deactivate_helper`.
 
-    Helper function called when setting `davos.config.active = False` or
-    running `davos.deactivate()`. Removes the `davos` parser
+    Helper function called when setting `davos.active = False` (or
+    `davos.config.active = False`). Removes the `davos` parser
     (`parser_func`) from the set of `IPython` input transformers and
     deletes the variable named "`smuggle`" from the `IPython` user
     namespace if it (a) exists and (b) holds a reference to
@@ -72,7 +72,7 @@ def _deactivate_helper(smuggle_func, parser_func):
 
     Notes
     -----
-    1. Any `smuggle` statements following a call to `davos.deactivate()`
+    1. Any `smuggle` statements following setting `davos.active = False`
        will result in `SyntaxError`s unless the parser is reactivated
        first.
     2. The `davos` parser adds minimal overhead to cell execution.

### 2023-06-21 davos/implementations/ipython_pre7.py

@@ -21,8 +21,8 @@ def _activate_helper(smuggle_func, parser_func):
     """
     `IPython<7.0.0`-specific implementation of `_activate_helper`.
 
-    Helper function called when setting `davos.config.active = True` or
-    running `davos.activate()`. Wraps the the `davos` parser
+    Helper function called when setting `davos.active = True` (or
+    `davos.config.active = True`). Wraps the `davos` parser
     (`parser_func`) in an
     `IPython/core.inputtransformer.StatelessInputTransformer` instance
     and registers it as both an `IPython` input transformer *and* input
@@ -90,8 +90,8 @@ def _deactivate_helper(smuggle_func, parser_func):
     """
     `IPython<7.0.0`-specific implementation of `_deactivate_helper`.
 
-    Helper function called when setting `davos.config.active = False` or
-    running `davos.deactivate()`. Removes the
+    Helper function called when setting `davos.active = False` (or
+    `davos.config.active = False`). Removes the
     `IPython/core.inputtransformer.StatelessInputTransformer` instance
     whose `.func` is the `davos` parser (`parser_func`) from both the
     `.input_splitter` and `input_transformer_manager` attributes the
@@ -119,7 +119,7 @@ def _deactivate_helper(smuggle_func, parser_func):
 
     Notes
     -----
-    1. Any `smuggle` statements following a call to `davos.deactivate()`
+    1. Any `smuggle` statements following setting `davos.active = False`
        will result in `SyntaxError`s unless the parser is reactivated
        first.
     2. The `davos` parser adds minimal overhead to cell execution.

### 2023-06-21 davos/core/core.py
update references to setting values via davos.config to use top-level namespace property

@@ -183,7 +183,7 @@ def check_conda():
         raise DavosError(
             "Failed to programmatically determine path to conda environment "
             "directory. If you want to install smuggled packages using conda, "
-            "you can either:\n\t1. set `davos.config.conda_env_path` to your "
+            "you can either:\n\t1. set `davos.conda_env_path` to your "
             "environment's path (e.g., $CONDA_PREFIX/envs/this_env)\n\t2. "
             "pass the environment path to `-p`/`--prefix` in each onion "
             "comment\n\t3. pass your environment's name to `-n`/`--name` in "
@@ -273,10 +273,9 @@ def handle_alternate_pip_executable(installed_name):
 
     Context manager that makes it possible to load packages installed
     into a different Python environment by changing the `pip` executable
-    (`davos.config.pip_executable`). This is done by using the `pip`
-    executable with which the package was installed to determine its
-    location, and then temporarily prepending that location to the
-    module search path.
+    (`davos.pip_executable`). This is done by using the `pip` executable
+    with which the package was installed to determine its location, and
+    then temporarily prepending that location to the module search path.
 
     Parameters
     ----------
@@ -299,7 +298,7 @@ def handle_alternate_pip_executable(installed_name):
         dist_name = installed_name
 
     # get install location from `pip show ___` command.
-    # In most cases, this will be davos.config.pip_executable with
+    # In most cases, this will be `davos.pip_executable` with
     # trailing 'bin/pip' replaced with python<major.minor>/site-packages
     # but since this runs only if non-default pip_executable is set,
     # it's worth the extra run time to check the safer way in order to
@@ -854,7 +853,7 @@ def run_shell_command(command, live_stdout=None):
         Whether to display streaming stdout from `command` execution in
         real time *in addition to* capturing and returning it. If `None`
         (default), behavior is determined by the current value of
-        `davos.config.suppress_stdout`.
+        `davos.suppress_stdout`.
 
     Returns
     -------
@@ -1116,7 +1115,7 @@ def smuggle(
                 if config.environment != 'Colaboratory':
                     msg = (
                         f"{msg}\nTo make this happen automatically, set "
-                        "'davos.config.auto_rerun = True'."
+                        "'davos.auto_rerun = True'."
                     )
                 raise SmugglerError(msg)
             else:
@@ -1126,7 +1125,7 @@ def smuggle(
                 config._project is None and
                 config._pip_executable != config._default_pip_executable
         ):
-            # setting davos.config.pip_executable to a non-default value
[…]

### 2023-06-21 davos/core/project.py

@@ -827,7 +827,7 @@ def use_default_project():
     Switch (back) to using the default project.
 
     Determine the default davos Project from the environment and set
-    `davos.config.project` to it. In IPython notebooks, this is a
+    `davos.project` to it. In IPython notebooks, this is a
     notebook-specific project named for the notebook's filepath. In an
     IPython shell, this is a project named "ipython-shell", which is
     shared by all IPython shell instances.

### 2023-06-21 davos/implementations/colab.py

@@ -13,9 +13,9 @@ def auto_restart_rerun(pkgs):
 
     Raises `NotImplementedError` whenever called, though this should
     never happen except when done intentionally as trying to set
-    `davos.config.auto_rerun = True` should raise an error. This feature
-    is not available in Colab notebooks because it requires accessing
-    the notebook frontend through the `colab.global.notebook` JavaScript
+    `davos.auto_rerun = True` should raise an error. This feature is not
+    available in Colab notebooks because it requires accessing the
+    notebook frontend through the `colab.global.notebook` JavaScript
     object, which Colab blocks you from doing from the kernel.
 
     Parameters

### 2023-06-21 davos/implementations/jupyter.py

@@ -23,9 +23,9 @@ def auto_restart_rerun(pkgs):
     Automatically restarts the notebook kernel and reruns all cells
     above, *including the current cell*. Called when one or more
     smuggled `pkgs` that were previously imported cannot be reloaded by
-    the current interpreter, and `davos.config.auto_rerun` is set to
-    `True`. Displays a message in the cell output area with the
-    package(s) that required the kernel restart, calls
+    the current interpreter, and `davos.auto_rerun` is set to `True`.
+    Displays a message in the cell output area with the package(s) that
+    required the kernel restart, calls
     `JS_FUNCTIONS.jupyter.restartRunCellsAbove`, and then blocks until
     the kernel is restarted.
 
@@ -43,7 +43,7 @@ def auto_restart_rerun(pkgs):
     Notes
     -----
     1. The message displayed before restarting the kernel can be
-       silenced by setting `davos.config.suppress_stdout` to `True`.
+       silenced by setting `davos.suppress_stdout` to `True`.
     2. After calling `JS_FUNCTIONS.jupyter.restartRunCellsAbove`, this
        function sleeps until the kernel restarts to prevent any further
        code in the current cell or other queued cells from executing.

### 2023-06-21 paper/main.tex

@@
 
-\subsubsection{Projects}\label{subsec:projects}
+\subsubsection{The Davos config object}\label{subsec:config}
 
-Because Davos can install new packages, running the code in a
-Davos-enhanced notebook might (in principle) affect the behavior of
-\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
-altering which packages are installed in the runtime environment. This could
-lead to undesired consequences. For example, suppose Person A develops a
-notebook (Notebook A) for their research project. We will assume that Notebook
-A does not use Davos to manage project dependencies.  If Person A
-runs a Davos-enhanced Notebook B, e.g., sent by another developer,
-might this unexpectedly affect the behavior of Notebook A?
-
-We implemented a ``project'' system in Davos to protect against the
-above scenario. By default, importing Davos creates a new project
-folder in the user's home directory (contained within a hidden \texttt{.davos}
-folder). The default project name is computed to uniquely identify each
-notebook according to its filename and path. Any packages that were not
-originally available in the notebook's runtime environment are installed to the
-notebook's project directory. When external libraries are \texttt{smuggle}d,
-Davos temporally appends the current project directory to the search
-path. Because the user's system path remains unchanged, and because none of the
-runtime environment's packages are altered, the user's system and runtime
-environment remain unaffected (aside from installing the Davos package
-itself to the runtime environment).
-
-Each notebook's project may be customized by setting \texttt{davos.project} to
-any string that can be used as a valid folder name in the user's operating
-system. By customizing the project name, users can build multi-notebook
-projects that share the same core set of dependencies without needing to
-duplicate each package for each notebook in the project.
-
-Finally, if the user \textit{does} wish to modify their runtime environment,
-this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
-will cause any packages installed by Davos to affect the user's
-runtime environment.  This is generally not recommended, as it can lead to
-unintended consequences for other code that shares the runtime environment.
-
-\subsubsection{Configuring and querying Davos}\label{subsec:config}
-
-Davos's behavior may be customized by modifying a set of attributes attached to
-the \texttt{davos} module object that is added to the workspace when Davos is
-imported. These attributes may be modified, displayed, or checked
-programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
-illustrative example or Sec.~\ref{subsec:implementation} for implementation
-details and additional information). These include:
+The Davos config object provides a high-level interface for
+controlling various aspects of Davos's behavior. After
+importing Davos, the \texttt{davos.con\-fig} object (a
+singleton) exposes configurable options as attributes that can be
+modified, displayed in the notebook, or checked programmatically at runtime
+(see Sec.~\ref{sec:illustrative-example} for an illustrative example or
+Sec.~\ref{subsec:implementation} for implementation details and
+additional information). These include:
 
@@
   displayed alongside the Python traceback to allow for debugging.
-
-\item \texttt{.project}: This attribute is a string that specifies the name of
-the ``project'' associated with the current notebook. As described in
-Section~\ref{subsec:projects}, a notebook's project determines where and how
-any \textttt{smuggle}d dependencies are installed if they are not available in
-the current runtime environment. By default, this attribute is named according
-to the current notebook's absolute file path. However, the project name may be
-customized to enable shared dependency installations across notebooks (see
-Sec.~\ref{subsec:projects}).
-
 \end{itemize}
 
-\noindent Davos namespace also defines the \texttt{davos.configure()} function,
-which allows setting multiple configuration options simultaneously. In addition
-to the above configurable attributes, the \texttt{davos} object also includes
-several read-only attributes that contain potentially useful information about
-the current environment or Davos's behavior:
+\noindent The top-level Davos namespace also defines
+convenience functions for setting and checking whether Davos
+is active (\texttt{davos.activate()}; \texttt{davos.deactivate()};
+\texttt{davos.is\_active()}) as well as the \texttt{davos.configure()}
+function, which allows setting multiple configuration options
+simultaneously.
 
-\begin{itemize}
+\subsubsection{Projects}\label{subsec:projects}
 
-\item \texttt{.environment}: This attribute's value is a string describing the notebook
-environment Davos was imported into. As of the current version (0.2.0), this
-attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”}.
+Because Davos can install new packages, running the code in a
+Davos-enhanced notebook might (in principle) affect the behavior of
+\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
+altering which packages are installed in the runtime environment. This could
+lead to undesired consequences. For example, suppose Person A develops a
+notebook (Notebook A) for their research project. We will assume that Notebook
+A does not use Davos to manage project dependencies.  If Person A
+runs a Davos-enhanced Notebook B, e.g., sent by another developer,
+might this unexpectedly affect the behavior of Notebook A?
 
-  \item \texttt{.ipython\_shell}: This attribute contains the global IPython \texttt{InteractiveShell} instance underlying the notebook kernel session.
+We implemented a ``project'' system in Davos to protect against the
+above scenario. By default, importing Davos creates a new project
+folder in the user's home directory (contained within a hidden \texttt{.davos}
+folder). The default project name is computed to uniquely identify each
+notebook according to its filename and path. Any packages that were not
+originally available in the notebook's runtime environment are installed to the
+notebook's project directory. When external libraries are \texttt{smuggle}d,
+Davos temporally appends the current project directory to the search
+path. Because the user's system path remains unchanged, and because none of the
+runtime environment's packages are altered, the user's system and runtime
+environment remain unaffected (aside from installing the Davos package
+itself to the runtime environment).
 
-  \item \texttt{.smuggled}: This attribute is set to a Python dictionary that functions as a cache of any \texttt{smuggle} commands run during the current
-session.  The dictionary's keys are package names and the values are arguments passed via the corresponding smuggle statement's onion comment.
+Each notebook's project may be customized by setting \texttt{davos.project} to
+any string that can be used as a valid folder name in the user's operating
+system. By customizing the project name, users can build multi-notebook
+projects that share the same core set of dependencies without needing to
+duplicate each package for each notebook in the project.
 
-  \item \texttt{.all\_projects}: This attribute contains a list of all local projects (i.e., projects with virtual environment directories located in \texttt{\$HOME/.davos/projects}).
-See Section~\ref{subsec:projects} for additional information about Davos projects.
-
-\end{itemize}
+Finally, if the user \textit{does} wish to modify their runtime environment,
+this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
+will cause any packages installed by Davos to affect the user's
+runtime environment.  This is generally not recommended, as it can lead to
+unintended consequences for other code that shares the runtime environment.
 

### 2023-06-21 davos/__init__.py
remove argument relevant to conda support from davos.configure() signature and docstring

@@ -121,7 +121,6 @@ def configure(
         *,
         active=...,
         auto_rerun=...,
-        conda_env=...,
         confirm_install=...,
         noninteractive=...,
         pip_executable=...,
@@ -138,9 +137,6 @@ def configure(
     auto_rerun : bool, optional
         Value to assign to "`auto_rerun`" field. Must be `False`
         (default) in Colaboratory notebooks.
-    conda_env : str, optional
-        Value to assign to "`conda_env`" field. Not settable if `conda`
-        is not installed (defaults to `None`).
     confirm_install : bool, optional
         Value to assign to "`confirm_install`" field.
     noninteractive : bool, optional

### 2023-06-21 davos/__init__.py
deal with incompatible config values separately and upfront in davos.configure() to fail early and avoid order-dependent errors

@@ -45,6 +45,7 @@ config = DavosConfig()
 
 import davos.implementations
 from davos.core.core import smuggle
+from davos.core.exceptions import DavosConfigError
 from davos.core.project import (
     DAVOS_CONFIG_DIR,
     DAVOS_PROJECT_DIR,
@@ -161,11 +162,59 @@ def configure(
         The global `davos` Config object. Offers more detailed
         descriptions of each field.
     """
-    # TODO: perform some value checks upfront to raise relevant errors
-    #  before setting some fields and make setting values
-    #  order-independent (e.g., noninteractive & confirm_install)
     kwargs = locals()
     old_values = {}
+    # deal with incompatible arguments separately and upfront so that
+    # (A) the function fails early rather than having to undo multiple
+    # assignments, and (B) the order in which assignments are undone in
+    # the event that a *different* assignment fails doesn't cause an
+    # incompatibility error.
+    # Need to explicitly check if value is True since Ellipsis evaluates
+    # to True.
+    if kwargs['confirm_install'] is True:
+        if kwargs['noninteractive'] is True:
+            # passed both `confirm_install=True` and `noninteractive=True`
+            raise DavosConfigError(
+                'confirm_install',
+                "confirm_install=True is incompatible with noninteractive=True"
+            )
+        if config._noninteractive:
+            if kwargs['noninteractive'] is False:
+                # if simultaneously disabling non-interactive mode and
+                # enabling the confirm_install option (i.e.,
+                # `config.noninteractive` is currently `True`,
+                # `noninteractive=False` is passed, and
+                # `confirm_install=True` is passed), then
+                # `config.noninteractive` must be set to `False` before
+                # `config.confirm_install` is set to `True`, since both
+                # options may not be `True` at the same time. The loop
+                # below sets config values based on the `kwargs` dict's
+                # insertion order, so simply removing `confirm_install`
+                # and re-adding it as the most recent entry ensures that
+                # `config.noninteractive` is set first.
+                kwargs['confirm_install'] = kwargs.pop('confirm_install')
+            else:
+                # if `confirm_install=True` is passed,
+                # `config.noninteractive` is currently `True`, and
+                # `noninteractive=False` is *not* passed, then the
+                # resulting values will be incompatible
+                raise DavosConfigError(
+                    'confirm_install',
+                    "field may not be 'True' in noninteractive mode"
+                )
+    elif (
+            kwargs['noninteractive'] is True and
+            kwargs['confirm_install'] is False
[…]

### 2023-06-21 davos/core/config.py
updated pip install command parser to support arguments added in recent pip releases; removed some stray TODO items

@@ -13,9 +13,6 @@ multiple fields can be set simultaneously via the `davos.configure()`
 function. As of v0.2, `davos.config` fields can also be accessed and set
 via attributes of the top-level `davos` module.
 """
-# TODO: standardize single vs double quotes (just for style consistency)
-# TODO: standardize line breaks in function calls -- first arg on same
-#  line or new line?
 
 
 __all__ = ['DavosConfig']
@@ -347,8 +344,6 @@ class DavosConfig(metaclass=SingletonConfig):
 
     @pip_executable.setter
     def pip_executable(self, exe_path):
-        # TODO: separate this off into some sort of "resolve path"
-        #  utility function?
         try:
             exe_path = Path(expandvars(exe_path)).expanduser().resolve(strict=True)
         except FileNotFoundError as e:

### 2023-06-21 davos/core/parsers.py

@@ -5,7 +5,6 @@ This module reimplements the command line parsers for installer programs
 supported by `davos` (currently, just `pip`). The reimplementations are
 slightly modified to parse arguments supplied via Onion comments.
 """
-# TODO: update with new pip install arguments as of v23
 
 
 __all__ = ['EditableAction', 'OnionParser', 'pip_parser', 'SubtractAction']
@@ -417,6 +416,32 @@ pep_517_subgroup.add_argument(
 )
 
 pip_install_opts.add_argument(
+    '--check-build-dependencies',
+    action='store_true',
+    help="Check the build dependencies when PEP517 is used."
+)
+
+# see PEP 668: https://peps.python.org/pep-0668/
+pip_install_opts.add_argument(
+    '--break-system-packages',
+    action='store_true',
+    help="Allow pip to modify an EXTERNALLY-MANAGED Python installation."
+)
+
+pip_install_opts.add_argument(
+    '-C',
+    '--config-settings',
+    action='append',
+    metavar='<settings>',
+    help="Configuration settings to be passed to the PEP 517 build backend. "
+         "Settings take the form KEY=VALUE. Use multiple --config-settings "
+         "options to pass multiple keys to the backend."
+)
+
+# NOTE: this option was deprecated in pip v22.3 and removed in v23.1.
+# davos is continuing to support it for now to maintain compatibility
+# with older `pip` versions, but it will be removed in a future release.
+pip_install_opts.add_argument(
     '--install-option',
     action='append',
     metavar='<options>',
@@ -426,6 +451,7 @@ pip_install_opts.add_argument(
          'setup.py install. If you are using an option with a directory path, '
          'be sure to use absolute path.'
 )
+
 pip_install_opts.add_argument(
     '--global-option',
     action='append',
@@ -494,6 +520,8 @@ pip_install_opts.add_argument(
          "installs. This option is implied when any package in a requirements "
          "file has a --hash option."
 )
+
+# NOTE: recent pip versions support only "off" and "on" for this option
 pip_install_opts.add_argument(
     '--progress-bar',
     choices=('off', 'on', 'ascii', 'pretty', 'emoji'),
@@ -501,6 +529,15 @@ pip_install_opts.add_argument(
     help="Specify type of progress to be displayed "
          "[off|on|ascii|pretty|emoji] (default: on)"
 )
+
+pip_install_opts.add_argument(
+    '--root-user-action',
+    choices=('warn', 'ignore'),
[…]

### 2023-06-21 davos/core/core.py
removed a couple stray TODO notes

@@ -378,7 +378,6 @@ def import_name(name):
     return __import__(parts[0])
 
 
-# TODO: move to top?
 class Onion:
     """
     Class representing a single package to be smuggled.
@@ -1029,7 +1028,6 @@ def smuggle(
         install_pkg = True
 
     if install_pkg:
-        # TODO: for v0.2 conda implementation: bypass if -y/--yes passed
         if config.confirm_install and not installer_kwargs.get('no_input'):
             msg = (f"package {pkg_name!r} will be installed with the "
                    f"following command:\n\t`{onion.install_cmd}`\n"

### 2023-06-21 tests/conftest.py
fix regexp for test functions to account for commented-out code

@@ -497,7 +497,7 @@ class JupyterDriver(NotebookDriver):
 
 
 class NotebookFile(pytest.File):
-    test_func_pattern = re.compile(r'(?:^@.+\n)*def test_[^(]+\(.*\):', re.M)
+    test_func_pattern = re.compile(r'(?:^@.+\n)*^def test_[^(]+\(.*\):', re.M)
 
     @staticmethod
     def process_decorators(

### 2023-06-21 tests/conftest.py
write json to notebook file in its original format after editing

@@ -446,7 +446,7 @@ class JupyterDriver(NotebookDriver):
             'name': 'kernel-env'
         }
         with notebook_path.open('w') as nb:
-            json.dump(notebook_json, nb)
+            json.dump(notebook_json, nb, indent=1)
 
     def __init__(
             self,

### 2023-07-11 davos/core/project.py
add --disable-pip-version-check arg to pip list command to ensure output is valid json format

@@ -199,7 +199,12 @@ class Project(metaclass=ProjectChecker):
             self._installed_packages = []
             return
         if site_pkgs_mtime != self._site_packages_mtime:
-            cmd = f'{config.pip_executable} list --path {self.site_packages_dir} --format json'
+            cmd = (
+                f'{config.pip_executable} list '
+                '--disable-pip-version-check '
+                f'--path {self.site_packages_dir} '
+                f'--format json'
+            )
             pip_list_stdout = run_shell_command(cmd, live_stdout=False)
             try:
                 pip_list_json = json.loads(pip_list_stdout)

### 2023-07-12 davos/__init__.py
add top-level require-python function

@@ -21,14 +21,17 @@ __all__ = [
     'get_project',
     'Project',
     'prune_projects',
+    'require_python',
     'smuggle',
     'use_default_project'
 ]
 
 
 import sys
+import warnings
 from types import ModuleType
 
+from packaging.specifiers import SpecifierSet
 if sys.version_info < (3, 8):
     import importlib_metadata as metadata
 else:
@@ -45,7 +48,7 @@ config = DavosConfig()
 
 import davos.implementations
 from davos.core.core import smuggle
-from davos.core.exceptions import DavosConfigError
+from davos.core.exceptions import DavosConfigError, DavosError
 from davos.core.project import (
     DAVOS_CONFIG_DIR,
     DAVOS_PROJECT_DIR,
@@ -229,6 +232,69 @@ def configure(
                     setattr(config, f"_{_name}", old_value)
                 raise
             old_values[name] = old_value
+
+
+def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
+    """
+    Ensure the Python version satisfies a given constraint.
+
+    Specify or constrain the Python version that should be used to run a
+    davos-enhanced notebook. Adding a call to this function before
+    smuggling packages in a notebook can be useful for communicating to
+    users that one or more smuggled packages require a particular Python
+    version or range of versions. If the user's Python version
+    isn't compatible with `version_spec`, this function will raise an
+    error. Additional information can be added to the error message
+    via the `extra_msg` argument. A "soft" or suggested constraint can
+    be specified by passing `warn=True` to issue a warning rather than
+    raise an error.
+
+    Parameters
+    ----------
+    version_spec : str
+        A version specifier string in the format described in PEP 440.
+        See https://peps.python.org/pep-0440/#version-specifiers.
+    warn : bool, optional
+        If True (default: False), issue a warning rather than raising an
+        exception.
+    extra_msg : str, optional
+        Additional message to include in the
+    prereleases : bool, optional
+        Whether to allow prerelease versions. If `None` (default), the
+        rule is autodetected from the version specifier. See
+        https://packaging.pypa.io/en/stable/specifiers.html#packaging.specifiers.SpecifierSet
+
+    Examples
+    --------
+    ```
+    import davos
+
+    pandas_message = "pandas v1.1.3 supports 3.6.1 and above, 3.7, 3.8, and 3.9"
[…]

### 2023-07-12 davos/__init__.py
tweak formatting of incompatible python error message

@@ -285,8 +285,8 @@ def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
     if python_version not in version_constraint:
         msg = (
             "The Python version installed in the environment "
-            f"({python_version}) does not satisfy the constraint "
-            f"{version_constraint}"
+            f"(v{python_version}) does not satisfy the constraint "
+            f"'{version_constraint}'"
         )
         if extra_msg is not None:
             msg = f"{msg}.\n{extra_msg}"

### 2023-07-12 paper/main.tex
fix for frontmatter bug, edits to abstract

--- 2023-06-16 paper/main.tex
@@
 \author{Paxton C. Fitzpatrick}
-\author{Jeremy R. Manning\corref{cor}}
+\author{Jeremy R. Manning\textsuperscript{\textsubscript{\scriptsize *}}}
 \ead{Jeremy.R.Manning@Dartmouth.edu}
@@
   notebook-based Python project, Davos provides a mechanism
-  for specifying (and automatically installing) the correct versions
-  of the project's dependencies.  The Davos package further
+  for specifying the correct versions of the project's 
+  dependencies directly within the code that requires them, 
+  and automatically installing them in an isolated environment 
+  when the code is run. The Davos package further
   ensures that those packages and specific versions are used every
@@
 Section~\ref{subsec:projects}, a notebook's project determines where and how
-any \textttt{smuggle}d dependencies are installed if they are not available in
+any \texttt{smuggle}d dependencies are installed if they are not available in
 the current runtime environment. By default, this attribute is named according
@@
 
-As of this writing, Davos can install packages using \textt{pip}, but
+As of this writing, Davos can install packages using \texttt{pip}, but
 not other standard Python package management systems such as \texttt{conda}.

### 2023-07-13 paper/main.tex
edits to metadata table

@@
   when the code is run. The Davos package further
-  ensures that those packages and specific versions are used every
+  ensures that these packages and specific versions are used every
   time the notebook's code is executed.  This enables researchers to
@@
 \hline
-C1 & Current code version &  v0.1.1 \\
+C1 & Current code version &  v0.2.0 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.0} \\
 \hline
@@
 \hline
-C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.
-Additional tools used for tests: pytest, Selenium, Requests, Mypy, GitHub Actions \\
+C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
 \hline
 C7 & Compilation requirements, operating environments, and
-     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
 \\
@@
 \hline
-C9 & Support email for questions & contextualdynamics@gmail.com \\
+C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
 \hline

### 2023-07-13 paper/main.tex
edits through section 2.1

@@
 Sec.~\ref{subsec:smuggle}) and onion comment (see
-Sec.~\ref{subsec:onion}), and a runtime interface for configuring
-Davos's behavior (see Sec.~\ref{subsec:config}). However,
-certain critical aspects of this
+Sec.~\ref{subsec:onion}), a system for isolating dependencies of
+different projects (see Sec.~\ref{subsec:projects}), and a runtime
+interface for configuring Davos's behavior (see Sec.~\ref{subsec:config}).
+However, certain critical aspects of this
 functionality require (often substantially) different implementations
@@
 IPython~\cite{PereGran07} is used by the notebook kernel). To deal
-with this, environment-dependent parts of core features and behaviors
+with this, environment-dependent components of core features and behaviors
 are isolated and abstracted to ``helper functions'' in the

### 2023-07-14 paper/main.tex
edits through section 2.2.1

@@
   subpackage includes modules for parsing \texttt{smuggle} statements
-  and onion comments, installing and validating packages, and
+  and onion comments, installing and validating packages, isolating and managing and
   configuring Davos's behavior.  The
@@
 consistent location. An additional benefit of this design is that it
-allows maintainers, developers, and users to extend Davos to
-support new, updated, or custom notebook variants by creating new
+allows both maintainers and users to easily extend Davos to
+support new, updated, or custom notebook variants by adding new
 \texttt{davos.implementations} modules that define their own versions
@@
 Sec.~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} keyword-like object can be used as a drop-in
+The \texttt{smuggle} keyword can be used as a drop-in
 replacement for Python's built-in \texttt{import} keyword to load
-packages, modules, and other objects into the current namespace.
+packages, modules, and other objects into the notebook's namespace.
 However, whereas \texttt{import} will fail if the requested package is
@@
 packages on the fly.  If a smuggled package does not exist in the
-local environment, Davos will download and install it automatically,
+user's Python environment, Davos will download and install it automatically,
 expose its contents to Python's \texttt{import} machinery, and load it
-into the namespace for immediate use.
+into the notebook for immediate use.
 
-Installing new packages in a notebook using standard approaches (e.g., system
-commmands) affect the runtime environment. This could lead to undesired
-behaviors. For example, running a notebook that installs new packages in the
-user's primary system environment might alter their main system installation
-and/or containerized environment in unexpected ways (e.g., changing package
-versions, causing conflicts with other packages, etc.). To protect against
-undesired changes to the runtime environment, Davos incorporates its
-own virtual environment for managing packages it installs. When Davos
-is imported, a new virtual environment (folder) is created automatically. The
-folder's name may be customized to support multi-notebook projects. Any
-\texttt{smuggle}d packages that were not available in the notebook's runtime
-environment are installed to the current project folder. The runtime
-environment remains unaffected by Davos's behavior (see
-Sec.~\ref{subsec:projects}).
+Importantly, packages installed by Davos are made available for use in the
+notebook without affecting the user's Python environment. By default,
+\texttt{smuggle} statements install missing packages (and any missing
+dependencies of those packages) into a notebook-specific, virtual
+environment-like directory called a ``project'' (see
+Sec.~\ref{subsec:projects}). When a \texttt{smuggle} statement in a particular
+notebook is executed, Davos will first check for the smuggled package in that
+notebook's corresponding project directory before searching the user's main
+Python environment. In this way, \texttt{smuggle} statements can be substituted
+for \texttt{import} statements to automatically ensure that all packages needed
+to run a notebook are installed and available at runtime without risking
+interfering with dependencies of the user's other Python programs, or other
+Davos-enhanced notebooks.
 

### 2023-07-14 paper/main.tex
edits through section 2.2.2

@@
 use to manually install the package as desired via the command line:
-\begin{center} \includegraphics[width=0.9\textwidth]{figs/snippet1}
-\end{center} Occasionally, a package's distribution name (i.e., the name used
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{figs/snippet1}
+\end{center}
+Occasionally, a package's distribution name (i.e., the name used
 when installing it) may differ from its top-level module name (i.e., the name
@@
 that Davos installs the proper package if it cannot be found locally:
-\begin{center} \includegraphics[width=0.9\textwidth]{figs/snippet2}
-\end{center} Because onion comments may be constructed to specify any aspect of
-the installer's behavior, they provide a mechanism for precisely controlling
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{figs/snippet2}
+\end{center}
+Because onion comments may be constructed to specify any aspect of
+the installer program's behavior, they provide a mechanism for precisely controlling
 how, where, and when smuggled packages are installed. Critically, if an onion
@@
 (or no local installation is found), Davos will download, install, and load a
-suitable version of the package instead: \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet3} \end{center} Onion
-comments can also be used to \texttt{smuggle} specific VCS references (e.g.,
-Git~\cite{TorvHama05} branches, commits, tags, etc.): \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet4} \end{center} Davos
-processes onion comments internally before forwarding arguments to the
-installer program. In addition to preventing onion comments from being used as
-a vehicle for shell injection attacks, this enables Davos to adapt its behavior
+suitable version of the package instead:
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{figs/snippet3}
+\end{center}
+Onion comments can also be used to \texttt{smuggle} specific VCS references (e.g.,
+Git~\cite{TorvHama05} branches, commits, tags, etc.):
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{figs/snippet4}
+\end{center}
+Davos processes onion comments internally before forwarding arguments to the
+installer program. In addition to preventing shared notebooks from executing
+arbitrary code in a user's shell, this enables Davos to adapt its behavior
 based on how particular flags will affect the behavior of the installer
-program. For example, if an onion comment contains either the
-\texttt{-I}/\texttt{--ignore-installed}, \texttt{-U}/\texttt{--upgrade}, or
-\texttt{--force-reinstall} flag, Davos will not bother checking for a local
-copy of the smuggled package before installing a new one: \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/snippet5} \end{center} Similarly,
-the \texttt{--no-input} flag will temporarily enable Davos's non-interactive
-mode (see Sec.~\ref{subsec:config}). Installation flags that affect the user's
-system outside of the current notebook are disabled by default (see
-Sec.~\ref{subsec:projects}), and installing a smuggled package into a custom
-directory (\texttt{<dir>}) using the \texttt{--target <dir>} flag will cause
-Davos to prepend \texttt{<dir>} to the module search path (i.e.,
-\texttt{sys.path}), if necessary, so the package can be imported.
+program. For example, including \texttt{pip}'s \texttt{--no-input} flag will also
+temporarily enable Davos's non-interactive mode (see Sec.~\ref{subsec:config}).
+Similarly, if an onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
+\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag, Davos will
+skip checking for a local copy of the smuggled package before installing a
+new one:
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{figs/snippet5}
+\end{center}
+Since the purpose of an onion comment is to describe how a smuggled package
+should be installed (if necessary) so that it can be loaded and used
+immediately, options that would cause the package not to be installed (such as
+\texttt{-h}/\texttt{--help} or \texttt{--dry-run}) are disallowed. Additionally,
+when using a Davos project to isolate smuggled packages (the default behavior;
+see Sec.~\ref{subsec:projects}), onion comments may not contain options that
+would change the package's installation location (such as
+\texttt{-t}/\texttt{--target}, \texttt{--root}, or \texttt{--prefix}). However, if
+the user disables project-based isolation and specifies \texttt{--target <dir>},
+Davos will ensure that \texttt{<dir>} is included in the module search path (i.e.,
+\texttt{sys.path}), prepending it if necessary, so the package can be loaded.
 

### 2023-07-15 davos/__init__.py
support passing a version identifier without a comparison operator as analogous to passing a compatible release operator

@@ -31,7 +31,7 @@ import sys
 import warnings
 from types import ModuleType
 
-from packaging.specifiers import SpecifierSet
+from packaging.specifiers import InvalidSpecifier, SpecifierSet
 if sys.version_info < (3, 8):
     import importlib_metadata as metadata
 else:
@@ -249,19 +249,31 @@ def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
     be specified by passing `warn=True` to issue a warning rather than
     raise an error.
 
+    `version_spec` may be any valid version specifier defined by PEP
+    440 (see https://peps.python.org/pep-0440/#version-specifiers).
+    Additionally, passing just a version identifier *without* a
+    comparison operator (e.g., "3.9") will be interpreted as a
+    "compatible release" specifier. For example,
+    `davos.require_python("3.9")` is equivalent to
+    `davos.require_python("~=3.9")` and will accept any Python
+    patch/macro version in the 3.9 series (i.e., >=3.9.0,<3.10.0).
+
+
     Parameters
     ----------
     version_spec : str
         A version specifier string in the format described in PEP 440.
-        See https://peps.python.org/pep-0440/#version-specifiers.
+        See https://peps.python.org/pep-0440/#version-specifiers. Bare
+        version identifiers without a comparison operator are also
+        accepted (see above).
     warn : bool, optional
         If True (default: False), issue a warning rather than raising an
         exception.
     extra_msg : str, optional
-        Additional message to include in the
+        Additional text to include in the error or warning message.
     prereleases : bool, optional
         Whether to allow prerelease versions. If `None` (default), the
-        rule is autodetected from the version specifier. See
+        rule is auto-detected from the version specifier. See
         https://packaging.pypa.io/en/stable/specifiers.html#packaging.specifiers.SpecifierSet
 
     Examples
@@ -280,8 +292,20 @@ def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
     msg = "This notebook replicates analyses originally run with Python 3.9.16"
     davos.require_python("==3.9.16", extra_msg=msg)
     """
-    python_version = sys.version.split()[0]
+    valid_specifiers = ('==', '<=', '>=', '!=', '~=', '<', '>')
+    for spec in valid_specifiers:
+        if version_spec.startswith(spec):
+            break
+    else:
+        if version_spec[0].isdigit():
+            version_spec = f'~={version_spec}'
+        else:
+            raise InvalidSpecifier(
[…]

### 2023-07-15 davos/__init__.py
support PEP 440's "arbitrary equality" specifier

@@ -292,7 +292,7 @@ def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
     msg = "This notebook replicates analyses originally run with Python 3.9.16"
     davos.require_python("==3.9.16", extra_msg=msg)
     """
-    valid_specifiers = ('==', '<=', '>=', '!=', '~=', '<', '>')
+    valid_specifiers = ('===', '==', '<=', '>=', '!=', '~=', '<', '>')
     for spec in valid_specifiers:
         if version_spec.startswith(spec):
             break

### 2023-07-15 davos/__init__.py
top-level require_pip function for constraining pip version used to install missing packages

@@ -234,6 +234,79 @@ def configure(
             old_values[name] = old_value
 
 
+def require_pip(version_spec, warn=False, extra_msg=None, prereleases=None):
+    """
+    Ensure the pip version satisfies a given constraint.
+
+    Specify or constrain the pip version that should be used to install
+    smuggled packages in a davos-enhanced notebook. Adding a call to
+    this function before smuggling packages in a notebook can be useful
+    for communicating to users that installing one or more smuggled
+    packages requires a particular pip version (or, more likely, a
+    certain minimum version). This function's behavior and arguments are
+    analogous to those of davos's `require_python` function. See that
+    function's docstring for additional details.
+
+    Parameters
+    ----------
+    version_spec : str
+        A version specifier string in the format described in PEP 440.
+        See https://peps.python.org/pep-0440/#version-specifiers. Bare
+        version identifiers without a comparison operator are also
+        accepted (see the `davos.require_python` function's docstring).
+    warn : bool, optional
+        If `True`, issue a warning rather than raise an exception if the
+        user's pip version doesn't satisfy `version_spec`.
+    extra_msg : str, optional
+        Additional information to include in the error message.
+    prereleases : bool, optional
+        Whether to allow prerelease versions. If `None` (default), the
+        rule is auto-detected from the version specifier. See
+        https://packaging.pypa.io/en/stable/specifiers.html#packaging.specifiers.SpecifierSet
+
+    Examples
+    --------
+    ```
+    import davos
+
+    extra_msg = "pip>=19.0 is needed to install PEP 517-based packages"
+    davos.require_pip('>=19.0', extra_msg=extra_msg)
+    ```
+
+    See Also
+    --------
+    require_python :
+        Analogous function for constraining the user's Python version.
+    """
+    valid_specifiers = ('===', '==', '<=', '>=', '!=', '~=', '<', '>')
+    for spec in valid_specifiers:
+        if version_spec.startswith(spec):
+            break
+    else:
+        if version_spec[0].isdigit():
+            version_spec = f'~={version_spec}'
+        else:
+            raise InvalidSpecifier(
+                f"Invalid version specifier: '{version_spec}'"
+            )
+
+    version_constraint = SpecifierSet(version_spec, prereleases=prereleases)
+    pip_version = metadata.version('pip')
+    if pip_version not in version_constraint:
+        msg = (
[…]

### 2023-07-15 davos/__init__.py
add require_pip to __all__

@@ -21,6 +21,7 @@ __all__ = [
     'get_project',
     'Project',
     'prune_projects',
+    'require_pip',
     'require_python',
     'smuggle',
     'use_default_project'
@@ -330,7 +331,6 @@ def require_python(version_spec, warn=False, extra_msg=None, prereleases=None):
     `davos.require_python("3.9")` is equivalent to
     `davos.require_python("~=3.9")` and will accept any Python
     patch/macro version in the 3.9 series (i.e., >=3.9.0,<3.10.0).
-
 
     Parameters
     ----------

### 2023-07-16 paper/main.tex
additional edits to section 2.2.1

@@
 Importantly, packages installed by Davos are made available for use in the
-notebook without affecting the user's Python environment. By default,
-\texttt{smuggle} statements install missing packages (and any missing
-dependencies of those packages) into a notebook-specific, virtual
+notebook without affecting the user's Python environment or existing packages.
+By default, \texttt{smuggle} statements will install missing packages (and any
+missing dependencies of those packages) into a notebook-specific, virtual
 environment-like directory called a ``project'' (see
-Sec.~\ref{subsec:projects}). When a \texttt{smuggle} statement in a particular
-notebook is executed, Davos will first check for the smuggled package in that
-notebook's corresponding project directory before searching the user's main
-Python environment. In this way, \texttt{smuggle} statements can be substituted
-for \texttt{import} statements to automatically ensure that all packages needed
-to run a notebook are installed and available at runtime without risking
-interfering with dependencies of the user's other Python programs, or other
-Davos-enhanced notebooks.
+Sec.~\ref{subsec:projects}). In turn, \texttt{smuggle} statements executed in a
+particular notebook will preferentially load packages from the notebook's
+project directory whenever they are available, rather than searching for them
+in the user's main Python environment. In this way, \texttt{smuggle}
+statements can be substituted for \texttt{import} statements to automatically
+ensure that all packages needed to run a notebook are installed and available
+at runtime each time the notebook is run, without risking interfering with
+dependencies of the user's other Python programs, or other Davos-enhanced
+notebooks.
 

### 2023-07-16 paper/main.tex
checking in WIP edits to section 2.2.3

@@
 
-Because Davos can install new packages, running the code in a
-Davos-enhanced notebook might (in principle) affect the behavior of
-\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
-altering which packages are installed in the runtime environment. This could
-lead to undesired consequences. For example, suppose Person A develops a
-notebook (Notebook A) for their research project. We will assume that Notebook
-A does not use Davos to manage project dependencies.  If Person A
-runs a Davos-enhanced Notebook B, e.g., sent by another developer,
-might this unexpectedly affect the behavior of Notebook A?
+Standard approaches to installing new packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
+For example, running a notebook that installs its dependencies via IPython system shell commands (prefixed with ``\texttt{!}'') or magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
+This can lead to incompatibilities between packages, affect the behavior of other scripts or notebooks, or even interfere with system applications.
+
+To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Davos projects function similarly to simplified versions of standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few differences: they do not need to be manually activated and deactivated, they do not contain separate Python or \texttt{pip} executables, and they \textit{extend} the main Python environment rather than replace it.
+
+% Davos implements a custom scheme for isolating packages installed by \texttt{smuggle} statements, called ``projects.''
+
+%A Davos project consists of a directory 
+%
+%
+% function similarly to simplified versions of 
+%
+%
+%
+%Additionally, Davos projects \textit{extend}, rather than replace, the main Python environment. 
+%
+%
+%Davos projects function similarly to a simplified version of a virtual environment created with Python's built-in \texttt{venv} module, or a third-party tool like
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ADD THIS EITHER TO START OF PROJECTS SUBSUBSECTION OR IN IMPACT SECTION   %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%Standard approaches to installing new packages from within a notebook can alter a user's Python environment in potentially unexpected and undesired ways.
+For example, running a notebook that installs its dependencies using IPython system shell commands (prefixed with ``\texttt{!}'') or magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
+This can lead to conflicts between package versions, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
+%
+%A common way of avoiding this is to create a virtual environment in which to run the notebook, and instruct anyone with whom the notebook is shared to do the same.
+While effective, this added requirement introduces additional
+%
+%
+%(or group of related notebooks) that require different 
+%
+%
+%\begin{itemize}
+%  \item{common solution is to use a virtual environment}
+%  \item{this introduces complexity}
+%  \item{davos's solution is projects}
+%\end{itemize}
+
+%Standard approaches to installing new packages from within a notebook (e.g., system shell commands prefixed with ``\texttt{!}'' or IPython magic commands prefixed with ``\texttt{\%}'') can alter the local Python environment in potentially unexpected and undesired ways.
+For example, running a notebook that installs its dependencies in the user's main environment may cause other existing packages to be uninstalled and replaced with alternate versions.
+This can lead to conflicts between package versions, affect the behavior of the user's other scripts or notebooks, or even break system applications.
+
+%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos implements its own virtual environment-like scheme for isolating packages it installs.
+
+\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
+
+%Because Davos can install new packages, running the code in a
+%Davos-enhanced notebook might (in principle) affect the behavior of
+%\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
+%altering which packages are installed in the runtime environment. This could
+%lead to undesired consequences. For example, suppose Person A develops a
+%notebook (Notebook A) for their research project. We will assume that Notebook
+%A does not use Davos to manage project dependencies.  If Person A
+%runs a Davos-enhanced Notebook B, e.g., sent by another developer,
+%might this unexpectedly affect the behavior of Notebook A?
+
+%To prevent unwanted
+%changes to the user's Python environment, Davos incorporates its
+%own virtual environment-like scheme for isolating packages it installs. When Davos
+%is imported, a new virtual environment (folder) is created automatically. The
+%folder's name may be customized to support multi-notebook projects. Any
+%\texttt{smuggle}d packages that were not available in the notebook's runtime
+%environment are installed to the current project folder. The runtime
+%environment remains unaffected by Davos's behavior (see
+%Sec.~\ref{subsec:projects}).
+%By default, projects are notebook-specific, but can also be shared by multiple notebooks, and can be managed interactively from within a Davos-enhanced notebook.
+
+%%%%%%%% JEREMY VERSION %%%%%%%%%
+%Installing new packages in a notebook using standard approaches (e.g., system commmands) affect the
+%runtime environment. This could lead to undesired behaviors. For example, running a notebook that
+%installs new packages in the user’s primary system environment might alter their main system installation
+%and/or containerized environment in unexpected ways (e.g., changing package versions, causing conflicts
+%with other packages, etc.). To protect against undesired changes to the runtime environment, Davos
+%incorporates its own virtual environment for managing packages it installs. When Davos is imported,
+%a new virtual environment (folder) is created automatically. The folder’s name may be customized to
+%support multi-notebook projects. Any smuggled packages that were not available in the notebook’s
+%runtime environment are installed to the current project folder. The runtime environment remains unaffected
+%by Davos’s behavior (see Sec. 2.2.3).
 

### 2023-07-16 paper/main.tex
fixed corresponding author notation issue

@@
 \author{Paxton C. Fitzpatrick}
-\author{Jeremy R. Manning\textsuperscript{\textsubscript{\scriptsize *}}}
+\author{Jeremy R. Manning\corref{cor}}
 \ead{Jeremy.R.Manning@Dartmouth.edu}
@@
 
-Since its initial release, Davos has found use in a variety of
-applications. In addition to managing computing environments for multiple prior
-and ongoing research studies~\citep{MannEtal23, OwenMann23, ZimaEtal23},
-Davos is being used by both students and instructors in programming
-and methods courses such as Storytelling with Data~\cite{Mann21d} (an open
-course on data science, visualization, and communication) and Laboratory in
-Psychological Science~\cite{Mann22} (an open course on experimental and
-statistical methods for psychology research) to simplify distributing lessons
-and submitting assignments, as well as in online demos such as
+Since its initial release, Davos has found use in a variety of applications. In
+addition to managing computing environments for multiple prior and ongoing
+research studies~\citep{MannEtal23, OwenMann23, ZimaEtal23}, Davos is being
+used by both students and instructors in programming and methods courses such
+as Storytelling with Data~\cite{Mann21d} (an open course on data science,
+visualization, and communication) and Laboratory in Psychological
+Science~\cite{Mann22} (an open course on experimental and statistical methods
+for psychology research) to simplify distributing lessons and submitting
+assignments, as well as in online demos such as
 \texttt{abstract2paper}~\cite{Mann21e} (an example application of
 GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
-dependencies automatically.
+dependencies automatically. The 2023 offering of Neuromatch
+Academy~\cite{Neuromatch} also included an ``experimental'' module that uses
+Davos to manage dependencies related to a large language model-based
+tutor~\cite{Chatify}.
 
@@
 dependencies, there are some edge cases and limitations that are worth
-considering. Many Python packages include (in their \texttt{setup} options)
-additional dependencies that often carry their own version specifications.
-Although Davos will check that the correct version of the requested
-top-level package is installed and imported into the workspace, the version
-numbers of any \textit{dependencies} of the request package are \textit{not}
-checked. In principle, this could lead to unexpected behavior, for example if a
-given package's dependencies (or dependencies of those dependencies, etc.) were
-left under-specified. A developer could mitigate this by explicitly smuggling
-exact version numbers of \textit{every} project dependency (e.g., obtained via
-\texttt{pip freeze}). However, for projects where the versions of dependencies
-of \texttt{smuggle}d packages also need to be precisely controlled, a lockfile
-or a \texttt{requirements.txt} file produced by \texttt{pip freeze} (i.e.,
-explicitly specifying \textit{all} package's version numbers) may provide a
-more comprehensive alternative to Davos.
-
-Reproducibility is not solely about dependency management. In addition to
-ensuring that project dependencies are satisfied, the user running a given
-notebook must also execute the code in the indicated order. For example, the
-cells in a notebook may be manually run out of order. If different cells in a
-Davos-enhanced notebook made use of different versions of the same
+considering. First, reproducibility is not solely about dependency management.
+In addition to ensuring that project dependencies are satisfied, the user
+running a given notebook must also execute the code in the indicated order. For
+example, the cells in a notebook may be manually run out of order. If different
+cells in a Davos-enhanced notebook made use of different versions of the same
 package, this could result in \textit{more} confusion or \textit{greater}
@@
 important to execute notebook cells in order than would be the case in the
-standard (non-Davos) setup.  We suggest that developers who wish to use
-Davos include notes regarding which cells must be executed in sequence.
-
-As of this writing, Davos can install packages using \texttt{pip}, but
-not other standard Python package management systems such as \texttt{conda}.
+standard (non-Davos) setup. One approach to mitigating this risk for notebooks
+that use several versions of the same library would be to include
+\texttt{smuggle} statements in the same cell(s) where the library was called. A
+second approach would be for developers who wish to use Davos to include notes
+regarding which cells must be executed in sequence. This is already a common
+practice for notebooks that include system calls to install required packages
+and dependencies, and the same approach would work well for Davos-enhanced
+notebooks as well.
+
+A second limitation of Davos relates to how packages are installed and managed.
+As of this writing, Davos can install packages using \texttt{pip}, but not
+other standard Python package management systems such as \texttt{conda}.
 Therefore packages that are not installable via \texttt{pip} are currently
-unsupported by Davos.  We anticipate adding support for other
-package management systems, including \texttt{conda} in a future release.
+unsupported by Davos. We anticipate adding support for other package management
+systems, including \texttt{conda}, in a future release.
+
+A third limitation of Davos is that it cannot be used to manage projects that
+depend on non-Python software. For example, system software or libraries from
+other languages (e.g., in a mixed Python and R notebook), cannot be
+\texttt{smuggle}d by Davos. A notebook that utilizes or depends on non-Python
+software would therefore need to use existing non-Davos approaches to managing
+those requirements.
 

### 2023-08-05 paper/main.tex
update main.tex with updated bibtex keys

@@
 for building and working with machine learning models, and
-\texttt{UMAP}~\cite{McInEtal18b}, a package that implements a family
+\texttt{UMAP}~\cite{McInEtal18}, a package that implements a family
 of related manifold learning techniques. The onion comment in line 19
@@
 addition to managing computing environments for multiple prior and ongoing
-research studies~\citep{MannEtal23, OwenMann23, ZimaEtal23}, Davos is being
+research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
 used by both students and instructors in programming and methods courses such
-as Storytelling with Data~\cite{Mann21d} (an open course on data science,
+as Storytelling with Data~\cite{Mann21a} (an open course on data science,
 visualization, and communication) and Laboratory in Psychological
@@
 assignments, as well as in online demos such as
-\texttt{abstract2paper}~\cite{Mann21e} (an example application of
+\texttt{abstract2paper}~\cite{Mann21b} (an example application of
 GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
 dependencies automatically. The 2023 offering of Neuromatch
-Academy~\cite{Neuromatch} also included an ``experimental'' module that uses
+Academy~\cite{vanVEtal21} also included an ``experimental'' module that uses
 Davos to manage dependencies related to a large language model-based
-tutor~\cite{Chatify}.
+tutor~\cite{MannEtal23b}.
 
@@
 to providing notebook-specific functionality (e.g.,
-\cite{Hunt07,HeusEtal18a}), this approach also has the potential to be
+\cite{Hunt07,HeusEtal18}), this approach also has the potential to be
 exploited for more nefarious purposes. For example, a malicious user

### 2023-08-07 paper/main.tex

@@
 Sec.~\ref{subsec:projects}). In turn, \texttt{smuggle} statements executed in a
-particular notebook will preferentially load packages from the notebook's
+particular notebook will preferentially load packages from that notebook's
 project directory whenever they are available, rather than searching for them
@@
 
-Standard approaches to installing new packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies via IPython system shell commands (prefixed with ``\texttt{!}'') or magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
-This can lead to incompatibilities between packages, affect the behavior of other scripts or notebooks, or even interfere with system applications.
-
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Davos projects function similarly to simplified versions of standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few differences: they do not need to be manually activated and deactivated, they do not contain separate Python or \texttt{pip} executables, and they \textit{extend} the main Python environment rather than replace it.
-
-% Davos implements a custom scheme for isolating packages installed by \texttt{smuggle} statements, called ``projects.''
-
-%A Davos project consists of a directory
-%
-%
-% function similarly to simplified versions of
-%
-%
-%
-%Additionally, Davos projects \textit{extend}, rather than replace, the main Python environment.
-%
-%
-%Davos projects function similarly to a simplified version of a virtual environment created with Python's built-in \texttt{venv} module, or a third-party tool like
+Standard approaches to installing packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
+For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
+This can lead to incompatibilities between installed packages, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
+
+To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task.
+However, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.
+
+When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already). 
+%When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already), named for the absolute path to the notebook file.
+
+Notebook-specific projects are named for the absolute path to the notebook file.
+
+ %Davos projects function similarly to simplified versions of standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few differences: they do not need to be manually activated and deactivated, they do not contain separate Python or \texttt{pip} executables, and they \textit{extend} the main Python environment rather than replace it.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%Standard approaches to installing new packages from within a notebook can alter a user's Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies using IPython system shell commands (prefixed with ``\texttt{!}'') or magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
-This can lead to conflicts between package versions, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
-%
 %A common way of avoiding this is to create a virtual environment in which to run the notebook, and instruct anyone with whom the notebook is shared to do the same.
@@
 %\end{itemize}
-
-%Standard approaches to installing new packages from within a notebook (e.g., system shell commands prefixed with ``\texttt{!}'' or IPython magic commands prefixed with ``\texttt{\%}'') can alter the local Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies in the user's main environment may cause other existing packages to be uninstalled and replaced with alternate versions.
-This can lead to conflicts between package versions, affect the behavior of the user's other scripts or notebooks, or even break system applications.
-
-%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos implements its own virtual environment-like scheme for isolating packages it installs.
 

### 2023-08-07 davos/core/project.py
patches for determining Project type/subclass in colab notebooks

@@ -305,6 +305,17 @@ class Project(metaclass=ProjectChecker):
             (i.e., no packages have been installed into it).
         """
         new_project_name, new_project_type = _get_project_name_type(new_name)
+        if config.environment == 'Colaboratory':
+            # colab name/type logic works slightly differently and needs
+            # to be handled separately
+            new_project_name = Path(new_project_name).name
+            # currently running notebook should be the only "real" one
+            # for the current VM session
+            curr_nb_name = get_notebook_path()
+            if new_project_name == curr_nb_name:
+                new_project_type = ConcreteProject
+            else:
+                new_project_type = AbstractProject
         if new_project_name == self.name:
             # no change
             return
@@ -849,5 +860,8 @@ def use_default_project():
     else:
         proj_name = get_notebook_path()
 
-    default_project = Project(proj_name)
+    # will always be an absolute path to a real Jupyter notebook file,
+    # or name of real Colab notebook, so we can skip project type
+    # decision logic
+    default_project = ConcreteProject(proj_name)
     config.project = default_project

### 2023-08-07 davos/core/project.py
simpler patch for project type detection in colab

@@ -305,17 +305,6 @@ class Project(metaclass=ProjectChecker):
             (i.e., no packages have been installed into it).
         """
         new_project_name, new_project_type = _get_project_name_type(new_name)
-        if config.environment == 'Colaboratory':
-            # colab name/type logic works slightly differently and needs
-            # to be handled separately
-            new_project_name = Path(new_project_name).name
-            # currently running notebook should be the only "real" one
-            # for the current VM session
-            curr_nb_name = get_notebook_path()
-            if new_project_name == curr_nb_name:
-                new_project_type = ConcreteProject
-            else:
-                new_project_type = AbstractProject
         if new_project_name == self.name:
             # no change
             return
@@ -504,6 +493,14 @@ def _get_project_name_type(project_name):
         )
 
     project_type = ConcreteProject
+    if config.environment == 'Colaboratory':
+        # colab name/type logic works slightly differently -- there's
+        # only ever one "real" notebook per VM session, but it doesn't
+        # exist on the VM filesystem
+        curr_notebook_name = get_notebook_path()
+        if project_name == curr_notebook_name:
+            return project_name, project_type
+        return project_name, AbstractProject
     if project_name.endswith('.ipynb'):
         # `project_name` is a path to a notebook file, either the
         # default (absolute path to the current notebook) or

### 2023-08-16 paper/main.tex
[DATALAD RUNCMD] run codespell throughout but ignore fail
=== Do not change lines below ===
{
 "chain": [],
 "cmd": "codespell -w || :",
 "exit": 0,
 "extra_inputs": [],
 "inputs": [],
 "outputs": [],
 "pwd": "."
}
^^^ Do not change lines above ^^^

@@
 %%%%%%%% JEREMY VERSION %%%%%%%%%
-%Installing new packages in a notebook using standard approaches (e.g., system commmands) affect the
+%Installing new packages in a notebook using standard approaches (e.g., system commands) affect the
 %runtime environment. This could lead to undesired behaviors. For example, running a notebook that
@@
 additional environments each providing their own separate,
-interchangeable IPython kernels.  To accomodate this multi-environment
+interchangeable IPython kernels.  To accommodate this multi-environment
 scenario, on lines 26 and 28, we use the \texttt{pip\_executable} option to control which environments each
@@
 (Sec.~\ref{subsec:projects}). In many setups this feature can eliminate the
-need to set up a seperate virtual environment or container (e.g., in
+need to set up a separate virtual environment or container (e.g., in
 conjunction with a \texttt{requirements.txt}, \texttt{project.toml}, or

### 2023-08-21 paper/old/main-old.tex

--- 2023-08-16 paper/main.tex
@@
 \usepackage{geometry}
-
-\geometry{left=1in, right=1in, top=1in, bottom=1in, headsep=0pt}
+\geometry{left=1in,right=1in,top=1in,bottom=1in,headsep=0pt}
 
@@
 
-\title{Davos: a Python package ``smuggler'' for constructing
+\title{\texttt{davos}: a Python package ``smuggler'' for constructing
   lightweight reproducible notebooks}
@@
   science. Here, we propose a lighter-weight solution: the
-  Davos package.  When used in combination with a
-  notebook-based Python project, Davos provides a mechanism
-  for specifying the correct versions of the project's
-  dependencies directly within the code that requires them,
-  and automatically installing them in an isolated environment
-  when the code is run. The Davos package further
-  ensures that these packages and specific versions are used every
+  \texttt{davos} package.  When used in combination with a
+  notebook-based Python project, \texttt{davos} provides a mechanism
+  for specifying (and automatically installing) the correct versions
+  of the project's dependencies.  The \texttt{davos} package further
+  ensures that those packages and specific versions are used every
   time the notebook's code is executed.  This enables researchers to
@@
 \hline
-C1 & Current code version &  v0.2.0 \\
+C1 & Current code version &  v0.1.1 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.0} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.1.1} \\
 \hline
@@
 \hline
-C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.\newline Additional tools used for tests: pytest, Selenium, Requests, mypy, GitHub Actions \\
+C6 & Software code languages, tools, and services used & Python, JavaScript, PyPI/pip, IPython, Jupyter, ipykernel, PyZMQ.
+Additional tools used for tests: pytest, Selenium, Requests, Mypy, GitHub Actions \\
 \hline
 C7 & Compilation requirements, operating environments, and
-     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.~Supported OSes: MacOS, Linux, Unix-like.~Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
 \\
@@
 \hline
-C9 & Support email for questions & \href{mailto:contextualdynamics@gmail.com}{contextualdynamics@gmail.com} \\
+C9 & Support email for questions & contextualdynamics@gmail.com \\
 \hline
@@
 unspecified, replicating the original computing environment becomes
-difficult or impossible~\citep{PimeEtal19}.
+difficult or impossible.
 
@@
   text, executable code, and media (including rendered figures, code
-  output, etc.).  When the \textbf{Davos package} is imported
+  output, etc.).  When the \textbf{\texttt{davos} package} is imported
   into a Jupyter notebook, the notebook's functionality is extended to
@@
   precise control over dependencies and versioning.  Notebooks
-  enhanced using the Davos package are easily shareable and
+  enhanced using the \texttt{davos} package are easily shareable and
   require minimal setup costs, while also facilitating high
@@
 
-We designed Davos to occupy a ``sweet spot'' between these extremes.
-Davos is a notebook-installable package that adds functionality to the
-default notebook experience. Like standard Jupyter notebooks,
-Davos-enhanced notebooks allow researchers to include text, executable
-code, and media within a single file. No further setup or installation is
-required from the user, beyond what is needed to run standard Jupyter
-notebooks. And like virtual environments, Davos provides a convenient
-mechanism for fully specifying (and installing, as needed) a complete set of
-Python dependencies, including specific package versions, which are contained
-and isolated from the rest of the user's system.
+We designed \texttt{davos} to occupy a ``sweet spot'' between these
+extremes.  \texttt{davos} is a notebook-installable package that adds
+functionality to the default notebook experience. Like standard
+Jupyter notebooks, \texttt{davos}-enhanced notebooks allow researchers
+to include text, executable code, and media within a single file. No
+further setup or installation is required, beyond what is needed to
+run standard Jupyter notebooks. And like virtual environments,
+\texttt{davos} provides a convenient mechanism for fully specifying
+(and installing, as needed) a complete set of Python dependencies,
+including specific package versions.
 
@@
 
-The Davos package is named after Davos Seaworth, a smuggler referred
-to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by
-George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by
-Davos is a play on Python's \texttt{import} keyword: whereas importing
-can load a package into the Python workspace within the existing rules and
-frameworks provided by the Python language, ``smuggling'' provides an
-alternative that expands the scope and reach of ``importing.'' Like the
-character Davos Seaworth (who became famous for smuggling onions through a
-blockade on his homeland), we use ``onion'' comments to precisely control how
-packages are smuggled into the Python workspace.
+The \texttt{davos} package is named after Davos Seaworth, a smuggler
+referred to as ``the Onion Knight" from the series \textit{A Song of
+  Ice and Fire} by George R. R. Martin~\cite{Mart98}.  The
+\texttt{smuggle} keyword provided by \texttt{davos}
+is a play on Python's \texttt{import} keyword: whereas importing can
+load a package into the Python workspace within the existing rules
+and frameworks provided by the Python language, ``smuggling'' provides
+an alternative that expands the scope and reach of ``importing.''
+Like the character Davos Seaworth (who became famous for smuggling
+onions through a blockade on his homeland), we use ``onion'' comments
+to precisely control how packages are smuggled into the Python
+workspace.
 
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The Davos package
+\caption{\small \textbf{Package structure.} The \texttt{davos} package
   comprises two interdependent subpackages.  The \texttt{davos.core}
   subpackage includes modules for parsing \texttt{smuggle} statements
-  and onion comments, installing and validating packages, isolating and managing and
-  configuring Davos's behavior.  The
+  and onion comments, installing and validating packages, and
+  configuring \texttt{davos}'s behavior.  The
   \texttt{davos.implementations} subpackage includes
@@
 
-The Davos package consists of two interdependent subpackages
+The \texttt{davos} package consists of two interdependent subpackages
 (see Fig.~\ref{fig:package-structure}). The first,
@@
 Sec.~\ref{subsec:smuggle}) and onion comment (see
-Sec.~\ref{subsec:onion}), a system for isolating dependencies of
-different projects (see Sec.~\ref{subsec:projects}), and a runtime
-interface for configuring Davos's behavior (see Sec.~\ref{subsec:config}).
-However, certain critical aspects of this
+Sec.~\ref{subsec:onion}), and a runtime interface for configuring
+\texttt{davos}'s behavior (see Sec.~\ref{subsec:config}). However,
+certain critical aspects of this
 functionality require (often substantially) different implementations
 depending on properties of the notebook environment in which
-Davos is used (e.g., whether the frontend is provided by
+\texttt{davos} is used (e.g., whether the frontend is provided by
 Jupyter or Google Colaboratory, or which version of
 IPython~\cite{PereGran07} is used by the notebook kernel). To deal
-with this, environment-dependent components of core features and behaviors
+with this, environment-dependent parts of core features and behaviors
 are isolated and abstracted to ``helper functions'' in the
@@
 organized into modules by the conditions that trigger their use. At
-runtime, Davos detects various features in the notebook
+runtime, \texttt{davos} detects various features in the notebook
 environment and selectively imports a single version of each helper
@@
 consistent location. An additional benefit of this design is that it
-allows both maintainers and users to easily extend Davos to
-support new, updated, or custom notebook variants by adding new
+allows maintainers, developers, and users to extend \texttt{davos} to
+support new, updated, or custom notebook variants by creating new
 \texttt{davos.implementations} modules that define their own versions
@@
 
-Functionally, importing Davos in an IPython notebook enables
+Functionally, importing \texttt{davos} in an IPython notebook enables
 an additional Python keyword: ``\texttt{smuggle}'' (see
 Sec.~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} keyword can be used as a drop-in
+The \texttt{smuggle} keyword-like object can be used as a drop-in
 replacement for Python's built-in \texttt{import} keyword to load
-packages, modules, and other objects into the notebook's namespace.
+packages, modules, and other objects into the current namespace.
 However, whereas \texttt{import} will fail if the requested package is
@@
 packages on the fly.  If a smuggled package does not exist in the
-user's Python environment, Davos will download and install it automatically,
+local environment, \texttt{davos} will download and install it automatically,
 expose its contents to Python's \texttt{import} machinery, and load it
-into the notebook for immediate use.
-
-Importantly, packages installed by Davos are made available for use in the
-notebook without affecting the user's Python environment or existing packages.
-By default, \texttt{smuggle} statements will install missing packages (and any
-missing dependencies of those packages) into a notebook-specific, virtual
-environment-like directory called a ``project'' (see
-Sec.~\ref{subsec:projects}). In turn, \texttt{smuggle} statements executed in a
-particular notebook will preferentially load packages from that notebook's
-project directory whenever they are available, rather than searching for them
-in the user's main Python environment. In this way, \texttt{smuggle}
-statements can be substituted for \texttt{import} statements to automatically
-ensure that all packages needed to run a notebook are installed and available
-at runtime each time the notebook is run, without risking interfering with
-dependencies of the user's other Python programs, or other Davos-enhanced
-notebooks.
+into the namespace for immediate use.
 
@@
 
-For greater control over the behavior of \texttt{smuggle} statements, Davos
-defines an additional construct called the ``onion comment.'' An onion comment
-is a special type of inline comment that may be placed on a line containing a
-\texttt{smuggle} statement to customize how Davos searches for the smuggled
-package locally and, if necessary, downloads and installs it. Onion comments
-follow a simple format based on the ``type comment'' syntax introduced in PEP
-484~\cite{vanREtal14}, and are designed to make managing packages with Davos
-intuitive and familiar. To construct an onion comment, users provide the name
-of the installer program (e.g., \texttt{pip}) and the same arguments one would
-use to manually install the package as desired via the command line:
+For greater control over the behavior of \texttt{smuggle} statements,
+\texttt{davos} defines an additional construct called the ``onion
+comment.'' An onion comment is a special type of inline comment that
+may be placed on a line containing a \texttt{smuggle} statement to
+customize how \texttt{davos} searches for the smuggled package locally
+and, if necessary, downloads and installs it. Onion comments follow a
+simple format based on the ``type comment'' syntax introduced in PEP
+484~\cite{vanREtal14}, and are designed to make managing packages with
+\texttt{davos} intuitive and familiar. To construct an onion comment,
+users provide the name of the installer program (e.g., \texttt{pip})
+and the same arguments one would use to manually install the package
+as desired via the command line:
 \begin{center}
@@
 \end{center}
-Occasionally, a package's distribution name (i.e., the name used
-when installing it) may differ from its top-level module name (i.e., the name
-used when importing it). In such cases, an onion comment may be used to ensure
-that Davos installs the proper package if it cannot be found locally:
+Occasionally, a package's distribution name (i.e., the name used when
+installing it) may differ from its top-level module name (i.e., the
+name used when importing it). In such cases, an onion comment may be
+used to ensure that \texttt{davos} installs the proper package if it
+cannot be found locally:
 \begin{center}
@@
 \end{center}
-Because onion comments may be constructed to specify any aspect of
-the installer program's behavior, they provide a mechanism for precisely controlling
-how, where, and when smuggled packages are installed. Critically, if an onion
-comment includes a version specifier~\cite{CoghStuf13}, Davos will ensure that
-the version of the package loaded into the notebook matches the specific
-version requested, or satisfies the given version constraints. If the smuggled
-package exists locally, Davos will extract its version information from its
-metadata and compare it to the specifier provided. If the two are incompatible
-(or no local installation is found), Davos will download, install, and load a
-suitable version of the package instead:
+Because onion comments may be constructed to specify any aspect of the
+installer's behavior, they provide a mechanism for precisely
+controlling how, where, and when smuggled packages are installed.
+Critically, if an onion comment includes a version
+specifier~\cite{CoghStuf13}, \texttt{davos} will ensure that the
+version of the package loaded into the notebook matches the specific
+version requested, or satisfies the given version constraints. If the
+smuggled package exists locally, \texttt{davos} will extract its
+version information from its metadata and compare it to the specifier
+provided. If the two are incompatible (or no local installation is
+found), \texttt{davos} will download, install, and load a suitable
+version of the package instead:
 \begin{center}
@@
 \end{center}
-Onion comments can also be used to \texttt{smuggle} specific VCS references (e.g.,
-Git~\cite{TorvHama05} branches, commits, tags, etc.):
+Onion comments can also be used to \texttt{smuggle} specific VCS references
+(e.g., Git~\cite{TorvHama05} branches, commits, tags, etc.):
 \begin{center}
@@
 \end{center}
-Davos processes onion comments internally before forwarding arguments to the
-installer program. In addition to preventing shared notebooks from executing
-arbitrary code in a user's shell, this enables Davos to adapt its behavior
-based on how particular flags will affect the behavior of the installer
-program. For example, including \texttt{pip}'s \texttt{--no-input} flag will also
-temporarily enable Davos's non-interactive mode (see Sec.~\ref{subsec:config}).
-Similarly, if an onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
-\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag, Davos will
-skip checking for a local copy of the smuggled package before installing a
-new one:
+\texttt{davos} processes onion comments internally before forwarding
+arguments to the installer program. In addition to preventing onion
+comments from being used as a vehicle for shell injection attacks,
+this enables \texttt{davos} to adapt its behavior based on how particular
+flags will affect the behavior of the installer program. For example, if an
+onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
+\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag,
+\texttt{davos} will not bother checking for a local copy of the smuggled
+package before installing a new one:
 \begin{center}
@@
 \end{center}
-Since the purpose of an onion comment is to describe how a smuggled package
-should be installed (if necessary) so that it can be loaded and used
-immediately, options that would cause the package not to be installed (such as
-\texttt{-h}/\texttt{--help} or \texttt{--dry-run}) are disallowed. Additionally,
-when using a Davos project to isolate smuggled packages (the default behavior;
-see Sec.~\ref{subsec:projects}), onion comments may not contain options that
-would change the package's installation location (such as
-\texttt{-t}/\texttt{--target}, \texttt{--root}, or \texttt{--prefix}). However, if
-the user disables project-based isolation and specifies \texttt{--target <dir>},
-Davos will ensure that \texttt{<dir>} is included in the module search path (i.e.,
-\texttt{sys.path}), prepending it if necessary, so the package can be loaded.
+Similarly, the \texttt{--no-input} flag will temporarily enable
+\texttt{davos}'s non-interactive mode (see
+Sec.~\ref{subsec:config}), and installing a smuggled package into a
+custom directory (\texttt{<dir>}) using the \texttt{--target <dir>}
+flag will cause \texttt{davos} to prepend \texttt{<dir>} to the module
+search path (i.e., \texttt{sys.path}), if necessary, so the package
+can be imported.
 
-\subsubsection{Projects}\label{subsec:projects}
+\subsubsection{The \texttt{davos} config object}\label{subsec:config}
 
-Standard approaches to installing packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
-This can lead to incompatibilities between installed packages, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
-
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task.
-However, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.
-
-When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already). 
-%When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already), named for the absolute path to the notebook file.
-
-Notebook-specific projects are named for the absolute path to the notebook file.
-
- %Davos projects function similarly to simplified versions of standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few differences: they do not need to be manually activated and deactivated, they do not contain separate Python or \texttt{pip} executables, and they \textit{extend} the main Python environment rather than replace it.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ADD THIS EITHER TO START OF PROJECTS SUBSUBSECTION OR IN IMPACT SECTION   %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A common way of avoiding this is to create a virtual environment in which to run the notebook, and instruct anyone with whom the notebook is shared to do the same.
-While effective, this added requirement introduces additional
-%
-%
-%(or group of related notebooks) that require different 
-%
-%
-%\begin{itemize}
-%  \item{common solution is to use a virtual environment}
-%  \item{this introduces complexity}
-%  \item{davos's solution is projects}
-%\end{itemize}
-
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
-
-%Because Davos can install new packages, running the code in a
-%Davos-enhanced notebook might (in principle) affect the behavior of
-%\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
-%altering which packages are installed in the runtime environment. This could
-%lead to undesired consequences. For example, suppose Person A develops a
-%notebook (Notebook A) for their research project. We will assume that Notebook
-%A does not use Davos to manage project dependencies.  If Person A
-%runs a Davos-enhanced Notebook B, e.g., sent by another developer,
-%might this unexpectedly affect the behavior of Notebook A?
-
-%To prevent unwanted
-%changes to the user's Python environment, Davos incorporates its
-%own virtual environment-like scheme for isolating packages it installs. When Davos
-%is imported, a new virtual environment (folder) is created automatically. The
-%folder's name may be customized to support multi-notebook projects. Any
-%\texttt{smuggle}d packages that were not available in the notebook's runtime
-%environment are installed to the current project folder. The runtime
-%environment remains unaffected by Davos's behavior (see
-%Sec.~\ref{subsec:projects}).
-%By default, projects are notebook-specific, but can also be shared by multiple notebooks, and can be managed interactively from within a Davos-enhanced notebook.
-
-%%%%%%%% JEREMY VERSION %%%%%%%%%
-%Installing new packages in a notebook using standard approaches (e.g., system commands) affect the
-%runtime environment. This could lead to undesired behaviors. For example, running a notebook that
-%installs new packages in the user’s primary system environment might alter their main system installation
-%and/or containerized environment in unexpected ways (e.g., changing package versions, causing conflicts
-%with other packages, etc.). To protect against undesired changes to the runtime environment, Davos
-%incorporates its own virtual environment for managing packages it installs. When Davos is imported,
-%a new virtual environment (folder) is created automatically. The folder’s name may be customized to
-%support multi-notebook projects. Any smuggled packages that were not available in the notebook’s
-%runtime environment are installed to the current project folder. The runtime environment remains unaffected
-%by Davos’s behavior (see Sec. 2.2.3).
-
-We implemented a ``project'' system in Davos to protect against the
-above scenario. By default, importing Davos creates a new project
-folder in the user's home directory (contained within a hidden \texttt{.davos}
-folder). The default project name is computed to uniquely identify each
-notebook according to its filename and path. Any packages that were not
-originally available in the notebook's runtime environment are installed to the
-notebook's project directory. When external libraries are \texttt{smuggle}d,
-Davos temporally appends the current project directory to the search
-path. Because the user's system path remains unchanged, and because none of the
-runtime environment's packages are altered, the user's system and runtime
-environment remain unaffected (aside from installing the Davos package
-itself to the runtime environment).
-
-Each notebook's project may be customized by setting \texttt{davos.project} to
-any string that can be used as a valid folder name in the user's operating
-system. By customizing the project name, users can build multi-notebook
-projects that share the same core set of dependencies without needing to
-duplicate each package for each notebook in the project.
-
-Finally, if the user \textit{does} wish to modify their runtime environment,
-this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
-will cause any packages installed by Davos to affect the user's
-runtime environment.  This is generally not recommended, as it can lead to
-unintended consequences for other code that shares the runtime environment.
-
-\subsubsection{Configuring and querying Davos}\label{subsec:config}
-
-Davos's behavior may be customized by modifying a set of attributes attached to
-the \texttt{davos} module object that is added to the workspace when Davos is
-imported. These attributes may be modified, displayed, or checked
-programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
-illustrative example or Sec.~\ref{subsec:implementation} for implementation
-details and additional information). These include:
+The \texttt{davos} config object provides a high-level interface for
+controlling various aspects of \texttt{davos}'s behavior. After
+importing \texttt{davos}, the \texttt{davos.con\-fig} object (a
+singleton) exposes configurable options as attributes that can be
+modified, displayed in the notebook, or checked programmatically at runtime
+(see Sec.~\ref{sec:illustrative-example} for an illustrative example or
+Sec.~\ref{subsec:implementation} for implementation details and
+additional information). These include:
 
@@
   statements and onion comments is enabled (\texttt{True}) or
-  disabled (\texttt{False}).  When Davos is first imported,
+  disabled (\texttt{False}).  When \texttt{davos} is first imported,
   the \texttt{.active} attribute is set to \texttt{True}.
@@
 \item \texttt{.auto\_rerun}: This attribute controls how
-  Davos behaves when attempting to \texttt{smuggle} a new
+  \texttt{davos} behaves when attempting to \texttt{smuggle} a new
   version of a package that was previously imported and cannot be
@@
   previously imported and to-be-smuggled versions.  If this attribute
-  is set to \texttt{True}, Davos will automatically restart
+  is set to \texttt{True}, \texttt{davos} will automatically restart
   the notebook kernel and rerun all code up to (and including) the
   current \texttt{smuggle} statement. If set to \texttt{False} (the default),
-  Davos will instead issue a warning, pause execution, and
+  \texttt{davos} will instead issue a warning, pause execution, and
   prompt the user to either restart and rerun the notebook, or
@@
 \item \texttt{.confirm\_install}: If set to \texttt{True} (default:
-  \texttt{False}), Davos will require user confirmation
+  \texttt{False}), \texttt{davos} will require user confirmation
   before installing a smuggled package that does not yet exist in the
@@
   \texttt{auto\_rerun} is set to \texttt{False} while in non-interactive
-  mode, Davos will raise an exception if a smuggled package
+  mode, \texttt{davos} will raise an exception if a smuggled package
   cannot be reloaded, rather than prompting the user.
@@
 \item \texttt{.suppress\_stdout}: If this attribute is set to
-  \texttt{True} (default: \texttt{False}), Davos suppresses
+  \texttt{True} (default: \texttt{False}), \texttt{davos} suppresses
   printed (console) outputs from both itself and the installer program.
@@
   displayed alongside the Python traceback to allow for debugging.
-
-\item \texttt{.project}: This attribute is a string that specifies the name of
-the ``project'' associated with the current notebook. As described in
-Section~\ref{subsec:projects}, a notebook's project determines where and how
-any \texttt{smuggle}d dependencies are installed if they are not available in
-the current runtime environment. By default, this attribute is named according
-to the current notebook's absolute file path. However, the project name may be
-customized to enable shared dependency installations across notebooks (see
-Sec.~\ref{subsec:projects}).
-
 \end{itemize}
 
-\noindent Davos namespace also defines the \texttt{davos.configure()} function,
-which allows setting multiple configuration options simultaneously. In addition
-to the above configurable attributes, the \texttt{davos} object also includes
-several read-only attributes that contain potentially useful information about
-the current environment or Davos's behavior:
-
-\begin{itemize}
-
-\item \texttt{.environment}: This attribute's value is a string describing the notebook
-environment Davos was imported into. As of the current version (0.2.0), this
-attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”}.
-
-  \item \texttt{.ipython\_shell}: This attribute contains the global IPython \texttt{InteractiveShell} instance underlying the notebook kernel session.
-
-  \item \texttt{.smuggled}: This attribute is set to a Python dictionary that functions as a cache of any \texttt{smuggle} commands run during the current
-session.  The dictionary's keys are package names and the values are arguments passed via the corresponding smuggle statement's onion comment.
-
-  \item \texttt{.all\_projects}: This attribute contains a list of all local projects (i.e., projects with virtual environment directories located in \texttt{\$HOME/.davos/projects}).
-See Section~\ref{subsec:projects} for additional information about Davos projects.
-
-\end{itemize}
+\noindent The top-level \texttt{davos} namespace also defines
+convenience functions for setting and checking whether \texttt{davos}
+is active (\texttt{davos.activate()}; \texttt{davos.deactivate()};
+\texttt{davos.is\_active()}) as well as the \texttt{davos.configure()}
+function, which allows setting multiple configuration options
+simultaneously.
 
@@
 
-Although Davos is designed to \textit{appear} to add a new
+Although \texttt{davos} is designed to \textit{appear} to add a new
 keyword to Python's vocabulary, this illusion is actually created through
@@
 for processing and executing users' code.  Specifically, when
-Davos is first imported, or when it is activated after having been
+\texttt{davos} is first imported, or when it is activated after having been
 set to an inactive state, two actions are triggered.  First, the
 \texttt{smuggle()} function is injected into the IPython user
-namespace.  Second, the Davos parser is registered as a
+namespace.  Second, the \texttt{davos} parser is registered as a
 custom IPython input transformer.
@@
 to the Python compiler, in order to handle special constructs like
-\texttt{\%magic} and \texttt{!shell} commands. Davos uses
+\texttt{\%magic} and \texttt{!shell} commands. \texttt{davos} uses
 this process to transform \texttt{smuggle} statements into
-syntactically valid Python code. The Davos parser uses a
+syntactically valid Python code. The \texttt{davos} parser uses a
 regular expression to match lines of code containing \texttt{smuggle}
@@
 The call to the \texttt{smuggle()} function carries out
-Davos's central logic by determining whether the smuggled
+\texttt{davos}'s central logic by determining whether the smuggled
 package must be installed, carrying out the installation if necessary,
@@
 is also possible (though never necessary) to call it
-directly. Deactivating Davos will delete the name
+directly. Deactivating \texttt{davos} will delete the name
 ``\texttt{smuggle}'' from the namespace, unless its value has been
 overwritten and no longer refers to the \texttt{smuggle()}
-function. It will also deregister the Davos parser from the
+function. It will also deregister the \texttt{davos} parser from the
 set of input transformers run when each notebook cell is
-executed. While the overhead added by the Davos parser is
+executed. While the overhead added by the \texttt{davos} parser is
 minimal, this may be useful, for example, when optimizing or precisely
@@
   high level, the \texttt{smuggle()} function may be conceptualized as
-following two basic steps.  First (left), Davos ensures that the
+following two basic steps.  First (left), \texttt{davos} ensures that the
 correct version of the desired package has been installed, carrying
 out the installation automatically if needed.  Second (right),
-Davos imports the package and updates the current runtime environment.}
+\texttt{davos} imports the package and updates the current runtime environment.}
 \label{fig:flow-chart}
@@
 \includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for Davos.}
+\caption{\small \textbf{Example use case for \texttt{davos}.}
   Snippets from this example are also excerpted in the main text of
@@
 
-Across different versions of a given package, particular modules, functions,
-and other objects may be updated, removed, renamed, or otherwise altered. In
-addition to changing the behaviors of active computations, these changes can
-render saved objects created using one version of a package incompatible with
-other versions of the same package. For example, the popular
-\texttt{pandas}~\cite{McKi10} library used to include the \texttt{Panel} data
-structure for storing 3-dimensional arrays. Since version 0.20.0, however, the
-\texttt{Panel} class has been deprecated, and in version 0.25.0, it was removed
-entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
-(created using an older version of \texttt{pandas}) and had saved it to their
-disk (e.g., for later reuse or to share with other users) by serializing the
-\texttt{Panel} with Python's \texttt{pickle} protocol. The \texttt{pickle}
-protocol is a popular built-in method of persisting data in Python, allowing
-users to save, share, and load arbitrary objects. However, in order to
-successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved)
-object, the object's class must be defined in and importable from the same
-module as when it was saved. Thus, because of the \texttt{Panel} class's
-removal, the user's dataset could not be read by any version of \texttt{pandas}
-from 0.25.0 or beyond. These incompatibilities are also not limited solely to
-traditional forms of data. For example, saved model states and other objects
-may reference modules, functions, attributes, classes, or other objects that
-may not be identical (or even present) across all versions of their associated
-package.
+Across different versions of a given package, particular modules, functions, and other objects
+may be updated, removed, renamed, or otherwise altered.  In addition to changing the
+behaviors of active computations, these changes can render saved objects created using one
+version of a package incompatible with other versions of the
+same package.  For example, the popular \texttt{pandas}~\cite{McKi10}
+library used to include the \texttt{Panel} data structure for storing 3-dimensional arrays.
+Since version 0.20.0, however, the \texttt{Panel} class has been deprecated, and in
+version 0.25.0, it was removed entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
+(created using an older version of \texttt{pandas}) and had saved it to their disk (e.g., for later reuse
+or to share with other users) by serializing the \texttt{Panel} with Python's \texttt{pickle} protocol.
+The \texttt{pickle} protocol is a popular built-in method of persisting data in Python, allowing users to save, share, and load arbitrary objects.
+However, in order to successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved) object, the object's class must be defined in and importable from the same module as when it was saved.
+Thus, because of the \texttt{Panel} class's removal, the user's dataset could not be read by any version of \texttt{pandas} from 0.25.0 or beyond. These
+incompatibilities are also not limited solely to traditional forms of data.
+For example, saved model states and other objects may reference
+modules, functions, attributes, classes, or other objects that may not be identical (or even present)
+across all versions of their associated package.
 
-The example provided in Figure~\ref{fig:illustrative-example} demonstrates how
-the Davos package can be used to circumvent these incompatibilities by
-carefully controlling which versions of each package are used in different
-parts of the notebook. The example shows how a dataset and model that require
-now-incompatible components of the \texttt{pandas} and
-\texttt{scikit-learn}~\cite{PedrEtal11} packages may be loaded in (using older
-versions of each package) and used alongside more recent versions of each
-package that provide new and improved functionality. When included at the top
-of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
-ensures that these objects will be loaded successfully and analyzed using the
-same set of package versions, no matter when or by whom the notebook is run.
+The example provided in Figure~\ref{fig:illustrative-example}
+demonstrates how the \texttt{davos} package can be used to circumvent
+these incompatibilities by carefully controlling which versions of
+each package are used in different parts of the notebook.  The example
+shows how a dataset and model that require now-incompatible components of
+the \texttt{pandas} and \texttt{scikit-learn}~\cite{PedrEtal11}
+packages may be loaded in (using older versions of each package) and used
+alongside more recent versions of each package that provide new and improved functionality.
+When included at the top of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
+ensures that these objects will be loaded successfully and analyzed using the same set
+of package versions, no matter when or by whom the notebook is run.
 
-After installing and importing Davos (lines 1--2), we first \texttt{smuggle} two
+After installing and importing \texttt{davos} (lines 1--2), we first \texttt{smuggle} two
 utilities for interacting with local files in the code below. The
@@
 Line 7 then uses the \texttt{davos.config} object to enable
-Davos's \texttt{auto\_rerun} option before smuggling the next
+\texttt{davos}'s \texttt{auto\_rerun} option before smuggling the next
 two packages: \texttt{NumPy}~\cite{HarrEtal20} and
@@
 
-Newer versions of \texttt{pandas} have brought substantial improvements
-including better performance, bug fixes, and additional functionality. Although
-the original dataset had to be read in using an older version of the package,
-we can take advantage of these more recent updates by smuggling \texttt{pandas}
-a second time on line 15 (whose onion comment specifies that version 1.3.5
-should be installed and loaded). Since a different version of \texttt{pandas}
-had already been loaded by the Python interpreter (on line 11), the notebook
-kernel must be restarted in order to replace the old version's custom C
-extensions with those from the new version. The \texttt{auto\_rerun} flag set
-on line 7 enables Davos to trigger this process automatically so that
-the code can continue running without user intervention, and converting the
-dataset to a CSV file in lines 10--13 ensures that the older version of
-\texttt{pandas} does not need to be reinstalled.
+Newer versions of \texttt{pandas} have brought substantial
+improvements including better performance, bug fixes, and additional functionality.
+Although the original dataset had to be read in using an older version
+of the package, we can take advantage of these more recent updates
+by smuggling \texttt{pandas} a second time on line 15 (whose onion comment
+specifies that version 1.3.5 should be installed and loaded).  Since
+a different version of \texttt{pandas} had already been loaded by the Python interpreter
+(on line 11), the notebook kernel must be restarted in order to replace the old
+version's custom C extensions with those from the new version.  The \texttt{auto\_rerun} flag
+set on line 7 enables \texttt{davos} to trigger this process automatically so that
+the code can continue running without user intervention, and converting
+the dataset to a CSV file in lines 10--13 ensures that
+the older version of \texttt{pandas} does not need to be reinstalled.
 
@@
 for building and working with machine learning models, and
-\texttt{UMAP}~\cite{McInEtal18}, a package that implements a family
+\texttt{UMAP}~\cite{McInEtal18b}, a package that implements a family
 of related manifold learning techniques. The onion comment in line 19
@@
 statements to load the packages into the notebook namespace. If they
-differ, Davos will download the requested versions in place
+differ, \texttt{davos} will download the requested versions in place
 of the installed versions before doing so.
@@
 
-In lines 26--29, we demonstrate another aspect of Davos's
+In lines 26--29, we demonstrate another aspect of \texttt{davos}'s
 functionality that supports more advanced installation scenarios.  The
@@
 \texttt{scikit-learn} in line 36.  Taken together, the code in
-Figure~\ref{fig:illustrative-example} shows how Davos can
+Figure~\ref{fig:illustrative-example} shows how \texttt{davos} can
 enable users to load in data and models that are incompatible with
@@
 Like virtual environments, containers, and virtual machines, the
-Davos package (when used in conjunction with Jupyter
+\texttt{davos} package (when used in conjunction with Jupyter
 notebooks) provides a light\-weight mechanism for sharing code and
 ensuring reproducibility across users and computing environments
-(Fig.~\ref{fig:code-sharing}). Further, Davos enables users
+(Fig.~\ref{fig:code-sharing}). Further, \texttt{davos} enables users
 to fully specify (and install, as needed) any project dependencies
@@
 
-Although existing notebooks \textit{can} incorporate system calls that install
-project requirements, handling project requirements in the general case is
-non-trivial (e.g., see Fig.~\ref{fig:flow-chart}). Further, Davos
-incorporates its own virtual environment system that isolates
-notebook-installed packages from the runtime environment
-(Sec.~\ref{subsec:projects}). In many setups this feature can eliminate the
-need to set up a separate virtual environment or container (e.g., in
-conjunction with a \texttt{requirements.txt}, \texttt{project.toml}, or
-\texttt{environment.yml} file specifying the project's dependencies).
-
-We designed Davos for use in research applications. For
-example, in many settings, Davos may be used as a drop-in
+We designed \texttt{davos} for use in research applications. For
+example, in many settings, \texttt{davos} may be used as a drop-in
 replacement for more-difficult-to-set-up virtual environments,
@@
 reconstructing the original researchers' computing environment,
-Davos also lowers barriers to entry for members of the
+\texttt{davos} also lowers barriers to entry for members of the
 scientific community and the public who seek to run shared code.
 
-Beyond research applications, Davos is also useful in
+Beyond research applications, \texttt{davos} is also useful in
 pedagogical settings. For example, in programming courses, instructors
-and students may use the Davos package to ensure their
+and students may use the \texttt{davos} package to ensure their
 notebooks will run correctly on others' machines. When combined with
 online notebook-based platforms like Google Colaboratory,
-Davos provides a convenient way to manage dependencies within
+\texttt{davos} provides a convenient way to manage dependencies within
 a notebook, without requiring any software (beyond a web browser) to
 be installed on the students' or instructors' systems. For the same
-reasons, Davos also provides an elegant means of sharing
+reasons, \texttt{davos} also provides an elegant means of sharing
 ready-to-run notebook-based demonstrations or tutorials that install
@@
 
-Since its initial release, Davos has found use in a variety of applications. In
-addition to managing computing environments for multiple prior and ongoing
-research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
-used by both students and instructors in programming and methods courses such
-as Storytelling with Data~\cite{Mann21a} (an open course on data science,
-visualization, and communication) and Laboratory in Psychological
-Science~\cite{Mann22} (an open course on experimental and statistical methods
-for psychology research) to simplify distributing lessons and submitting
-assignments, as well as in online demos such as
-\texttt{abstract2paper}~\cite{Mann21b} (an example application of
-GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share ready-to-run code that installs
-dependencies automatically. The 2023 offering of Neuromatch
-Academy~\cite{vanVEtal21} also included an ``experimental'' module that uses
-Davos to manage dependencies related to a large language model-based
-tutor~\cite{MannEtal23b}.
+Since its initial release, \texttt{davos} has found use in a variety
+of applications. In addition to managing computing environments for
+multiple ongoing research studies, \texttt{davos} is being used by
+both students and instructors in programming and methods courses such
+as Storytelling with Data~\cite{Mann21d} (an open course on data
+science, visualization, and communication) and Laboratory in
+Psychological Science~\cite{Mann22} (an open course on experimental
+and statistical methods for psychology research) to simplify
+distributing lessons and submitting assignments, as well as in online
+demos such as \texttt{abstract2paper}~\cite{Mann21e} (an example
+application of GPT-Neo~\cite{GaoEtal20, BlacEtal21}) to share
+ready-to-run code that installs dependencies automatically.
 
-Our work also has several more subtle ``advanced'' use cases and potential
-impacts. Whereas Python's built-in \texttt{import} statement is agnostic to
-packages' version information, \texttt{smuggle} statements (when combined with
-onion comments) are version-sensitive. And because onion comments are parsed at
-runtime, required packages and their specified versions are installed in a
-just-in-time manner. Thus, it is possible in most cases to \texttt{smuggle} a
-specific package version or revision even if a different version has already
-been loaded. This enables more complex uses that take advantage of multiple
-versions of a package within a single interpreter session (e.g., see
-Sec.~\ref{sec:illustrative-example} and Fig.~\ref{fig:illustrative-example}).
-This could be useful in cases where specific features are added or removed from
-a package across different versions, or in comparing the performance or
-functionality of particular features across different versions of the same
-package.
+Our work also has several more subtle ``advanced'' use cases and
+potential impacts. Whereas Python's built-in \texttt{import} statement
+is agnostic to packages' version information, \texttt{smuggle}
+statements (when combined with onion comments) are version-sensitive.
+And because onion comments are parsed at runtime, required packages
+and their specified versions are installed in a just-in-time
+manner. Thus, it is possible in most cases to \texttt{smuggle} a
+specific package version or revision even if a different version has
+already been loaded. This enables more complex uses that take
+advantage of multiple versions of a package within a single
+interpreter session (e.g., see
+Sec.~\ref{sec:illustrative-example} and Fig.~\ref{fig:illustrative-example}). This could be useful in cases
+where specific features are added or removed from a package across
+different versions, or in comparing the performance or functionality
+of particular features across different versions of the same package.
 
@@
 operators to the Python language could be specifically useful to
-researchers. With Davos, we accomplish this by leveraging
+researchers. With \texttt{davos}, we accomplish this by leveraging
 IPython notebooks' internal code parsing and execution machinery. We
@@
 to providing notebook-specific functionality (e.g.,
-\cite{Hunt07,HeusEtal18}), this approach also has the potential to be
+\cite{Hunt07,HeusEtal18a}), this approach also has the potential to be
 exploited for more nefarious purposes. For example, a malicious user
@@
 keyword-like objects (e.g., based around common typos). We also note
-that this implementation approach means Davos's functionality
+that this implementation approach means \texttt{davos}'s functionality
 is currently restricted to IPython notebook environments. However,
@@
 including a draft proposal~\cite{Shan20}. In addition to enabling
-Davos to be extended for use outside of notebooks, this could
-lead to exciting new tools that, like Davos, extend the
+\texttt{davos} to be extended for use outside of notebooks, this could
+lead to exciting new tools that, like \texttt{davos}, extend the
 Python language in useful and more secure ways.
-
-\subsection{Pitfalls and limitations}
-
-While Davos enables developers to conveniently specify all project
-dependencies, there are some edge cases and limitations that are worth
-considering. First, reproducibility is not solely about dependency management.
-In addition to ensuring that project dependencies are satisfied, the user
-running a given notebook must also execute the code in the indicated order. For
-example, the cells in a notebook may be manually run out of order. If different
-cells in a Davos-enhanced notebook made use of different versions of the same
-package, this could result in \textit{more} confusion or \textit{greater}
-replication failure rates relative to standard Jupyter notebooks. Therefore an
-important consideration when using Davos is that it is perhaps even more
-important to execute notebook cells in order than would be the case in the
-standard (non-Davos) setup. One approach to mitigating this risk for notebooks
-that use several versions of the same library would be to include
-\texttt{smuggle} statements in the same cell(s) where the library was called. A
-second approach would be for developers who wish to use Davos to include notes
-regarding which cells must be executed in sequence. This is already a common
-practice for notebooks that include system calls to install required packages
-and dependencies, and the same approach would work well for Davos-enhanced
-notebooks as well.
-
-A second limitation of Davos relates to how packages are installed and managed.
-As of this writing, Davos can install packages using \texttt{pip}, but not
-other standard Python package management systems such as \texttt{conda}.
-Therefore packages that are not installable via \texttt{pip} are currently
-unsupported by Davos. We anticipate adding support for other package management
-systems, including \texttt{conda}, in a future release.
-
-A third limitation of Davos is that it cannot be used to manage projects that
-depend on non-Python software. For example, system software or libraries from
-other languages (e.g., in a mixed Python and R notebook), cannot be
-\texttt{smuggle}d by Davos. A notebook that utilizes or depends on non-Python
-software would therefore need to use existing non-Davos approaches to managing
-those requirements.
 
@@
 
-The Davos package supports reproducible research by providing
+The \texttt{davos} package supports reproducible research by providing
 a novel, lightweight system for sharing notebook-based code. But
-perhaps the most exciting uses of the Davos package are those
+perhaps the most exciting uses of the \texttt{davos} package are those
 that we have \textit{not} yet considered or imagined. We hope that the
-research and scientific Python communities will find Davos to provide a convenient
+research and scientific Python communities will find \texttt{davos} to provide a convenient
 means of managing project dependencies to facilitate code sharing and collaboration. We

### 2023-09-06 davos/core/project.py
quote directory path to handle spaces

@@ -202,7 +202,7 @@ class Project(metaclass=ProjectChecker):
             cmd = (
                 f'{config.pip_executable} list '
                 '--disable-pip-version-check '
-                f'--path {self.site_packages_dir} '
+                f'--path "{self.site_packages_dir}" '
                 f'--format json'
             )
             pip_list_stdout = run_shell_command(cmd, live_stdout=False)

### 2023-09-06 paper/main.tex
minor wording tweaks and TODO notes

--- 2023-08-07 paper/main.tex
@@
 To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task.
-However, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.
 
@@
 
-\item \texttt{.project}: This attribute is a string that specifies the name of
+\item \texttt{.project}: \textcolor{red}{\textbf{TODO: fix this}} This attribute is a string that specifies the name of
 the ``project'' associated with the current notebook. As described in

### 2023-09-06 davos/core/project.py
VS Code support -- get notebook path despite no running Jupyter server

@@ -678,6 +678,15 @@ def get_notebook_path():
                 notebook_relpath = unquote(session['notebook']['path'])
                 return f'{nbserver_root_dir}/{notebook_relpath}'
 
+    # VS Code doesn't actually start a Jupyter server when connecting to
+    # kernels, so the Jupyter API won't work. Fortunately, it's easy to
+    # check if the notebook is being run through VS Code, and to get its
+    # absolute path, if so.
+    # environment variable defined only if running in VS Code
+    if os.getenv('VSCODE_PID') is not None:
+        # global variable that holds absolute path to notebook file
+        return config.ipython_shell.user_ns['__vsc_ipynb_file__']
+
     # shouldn't ever get here, but just in case
     raise RuntimeError("Could not find notebook path for current kernel")
 

### 2023-09-06 davos/core/project.py
fallback project to isolate smuggled packages in cases where notebook path can't be identified

@@ -49,6 +49,7 @@ import json
 import os
 import shutil
 import sys
+import warnings
 from os.path import expandvars
 from pathlib import Path
 from urllib.request import urlopen
@@ -864,10 +865,24 @@ def use_default_project():
     if isinstance(config._ipython_shell, TerminalInteractiveShell):
         proj_name = "ipython-shell"
     else:
-        proj_name = get_notebook_path()
+        try:
+            proj_name = get_notebook_path()
+        except RuntimeError:
+            # failed to identify the notebook's name/path for some
+            # reason. This may happen if the notebook is being run
+            # through an IDE or other application that accesses the
+            # notebook kernel in a non-standard way, such that the
+            # Jupyter server is never launched. In this case, fall back
+            # to a generic project so smuggled packages are still
+            # isolated from the user's main environment
+            proj_name = "davos-fallback"
+            warnings.warn(
+                "Failed to identify notebook path. Falling back to generic "
+                "default project"
+            )
 
     # will always be an absolute path to a real Jupyter notebook file,
-    # or name of real Colab notebook, so we can skip project type
-    # decision logic
+    # name of real Colab notebook, or one of the non-path strings
+    # explicitly set above, so we can skip project type decision logic
     default_project = ConcreteProject(proj_name)
     config.project = default_project

### 2023-09-08 paper/main.tex
bump version string and URL for eventual resubmission release
note support for IPython shells in metadata table

@@
 \hline
-C1 & Current code version &  v0.2.0 \\
+C1 & Current code version &  v0.2.4 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.0} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.4} \\
 \hline
@@
 C7 & Compilation requirements, operating environments, and
-     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors.
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors, IPython shell.
 \\

### 2023-09-09 paper/main.tex
fix missing text in fig 2 caption

@@
   subpackage includes modules for parsing \texttt{smuggle} statements
-  and onion comments, installing and validating packages, isolating and managing and
-  configuring Davos's behavior.  The
+  and onion comments, installing and validating packages, isolating and managing 
+  installed packages, and configuring Davos's behavior.  The
   \texttt{davos.implementations} subpackage includes

### 2023-09-10 paper/main.tex
WIP rewriting projects section

@@
 the version of the package loaded into the notebook matches the specific
-version requested, or satisfies the given version constraints. If the smuggled
+version requested (or satisfies the given version constraints). If the smuggled
 package exists locally, Davos will extract its version information from its
@@
 installer program. In addition to preventing shared notebooks from executing
-arbitrary code in a user's shell, this enables Davos to adapt its behavior
+arbitrary code in a user's shell, this enables Davos to adjust its behavior
 based on how particular flags will affect the behavior of the installer
@@
 temporarily enable Davos's non-interactive mode (see Sec.~\ref{subsec:config}).
-Similarly, if an onion comment contains either the \texttt{-I}/\texttt{--ignore-installed},
-\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall} flag, Davos will
-skip checking for a local copy of the smuggled package before installing a
-new one:
+Similarly, if an onion comment contains either \texttt{-I}/\texttt{--ignore-installed},
+\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall}, Davos will
+install and load a new copy of the smuggled package without first checking
+for it locally:
 \begin{center}
@@
 should be installed (if necessary) so that it can be loaded and used
-immediately, options that would cause the package not to be installed (such as
-\texttt{-h}/\texttt{--help} or \texttt{--dry-run}) are disallowed. Additionally,
-when using a Davos project to isolate smuggled packages (the default behavior;
+immediately, options that would normally cause the package not to be installed
+(such as \texttt{-h}/\texttt{--help} or \texttt{--dry-run}) are disallowed. Additionally,
+when using a Davos ``project'' to isolate smuggled packages (the default behavior;
 see Sec.~\ref{subsec:projects}), onion comments may not contain options that
@@
 
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom scheme called ``projects.'' Functionally, a Davos project is similar to a standard Python virtual environment (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): it consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular project or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually activated and deactivated, do not contain separate Python or \texttt{pip} executables, and \textit{extend} the user's main Python environment rather than replace it.
-
-When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already). 
-%When Davos is imported into a notebook, a notebook-specific project directory is automatically created (if it does not exist already), named for the absolute path to the notebook file.
-
-Notebook-specific projects are named for the absolute path to the notebook file.
+%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom, virtual environment-like system called ``projects.''
+%Functionally, Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}), but are lighter-weight and simpler to use.
+%Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python-based project \textcolor{red}{[confusing reuse of ``project''?]}, workflow, or task.
+%However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated; do not contain separate Python or \texttt{pip} executables; and function to \textit{extend} the user's main Python environment rather than replace it.
+To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few important differences.
+Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed to run a particular Python program, workflow, or task.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and
+%function to \textit{extend} 
+serve to \textit{supplement}
+the user's existing Python environment rather than replace it.
+%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+%Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): a project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed to run a particular Python program, workflow, or task.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and
+%%function to \textit{extend} 
+%serve to \textit{supplement}
+%the user's existing Python environment rather than replace it.
+
+When Davos is imported into a notebook, a project directory specific to that notebook is automatically created (if it does not exist already).
+Any packages (or specific package versions) smuggled into that notebook that are not already available in the notebook's main runtime environment will be installed into the notebook's project directory, along with any dependencies of those packages not available in the main environment.
+
+Additionally, when a \texttt{smuggle} statement in that notebook is executed, the notebook's project directory is temporarily prepended to the module search path/
+
+%Notebook-specific projects are named for the absolute path to the notebook file.
 

### 2023-09-13 davos/core/core.py
slightly tweak exception name

@@ -50,7 +50,7 @@ from davos.core.exceptions import (
     OnionParserError,
     ParserNotImplementedError,
     SmugglerError,
-    TheNightIsDarkAndFullOfTErrors
+    TheNightIsDarkAndFullOfErrors
 )
 from davos.core.parsers import pip_parser
 from davos.core.regexps import (
@@ -1041,7 +1041,7 @@ def smuggle(
     pkg_name = name.split('.')[0]
 
     if pkg_name == 'davos':
-        raise TheNightIsDarkAndFullOfTErrors("Don't do that.")
+        raise TheNightIsDarkAndFullOfErrors("Don't do that.")
 
     onion = Onion(pkg_name, installer=installer,
                   args_str=args_str, **installer_kwargs)

### 2023-09-13 paper/main.tex
progress through tricky section of projects description

@@
 %However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated; do not contain separate Python or \texttt{pip} executables; and function to \textit{extend} the user's main Python environment rather than replace it.
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few important differences.
-Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed to run a particular Python program, workflow, or task.
+To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
+Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
 However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and
@@
 serve to \textit{supplement}
+%work by \textit{supplementing}
 the user's existing Python environment rather than replace it.
@@
 
-When Davos is imported into a notebook, a project directory specific to that notebook is automatically created (if it does not exist already).
-Any packages (or specific package versions) smuggled into that notebook that are not already available in the notebook's main runtime environment will be installed into the notebook's project directory, along with any dependencies of those packages not available in the main environment.
-
-Additionally, when a \texttt{smuggle} statement in that notebook is executed, the notebook's project directory is temporarily prepended to the module search path/
+When Davos is imported into a notebook, a project directory for that notebook is automatically created (if it does not exist already).
+When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment will be installed into the notebook's project directory (along with any missing dependencies of those packages).
+%Davos will also check for smuggled packages in the notebook's project directory before searching the user's main environment such that project-installed packages are always prioritized when available.
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path (\texttt{sys.path}), so that project-installed packages are visible when searching for smuggled packages locally, and are prioritized over those in the user's main environment whenever they are available.
+
+Thus, rather than recreating a complete package environment from scratch, Davos projects provide any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook.
+In some cases,
+
+Thus, a Davos project provides any additions and modifications to the user's existing package environment needed to satisfy
+
+By default, projects are named
+
+Because \texttt{smuggle} statements are evaluated each time the notebook is run, this system ensures that all required packages and specified package versions are always available and used, even if the notebook's main runtime environment is changed.
+For example, if a user
 
@@
 \texttt{Panel} with Python's \texttt{pickle} protocol. The \texttt{pickle}
-protocol is a popular built-in method of persisting data in Python, allowing
+protocol is a popular built-in method of persisting data in Python that allows
 users to save, share, and load arbitrary objects. However, in order to
-successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., saved)
+successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., previously saved)
 object, the object's class must be defined in and importable from the same

### 2023-09-13 paper/main.tex
more progress on projects section

@@
 To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
+Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}), but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
@@
 %Davos will also check for smuggled packages in the notebook's project directory before searching the user's main environment such that project-installed packages are always prioritized when available.
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path (\texttt{sys.path}), so that project-installed packages are visible when searching for smuggled packages locally, and are prioritized over those in the user's main environment whenever they are available.
-
-Thus, rather than recreating a complete package environment from scratch, Davos projects provide any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook.
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and given priority over packages in the user's main environment.
+%and prioritized over packages in the user's main environment when they are available.
+
+% Thus, rather than constructing a fully separate Python environment from scratch, a Davos project works by providing any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook.
+
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by providing any additions or modifications to the user's existing package environment needed to satisfy the dependencies of their corresponding notebooks.
+In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
+In other cases, the existing environment might provide all required packages already, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
+But in all cases, any packages installed are confined to the project directory and the user's existing environment will remain unaltered.
+
+%Thus, rather than creating fully independent Python environments created from scratch, Davos projects provide any additions or modifications to the user's existing package environment needed to satisfy the dependencies of their corresponding notebooks.
+In some cases, this may be the full set of packages smuggled into a notebook (e.g., if the notebook's runtime environment is a freshly created, empty virtual environment).
+In other cases, the user's existing environment may
+
+%Thus, rather than creating a fully separate Python environment from scratch, a Davos project provides any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook---and does so without
+
+%In some cases... In other cases... In all cases, existing environment unaffected.
+
+%Thus, rather than a fully separate Python environment created from scratch, a Davos project provides any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook---without affecting the existing environment itself.
+
+%Thus, rather than complete Python environments recreated from scratch, Davos projects provide any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook --- and does so without altering the existing package environment.
+%
+%Thus, rather than a fully separate Python environment created from scratch, a Davos project provides any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook --- and does so without altering the existing package environment
+%
+%
+%Thus, rather than recreating a complete Python environment from scratch, a Davos project provides any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook --- without altering the existing package environment.
 In some cases,
-
-Thus, a Davos project provides any additions and modifications to the user's existing package environment needed to satisfy
-
-By default, projects are named
+%
+%Thus, a Davos project provides any additions and modifications to the user's existing package environment needed to satisfy
+
+By default, Davos projects are named based on the absolute path to their corresponding notebooks, and are therefore notebook-specific.
 

### 2023-09-13 davos/core/core.py
fix typo in comment

@@ -967,8 +967,8 @@ def use_project(smuggle_func):
             # invalidate sys.meta_path finder caches so the global
             # working set is regenerated based on the updated sys.path.
             # Note: after pretty extensive spot checking, I haven't
-            # managed found a case where this is actually since
-            # migrating to importlib.metadata instead of pkg_resources,
+            # managed to find a case where this is actually necessary
+            # since migrating from pkg_resources to importlib.metadata,
             # but the docs recommend it and the overhead is extremely
             # minor, so probably worth including in case the user or
             # notebook environment has implemented some unusual custom

### 2023-09-13 paper/main.tex
cleaned up tex file

--- 2023-09-13 paper/main.tex
@@
 
-%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, Davos automatically isolates packages installed via \texttt{smuggle} statements using a custom, virtual environment-like system called ``projects.''
-%Functionally, Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}), but are lighter-weight and simpler to use.
-%Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python-based project \textcolor{red}{[confusing reuse of ``project''?]}, workflow, or task.
-%However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated; do not contain separate Python or \texttt{pip} executables; and function to \textit{extend} the user's main Python environment rather than replace it.
 To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
+Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}), but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and
-%function to \textit{extend} 
-serve to \textit{supplement}
-%work by \textit{supplementing}
-the user's existing Python environment rather than replace it.
-%To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-%Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}): a project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed to run a particular Python program, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and
-%%function to \textit{extend} 
-%serve to \textit{supplement}
-%the user's existing Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and serve to \textit{supplement} the user's existing Python environment rather than replace it.
 
@@
 When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment will be installed into the notebook's project directory (along with any missing dependencies of those packages).
-%Davos will also check for smuggled packages in the notebook's project directory before searching the user's main environment such that project-installed packages are always prioritized when available.
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path (\texttt{sys.path}), so that project-installed packages are visible when searching for smuggled packages locally, and are prioritized over those in the user's main environment whenever they are available.
-
-Thus, rather than recreating a complete package environment from scratch, Davos projects provide any additions or modifications to the user's existing package environment needed to satisfy the dependencies of a particular notebook.
-In some cases,
-
-Thus, a Davos project provides any additions and modifications to the user's existing package environment needed to satisfy
-
-By default, projects are named
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized for use over packages in the user's main environment.
+
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by providing any additions or modifications to the user's existing package environment needed to satisfy the dependencies of their corresponding notebooks.
+In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
+In other cases, the existing environment may already provide all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
+But in all cases, dependencies installed by Davos are confined to the project directory and the user's existing environment will be unaffected.
+
+By default, Davos projects are named based on the absolute path to their corresponding notebooks, and are therefore notebook-specific.
 

### 2023-09-13 paper/main.tex
progress on projects section

@@
 To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}), but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
+Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and serve to \textit{supplement} the user's existing Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and function to \textit{extend} the user's existing Python environment rather than replace it.
 
@@
 When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment will be installed into the notebook's project directory (along with any missing dependencies of those packages).
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized for use over packages in the user's main environment.
-
-Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by providing any additions or modifications to the user's existing package environment needed to satisfy the dependencies of their corresponding notebooks.
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over packages in the user's main environment.
+
+%Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by providing any additions or modifications to the user's existing package environment needed to satisfy their corresponding notebooks' dependencies.
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy
+%their corresponding notebooks' dependencies. 
+the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
-In other cases, the existing environment may already provide all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
-But in all cases, dependencies installed by Davos are confined to the project directory and the user's existing environment will be unaffected.
+In other cases, the user's environment may already contain all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
+But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and 
+%loaded into the notebook successfully, 
+can be loaded successfully at runtime,
+but that the contents of the user's Python environment are never altered.
+Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will continue to be satisfied even if the user's Python environment changes.
+For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a Davos-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
+Since the user's existing version of the package satisfies this requirement, Davos will happily load it into the notebook.
+But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently reruns the notebook, the local version will longer satisfy the requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
+From then on, further changes to the user's \texttt{Numpy} installation would not have any effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory (if the version in the onion comment were changed, Davos would install it in the project directory in place of the current version).
+For efficiency, Davos projects will generally avoid duplicating dependencies already satisfied by the user's Python environment.
+However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause the smuggled package to be installed in the project directory whether or not it already exists locally.
+
+it is possible to achieve a more ``traditional'' virtual environment-like experience by
+
+In general, Davos will not duplicate dependencies satisfied by the existing Python environment in the project directory unless
+
+.
+
+.
+
+For example, suppose a user runs a Davos-enhanced notebook that smuggles \texttt{NumPy}~\cite{HarrEtal20} with \texttt{numpy==1.24.3} specified in an onion comment (see Sec.~\ref{subsec:onion}), and happens to have \texttt{NumPy} v1.24.3 installed in their current Python environment.
+
+.
+
+.
+
+.
+
+For example, suppose a user runs a Davos-enhanced notebook that smuggles \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 (specified via an onion comment; see Sec.~\ref{subsec:onion}) and happens to have that exact version of \texttt{NumPy} installed in their current Python environment.
+
+.
+
+.
+
+.
+
+Davos will load the user's existing \texttt{NumPy} version rather than
+
+.
+
+.
+
+.
+
+For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment, and runs a Davos-enhanced notebook that smuggles that exact version of \texttt{NumPy} (specified via an onion comment; see Sec.~\ref{subsec:onion}).
+Since this requirement
+
+%continue to be available and properly loaded, even if the user's Python environment changes. For example, if a user
+
+%But in all cases, Davos's project system ensures that all dependencies of a given notebook are satisfied, and the user's Python environment is unaffected.
+%But in all cases, Davos's project system ensures that the \textit{potential} effects of \texttt{smuggle} statements are confined to a single, isolated directory, and that all dependencies of a notebook can be satisfied while the user's Python environment remains unchanged.
+Additionally, because \texttt{smuggle} statements are evaluated each time the notebook is run, this system also ensures that all of its dependencies remain satisfied, even if the user's Python environment is changed.
+For example,
+
+.
+
+.
+
+%But in all cases, Davos's project system ensures that the possible effects of \texttt{smuggle} statements are confined to a single, isolated directory, and that the user's Python environment remains unchanged.
+Additionally, because \texttt{smuggle} statements in a given notebook are evaluated each time that notebook is run, this system also ensures that all specified dependencies \textit{remain} satisfied, even if the user's main environment changes.
+
+But in all cases, Davos's project system ensures that any packages installed are confined to an isolated directory, and that the user's Python environment is not affected.
+Additionally, because \texttt{smuggle} statements in a given notebook are evaluated each time that notebook is run, this system also ensures that all of its specified dependencies \textit{remain} satisfied, even if the user's main environment changes.
+For example, if a user
+
+Additionally, because \texttt{smuggle} statements are evaluated each time a notebook is run, this system ensures that all required packages and specified package versions are always available and used, even if the notebook's main runtime environment is changed.
+For example, if a user
 
 By default, Davos projects are named based on the absolute path to their corresponding notebooks, and are therefore notebook-specific.
-
-Because \texttt{smuggle} statements are evaluated each time the notebook is run, this system ensures that all required packages and specified package versions are always available and used, even if the notebook's main runtime environment is changed.
-For example, if a user
 
@@
 \item \texttt{.environment}: This attribute's value is a string describing the notebook
-environment Davos was imported into. As of the current version (0.2.0), this
-attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”}.
+environment Davos was imported into. As of the current version (0.2.0 \textcolor{red}{\textbf{TODO: fix version}}), this
+attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”} \textcolor{red}{\textbf{TODO: fix quotes}}.
 
@@
 Davos's \texttt{auto\_rerun} option before smuggling the next
-two packages: \texttt{NumPy}~\cite{HarrEtal20} and
+two packages: \texttt{NumPy} and
 \texttt{pandas}. Because these packages rely heavily on custom C data

### 2023-09-13 paper/main.tex
cleaned up tex file formatting

@@
 
-%Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by providing any additions or modifications to the user's existing package environment needed to satisfy their corresponding notebooks' dependencies.
-Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy
-%their corresponding notebooks' dependencies. 
-the dependencies of their corresponding notebooks.
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment). 
 In other cases, the user's environment may already contain all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
-But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and 
-%loaded into the notebook successfully, 
-can be loaded successfully at runtime,
-but that the contents of the user's Python environment are never altered.
+But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and can be loaded successfully at runtime, but that the contents of the user's Python environment are never altered.
 Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will continue to be satisfied even if the user's Python environment changes.
@@
 
-it is possible to achieve a more ``traditional'' virtual environment-like experience by
-
-In general, Davos will not duplicate dependencies satisfied by the existing Python environment in the project directory unless
-
-.
-
-.
-
-For example, suppose a user runs a Davos-enhanced notebook that smuggles \texttt{NumPy}~\cite{HarrEtal20} with \texttt{numpy==1.24.3} specified in an onion comment (see Sec.~\ref{subsec:onion}), and happens to have \texttt{NumPy} v1.24.3 installed in their current Python environment.
-
-.
-
-.
-
-.
-
-For example, suppose a user runs a Davos-enhanced notebook that smuggles \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 (specified via an onion comment; see Sec.~\ref{subsec:onion}) and happens to have that exact version of \texttt{NumPy} installed in their current Python environment.
-
-.
-
-.
-
-.
-
-Davos will load the user's existing \texttt{NumPy} version rather than
-
-.
-
-.
-
-.
-
-For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment, and runs a Davos-enhanced notebook that smuggles that exact version of \texttt{NumPy} (specified via an onion comment; see Sec.~\ref{subsec:onion}).
-Since this requirement
-
-%continue to be available and properly loaded, even if the user's Python environment changes. For example, if a user
-
-%But in all cases, Davos's project system ensures that all dependencies of a given notebook are satisfied, and the user's Python environment is unaffected.
-%But in all cases, Davos's project system ensures that the \textit{potential} effects of \texttt{smuggle} statements are confined to a single, isolated directory, and that all dependencies of a notebook can be satisfied while the user's Python environment remains unchanged.
-Additionally, because \texttt{smuggle} statements are evaluated each time the notebook is run, this system also ensures that all of its dependencies remain satisfied, even if the user's Python environment is changed.
-For example,
-
-.
-
-.
-
-%But in all cases, Davos's project system ensures that the possible effects of \texttt{smuggle} statements are confined to a single, isolated directory, and that the user's Python environment remains unchanged.
-Additionally, because \texttt{smuggle} statements in a given notebook are evaluated each time that notebook is run, this system also ensures that all specified dependencies \textit{remain} satisfied, even if the user's main environment changes.
-
-But in all cases, Davos's project system ensures that any packages installed are confined to an isolated directory, and that the user's Python environment is not affected.
-Additionally, because \texttt{smuggle} statements in a given notebook are evaluated each time that notebook is run, this system also ensures that all of its specified dependencies \textit{remain} satisfied, even if the user's main environment changes.
-For example, if a user
-
-Additionally, because \texttt{smuggle} statements are evaluated each time a notebook is run, this system ensures that all required packages and specified package versions are always available and used, even if the notebook's main runtime environment is changed.
-For example, if a user
-
 By default, Davos projects are named based on the absolute path to their corresponding notebooks, and are therefore notebook-specific.
-
-%Notebook-specific projects are named for the absolute path to the notebook file.
-
- %Davos projects function similarly to simplified versions of standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) with a few differences: they do not need to be manually activated and deactivated, they do not contain separate Python or \texttt{pip} executables, and they \textit{extend} the main Python environment rather than replace it.
 

### 2023-09-17 paper/main.tex
additional text in projects section

@@
 when installing it) may differ from its top-level module name (i.e., the name
-used when importing it). In such cases, an onion comment may be used to ensure
+used when importing it). In such cases, an onion comment can be used to ensure
 that Davos installs the proper package if it cannot be found locally:
@@
 
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
 Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and function to \textit{extend} the user's existing Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, 
+%and work by \textit{supplementing} the user's existing Python environment rather than replacing it.
+and function to \textit{extend} the user's existing Python environment rather than replace it.
 
 When Davos is imported into a notebook, a project directory for that notebook is automatically created (if it does not exist already). 
-When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment will be installed into the notebook's project directory (along with any missing dependencies of those packages).
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over packages in the user's main environment.
-
-Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
+When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment are installed into the notebook's project directory (along with any missing dependencies of those packages).
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the user's main environment.
+
+Thus, rather than constructing fully separate Python environments from scratch, 
+%Davos projects serve to fill in the gap between the user's existing environment and the dependencies of their corresponding notebooks. 
+Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment). 
-In other cases, the user's environment may already contain all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
-But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and can be loaded successfully at runtime, but that the contents of the user's Python environment are never altered.
+In other cases, the user's environment may already provide all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
+But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
 Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will continue to be satisfied even if the user's Python environment changes.
@@
 Since the user's existing version of the package satisfies this requirement, Davos will happily load it into the notebook. 
-But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently reruns the notebook, the local version will longer satisfy the requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
-From then on, further changes to the user's \texttt{Numpy} installation would not have any effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory (if the version in the onion comment were changed, Davos would install it in the project directory in place of the current version).
+But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently reruns this notebook, the local version will longer satisfy this requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
+From then on, any further changes to the user's \texttt{Numpy} installation would have no effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory.
+(If the version specified in the onion comment were changed, Davos would install it in the project directory in place of the previous version.)
 For efficiency, Davos projects will generally avoid duplicating dependencies already satisfied by the user's Python environment. 
-However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause the smuggled package to be installed in the project directory whether or not it already exists locally.
-
-By default, Davos projects are named based on the absolute path to their corresponding notebooks, and are therefore notebook-specific.
+However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause the smuggled package to be installed into the project directory whether or not it already exists locally.
 

### 2023-09-17 paper/main.tex
finished projects section

@@
 For efficiency, Davos projects will generally avoid duplicating dependencies already satisfied by the user's Python environment. 
-However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause the smuggled package to be installed into the project directory whether or not it already exists locally.
+However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause Davos to install the smuggled package into the project directory whether or not it already exists locally.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% ADD THIS EITHER TO START OF PROJECTS SUBSUBSECTION OR IN IMPACT SECTION   %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%A common way of avoiding this is to create a virtual environment in which to run the notebook, and instruct anyone with whom the notebook is shared to do the same.
-While effective, this added requirement introduces additional
-%
-%
-%(or group of related notebooks) that require different 
-%
-%
-%\begin{itemize}
-%  \item{common solution is to use a virtual environment}
-%  \item{this introduces complexity}
-%  \item{davos's solution is projects}
-%\end{itemize}
+By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file. 
+However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project}.
+This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one. 
+%This provides a convenient way to share a single Davos project across multiple related notebooks that share a common set of requirements, by setting \texttt{davos.project} to the same string in each one.
+It is also possible (though not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
+
+When accessed (unless its value has been set to \texttt{None}), \texttt{davos.project} will return a \texttt{Project} object that represents the project used by the current notebook (strings assigned to \texttt{davos.project} are converted to \texttt{Project}s internally).
+This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
+\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects.
 
 \bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
-
-%Because Davos can install new packages, running the code in a
-%Davos-enhanced notebook might (in principle) affect the behavior of
-%\textit{other} Python-based software (e.g., other notebooks, scripts, etc.) by
-%altering which packages are installed in the runtime environment. This could
-%lead to undesired consequences. For example, suppose Person A develops a
-%notebook (Notebook A) for their research project. We will assume that Notebook
-%A does not use Davos to manage project dependencies.  If Person A
-%runs a Davos-enhanced Notebook B, e.g., sent by another developer,
-%might this unexpectedly affect the behavior of Notebook A?
-
-%To prevent unwanted
-%changes to the user's Python environment, Davos incorporates its
-%own virtual environment-like scheme for isolating packages it installs. When Davos
-%is imported, a new virtual environment (folder) is created automatically. The
-%folder's name may be customized to support multi-notebook projects. Any
-%\texttt{smuggle}d packages that were not available in the notebook's runtime
-%environment are installed to the current project folder. The runtime
-%environment remains unaffected by Davos's behavior (see
-%Sec.~\ref{subsec:projects}).
-%By default, projects are notebook-specific, but can also be shared by multiple notebooks, and can be managed interactively from within a Davos-enhanced notebook.
-
-%%%%%%%% JEREMY VERSION %%%%%%%%%
-%Installing new packages in a notebook using standard approaches (e.g., system commands) affect the
-%runtime environment. This could lead to undesired behaviors. For example, running a notebook that
-%installs new packages in the user’s primary system environment might alter their main system installation
-%and/or containerized environment in unexpected ways (e.g., changing package versions, causing conflicts
-%with other packages, etc.). To protect against undesired changes to the runtime environment, Davos
-%incorporates its own virtual environment for managing packages it installs. When Davos is imported,
-%a new virtual environment (folder) is created automatically. The folder’s name may be customized to
-%support multi-notebook projects. Any smuggled packages that were not available in the notebook’s
-%runtime environment are installed to the current project folder. The runtime environment remains unaffected
-%by Davos’s behavior (see Sec. 2.2.3).
-
-We implemented a ``project'' system in Davos to protect against the
-above scenario. By default, importing Davos creates a new project
-folder in the user's home directory (contained within a hidden \texttt{.davos}
-folder). The default project name is computed to uniquely identify each
-notebook according to its filename and path. Any packages that were not
-originally available in the notebook's runtime environment are installed to the
-notebook's project directory. When external libraries are \texttt{smuggle}d,
-Davos temporally appends the current project directory to the search
-path. Because the user's system path remains unchanged, and because none of the
-runtime environment's packages are altered, the user's system and runtime
-environment remain unaffected (aside from installing the Davos package
-itself to the runtime environment).
-
-Each notebook's project may be customized by setting \texttt{davos.project} to
-any string that can be used as a valid folder name in the user's operating
-system. By customizing the project name, users can build multi-notebook
-projects that share the same core set of dependencies without needing to
-duplicate each package for each notebook in the project.
-
-Finally, if the user \textit{does} wish to modify their runtime environment,
-this may be done by setting \texttt{davos.project} to \texttt{None}. Doing so
-will cause any packages installed by Davos to affect the user's
-runtime environment.  This is generally not recommended, as it can lead to
-unintended consequences for other code that shares the runtime environment.
 
@@
 \end{itemize}
+
+% \subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
 
@@
 
+\textcolor{red}{\textbf{TODO: add note about default/fallback project for non-traditional notebook interfaces}}
+
 \section{Conclusions}

### 2023-09-17 paper/main.tex
add subsection for top-level functions

@@
 This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
-\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects.
+\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects (see Sec.~\ref{subsec:toplevel}).
 
@@
 
-% \subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
+\subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
+\textcolor{red}{\textbf{TODO: add content}}
 

### 2023-09-17 paper/main.tex
add reference for MIND 2023

@@
 as Storytelling with Data~\cite{Mann21a} (an open course on data science,
-visualization, and communication) and Laboratory in Psychological
+visualization, and communication), Laboratory in Psychological
 Science~\cite{Mann22} (an open course on experimental and statistical methods
-for psychology research) to simplify distributing lessons and submitting
-assignments, as well as in online demos such as
+for psychology research), and the Methods in Neuroscience at Dartmouth (MIND)
+Computational Summer School~\cite{MIND23} (a week-long intensive course on 
+computational neuroscience methods) to simplify distributing lessons 
+and submitting assignments, as well as in online demos such as
 \texttt{abstract2paper}~\cite{Mann21b} (an example application of

### 2023-09-17 paper/main.tex
add note on MIND to acknowledgements

@@
 JRM's \textit{Storytelling with Data} course (Winter, 2022 offering)
-who used preliminary versions of our package in several assignments.
+who used preliminary versions of our package in several assignments,
+and the students of the Methods in Neuroscience at Dartmouth (MIND)
+Computational Summer School (2023 offering) who used our package
+during several workshops and tutorials.
 

### 2023-09-18 paper/main.tex
add reference to config section

@@
 By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file.
-However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project}.
+However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project} (see Sec.~\ref{subsec:config}).
 This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.

### 2023-09-18 paper/main.tex
edits to section 2.2.4 up through writeable options

@@
 
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
-
 \subsubsection{Configuring and querying Davos}\label{subsec:config}
 
-Davos's behavior may be customized by modifying a set of attributes attached to
-the \texttt{davos} module object that is added to the workspace when Davos is
-imported. These attributes may be modified, displayed, or checked
-programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
-illustrative example or Sec.~\ref{subsec:implementation} for implementation
-details and additional information). These include:
+After importing Davos into a notebook, the top-level \texttt{davos} module provides a set of attributes whose values determine various aspects of Davos's behavior.
+A subset of these attributes are writeable options that may be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
+These include:
+
+%After importing Davos into a notebook, the top-level \texttt{davos} module provides a set of attributes whose values may be displayed interactively, checked programmatically at runtime, or modified to customize various aspects of Davos's behavior (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
+%These writeable attributes include:
+
+%Davos's behavior may be customized by modifying a set of attributes attached to
+%the \texttt{davos} module object that is added to the workspace when Davos is
+%imported. These attributes may be modified, displayed, or checked
+%programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
+%illustrative example or Sec.~\ref{subsec:implementation} for implementation
+%details and additional information). These include:
 
@@
   disabled (\texttt{False}).  When Davos is first imported,
-  the \texttt{.active} attribute is set to \texttt{True}.
+  \texttt{davos.active} is set to \texttt{True}.
 
@@
   Davos behaves when attempting to \texttt{smuggle} a new
-  version of a package that was previously imported and cannot be
+  version of a package that was previously loaded (via an \texttt{import} or \texttt{smuggle} statement) and cannot be
   reloaded. This can happen if the package includes extension modules
@@
   and the code that generates those objects was changed between the
-  previously imported and to-be-smuggled versions.  If this attribute
+  previously loaded and to-be-smuggled versions.  If this attribute
   is set to \texttt{True}, Davos will automatically restart
@@
   prompt the user to either restart and rerun the notebook, or
-  continue running with the previously imported package version until
+  continue running with the previously loaded package version until
   the next time the kernel is restarted manually.  Note that, as of
-  this writing, the \texttt{.auto\_rerun} attribute is not supported
-  in Google Colaboratory notebooks.
+  this writing, setting \texttt{davos.auto\_rerun} to \texttt{True} is not 
+  supported in Google Colaboratory notebooks.
 
@@
   \texttt{False}), Davos will require user confirmation
-  before installing a smuggled package that does not yet exist in the
-  user's environment.
+  before installing a smuggled package that is not already
+  available locally. This is primarily useful if the user has disabled 
+  Davos's ``project'' system for isolating smuggled packages (see 
+  Sec.~\ref{subsec:projects}) but still wants to carefully control what 
+  packages are installed into their main Python environment.
 
@@
   path to the \texttt{pip} executable used to install smuggled
-  packages. The default is programmatically determined from the Python
-  environment and falls back to \texttt{sys.executable -m pip} if no
+  packages. The default is programmatically determined from the user's Python
+  environment and falls back to \texttt{<sys.executable> -m pip} if no
   executable can be found.
+
+\item \texttt{.project}: This attribute's value is a \texttt{Project} instance representing the Davos project associated with the current notebook.
+As described in Section~\ref{subsec:projects}, Davos projects serve to isolate packages installed by \texttt{smuggle} statements from the user's main Python environment, and the \texttt{Project} class provides an interface for inspecting and managing projects at runtime.
+This attribute's default value is a notebook-specific project named for the absolute path to the notebook file.
+To change the project used in the current notebook (e.g., in order to share a project between multiple related notebooks), this attribute may be assigned a different \texttt{Project} instance or, for simplicity, the name of the desired project as a string or \texttt{pathlib.Path} (which will be converted to a \texttt{Project} on assignment).
+Alternatively, setting \texttt{davos.project} to \texttt{None} will disable project-based isolation for the current notebook and cause Davos to install packages directly into the main Python environment.
+This attribute is reset to its default value by the top-level \texttt{use\_default\_project()} function (see Sec.~\ref{subsec:toplevel}).
+For more information about Davos projects, see Section \ref{subsec:projects}.
 
@@
   printed (console) outputs from both itself and the installer program.
-  This can be useful when smuggling packages that need to install many
-  dependencies and/or generate extensive output. However, if the installer
-  program throws an error, both its stdout and stderr streams will be
+  This can be useful when smuggling packages that require installing many
+  dependencies and/or generate extensive output when built from source distributions. Note that if this option is enabled and the installer
+  program throws an error, both its stdout and stderr streams will still be
   displayed alongside the Python traceback to allow for debugging.
 
-\item \texttt{.project}: \textcolor{red}{\textbf{TODO: fix this}} This attribute is a string that specifies the name of
-the ``project'' associated with the current notebook. As described in
-Section~\ref{subsec:projects}, a notebook's project determines where and how
-any \texttt{smuggle}d dependencies are installed if they are not available in
-the current runtime environment. By default, this attribute is named according
-to the current notebook's absolute file path. However, the project name may be
-customized to enable shared dependency installations across notebooks (see
-Sec.~\ref{subsec:projects}).
+\end{itemize}
 
-\end{itemize}
+\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
 
@@
 \textcolor{red}{\textbf{TODO: add content}}
+%- .configure()
+%- .get_project()
+%- .prune_projects()
+%- .require_pip()
+%- .require_python()
+%- .use_default_project()
 
@@
 to the Python compiler, in order to handle special constructs like
-\texttt{\%magic} and \texttt{!shell} commands. Davos uses
+\texttt{!}-prefixed shell commands and \texttt{\%}-prefixed ``magic'' commands. Davos uses
+%``magic'' (i.e., \texttt{\%}-prefixed) and and `` \texttt{!shell} commands. Davos uses
 this process to transform \texttt{smuggle} statements into

### 2023-09-19 paper/main.tex
edits through section 2.2.4

@@
 
-\subsection{Software architecture}
+\subsection{Software architecture}\label{sec:architecture}
 
@@
 
-To prevent Davos-enhanced notebooks from having unwanted side-effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
 Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
@@
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment). 
-In other cases, the user's environment may already provide all required packages, and the notebook's project directory will be unused (in which case it will be deleted automatically when the notebook kernel is shut down).
+In other cases, the user's environment may already provide all required packages, and the notebook's project directory will go unused (in which case it will be deleted automatically when the notebook kernel is shut down).
 But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
-Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will continue to be satisfied even if the user's Python environment changes.
+Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
 For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a Davos-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
@@
 From then on, any further changes to the user's \texttt{Numpy} installation would have no effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory.
-(If the version specified in the onion comment were changed, Davos would install it in the project directory in place of the previous version.) 
-For efficiency, Davos projects will generally avoid duplicating dependencies already satisfied by the user's Python environment. 
+(If the version specified in the onion comment were changed, Davos would update the version installed in the project directory accordingly.) 
+For efficiency, Davos projects will generally not duplicate dependencies already satisfied by the user's Python environment. 
 However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause Davos to install the smuggled package into the project directory whether or not it already exists locally.
@@
 This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
-\texttt{Project}s can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects (see Sec.~\ref{subsec:toplevel}).
+\texttt{Project} instances can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects (see Sec.~\ref{subsec:toplevel}).
+\textcolor{red}{\textbf{TODO}: mention \texttt{AbstractProject}s? Note default project name if imported in IPython shell, or fail to get notebook name?}
 
@@
 
-After importing Davos into a notebook, the top-level \texttt{davos} module provides a set of attributes whose values determine various aspects of Davos's behavior.
-A subset of these attributes are writeable options that may be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
+After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior.
+Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
 These include:
@@
 This attribute's default value is a notebook-specific project named for the absolute path to the notebook file.
-To change the project used in the current notebook (e.g., in order to share a project between multiple related notebooks), this attribute may be assigned a different \texttt{Project} instance or, for simplicity, the name of the desired project as a string or \texttt{pathlib.Path} (which will be converted to a \texttt{Project} on assignment).
-Alternatively, setting \texttt{davos.project} to \texttt{None} will disable project-based isolation for the current notebook and cause Davos to install packages directly into the main Python environment.
-This attribute is reset to its default value by the top-level \texttt{use\_default\_project()} function (see Sec.~\ref{subsec:toplevel}).
+To change the project used in the current notebook (e.g., in order to use the same project in multiple related notebooks), this attribute may be assigned a different \texttt{Project} instance or, for simplicity, the name of the desired project as a string or \texttt{pathlib.Path} (either of which will be converted to a \texttt{Project} on assignment).
+Alternatively, setting \texttt{davos.project} to \texttt{None} will disable project-based isolation for the current notebook and cause Davos to install any missing packages directly into the main Python environment.
+This attribute can be reset to its default value using the top-level \texttt{use\_default\_project()} function (see Sec.~\ref{subsec:toplevel}).
 For more information about Davos projects, see Section \ref{subsec:projects}.
@@
 
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
+\noindent The attributes above can be modified directly or via the \texttt{davos.configure()} function, which allows setting multiple options simultaneously (see Sec.~\ref{subsec:toplevel} for more information or Sec.~\ref{sec:illustrative-example} for example usage).
+In addition to these writeable options, the top-level \texttt{davos} module also exposes several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and provide potentially useful information about the notebook environment or Davos's internal state:
 
-\noindent Davos namespace also defines the \texttt{davos.configure()} function,
-which allows setting multiple configuration options simultaneously. In addition
-to the above configurable attributes, the \texttt{davos} object also includes
-several read-only attributes that contain potentially useful information about
-the current environment or Davos's behavior:
+%\noindent Davos also provides a top-level \texttt{configure()} function that allows setting multiple of the above options simultaneously (see Sec.~\ref{subsec:toplevel} or Sec.~\ref{sec:illustrative-example} for example usage).
+In addition to these writeable options,
+%
+% for setting multiple of the above options simultaneously (see Sec.~\ref{sec:illustrative-example} for 
+%
+%\noindent Davos namespace also defines the \texttt{davos.configure()} function,
+%which allows setting multiple configuration options simultaneously. In addition
+%to the above configurable attributes, the \texttt{davos} object also includes
+%several read-only attributes that contain potentially useful information about
+%the current environment or Davos's behavior:
 
@@
 
-\item \texttt{.environment}: This attribute's value is a string describing the notebook
-environment Davos was imported into. As of the current version (0.2.0 \textcolor{red}{\textbf{TODO: fix version}}), this
-attribute will be set to either \texttt{“IPython<7.0"}, \texttt{“IPython>=7.0”}, or \texttt{“Colaboratory”} \textcolor{red}{\textbf{TODO: fix quotes}}.
+\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects (as \texttt{Project} objects) that exist on the user's local system.
+See Section~\ref{subsec:projects} for more information about Davos projects.
+
+\item \texttt{.environment}: This attribute's value is a string denoting the set of environment-dependent ``helper functions'' used by Davos in the current notebook.
+As described in Section \ref{sec:architecture}, Davos internally chooses between interchangeable implementations of certain core features
+%(defined in the \texttt{davos.implementations} subpackage) 
+based on various properties of the notebook's frontend and IPython kernel.
+As of this writing, three unique combinations of helper functions are required to support existing notebook environments, ergo this attribute has three possible values: \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, or \texttt{"Colaboratory"}.
+However, this attribute could take on additional values in the future, as new notebook interfaces are created and IPython's internals are updated, and additional versions of helper functions are added to Davos to support them.
+
+%\item \texttt{.environment}: This attribute's value is a string describing the notebook environment into which Davos was imported.
+Davos uses this value internally to select between interchangeable implementations of certain core features based on various properties of the current notebook's frontend and IPython kernel (see Sec.~\ref{sec:architecture} and Fig.~\ref{fig:package-structure}).
+As of this writing, possible values of this attribute are \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, and \texttt{"Colaboratory"}, though additional alternatives may be added in the future as new notebook interfaces and IPython versions are released, and Davos is updated to support them.
+ %are released and the IPython ecosystem continues to evolve.
+\textcolor{red}{\textbf{TODO}: tweak wording to convey new possibilities will be added when new things are released that aren't covered by existing implementations, and davos adds new mutually exclusive ones to support them}
 
@@
 
-  \item \texttt{.smuggled}: This attribute is set to a Python dictionary that functions as a cache of any \texttt{smuggle} commands run during the current
-session.  The dictionary's keys are package names and the values are arguments passed via the corresponding smuggle statement's onion comment.
-
-  \item \texttt{.all\_projects}: This attribute contains a list of all local projects (i.e., projects with virtual environment directories located in \texttt{\$HOME/.davos/projects}).
-See Section~\ref{subsec:projects} for additional information about Davos projects.
+\item \texttt{.smuggled}: This attribute's value is a Python dictionary that functions as a cache of \texttt{smuggle} statements executed during the current notebook kernel session.
+The dictionary's keys are names of smuggled packages, and its values are arguments passed to the installer program via onion comments.
+Entries appear in order of the \texttt{smuggle} statements' execution.
 
 \end{itemize}
+
+\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
 

### 2023-09-19 paper/main.tex
minor updates to projects section

@@
 But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
+
 Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
@@
 By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file.
-However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any string (that is a valid Unix directory name) to \texttt{davos.project} (see Sec.~\ref{subsec:config}).
+However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any (non-empty) string to \texttt{davos.project} (see Sec.~\ref{subsec:config}).
 This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
@@
 This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
-\texttt{Project} instances can also be created and managed programmatically, and Davos provides additional top-level functions for viewing and working with all existing projects (see Sec.~\ref{subsec:toplevel}).
+\texttt{Project} instances can also be created and managed programmatically, and Davos provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
 \textcolor{red}{\textbf{TODO}: mention \texttt{AbstractProject}s? Note default project name if imported in IPython shell, or fail to get notebook name?}

### 2023-09-19 paper/main.tex
add AbstractProject description to all_projects bullet in sec 2.2.4

@@
 After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior.
-Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
+Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example).
 These include:
@@
   disabled (\texttt{False}).  When Davos is first imported,
-  \texttt{davos.active} is set to \texttt{True}.
+  \texttt{davos.active} is set to \texttt{True} (see Sec.~\ref{subsec:implementation} for implementation details and additional information).
 
@@
 
-\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects (as \texttt{Project} objects) that exist on the user's local system.
-See Section~\ref{subsec:projects} for more information about Davos projects.
+\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects that exist on the user's local system (see Sec.~\ref{subsec:projects} for more information about Davos projects).
+Each item in this list is either a \texttt{Project} or \texttt{AbstractProject} instance.
+\texttt{AbstractProject}s represent notebook-specific projects whose associated notebooks no longer exist.
+They support all the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
+\textcolor{red}{\textbf{TODO}: mention that project can become AbstractProject when notebook is moved/renamed, and can be re-linked by renaming project to new path?}
 

### 2023-09-20 paper/main.tex
working on section 2.2.5

@@
 \subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
-\textcolor{red}{\textbf{TODO: add content}}
+
+The Davos package also provides a handful of top-level functions for convenience and to provide additional functionality:
+
+\begin{itemize}
+
 %- .configure()
+\item \texttt{configure(**kwargs)}: This function provides an alternate way of assigning values to the writeable attributes listed in Section \ref{subsec:config} and can be used to configure multiple options at once (see Sec.~\ref{sec:illustrative-example} for example usage).
+The function accepts attribute names as keyword-only arguments, to which their desired values are passed.
+If any of the options passed are incompatible (e.g., both \texttt{confirm\_install=True} and \texttt{noninteractive=True} are passed) or assignment to any of the specified attributes fails for any reason, none of the given options will be modified.
+
 %- .get_project()
+\item \texttt{get\_project(project\_name, create=False)}: This function can be passed the name of a Davos project (\texttt{project\_name}) to get the \texttt{Project} or \texttt{AbstractProject} instance representing it.
+If no project with the given name exists and \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will instead be created and returned.
+
 %- .prune_projects()
+\item \texttt{prune\_projects(yes=False)}: This function allows users to quickly ``clean up'' their local Davos projects by deleting notebook-specific projects whose corresponding notebooks no longer exist (i.e., \texttt{AbstractProject}s).
+As with standard virtual environments, periodically removing large package directories can be useful for reclaiming disk space once they are no longer needed.
+By default, this function will interactively display a list of all unused projects and allow the user to choose whether or not to delete each one.
+Alternatively, passing \texttt{yes=True} will immediately remove all unused projects without requiring confirmation.
+Note that if Davos's non-interactive mode is enabled (i.e., \texttt{davos.noninteractive} has been set to \texttt{True}), \texttt{yes=True} \textit{must} be explicitly passed in order to delete projects.
+This serves as a safeguard against accidentally deleting projects, since non-interactive mode disables all user input and confirmation.
+Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook filepaths), as they are not linked to a specific notebook whose existence can be checked automatically.
+However, any project can be deleted individually via its \texttt{Project} object's \texttt{.remove()} method.
+
 %- .require_pip()
+\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
 %- .require_python()
+\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
 %- .use_default_project()
+\item \texttt{use\_default\_project()}:
+\end{itemize}
 

### 2023-09-20 davos/core/project.py
Fix ContextLab/davos#97 - `davos.prune_projects()` now requires explicitly passing `yes=True` in non-interactive mode - both `davos.prune_projects()` and `davos.Project.remove()` now respect `davos.suppress_stdout`

@@ -256,12 +256,12 @@ class Project(metaclass=ProjectChecker):
         if not yes:
             if config.noninteractive:
                 raise DavosProjectError(
-                    "To remove a project when noninteractive mode is "
-                    "enabled, you must explicitly pass 'yes=True'."
+                    "To remove a project when noninteractive mode is enabled, "
+                    "you must explicitly pass 'yes=True'."
                 )
             prompt = f"Remove project {self.name!r} and all installed packages?"
             confirmed = prompt_input(prompt, default='n')
-            if not confirmed:
+            if not confirmed and not config.suppress_stdout:
                 print(f"{self.name} not removed")
                 return
         shutil.rmtree(self.project_dir)
@@ -773,6 +773,12 @@ def prune_projects(yes=False):
        the interpreter is shut down -- they're only checked for and
        dealt with here as a fallback in case one somehow sneaks through.
     """
+    if config.noninteractive and not yes:
+        raise DavosProjectError(
+            "To remove projects when noninteractive mode is enabled, you must "
+            "explicitly pass 'yes=True'."
+        )
+
     # dict of projects to remove -- keys: "safe"-formatted project
     # directory names; values: corresponding notebook filepaths
     to_remove = {}
@@ -848,7 +854,7 @@ def prune_projects(yes=False):
             clear_output(wait=False)
         # print final status for all projects processed
         print(template.format(*statuses))
-    else:
+    elif not config.suppress_stdout:
         print("No unused projects found.")
 
 

### 2023-09-22 paper/main.tex
add note about viewing all top-level attribute values via davos.config

@@
 
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
+The current values of all \texttt{davos} attributes may be viewed at once within a notebook by displaying the \texttt{davos.config} object.
 
@@
 %- .require_pip()
-\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
+%\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
 %- .require_python()

### 2023-09-22 paper/main.tex
expanded start of top-level functions section slightly

@@
 
-The Davos package also provides a handful of top-level functions for convenience and to provide additional functionality:
+The Davos package also provides a handful of functions available in the top-level \texttt{davos} namespace.
+Some of these function serve primarily as conveniences, while others provide additional functionality:
 

### 2023-09-22 paper/main.tex
fix close-quotes character

@@
 The Davos package is named after Davos Seaworth, a smuggler referred
-to as ``the Onion Knight" from the series \textit{A Song of Ice and Fire} by
+to as ``the Onion Knight'' from the series \textit{A Song of Ice and Fire} by
 George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by

### 2023-09-22 paper/main.tex
minor tweaks to section 2.2.4

@@
 After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior.
-Most of these attributes are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example).
+The majority of these are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example).
 These include:
@@
 \noindent The attributes above can be modified directly or via the \texttt{davos.configure()} function, which allows setting multiple options simultaneously (see Sec.~\ref{subsec:toplevel} for more information or Sec.~\ref{sec:illustrative-example} for example usage).
-In addition to these writeable options, the top-level \texttt{davos} module also exposes several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and provide potentially useful information about the notebook environment or Davos's internal state:
+In addition to these writeable options, the top-level \texttt{davos} module also provides several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and contain potentially useful information about the notebook environment or Davos's internal state:
 

### 2023-09-23 davos/core/config.py
fix ContextLab#98: check juptyer notebook vs lab interface, store value in config, use value in command to get running servers

@@ -20,6 +20,7 @@ __all__ = ['DavosConfig']
 
 import os
 import pprint
+import shlex
 import shutil
 import site
 import sys
@@ -29,6 +30,8 @@ import warnings
 from io import StringIO
 from os.path import expandvars
 from pathlib import Path
+from locale import getpreferredencoding
+from subprocess import CalledProcessError, check_output
 
 from davos.core.exceptions import (
     DavosConfigError,
@@ -199,6 +202,7 @@ class DavosConfig(metaclass=SingletonConfig):
         self._conda_envs_dirs = None
         self._default_pip_executable = self._find_default_pip_executable()
         self._ipy_showsyntaxerror_orig = None
+        self._jupyter_interface = _get_jupyter_interface()
         self._repr_formatter = pprint.PrettyPrinter()
         if sys.version_info.minor >= 8:
             # sort_dicts constructor param added in Python 3.8, defaults
@@ -556,6 +560,75 @@ def _block_greedy_ipython_completer():
             del sys.modules['davos.core.config']
             # pylint: disable=broad-exception-raised
             raise Exception
+
+
+def _get_jupyter_interface():
+    """
+    Determines whether the notebook is being run through the "classic"
+    Jupyter notebook interface or JupyterLab. Used to set the value of
+    `davos.config._jupyter_interface`.
+
+    Returns
+    -------
+    interface : str
+        "notebook" for classic Jupyter notebooks (or unknown); "lab" for
+        JupyterLab.
+
+    Notes
+    -----
+    1. This distinction is needed because recent versions of the
+       `jupyterlab` package no longer depend on `notebook`, so if the
+       user is running JupyterLab, some `jupyter notebook ...` shell
+       commands davos runs internally may not be available and will need
+       to be run as `jupyter lab ...` commands instead.
+    2. "notebook" is treated as a strong default assumption and returned
+       if the interface cannot be determined, for a few reasons:
+       - Only more recent JupyterLab versions have dropped `notebook` as
+         a dependency, so it's less likely the user will have JupyterLab
+         without `notebook` than vice versa.
+       - IDEs tend to run simple notebook servers rather than JupyterLab
+         for custom interfaces, but the command to launch the server may
+         not be the immediate parent process in that case and trying to
+         check all processes introduces a cascade of other issues.
+       - Colab notebooks also use the "classic" notebook server and make
+         up a fairly large percentage of Davos uses, but the Colab VM
+         environment is changed frequently and without notice, so it's
+         more likely to break or otherwise mess with users/packages'
[…]

### 2023-09-23 davos/core/project.py

@@ -52,6 +52,7 @@ import sys
 import warnings
 from os.path import expandvars
 from pathlib import Path
+from subprocess import CalledProcessError
 from urllib.request import urlopen
 from urllib.parse import parse_qs, unquote, urlencode, urljoin, urlparse
 
@@ -645,8 +646,18 @@ def get_notebook_path():
     kernel_filepath = ipykernel.connect.get_connection_file()
     kernel_id = kernel_filepath.split('/kernel-')[-1].split('.json')[0]
 
-    running_nbservers_stdout = run_shell_command('jupyter notebook list',
-                                                 live_stdout=False)
+    nbserver_list_cmd = f'jupyter {config._jupyter_interface} list'
+    try:
+        running_nbservers_stdout = run_shell_command(nbserver_list_cmd,
+                                                     live_stdout=False)
+    except CalledProcessError as e:
+        # raise RuntimeError so it's caught by `use_default_project` and
+        # the fallback project is used
+        raise RuntimeError(
+            "Shell command to get running Jupyter servers "
+            f"({nbserver_list_cmd}) failed"
+        ) from e
+
     for line in running_nbservers_stdout.splitlines():
         # should only need to exclude first line ("Currently running
         # servers:"), but handle safely in case output format changes in

### 2023-09-23 paper/main.tex
edits through end of section 2

@@
 
-%- .configure()
 \item \texttt{configure(**kwargs)}: This function provides an alternate way of assigning values to the writeable attributes listed in Section \ref{subsec:config} and can be used to configure multiple options at once (see Sec.~\ref{sec:illustrative-example} for example usage).
-The function accepts attribute names as keyword-only arguments, to which their desired values are passed.
+The function accepts attribute names as keyword-only arguments to which their desired values are passed.
 If any of the options passed are incompatible (e.g., both \texttt{confirm\_install=True} and \texttt{noninteractive=True} are passed) or assignment to any of the specified attributes fails for any reason, none of the given options will be modified.
 
-%- .get_project()
 \item \texttt{get\_project(project\_name, create=False)}: This function can be passed the name of a Davos project (\texttt{project\_name}) to get the \texttt{Project} or \texttt{AbstractProject} instance representing it.
-If no project with the given name exists and \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will instead be created and returned.
-
-%- .prune_projects()
+The optional \texttt{create} argument determines the function's behavior when no project with the given name exists: if \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will be created and returned.
+
+%If no project with the given name exists and \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will instead be created and returned.
+
 \item \texttt{prune\_projects(yes=False)}: This function allows users to quickly ``clean up'' their local Davos projects by deleting notebook-specific projects whose corresponding notebooks no longer exist (i.e., \texttt{AbstractProject}s).
-As with standard virtual environments, periodically removing large package directories can be useful for reclaiming disk space once they are no longer needed.
+As with standard virtual environments, periodically removing unused project directories can be useful for reclaiming disk space from dependencies of code that is no longer in use.
 By default, this function will interactively display a list of all unused projects and allow the user to choose whether or not to delete each one.
-Alternatively, passing \texttt{yes=True} will immediately remove all unused projects without requiring confirmation.
-Note that if Davos's non-interactive mode is enabled (i.e., \texttt{davos.noninteractive} has been set to \texttt{True}), \texttt{yes=True} \textit{must} be explicitly passed in order to delete projects.
-This serves as a safeguard against accidentally deleting projects, since non-interactive mode disables all user input and confirmation.
-Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook filepaths), as they are not linked to a specific notebook whose existence can be checked automatically.
-However, any project can be deleted individually via its \texttt{Project} object's \texttt{.remove()} method.
-
-%- .require_pip()
-%\item \texttt{require\_pip(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
-%- .require_python()
-\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}:
-%- .use_default_project()
-\item \texttt{use\_default\_project()}:
+Alternatively, passing \texttt{yes=True} will immediately remove all unused projects without prompting for confirmation.
+Note that if Davos's non-interactive mode is enabled (see Sec.~\ref{subsec:config}), \texttt{yes=True} must be explicitly passed, otherwise the function will raise an exception.
+This serves as a safeguard against accidentally deleting projects since non-interactive mode disables all user input and confirmation.
+Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook filepaths), as they are not linked to specific notebooks whose existence determines whether or not they are still needed.
+These (and any) projects may be deleted individually by calling their \texttt{Project} objects' \texttt{.remove()} method.
+
+\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}: Through \texttt{smuggle} statements and onion comments, Davos can automatically ensure that all Python packages needed to run a notebook are installed, and that the same versions of those packages are used no matter when or by whom the notebook is run.
+However, because Davos operates at runtime, one thing it cannot do automatically is install and switch to a specific version of Python itself.
+Distributing shared code along with a particular Python version for running it 
+%Ensuring that a particular Python version is used to run shared code typically
+%Ensuring that shared code is run with a particular Python version typically 
+requires a heavier-weight solution,
+%than Davos (or a virtual environment), 
+such as a Conda environment or Docker container (see Fig.~\ref{fig:code-sharing}). 
+Yet a Davos-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a specific Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
+The \texttt{davos.require\_python()} function can be added to the top of a Davos-enhanced notebook to communicate to users that the notebook's code should be run with a specific or constrained Python version (see Sec.~\ref{sec:illustrative-example} for example usage).
+The function may be passed a version string (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
+Alternatively, a ``soft'' or suggested constraint can be specified by passing \texttt{warn=True} to issue a warning rather than raise an error.
+Additional information can be added to the default error/warning message (e.g., the specific reason for this requirement) via the \texttt{extra\_msg} argument, and the optional \texttt{prereleases} argument can be used to explicitly allow (\texttt{True}) or disallow (\texttt{False}) pre-release versions (by default, the policy is determined by the value of \texttt{version\_spec}).
+
+\item \texttt{use\_default\_project()}: By default, each Davos-enhanced notebook will create and use a notebook-specific project named for the absolute path to the notebook file.
+If a user manually changes the project used by the current notebook (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to reset \texttt{davos.project} to its default value and switch back to the original default project.
+See Section \ref{subsec:projects} for more information about Davos projects and Section \ref{sec:illustrative-example} for an illustrative example.
+%If the user manually configures a notebook to use a different project (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to
+%This function can be called to reset the \texttt{davos.project} attribute (i.e., the project used by the current notebook; see Sec.~\ref{subsec:config}) to its default value if it has been manually set to a different value.
+The default project for a Davos-enhanced notebook will be a notebook-specific project named for the notebook's absolute path (see Sec.~\ref{subsec:projects}), with two (uncommon) exceptions.
+First, First, if Davos cannot determine \_\_\_.
+Second, Davos offers experimental support for use in IPython terminal shells.
+All terminal shell instances share a common project named \texttt{"ipython-shell"}.
+
 \end{itemize}
@@
 \end{figure}
+
+\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
 

### 2023-09-23 paper/main.tex
added new paragraph to start of section 3

@@
 
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
-
 \section{Illustrative Example}\label{sec:illustrative-example}
@@
 
-Across different versions of a given package, particular modules, functions,
+%The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: a series of \texttt{smuggle} statements and onion comments with version specifiers or other options collectively define a
+The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
+In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features and illustrate how they may be used to handle certain challenges that can arise with sharing reproducible scientific code.
+
+\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
+
+Across different versions of a given package, various modules, functions,
 and other objects may be updated, removed, renamed, or otherwise altered. In

### 2023-09-23 paper/main.tex
cleaned up source file from recent edits

@@
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated,
-%and work by \textit{supplementing} the user's existing Python environment rather than replacing it.
-and function to \textit{extend} the user's existing Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and function to \textit{extend} the user's existing Python environment rather than replace it.
 
@@
 
-Thus, rather than constructing fully separate Python environments from scratch,
-%Davos projects serve to fill in the gap between the user's existing environment and the dependencies of their corresponding notebooks.
-Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
@@
 This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
-%This provides a convenient way to share a single Davos project across multiple related notebooks that share a common set of requirements, by setting \texttt{davos.project} to the same string in each one.
 It is also possible (though not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
@@
 \texttt{Project} instances can also be created and managed programmatically, and Davos provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
-\textcolor{red}{\textbf{TODO}: mention \texttt{AbstractProject}s? Note default project name if imported in IPython shell, or fail to get notebook name?}
 
@@
 These include:
-
-%After importing Davos into a notebook, the top-level \texttt{davos} module provides a set of attributes whose values may be displayed interactively, checked programmatically at runtime, or modified to customize various aspects of Davos's behavior (see Sec.~\ref{sec:illustrative-example} for an illustrative example and Sec.~\ref{subsec:implementation} for implementation details and additional information).
-%These writeable attributes include:
-
-%Davos's behavior may be customized by modifying a set of attributes attached to
-%the \texttt{davos} module object that is added to the workspace when Davos is
-%imported. These attributes may be modified, displayed, or checked
-%programmatically at runtime (see Sec.~\ref{sec:illustrative-example} for an
-%illustrative example or Sec.~\ref{subsec:implementation} for implementation
-%details and additional information). These include:
 
@@
   This can be useful when smuggling packages that require installing many
-  dependencies and/or generate extensive output when built from source distributions. Note that if this option is enabled and the installer
+  dependencies and/or generate extensive output when built from source
+  distributions. Note that if this option is enabled and the installer
   program throws an error, both its stdout and stderr streams will still be
@@
 In addition to these writeable options, the top-level \texttt{davos} module also provides several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and contain potentially useful information about the notebook environment or Davos's internal state:
-
-%\noindent Davos also provides a top-level \texttt{configure()} function that allows setting multiple of the above options simultaneously (see Sec.~\ref{subsec:toplevel} or Sec.~\ref{sec:illustrative-example} for example usage).
-In addition to these writeable options,
-%
-% for setting multiple of the above options simultaneously (see Sec.~\ref{sec:illustrative-example} for
-%
-%\noindent Davos namespace also defines the \texttt{davos.configure()} function,
-%which allows setting multiple configuration options simultaneously. In addition
-%to the above configurable attributes, the \texttt{davos} object also includes
-%several read-only attributes that contain potentially useful information about
-%the current environment or Davos's behavior:
 
@@
   They support all the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
-\textcolor{red}{\textbf{TODO}: mention that project can become AbstractProject when notebook is moved/renamed, and can be re-linked by renaming project to new path?}
 
 \item \texttt{.environment}: This attribute's value is a string denoting the set of environment-dependent ``helper functions'' used by Davos in the current notebook.
-As described in Section \ref{sec:architecture}, Davos internally chooses between interchangeable implementations of certain core features
-%(defined in the \texttt{davos.implementations} subpackage)
-based on various properties of the notebook's frontend and IPython kernel.
+  As described in Section \ref{sec:architecture}, Davos internally chooses between interchangeable implementations of certain core features based on various properties of the notebook's frontend and IPython kernel.
   As of this writing, three unique combinations of helper functions are required to support existing notebook environments, ergo this attribute has three possible values: \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, or \texttt{"Colaboratory"}.
   However, this attribute could take on additional values in the future, as new notebook interfaces are created and IPython's internals are updated, and additional versions of helper functions are added to Davos to support them.
-
-%\item \texttt{.environment}: This attribute's value is a string describing the notebook environment into which Davos was imported.
-Davos uses this value internally to select between interchangeable implementations of certain core features based on various properties of the current notebook's frontend and IPython kernel (see Sec.~\ref{sec:architecture} and Fig.~\ref{fig:package-structure}).
-As of this writing, possible values of this attribute are \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, and \texttt{"Colaboratory"}, though additional alternatives may be added in the future as new notebook interfaces and IPython versions are released, and Davos is updated to support them.
- %are released and the IPython ecosystem continues to evolve.
-\textcolor{red}{\textbf{TODO}: tweak wording to convey new possibilities will be added when new things are released that aren't covered by existing implementations, and davos adds new mutually exclusive ones to support them}
 
@@
 
-The current values of all \texttt{davos} attributes may be viewed at once within a notebook by displaying the \texttt{davos.config} object.
+\noindent The current values of all \texttt{davos} attributes may be viewed at once within a notebook by displaying the \texttt{davos.config} object.
 
@@
   The optional \texttt{create} argument determines the function's behavior when no project with the given name exists: if \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will be created and returned.
-
-%If no project with the given name exists and \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will instead be created and returned.
 
@@
   However, because Davos operates at runtime, one thing it cannot do automatically is install and switch to a specific version of Python itself.
-Distributing shared code along with a particular Python version for running it
-%Ensuring that a particular Python version is used to run shared code typically
-%Ensuring that shared code is run with a particular Python version typically
-requires a heavier-weight solution,
-%than Davos (or a virtual environment),
-such as a Conda environment or Docker container (see Fig.~\ref{fig:code-sharing}).
-Yet a Davos-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a specific Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
+  Distributing shared code along with a precise Python version for running it requires a heavier-weight solution, such as a Conda environment or Docker container (see Fig.~\ref{fig:code-sharing}).
+  Yet a Davos-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a particular Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
   The \texttt{davos.require\_python()} function can be added to the top of a Davos-enhanced notebook to communicate to users that the notebook's code should be run with a specific or constrained Python version (see Sec.~\ref{sec:illustrative-example} for example usage).
-The function may be passed a version string (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
+  The function may be passed a version identifier (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
   Alternatively, a ``soft'' or suggested constraint can be specified by passing \texttt{warn=True} to issue a warning rather than raise an error.
@@
 
-\item \texttt{use\_default\_project()}: By default, each Davos-enhanced notebook will create and use a notebook-specific project named for the absolute path to the notebook file.
-If a user manually changes the project used by the current notebook (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to reset \texttt{davos.project} to its default value and switch back to the original default project.
+\item \texttt{use\_default\_project()}: By default, each Davos-enhanced notebook will create and use a notebook-specific project named based on its absolute path.
+  If a user manually changes the project used by the current notebook (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to switch back to using the notebook's default project and reset \texttt{davos.project} to its default value.
   See Section \ref{subsec:projects} for more information about Davos projects and Section \ref{sec:illustrative-example} for an illustrative example.
-%If the user manually configures a notebook to use a different project (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to
-%This function can be called to reset the \texttt{davos.project} attribute (i.e., the project used by the current notebook; see Sec.~\ref{subsec:config}) to its default value if it has been manually set to a different value.
-The default project for a Davos-enhanced notebook will be a notebook-specific project named for the notebook's absolute path (see Sec.~\ref{subsec:projects}), with two (uncommon) exceptions.
-First, First, if Davos cannot determine \_\_\_.
-Second, Davos offers experimental support for use in IPython terminal shells.
-All terminal shell instances share a common project named \texttt{"ipython-shell"}.
 
@@
 \texttt{!}-prefixed shell commands and \texttt{\%}-prefixed ``magic'' commands. Davos uses
-%``magic'' (i.e., \texttt{\%}-prefixed) and and `` \texttt{!shell} commands. Davos uses
-this process to transform \texttt{smuggle} statements into
+this same process to invisibly transform \texttt{smuggle} statements into
 syntactically valid Python code. The Davos parser uses a
@@
 set of input transformers run when each notebook cell is
-executed. While the overhead added by the Davos parser is
-minimal, this may be useful, for example, when optimizing or precisely
-profiling code.
+executed.
 
@@
 
-%The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: a series of \texttt{smuggle} statements and onion comments with version specifiers or other options collectively define a
-The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
+The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used:
+By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
 In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features and illustrate how they may be used to handle certain challenges that can arise with sharing reproducible scientific code.

### 2023-09-25 paper/main.tex
add ref for scikit-learn docs page
fixed a typo in section 2.2.5
update fig 3 caption, other minor wording changes & typo fixes pre-section 3

@@
 The Davos package also provides a handful of functions available in the top-level \texttt{davos} namespace.
-Some of these function serve primarily as conveniences, while others provide additional functionality:
+Some of these functions serve primarily as conveniences, while others provide additional functionality:
 
@@
   The function may be passed a version identifier (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
-  Alternatively, a ``soft'' or suggested constraint can be specified by passing \texttt{warn=True} to issue a warning rather than raise an error.
+  Alternatively, a ``soft'' or suggested constraint can be imposed by passing \texttt{warn=True} to issue a warning rather than raise an error.
   Additional information can be added to the default error/warning message (e.g., the specific reason for this requirement) via the \texttt{extra\_msg} argument, and the optional \texttt{prereleases} argument can be used to explicitly allow (\texttt{True}) or disallow (\texttt{False}) pre-release versions (by default, the policy is determined by the value of \texttt{version\_spec}).
@@
   following two basic steps.  First (left), Davos ensures that the
-correct version of the desired package has been installed, carrying
-out the installation automatically if needed.  Second (right),
-Davos imports the package and updates the current runtime environment.}
+  correct version of the desired package is available locally, installing
+  it automatically (into the notebook's project directory) if needed.  Second (right),
+  Davos loads the package into the notebook and updates the current
+  runtime environment.}
 \label{fig:flow-chart}
@@
 The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used:
-By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
-In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features and illustrate how they may be used to handle certain challenges that can arise with sharing reproducible scientific code.
-
-\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip
+By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional tools or setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
+In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features, and illustrate how they may be used to handle certain challenges that can arise when writing and sharing reproducible scientific code.
 
@@
 successfully ``unpickle'' (i.e., load and restore) a ``pickled'' (i.e., previously saved)
-object, the object's class must be defined in and importable from the same
-module as when it was saved. Thus, because of the \texttt{Panel} class's
+object, that object's class must be defined in and importable from the same
+module as it was when the object was originally saved. Thus, because of the \texttt{Panel} class's
 removal, the user's dataset could not be read by any version of \texttt{pandas}
-from 0.25.0 or beyond. These incompatibilities are also not limited solely to
+from 0.25.0 onward. These incompatibilities are also not limited solely to
 traditional forms of data. For example, saved model states and other objects
@@
 may not be identical (or even present) across all versions of their associated
-package.
+packages.
 
 The example provided in Figure~\ref{fig:illustrative-example} demonstrates how
-the Davos package can be used to circumvent these incompatibilities by
-carefully controlling which versions of each package are used in different
-parts of the notebook. The example shows how a dataset and model that require
+Davos can be used to circumvent these incompatibilities by
+temporarily switching between different versions of the same package within a single runtime.
+%carefully controlling which versions of each package are used in different parts of the notebook.
+The example shows how a dataset and model that require
 now-incompatible components of the \texttt{pandas} and
-\texttt{scikit-learn}~\cite{PedrEtal11} packages may be loaded in (using older
+\texttt{scikit-learn}~\cite{PedrEtal11} libraries may be loaded in (using older
 versions of each package) and used alongside more recent versions of each
 package that provide new and improved functionality. When included at the top
-of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
+of an IPython notebook, the code in Figure~\ref{fig:illustrative-example}
 ensures that these objects will be loaded successfully and analyzed using the
@@
 original creator using the \texttt{joblib} package, as
-\texttt{scikit-learn}'s documentation recommends.  Because
+\texttt{scikit-learn}'s documentation recommends \cite{skle22}.  Because
 \texttt{joblib} uses the \texttt{pickle} protocol internally, the

### 2023-09-25 paper/main.tex
update in-text example snippet fig numbers since there's now 8 instead of 7

@@
 
-After installing and importing Davos (lines 1--2), we first \texttt{smuggle} two
+\begin{center}
+\includegraphics[width=0.9\textwidth]{figs/example1}
+\end{center}
+Next, in lines 8--9 we \texttt{smuggle} two
 utilities for interacting with local files in the code below. The
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example1}
+\includegraphics[width=0.9\textwidth]{figs/example2}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example2}
+\includegraphics[width=0.9\textwidth]{figs/example3}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example3}
+\includegraphics[width=0.9\textwidth]{figs/example4}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example4}
+\includegraphics[width=0.9\textwidth]{figs/example5}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example5}
+\includegraphics[width=0.9\textwidth]{figs/example6}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example6}
+\includegraphics[width=0.9\textwidth]{figs/example7}
 \end{center}
@@
 interchangeable IPython kernels.  To accommodate this multi-environment
-scenario, on lines 26 and 28, we use the \texttt{pip\_executable} option to control which environments each
+scenario, in lines 26 and 28, we use the \texttt{pip\_executable} option to control which environments each
 package should be installed to.  Once these two packages are installed
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figs/example7}
+\includegraphics[width=0.9\textwidth]{figs/example8}
 \end{center}

### 2023-09-25 paper/main.tex
WIP updating illustrative example text

@@
 \geometry{left=1in, right=1in, top=1in, bottom=1in, headsep=0pt}
+
+\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO}: #1}}
+\newcommand{\stoppedhere}{\bigskip\bigskip\textcolor{red}{\textbf{========== TODO: finish editing from here to end ==========}}\bigskip\bigskip}
 
@@
 character Davos Seaworth (who became famous for smuggling onions through a
-blockade on his homeland), we use ``onion'' comments to precisely control how
+blockade on his homeland), the Davos package uses ``onion comments'' to precisely control how
 packages are smuggled into the Python workspace.
@@
 
+After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_python()} function to constrain the Python version used to run the code below (see Sec.~\ref{subsec:toplevel}).
+As described above, the example code in Figure \ref{fig:illustrative-example} uses two different versions of the \texttt{pandas} library: first, an older one needed to access a dataset saved in an outmoded format, then a newer one throughout the remainder of the notebook.
+Line 6 therefore ensures upfront that the notebook's Python version falls within the overlap between the ranges of Python versions that these two versions of \texttt{pandas} support.
+If it does not, the function in line 6 will raise an error that includes a message to this effect (lines 4--5).
 \begin{center}
@@
 utilities for interacting with local files in the code below. The
-\texttt{smuggle} statement in line 4 loads the \texttt{is\_file()}
+\texttt{smuggle} statement in line 8 loads the \texttt{is\_file()}
 function from the Python standard library's \texttt{os.path}
-module. Standard library modules are included with all Python
-distributions, so this line is functionally equivalent to an
+module. Since standard library modules are included with all Python
+distributions, this line is functionally equivalent to an
 \texttt{import} statement and does not need or benefit from an onion
-comment. Line 5 loads the \texttt{joblib} package~\cite{Varo10},
+comment. Line 9 loads the \texttt{joblib} package~\cite{Varo10},
 installing it first, if necessary. Since \texttt{joblib}'s I/O
 interface has historically remained stable and backwards-compatible
-across releases, requiring that users have a particular exact version
-installed would likely be unnecessarily restrictive. However, a
-\textit{future} release might introduce some breaking change.  The
-onion comment in line 5 helps ensure the analysis notebook continues
+across releases, requiring a particular exact version
+would likely be unnecessarily restrictive. However, it is possible a
+\textit{future} release could introduce some breaking change.  The
+onion comment in line 9 helps ensure the analysis notebook continues
 to run properly in the future by limiting allowable versions to those
@@
 \end{center}
+
+\stoppedhere
+
 Setting the \texttt{auto\_rerun} attribute to \texttt{True} is particularly useful
@@
 latest approaches and implementations.
+
+\todo{mention notebook reproducibility, cell order, multiple package versions re: reviewer's comment; note importance of running lines 14--19 \& 38--40 in single cell; say another option is to alias one version, e.g., \texttt{smuggle pandas as pd\_old}}
 

### 2023-09-25 paper/main.tex
rewrote section 3 intro paragraph

@@
 
-The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used:
-By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional tools or setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
-In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features, and illustrate how they may be used to handle certain challenges that can arise when writing and sharing reproducible scientific code.
+%The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used:
+%By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional tools or setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
+The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
+When added to the top of a Jupyter notebook, this allows researchers to bundle their code and its dependencies into a single file that can be easily shared and run without any additional tools or setup, automatically installs its required packages at runtime, isolates them from the user's main Python environment, and ensures their versions do not change unexpectedly over time.
+In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features, and illustrate how they may be used to handle certain challenges that can arise when writing, running, and sharing reproducible scientific code.
 

### 2023-09-25 paper/main.tex
refined first few illustrative example snippet descriptions:

@@
 other versions of the same package. For example, the popular
-\texttt{pandas}~\cite{McKi10} library used to include the \texttt{Panel} data
-structure for storing 3-dimensional arrays. Since version 0.20.0, however, the
-\texttt{Panel} class has been deprecated, and in version 0.25.0, it was removed
+\texttt{pandas}~\cite{McKi10} library originally included the \texttt{Panel} data
+structure for storing 3-dimensional arrays. In version 0.20.0, however, the
+\texttt{Panel} class was deprecated, and in version 0.25.0, it was removed
 entirely. Suppose a user had a dataset stored in a \texttt{Panel} object
@@
 now-incompatible components of the \texttt{pandas} and
-\texttt{scikit-learn}~\cite{PedrEtal11} libraries may be loaded in (using older
+\texttt{scikit-learn}~\cite{PedrEtal11} libraries can be loaded in (using older
 versions of each package) and used alongside more recent versions of each
 package that provide new and improved functionality. When included at the top
-of an IPython notebook, the code in Figure~\ref{fig:illustrative-example}
+of a Jupyter notebook, the code in Figure~\ref{fig:illustrative-example}
 ensures that these objects will be loaded successfully and analyzed using the
-same set of package versions, no matter when or by whom the notebook is run.
-
-After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_python()} function to constrain the Python version used to run the code below (see Sec.~\ref{subsec:toplevel}).
-As described above, the example code in Figure \ref{fig:illustrative-example} uses two different versions of the \texttt{pandas} library: first, an older one needed to access a dataset saved in an outmoded format, then a newer one throughout the remainder of the notebook.
-Line 6 therefore ensures upfront that the notebook's Python version falls within the overlap between the ranges of Python versions that these two versions of \texttt{pandas} support.
+same set of package versions no matter when or by whom the notebook is run.
+
+After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
+As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one for use throughout the remainder of the notebook.
+We therefore want to make sure upfront (in line 6) that the notebook's Python version falls within the range of versions that both of these two versions of \texttt{pandas} support.
+%Line 6 therefore ensures upfront that the notebook's Python version falls within the overlap between the ranges of Python versions that these two versions of \texttt{pandas} support.
 If it does not, the function in line 6 will raise an error that includes a message to this effect (lines 4--5).
@@
 \end{center}
-Next, in lines 8--9 we \texttt{smuggle} two
+
+Next, in lines 8--9, we \texttt{smuggle} two
 utilities for interacting with local files in the code below. The
@@
 function from the Python standard library's \texttt{os.path}
-module. Since standard library modules are included with all Python
-distributions, this line is functionally equivalent to an
+module. Standard library modules are included with all Python
+distributions, so this line is functionally equivalent to an
 \texttt{import} statement and does not need or benefit from an onion
-comment. Line 9 loads the \texttt{joblib} package~\cite{Varo10},
-installing it first, if necessary. Since \texttt{joblib}'s I/O
+comment (since there is no chance it will need to be installed).
+Line 9 then loads the \texttt{joblib} package~\cite{Varo10},
+installing it into the notebook's project directory, if necessary. Since \texttt{joblib}'s I/O
 interface has historically remained stable and backwards-compatible

### 2023-09-26 davos/core/core.py
pop submodule names from top-level module namespace to deal with relative import issue

@@ -1113,6 +1113,22 @@ def smuggle(
                 # run, which crashes it... (-_-* )
                 if mod_name.startswith(f'{dep_name}.'):
                     dep_modules_old[mod_name] = sys.modules.pop(mod_name)
+                    # when reloading package below, importlib.reload
+                    # doesn't seem to automatically follow and
+                    # recursively reload submodules/subpackages loaded
+                    # into the top-level module via relative import
+                    # (e.g., `from . import submodule`) based on their
+                    # *new* locations, if different from their old
+                    # locations. So if a previously smuggled package
+                    # came from the user's main Python environment, and
+                    # the just-smuggled version is now in a project
+                    # directory, the old subpackage/submodule object
+                    # will be re-used in the new top-level module's
+                    # namespace unless we explicitly remove them here
+                    # and force their loaders' paths to be recomputed
+                    submod_name = mod_name[len(dep_name) + 1:]
+                    if submod_name in sys.modules[dep_name].__dict__:
+                        del sys.modules[dep_name].__dict__[submod_name]
 
             # get (but don't pop) top-level package to that it can be
             # reloaded (must exist in sys.modules)

### 2023-09-26 davos/core/core.py
restore subpackage/submodule objects to top-level namespace if reload fails

@@ -1102,6 +1102,7 @@ def smuggle(
         failed_reloads = []
         for dep_name in prev_imported_pkgs:
             dep_modules_old = {}
+            top_level_names_old = []
             for mod_name in tuple(sys.modules.keys()):
                 # remove submodules of previously imported packages so
                 # new versions get imported when main package is
@@ -1128,6 +1129,7 @@ def smuggle(
                     # and force their loaders' paths to be recomputed
                     submod_name = mod_name[len(dep_name) + 1:]
                     if submod_name in sys.modules[dep_name].__dict__:
+                        top_level_names_old.append(submod_name)
                         del sys.modules[dep_name].__dict__[submod_name]
 
             # get (but don't pop) top-level package to that it can be
@@ -1138,7 +1140,9 @@ def smuggle(
             except (ImportError, RuntimeError):
                 # if we aren't able to reload the module, put the old
                 # version's submodules we removed back in sys.modules
-                # for now and prepare to show a warning post-execution.
+                # for now, add their names back to the top-level
+                # module's __dict__, and prepare to show a warning
+                # post-execution.
                 # This way:
                 #   1. the user still has a working module until they
                 #      restart the runtime
@@ -1146,6 +1150,10 @@ def smuggle(
                 #      we try to reload/import other modules that
                 #      import it
                 sys.modules.update(dep_modules_old)
+                for submod_name in top_level_names_old:
+                    sys.modules[dep_name].__dict__[submod_name] = (
+                        dep_modules_old[f'{dep_name}.{submod_name}']
+                    )
                 failed_reloads.append(dep_name)
 
         if any(failed_reloads):

### 2023-09-26 davos/core/core.py
issue warning about partial reload if user chooses to continue running

@@ -30,6 +30,7 @@ import functools
 import importlib
 import itertools
 import sys
+import warnings
 from contextlib import contextmanager, redirect_stdout
 from io import StringIO
 from pathlib import Path
@@ -1182,6 +1183,30 @@ def smuggle(
                 raise SmugglerError(msg)
             else:
                 prompt_restart_rerun_buttons(failed_reloads)
+                # if the function above returns, the user has chosen to
+                # continue running the notebook rather than restarting
+                # to properly reload the package. Issue a warning to let
+                # them know to proceed with caution
+                if len(failed_reloads) == 1:
+                    failed_reloads_str = failed_reloads[0]
+                    verb = 'was'
+                    failed_ver_string = f'{failed_reloads_str}.__version__'
+                else:
+                    verb = 'were'
+                    failed_ver_string = "These packages' '__version__' attributes"
+                    if len(failed_reloads) == 2:
+                        failed_reloads_str = " and ".join(failed_reloads)
+                    else:
+                        failed_reloads_str = (
+                            f"{', '.join(failed_reloads[:-1])}, and "
+                            f"{failed_reloads[-1]}"
+                        )
+
+                msg = (
+                    f"{failed_reloads_str} {verb} partially reloaded. "
+                    f"{failed_ver_string} may be misleading."
+                )
+                warnings.warn(msg, RuntimeWarning, stacklevel=2)
 
         if (
                 config._project is None and

### 2023-09-26 davos/core/core.py
increase stacklevel to show warning for relevent line in the notebook

@@ -1206,7 +1206,7 @@ def smuggle(
                     f"{failed_reloads_str} {verb} partially reloaded. "
                     f"{failed_ver_string} may be misleading."
                 )
-                warnings.warn(msg, RuntimeWarning, stacklevel=2)
+                warnings.warn(msg, RuntimeWarning, stacklevel=3)
 
         if (
                 config._project is None and

### 2023-09-26 paper/main.tex
edits to section 3 up through example snippet 4

@@
 Since the user's existing version of the package satisfies this requirement, Davos will happily load it into the notebook.
-But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently reruns this notebook, the local version will longer satisfy this requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
+But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently re-runs this notebook, the local version will longer satisfy this requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
 From then on, any further changes to the user's \texttt{Numpy} installation would have no effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory.
@@
   is set to \texttt{True}, Davos will automatically restart
-  the notebook kernel and rerun all code up to (and including) the
+  the notebook kernel and re-run all code up to (and including) the
   current \texttt{smuggle} statement. If set to \texttt{False} (the default),
   Davos will instead issue a warning, pause execution, and
-  prompt the user to either restart and rerun the notebook, or
+  prompt the user to either restart and re-run the notebook, or
   continue running with the previously loaded package version until
@@
 After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
-As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one for use throughout the remainder of the notebook.
+As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
 We therefore want to make sure upfront (in line 6) that the notebook's Python version falls within the range of versions that both of these two versions of \texttt{pandas} support.
@@
 \texttt{import} statement and does not need or benefit from an onion
-comment (since there is no chance it will need to be installed).
+comment (since there is no chance the module will need to be installed).
 Line 9 then loads the \texttt{joblib} package~\cite{Varo10},
-installing it into the notebook's project directory, if necessary. Since \texttt{joblib}'s I/O
+installing it into the notebook's project directory if necessary. Since \texttt{joblib}'s I/O
 interface has historically remained stable and backwards-compatible
@@
 \textit{future} release could introduce some breaking change.  The
-onion comment in line 9 helps ensure the analysis notebook continues
+onion comment in line 9 helps ensure that the analysis notebook will continue
 to run properly in the future by limiting allowable versions to those
@@
 \end{center}
-Line 7 then uses the \texttt{davos.config} object to enable
-Davos's \texttt{auto\_rerun} option before smuggling the next
+It is worth noting, however, that beyond illustrative purposes, the benefit of specifying only a maximum version for \texttt{joblib} rather than an exact version is relatively minor.
+The main advantage to relaxing a version constraint in an onion comment (when a package's behavior does not differ meaningfully between versions) is that doing so increases the likelihood that a satisfactory version will already be available in the user's Python environment, and therefore Davos will not need to install a new copy in the notebook's project directory.
+For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no required dependencies.
+Thus a more conservative approach that guarantees an exact version is used would also be reasonable in this case.
+
+Line 11 then enables
+Davos's \texttt{auto\_rerun} option (see Sec.~\ref{subsec:config}) before smuggling the next
 two packages: \texttt{NumPy} and
 \texttt{pandas}. Because these packages rely heavily on custom C data
-types, loading the particular versions from the onion comments may
-require restarting the notebook kernel if different versions had been previously
-imported during the same interpreter session (see
-Sec.~\ref{subsec:config}).
+types, loading the particular versions specified in their onion comments may
+require restarting the notebook kernel if different versions were previously
+imported during the same interpreter session---including internally by other packages.
+Enabling \texttt{auto\_rerun} allows Davos to handle kernel restarts automatically and continue running the code seamlessly without user intervention.
 \begin{center}
@@
 \end{center}
-
-\stoppedhere
-
-Setting the \texttt{auto\_rerun} attribute to \texttt{True} is particularly useful
-for managing the installation of \texttt{pandas} in the next
-lines:
+In the case of \texttt{NumPy}, whether or not a kernel restart is necessary will depend on the user's existing Python environment.
+The \texttt{joblib} package has an optional dependency on \texttt{NumPy} for memoizing and parallelizing array operations, and will \texttt{import numpy} internally to enable these features if the package is available.
+If the user already has \texttt{NumPy} installed in their Python environment when \texttt{joblib} is smuggled in line 9, their installed version is different from the one specified in the onion comment on line 12, and there were changes made to \texttt{NumPy}'s C extensions between those two versions, then Davos will automatically restart the kernel and re-run the lines above.
+The newly smuggled version would then be used both in the notebook itself and by \texttt{joblib} internally.
+% (Note that outside the context of an illustrative example, one could avoid a kernel restart here altogether simply by smuggling \texttt{NumPy} before \texttt{joblib}.)
+
+The primary reason for enabling the \texttt{auto\_rerun} option, however, is to manage the installation of \texttt{pandas} in the next set of lines:
 \begin{center}
@@
 \end{center}
-If we suppose that the data contained in \texttt{data-old.pkl} is
+If we suppose that the ``\texttt{data-old.pkl}'' file contains a dataset
 stored in a pickled \texttt{Panel} object, then we must use a version of
-\texttt{pandas} prior to 0.25.0 (i.e., the version in which the \texttt{Panel}
-class was removed) to be able to load it in. Line 11 ensures
-that an older version of \texttt{pandas} will be imported, enabling
-the data to be read in (and, in line 13, written to a CSV
-file, which is compatible with newer \texttt{pandas} versions).
+\texttt{pandas} prior to v0.25.0 (i.e., the version in which the \texttt{Panel}
+class was removed) to be able to read it. Line 15 ensures
+that a sufficiently old version of \texttt{pandas} will be imported, enabling
+the data to be successfully loaded in line 16 and (in line 17) written to a CSV
+file, which can be read by any \texttt{pandas} version.
 
 Newer versions of \texttt{pandas} have brought substantial improvements
-including better performance, bug fixes, and additional functionality. Although
+including performance enhancements, bug fixes, and additional functionality. Although
 the original dataset had to be read in using an older version of the package,
 we can take advantage of these more recent updates by smuggling \texttt{pandas}
-a second time on line 15 (whose onion comment specifies that version 1.3.5
-should be installed and loaded). Since a different version of \texttt{pandas}
-had already been loaded by the Python interpreter (on line 11), the notebook
-kernel must be restarted in order to replace the old version's custom C
-extensions with those from the new version. The \texttt{auto\_rerun} flag set
-on line 7 enables Davos to trigger this process automatically so that
-the code can continue running without user intervention, and converting the
-dataset to a CSV file in lines 10--13 ensures that the older version of
-\texttt{pandas} does not need to be reinstalled.
+a second time in line 19 (whose onion comment specifies that version 1.3.5
+should be installed and loaded). Since a different \texttt{pandas} version
+has already been loaded by the Python interpreter (line 15) and there have been
+substantial changes to the library (including its extension modules)
+between that version and v1.3.5, the notebook
+kernel must be restarted in order to fully unload the old version in favor of
+the new one. 
+When Davos automatically does so and re-runs the code above, having now converted the dataset to a CSV file means the old version does not need to be reinstalled (line 14).
+
+\stoppedhere
 

### 2023-09-27 paper/main.tex
progress on illustrative example walkthrough up to last snippet

@@
 This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
-It is also possible (though not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
+It is also possible (though typically not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
 
@@
 
-\stoppedhere
-
-Next, line 17 uses the \texttt{davos.configure()} function to disable
+Next, line 21 uses the \texttt{davos.configure()} function to disable
 the \texttt{auto\_rerun} option and simultaneously enable two other
 options: \texttt{suppress\_stdout} and \texttt{noninteractive}. With
-these options enabled, lines 18--19 \texttt{smuggle}
+these options enabled, lines 22--23 \texttt{smuggle}
 \texttt{TensorFlow}~\cite{AbadEtal15}, a powerful end-to-end platform
@@
 \texttt{UMAP}~\cite{McInEtal18}, a package that implements a family
-of related manifold learning techniques. The onion comment in line 19
+of related manifold learning techniques. The onion comment in line 23
 also specifies that \texttt{UMAP} should be installed with the
@@
 features. Together, these two packages depend on 36 other unique
-packages, most of which have dependencies of their own. And if many of
+packages, most of which have dependencies of their own. If many of
 these are not already installed in the user's environment, lines
-18--19 could take several minutes to run.  Enabling the
+22--23 could take several minutes to run.  Enabling the
 \texttt{noninteractive} option ensures that the installation will
@@
 
-After re-enabling these two options (line 20), we next \texttt{smuggle}
+After re-enabling these two options (line 24), we next \texttt{smuggle}
 specific versions of three plotting packages:
 \texttt{Matplotlib}~\cite{Hunt07}, \texttt{seaborn}~\cite{Wask21}, and
-\texttt{Quail}~\cite{HeusEtal17} (lines 22--24). Because the first two
+\texttt{Quail}~\cite{HeusEtal17} (lines 26--28). Because the first two
 are requirements of \texttt{UMAP}'s optional ``plot'' feature, they
-will have already been installed by line 19, though possibly as
+will have already been installed (if necessary) by line 23, though possibly as
 different versions than those specified in the onion comments on lines
-22 and 23. If the installed and specified versions are the same, these
+26 and 28. If the installed and specified versions are the same, these
 \texttt{smuggle} statements will function like standard \texttt{import}
-statements to load the packages into the notebook namespace. If they
+statements to load the packages into the notebook's namespace. If they
 differ, Davos will download the requested versions in place
-of the installed versions before doing so.
+of the installed versions, ensuring that they are used both in the notebook itself and by \texttt{UMAP} internally.
 \begin{center}
@@
 \end{center}
-Line 24 uses an onion comment to specify that \texttt{Quail} should be
-installed directly from a specific GitHub commit (\texttt{6c847a4}).
-This ability to load packages directly from GitHub repositories can
-enable developers to more easily use forked or modified versions of other
-packages in their notebooks, even if those versions have not been
+The onion comment in line 28 specifies that \texttt{Quail} should be
+installed from a fork of its GitHub repository (\texttt{myfork}), in its state as of a specific commit (\texttt{6c847a4}).
+This ability to load packages directly from remote (or local) Git repositories can
+enable developers to more easily use forked or customized versions of other
+packages in their code, even if those versions have not been
 officially released.
-
-In lines 26--29, we demonstrate another aspect of Davos's
-functionality that supports more advanced installation scenarios.  The
-\texttt{ipywidgets}~\cite{FredEtal15} package provides an API for
-creating various JavaScript widgets with Python code, and the \texttt{widgetsnbextension} package provides
-the machinery needed by the notebook frontend to display them.
+Targeting specific VCS references (e.g., commits, tags, etc.) can also provide even finer-grained control over smuggled package versions than is possible with traditional version specifiers.
+
+In lines 30--37, we demonstrate another aspect of Davos's functionality that supports more advanced installation scenarios.
+%The \texttt{ipywidgets}~\cite{FredEtal15} package (also known as Jupyter Widgets) provides a Python API for creating various JavaScript widgets within a notebook, and the \texttt{widgetsnbextension} package provides the JavaScript machinery needed by the the notebook frontend to display them.
+The \texttt{ipywidgets}~\cite{FredEtal15} package (also known as Jupyter Widgets) provides a Python API for creating interactive JavaScript widgets within a notebook. 
+It depends on the \texttt{widgetsnbextension} package, which provides the JavaScript machinery needed by the notebook frontend to display these widgets.
+%A complication is that, while \texttt{ipywidgets} must be installed in a location that is accessible from the IPython kernel (i.e., the Python runtime of the notebook itself), \texttt{widgetsnbextension} must be made accessible to the Jupyter notebook server, which is a separate Python runtime.
+%A complication is that, while \texttt{ipywidgets} must be installed in an environment accessible from the IPython kernel (i.e., importable into the notebook itself), \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server.
+A complication is that \texttt{ipywidgets} must be installed in a location that is accessible from the IPython kernel (i.e., the Python runtime within the notebook itself), while \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server (a separate Python runtime that serves and manages the notebook frontend client).
+In many basic setups, the IPython kernel and notebook server exist in the same environment. 
+However, a common ``advanced'' approach entails running the notebook server from a base environment, with additional environments each providing their own separate, interchangeable IPython kernels.
+
+Lines 30--37 account for both of these possibilities programmatically:
 \begin{center}
@@
 \end{center}
-A complication is that \texttt{ipywidgets} must be installed in the
-same environment as the IPython kernel, whereas
-\texttt{widgetsnbextension} must be installed in the environment that
-houses the Jupyter notebook server. In many basic setups, these two
-environments are the same.  However, a common ``advanced'' approach
-entails running the notebook server from a base environment, with
-additional environments each providing their own separate,
-interchangeable IPython kernels.  To accommodate this multi-environment
-scenario, in lines 26 and 28, we use the \texttt{pip\_executable} option to control which environments each
-package should be installed to.  Once these two packages are installed
-and imported, line 31 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which
-display progress bars to provide status updates for running code. In
+First, in line 30, we set the \texttt{davos.project} attribtue to \texttt{None} to temporarily 
+%disable Davos's project isolation system and
+allow installing smuggled packages outside of the notebook's project directory. 
+As noted in Section \ref{subsec:projects}, this is typically discouraged, as doing so can risk interfering with the user's Python environment if existing package versions are overwritten.
+In this particular case, however, a combination of factors make this relatively safe and inconsequential.
+First, the package we need to install directly into the notebook server environment (\texttt{widgetsnbextension}) is smuggled without an accompanying onion comment (line 34), meaning that Davos will not replace any version the user may already have installed.
+Second, the package has no dependencies of its own, so if Davos does install it, no other packages could potentially be installed or updated as a side effect.
+Third, the package itself provides no functionality outside of rendering Jupyter widgets, so its presence would not alter any other code's expected behavior.
+
+Next, in lines 31--33, we change the \texttt{pip} executable Davos uses to install smuggled packages (see Sec.~\ref{subsec:config}), storing the default executable's path in a variable before doing so.
+When Davos's project system is disabled, using a \texttt{pip} executable from a particular Python environment will cause smuggled packages to be installed into (and subsequently loaded from) that environment.
+The default \texttt{pip\_executable} will install packages into the environment used to run the IPython kernel. 
+Here, the new value assigned to \texttt{davos.pip\_executable} in line 33 is the output of running ``\texttt{command -v pip}'' as a \texttt{!}-prefixed IPython system shell command in line 32 (``\texttt{command -v}'' outputs the path to an executable, similar to ``\texttt{which}'' but more portable).
+Since IPython system shell command are always executed in the notebook server environment, this command's output will be the path to that environment's \texttt{pip} executable---which may or may not be different from the kernel environment's.
+
+After smuggling the \texttt{widgetsnbextension} package in line 34, we use the \texttt{davos.use\_default\_project()} function in line 35 to revert to installing package into the notebook's project directory, restore the default value of \texttt{davos.pip\_executable} in line 36, and \texttt{smuggle} the specified version of \texttt{ipywidgets} in line 37.
+With these two packages now installed
+and imported, line 39 smuggles \texttt{tqdm}~\cite{daCoEtal22}, which
+displays progress bars to provide status updates for running code. In
 Jupyter notebooks, the \texttt{tqdm.notebook} module can be imported
@@
 \texttt{ipywidgets} package was available.
+
+\stoppedhere
 
@@
 
-\todo{mention notebook reproducibility, cell order, multiple package versions re: reviewer's comment; note importance of running lines 14--19 \& 38--40 in single cell; say another option is to alias one version, e.g., \texttt{smuggle pandas as pd\_old}}
+\todo{mention notebook reproducibility, cell order, multiple package versions re: reviewer's comment; note importance of running lines 14--19 \& 38--40 in single cell}
 

### 2023-09-29 paper/main.tex
updated figure 1, inputted JRM written edits

@@
 \centering
-\includegraphics[width=\textwidth]{figs/shareable_code}
+\includegraphics[width=0.65\textwidth]{figs/shareable_code_2d}
 \caption{\small \textbf{Systems for sharing code within the Python
-  ecosystem.}  From left to right: plain-text \textbf{Python
+  ecosystem.}  The $x$-axis denotes the ``burden'' placed on users to
+  install and configure the given system (systems placed further to the right, that fall within the redder shading, impose a higher setup cost on the user).  The $y$-axis denotes the
+  degree to which the system guarantees that the code will run
+  similarly for different users (systems placed higher up, that fall within the bluer shading, support stronger guarantees).
+  From left to right, bottom to top: plain-text \textbf{Python
   scripts} (\texttt{.py} files) provide the most basic ``system''
@@
 consistent location. An additional benefit of this design is that it
-allows both maintainers and users to easily extend Davos to
+allows maintainers and users to extend Davos to
 support new, updated, or custom notebook variants by adding new
@@
 Sec.~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} keyword can be used as a drop-in
+The \texttt{smuggle} keyword-like object can be used as a drop-in
 replacement for Python's built-in \texttt{import} keyword to load
@@
 By default, \texttt{smuggle} statements will install missing packages (and any
-missing dependencies of those packages) into a notebook-specific, virtual
+missing dependencies of those packages) into a notebook-specific virtual
 environment-like directory called a ``project'' (see
@@
 Standard approaches to installing packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled and replaced with alternate versions.
+For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled or replaced with alternate versions.
 This can lead to incompatibilities between installed packages, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
 
-To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using custom virtual environment-like systems called ``projects.''
 Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
 Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and function to \textit{extend} the user's existing Python environment rather than replace it.
+However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and they function to \textit{extend} the user's existing Python environment rather than replace it.
 
 When Davos is imported into a notebook, a project directory for that notebook is automatically created (if it does not exist already).
-When \texttt{smuggle} statements within that notebook are then executed, any packages (or specific versions of packages) that are not already available in the user's Python environment are installed into the notebook's project directory (along with any missing dependencies of those packages).
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the user's main environment.
-
-Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's existing environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
+When \texttt{smuggle} statements within that notebook are executed, any packages (or specific versions of packages) that are not already available in the user's Python environment are installed into the notebook's project directory (along with any missing dependencies of those packages).
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the runtime environment.
+
+Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's runtime environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
 In other cases, the user's environment may already provide all required packages, and the notebook's project directory will go unused (in which case it will be deleted automatically when the notebook kernel is shut down).
-But regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
-
-Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time it is run, this system also ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
+Regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
+
+Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time the notebook is run, this design ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
 For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a Davos-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
-Since the user's existing version of the package satisfies this requirement, Davos will happily load it into the notebook.
+Since the user's existing version of the package satisfies this requirement, Davos will load it into the notebook.
 But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently re-runs this notebook, the local version will longer satisfy this requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
@@
 This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
-It is also possible (though typically not recommended) to disable Davos's project system entirely and install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
-
-When accessed (unless its value has been set to \texttt{None}), \texttt{davos.project} will return a \texttt{Project} object that represents the project used by the current notebook (strings assigned to \texttt{davos.project} are converted to \texttt{Project}s internally).
-This object supports methods for interacting with the current project, including locating its directory on the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents altogether.
+It is also possible (though typically not recommended) to disable Davos's project system and instead install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
+
+When accessed (unless its value has been set to \texttt{None}), \texttt{davos.project} will evaluate to a \texttt{Project} object that represents the project used by the current notebook (strings assigned to \texttt{davos.project} are converted to \texttt{Project}s internally).
+This object supports methods for interacting with the current project, including locating its directory within the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents.
 \texttt{Project} instances can also be created and managed programmatically, and Davos provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
@@
   \texttt{AbstractProject}s represent notebook-specific projects whose associated notebooks no longer exist.
-  They support all the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
+  They support the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
 
@@
   As of this writing, three unique combinations of helper functions are required to support existing notebook environments, ergo this attribute has three possible values: \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, or \texttt{"Colaboratory"}.
-  However, this attribute could take on additional values in the future, as new notebook interfaces are created and IPython's internals are updated, and additional versions of helper functions are added to Davos to support them.
+  However, this attribute could take on additional values in the future as new notebook interfaces are created and IPython's internals are updated, and as additional versions of helper functions are added to Davos to support them.
 
@@
 
-\noindent The current values of all \texttt{davos} attributes may be viewed at once within a notebook by displaying the \texttt{davos.config} object.
+\noindent The current values of all \texttt{davos} attributes may be viewed at once within a notebook by printing the \texttt{davos.config} object.
 
@@
   Note that if Davos's non-interactive mode is enabled (see Sec.~\ref{subsec:config}), \texttt{yes=True} must be explicitly passed, otherwise the function will raise an exception.
-  This serves as a safeguard against accidentally deleting projects since non-interactive mode disables all user input and confirmation.
+  This serves as a safeguard against accidentally deleting projects, since non-interactive mode disables all user input and confirmation.
   Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook filepaths), as they are not linked to specific notebooks whose existence determines whether or not they are still needed.
@@
 %By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional tools or setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
-The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
+The example code throughout Section \ref{subsec:onion} illustrates a typical use case that we envision for Davos: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
 When added to the top of a Jupyter notebook, this allows researchers to bundle their code and its dependencies into a single file that can be easily shared and run without any additional tools or setup, automatically installs its required packages at runtime, isolates them from the user's main Python environment, and ensures their versions do not change unexpectedly over time.
@@
 The main advantage to relaxing a version constraint in an onion comment (when a package's behavior does not differ meaningfully between versions) is that doing so increases the likelihood that a satisfactory version will already be available in the user's Python environment, and therefore Davos will not need to install a new copy in the notebook's project directory.
-For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no required dependencies.
+For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no other dependencies.
 Thus a more conservative approach that guarantees an exact version is used would also be reasonable in this case.
@@
 
-The primary reason for enabling the \texttt{auto\_rerun} option, however, is to manage the installation of \texttt{pandas} in the next set of lines:
+The primary reason for enabling the \texttt{auto\_rerun} option, however, is to manage the installation of \texttt{pandas} in the next lines:
 \begin{center}
@@
 \end{center}
-First, in line 30, we set the \texttt{davos.project} attribtue to \texttt{None} to temporarily 
+First, in line 30, we set the \texttt{davos.project} attribute to \texttt{None} to temporarily 
 %disable Davos's project isolation system and

### 2023-09-29 paper/main.tex
some additional wording updates to section 3

--- 2023-09-27 paper/main.tex
@@
 The default \texttt{pip\_executable} will install packages into the environment used to run the IPython kernel. 
-Here, the new value assigned to \texttt{davos.pip\_executable} in line 33 is the output of running ``\texttt{command -v pip}'' as a \texttt{!}-prefixed IPython system shell command in line 32 (``\texttt{command -v}'' outputs the path to an executable, similar to ``\texttt{which}'' but more portable).
-Since IPython system shell command are always executed in the notebook server environment, this command's output will be the path to that environment's \texttt{pip} executable---which may or may not be different from the kernel environment's.
+Here, the new value assigned to \texttt{davos.pip\_executable} in line 33 is the output of running ``\texttt{command -v pip}'' as a \mbox{\texttt{!}-prefixed} IPython system shell command in line 32 (``\texttt{command -v}'' outputs the path to an executable, similar to ``\texttt{which}'' but more portable).
+IPython system shell command are always executed in the notebook server's environment---which may or may not be different from the kernel's environment---so this command's output will be the path to the server environment's \texttt{pip} executable.
 
@@
 importable. Therefore, to take advantage of this feature, it was
-important to \texttt{smuggle} \texttt{tqdm} after ensuring the
-\texttt{ipywidgets} package was available.
-
-\stoppedhere
+important to first ensure ensure that both \texttt{ipywidgets} and \texttt{widgetsnbextension} were available.
 
@@
 through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
-instance converts text data to an array of word counts.  Second, the
-word counts are passed to a topic model~\cite{BleiEtal03} using a
+instance converts text data to an array of word counts.  The
+word counts are then passed to a topic model~\cite{BleiEtal03} using a
 pretrained \texttt{LatentDirichletAllocation} instance.
@@
 \texttt{LatentDirichletAllocation} class was defined in
-\texttt{sklearn.decomposition.online\_lda}.  However, in version
+the \texttt{sklearn.decomposition.online\_lda} module.  However, in version
 0.22.0, that module was renamed to \texttt{\_online\_lda}, and in

### 2023-09-29 paper/main.tex

--- 2023-09-29 paper/main.tex
@@
 
-\textcolor{red}{\textbf{TODO: add note about default/fallback project for non-traditional notebook interfaces}}
+While Davos enables developers to conveniently specify all project
+dependencies, there are some edge cases and limitations that are worth
+considering. Many Python packages include (in their setup options) additional
+dependencies that often carry their own version specifications. Although Davos
+will check that the correct version of the requested top-level package is
+installed and imported into the workspace, the version numbers of any
+\textit{dependencies} of the requested package are not checked. In principle,
+this could lead to unexpected behavior, for example if a given package's
+dependencies (or dependencies of those dependencies, etc.) were left
+under-specified. A developer could mitigate this by explicitly smuggling exact
+version numbers of every project dependency (e.g., obtained via pip freeze).
+However, for projects where the versions of dependencies of smuggled packages
+also need to be precisely controlled, a lockfile or a \texttt{requirements.txt}
+file produced by \texttt{pip freeze} (i.e., explicitly specifying \textit{all} packages'
+version numbers) may provide a more comprehensive alternative to Davos.
+
+Our Project infrastructure (Sec.~\ref{subsec:projects}) provides a ``safe'' way
+of managing project dependencies without interfering with the user's Python
+environment. However, our implementation of this functionality cannot
+anticipate every possible development environment. As of this writing, we
+support many common notebook environments, including classic Jupyter Notebooks,
+Google Colaboratory, Kaggle Notebooks, Visual Studio Code, among others.
+However, some environments (e.g., Visual Studio Code) implement their own
+mechanisms for rendering and running notebook code. In cases where our Project
+infrastructure is not equipped to handle a particular development or runtime
+environment, Davos will fall back to installing packages in a ``default''
+environment that is shared across all notebooks.  This enables Davos to protect against
+modifying the runtime environment, but it also means that packages may be installed
+or overwritten across notebooks that use different versions of those packages.
 

### 2023-09-29 paper/main.tex

@@
 
-\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, prereleases=None)}: Through \texttt{smuggle} statements and onion comments, Davos can automatically ensure that all Python packages needed to run a notebook are installed, and that the same versions of those packages are used no matter when or by whom the notebook is run.
+\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, pre\-re\-leases=\\None)}: Through \texttt{smuggle} statements and onion comments, Davos can automatically ensure that all Python packages needed to run a notebook are installed, and that the same versions of those packages are used no matter when or by whom the notebook is run.
   However, because Davos operates at runtime, one thing it cannot do automatically is install and switch to a specific version of Python itself.
@@
 
-After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
+After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_\-python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
 As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
@@
 
-After smuggling the \texttt{widgetsnbextension} package in line 34, we use the \texttt{davos.use\_default\_project()} function in line 35 to revert to installing package into the notebook's project directory, restore the default value of \texttt{davos.pip\_executable} in line 36, and \texttt{smuggle} the specified version of \texttt{ipywidgets} in line 37.
+After smuggling the \texttt{widgetsnbextension} package in line 34, we use the \texttt{davos.use\_\-default\_\-project()} function in line 35 to revert to installing package into the notebook's project directory, restore the default value of \texttt{davos.pip\_executable} in line 36, and \texttt{smuggle} the specified version of \texttt{ipywidgets} in line 37.
 With these two packages now installed
@@
 \texttt{LatentDirichletAllocation} class was defined in
-\texttt{sklearn.decomposition.online\_lda}.  However, in version
+\texttt{sklearn.de\-comp\-o\-si\-tion.online\_lda}.  However, in version
 0.22.0, that module was renamed to \texttt{\_online\_lda}, and in

### 2023-09-29 paper/main.tex

@@
 The default \texttt{pip\_executable} will install packages into the environment used to run the IPython kernel.
-Here, the new value assigned to \texttt{davos.pip\_executable} in line 33 is the output of running ``\texttt{command -v pip}'' as a \texttt{!}-prefixed IPython system shell command in line 32 (``\texttt{command -v}'' outputs the path to an executable, similar to ``\texttt{which}'' but more portable).
-Since IPython system shell command are always executed in the notebook server environment, this command's output will be the path to that environment's \texttt{pip} executable---which may or may not be different from the kernel environment's.
+Here, the new value assigned to \texttt{davos.pip\_executable} in line 33 is the output of running ``\texttt{command -v pip}'' as a \mbox{\texttt{!}-prefixed} IPython system shell command in line 32 (``\texttt{command -v}'' outputs the path to an executable, similar to ``\texttt{which}'' but more portable).
+IPython system shell command are always executed in the notebook server's environment---which may or may not be different from the kernel's environment---so this command's output will be the path to the server environment's \texttt{pip} executable.
 
@@
 \texttt{LatentDirichletAllocation} class was defined in
-\texttt{sklearn.de\-comp\-o\-si\-tion.online\_lda}.  However, in version
+the \texttt{sklearn.de\-comp\-o\-si\-tion.online\_lda} module.  However, in version
 0.22.0, that module was renamed to \texttt{\_online\_lda}, and in

### 2023-09-29 paper/main.tex
input changes from ContextLab#102

@@
 Sec.~\ref{subsec:implementation} for details on how this works).
-The \texttt{smuggle} keyword-like object can be used as a drop-in
+The \texttt{smuggle} keyword can be used as a drop-in
 replacement for Python's built-in \texttt{import} keyword to load
@@
 By default, \texttt{smuggle} statements will install missing packages (and any
-missing dependencies of those packages) into a notebook-specific virtual
+missing dependencies of those packages) into a notebook-specific, virtual
 environment-like directory called a ``project'' (see
@@
 Standard approaches to installing packages from within a notebook can alter the local Python environment in potentially unexpected and undesired ways.
-For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be uninstalled or replaced with alternate versions.
+For example, running a notebook that installs its dependencies via system shell commands (prefixed with ``\texttt{!}'') or IPython magic commands (prefixed with ``\texttt{\%}'') may cause other existing packages in the user's environment to be replaced with alternate versions.
 This can lead to incompatibilities between installed packages, affect the behavior of the user's other scripts or notebooks, or even interfere with system applications.
 
-To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using custom virtual environment-like systems called ``projects.''
+To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
 Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
@@
 When \texttt{smuggle} statements within that notebook are executed, any packages (or specific versions of packages) that are not already available in the user's Python environment are installed into the notebook's project directory (along with any missing dependencies of those packages).
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the runtime environment.
+During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the user's main environment.
 
@@
 The main advantage to relaxing a version constraint in an onion comment (when a package's behavior does not differ meaningfully between versions) is that doing so increases the likelihood that a satisfactory version will already be available in the user's Python environment, and therefore Davos will not need to install a new copy in the notebook's project directory.
-For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no other dependencies.
+For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no required dependencies.
 Thus a more conservative approach that guarantees an exact version is used would also be reasonable in this case.
@@
 
-While Davos enables developers to conveniently specify all project
-dependencies, there are some edge cases and limitations that are worth
-considering. Many Python packages include (in their setup options) additional
-dependencies that often carry their own version specifications. Although Davos
-will check that the correct version of the requested top-level package is
-installed and imported into the workspace, the version numbers of any
-\textit{dependencies} of the requested package are not checked. In principle,
-this could lead to unexpected behavior, for example if a given package's
-dependencies (or dependencies of those dependencies, etc.) were left
-under-specified. A developer could mitigate this by explicitly smuggling exact
-version numbers of every project dependency (e.g., obtained via pip freeze).
-However, for projects where the versions of dependencies of smuggled packages
-also need to be precisely controlled, a lockfile or a \texttt{requirements.txt}
-file produced by \texttt{pip freeze} (i.e., explicitly specifying \textit{all} packages'
-version numbers) may provide a more comprehensive alternative to Davos.
-
 Our Project infrastructure (Sec.~\ref{subsec:projects}) provides a ``safe'' way

### 2023-09-30 paper/main.tex
updates to fig 1 caption

@@
   degree to which the system guarantees that the code will run
-  similarly for different users (systems placed higher up, that fall within the bluer shading, support stronger guarantees).
+  similarly for different users (systems placed higher up, that fall within the bluer shading, offer stronger guarantees).
   From left to right, bottom to top: plain-text \textbf{Python
@@
   automatically install any required external packages (at their
-  correct versions, when specified).  \textbf{Virtual environments}
-  allow users to install an isolated copy of Python and all required
-  dependencies. This typically entails distributing a configuration
-  file (e.g., a \texttt{pyproject.toml}~\cite{CannEtal16} or
-  \texttt{environment.yml} file) that specifies all project
-  dependencies (including version numbers of external packages)
-  alongside the primary code base. Users can then install a
-  third-party tool~\cite[e.g.,][]{Anac12, Eust19} to read the file and
-  build the environment.  \textbf{Containers} provide a means of
+  correct versions, when specified) into an isolated directory kept separate
+  from the user's existing set of packages. \textbf{Virtual environments}
+  similarly allow users to install required packages into an isolated
+  directory, and \textbf{shareable Python environments} extend this to include
+  a specific version of Python itself. However, both of these systems require
+  users to create, populate, and manage environments manually. This
+  typically entails distributing a configuration file (e.g., a
+  \texttt{requirements.txt}, \texttt{pyproject.toml}~\cite{CannEtal16}, or
+  \texttt{environment.yml} file) that specifies all project dependencies
+  (including version numbers) alongside the primary code base. Users can then
+  install a third-party tool~\cite[e.g.,][]{BickEtal07, Eust19, Anac12} to read
+  the file and build the environment. \textbf{Containers} provide a means of
   defining an isolated environment that includes a complete operating
@@
   configurations needed to provide the necessary computing
-  environment.  Containers are typically defined using specification
-  files (e.g., a plain-text \texttt{Dockerfile}) that instruct the
+  environment. Containers are typically defined using
+  specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that instruct the
   virtualization engine regarding how to build the containerized
@@
   specified using binary image files) must also define operating
-  system-level properties of the computing environment.  Systems to
-  the left of the blue vertical line entail sharing individual files,
-  with no additional installation or configuration needed to run the
-  target code.  Systems to the right of the red vertical line support
-  precise control over dependencies and versioning.  Notebooks
-  enhanced using the Davos package are easily shareable and
-  require minimal setup costs, while also facilitating high
-  reproducibility by enabling precise control over project
-  dependencies.}
+  system-level properties of the computing environment.  $\Delta_1$
+  represents the increased reproducibility Davos provides over standard
+  Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
+  Davos's lower setup cost compared to standard virtual environments
+  despite more stringently ensuring reproducibility.}
 \label{fig:code-sharing}

### 2023-09-30 paper/main.tex
updates to section 1 text

@@
 complete operating system, in addition to a complete copy of Python
-and any relevant package dependencies. Virtual
-environments~\cite[e.g.,][]{Anac12, Eust19} also provide a computing
+and any relevant package dependencies. Shareable Python
+environments~\cite[e.g.,][]{Anac12} also provide a computing
 environment that is largely separated from the user's main
 environment. They incorporate a copy of Python and the target
-software's dependencies, but virtual environments do not specify or
-reproduce an operating system for the runtime environment. Each of
-these systems (virtual machines, containers, and virtual environments)
+software's dependencies, but do not specify or
+reproduce an operating system for the runtime environment.
+Virtual environments~\cite[e.g.,][]{BickEtal07, Eust19} work similarly, but
+reuse an existing copy of Python rather than bundling their own.
+Each of these systems (virtual machines, containers, Python environments, and virtual environments)
 guarantees (to differing degrees---at the hardware level, operating
-system level, and Python environment level, respectively) that the
+system level, Python environment level, and package environment level, respectively) that the
 relevant code will run similarly for different users. However, each of
@@
 
-We designed Davos to occupy a ``sweet spot'' between these extremes.
+We designed Davos to occupy a ``sweet spot'' within this spectrum.
 Davos is a notebook-installable package that adds functionality to the
@@
 code, and media within a single file. No further setup or installation is
-required from the user, beyond what is needed to run standard Jupyter
-notebooks. And like virtual environments, Davos provides a convenient
+required from the user, beyond what is needed to run a standard Jupyter
+notebook. And like virtual environments, Davos provides a convenient
 mechanism for fully specifying (and installing, as needed) a complete set of

### 2023-09-30 paper/main.tex
minor updates and fixes throughout

@@
   setting up a system for running the desired code, increasing the
-  complexity and time cost of sharing or engaging with reproducible
+  complexity and time cost of both sharing and engaging with reproducible
   science. Here, we propose a lighter-weight solution: the
@@
 C7 & Compilation requirements, operating environments, and
-     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, IDE-based notebook editors, IPython shell.
+     dependencies & Dependencies:~Python $\geq 3.6$, packaging, setuptools.\newline Supported OSes: MacOS, Linux, Unix-like.\newline Supported IPython environments: Jupyter Notebooks, JupyterLab, Google Colaboratory, Binder, Kaggle, IDE-based notebook editors, IPython shell.
 \\
@@
 to the Python compiler, in order to handle special constructs like
-\texttt{!}-prefixed shell commands and \texttt{\%}-prefixed ``magic'' commands. Davos uses
+\mbox{\texttt{!}-prefixed} shell commands and \mbox{\texttt{\%}-pre}\-fixed ``magic'' commands. Davos uses
 this same process to invisibly transform \texttt{smuggle} statements into
@@
 
-Next, we load in the reformatted dataset (line 33) and pre-trained
-model (line 35) that we wish to use in our analysis.  In our
+Next, we load in the reformatted dataset (line 41) and pre-trained
+model (line 43) that we wish to use in our analysis. In our
 hypothetical example, we can suppose that the model was provided as a
 \texttt{scikit-learn} \texttt{Pipeline} object that passes data
-through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
+through two pre-trained models in succession. First, a trained \texttt{CountVectorizer}
 instance converts text data to an array of word counts.  The
 word counts are then passed to a topic model~\cite{BleiEtal03} using a
-pretrained \texttt{LatentDirichletAllocation} instance.
+pre-trained \texttt{LatentDirichletAllocation} instance.
 \begin{center}
@@
 the \texttt{Pipeline} object was created using \texttt{scikit-learn}
-v0.21.3.  In that version of \texttt{scikit-learn}, the
+v0.21.3. In that version (and previous versions) of \texttt{scikit-learn}, the
 \texttt{LatentDirichletAllocation} class was defined in
 the \texttt{sklearn.de\-comp\-o\-si\-tion.online\_lda} module. However, in version
-0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
-version 0.22.1, it was again renamed to \texttt{\_lda}.
-
-In order to correctly load the model that includes the pre-trained
-\texttt{LatentDirichlet\-Allocation} instance, in line 34, we first
+0.22.0, that module was renamed to ``\texttt{\_online\_lda}'' and in
+version 0.22.1, it was again renamed to ``\texttt{\_lda}.''
+
+In order to successfully load the model that includes the pre-trained
+\texttt{Latent\-Dirichlet\-Allocation} instance, in line 42, we first
 \texttt{smuggle} a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
@@
 the model is loaded and reconstructed in memory from a compatible
-package version (line 35), we upgrade to a newer version of
-\texttt{scikit-learn} in line 36.  Taken together, the code in
+package version (line 43), we upgrade to a newer version of
+\texttt{scikit-learn} in line 44. Taken together, the code in
 Figure~\ref{fig:illustrative-example} shows how Davos can
@@
 research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
-used by both students and instructors in programming and methods courses such
+used by both students and instructors in programming and research methods courses such
 as Storytelling with Data~\cite{Mann21a} (an open course on data science,

### 2023-09-30 paper/main.tex
implemented some of @jeremymanning's edits -- thank you!

@@
 
-We designed Davos to occupy a ``sweet spot'' within this spectrum.
+We designed Davos to occupy a ``sweet spot'' within this space.
 Davos is a notebook-installable package that adds functionality to the
@@
   Each item in this list is either a \texttt{Project} or \texttt{AbstractProject} instance.
-  \texttt{AbstractProject}s represent notebook-specific projects whose associated notebooks no longer exist.
+  \texttt{Abstract\-Project}s represent notebook-specific projects whose associated notebooks no longer exist.
   They support the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
@@
 
-After re-enabling these two options (line 24), we next \texttt{smuggle}
+After reverting these two options (line 24) to their default values, we next \texttt{smuggle}
 specific versions of three plotting packages:
@@
 First, the package we need to install directly into the notebook server environment (\texttt{widgetsnbextension}) is smuggled without an accompanying onion comment (line 34), meaning that Davos will not replace any version the user may already have installed.
-Second, the package has no dependencies of its own, so if Davos does install it, no other packages could potentially be installed or updated as a side effect.
+Second, the package has no dependencies of its own, so if Davos does install it, no other packages will be installed or updated as a side effect.
 Third, the package itself provides no functionality outside of rendering Jupyter widgets, so its presence would not alter any other code's expected behavior.

### 2023-09-30 paper/main.tex
rough version of new impact paragraph

@@
 
+We designed Davos for use in research settings, where code for tasks such as processing and analyzing data or generating figures and tables is frequently shared among teams of collaborators during the research process, as well as with the broader scientific community and general public upon a project's completion.
+In such situations, ensuring that shared code yields consistent, reproducible outputs across users and over time can be critically important, while the tools used to achieve this goal can often be complex to set up and challenging to successfully use.
+In many cases, Davos can serve as a drop-in replacement for existing tools that are more challenging to set up and use, such as virtual environments, containers, and virtual machines.
+For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
+By eliminating most of the setup costs of reconstructing the original researchers' computing environment, Davos also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
+
+Among existing tools for sharing code within the Python ecosystem, Davos is most comparable to virtual environments, as it helps ensure reproducibility by
+
 Like virtual environments, containers, and virtual machines, the

### 2023-09-30 paper/main.tex
big update to impact section

--- 2023-09-30 paper/main.tex
@@
 
-Like virtual environments, containers, and virtual machines, the
-Davos package (when used in conjunction with Jupyter
-notebooks) provides a light\-weight mechanism for sharing code and
-ensuring reproducibility across users and computing environments
-(Fig.~\ref{fig:code-sharing}). Further, Davos enables users
-to fully specify (and install, as needed) any project dependencies
-within the same notebook. This provides a system whereby executable
-code (along with text and media) \textit{and} code for setting up and
-configuring the project dependencies, may be combined within a single
-notebook file.
-
-Although existing notebooks \textit{can} incorporate system calls that install
-project requirements, handling project requirements in the general case is
-non-trivial (e.g., see Fig.~\ref{fig:flow-chart}). Further, Davos
-incorporates its own virtual environment system that isolates
-notebook-installed packages from the runtime environment
-(Sec.~\ref{subsec:projects}). In many setups this feature can eliminate the
-need to set up a separate virtual environment or container (e.g., in
-conjunction with a \texttt{requirements.txt}, \texttt{project.toml}, or
-\texttt{environment.yml} file specifying the project's dependencies).
-
-We designed Davos for use in research applications. For
-example, in many settings, Davos may be used as a drop-in
-replacement for more-difficult-to-set-up virtual environments,
-containers, and/or virtual machines. For researchers, this lowers
-barriers to sharing code. By eliminating most of the setup costs of
-reconstructing the original researchers' computing environment,
-Davos also lowers barriers to entry for members of the
-scientific community and the public who seek to run shared code.
+We designed Davos for use in research settings, where code for numerous different tasks---from processing data, to running statistical analyses, to generating figures and tables for publication---is frequently shared among collaborators while working on a project, and eventually with the broader scientific community and general public upon a its completion.
+In these contexts, ensuring that shared code yields consistent, reproducible outputs across users and over time is crucially important, yet the tools available to researchers for doing so can be complex to set up and challenging to properly use.
+This has the dual effect of discouraging scientists from sharing their code in a reproducible way (or at all), and making it significantly harder (or impossible) for others to successfully reproduce their results, adopt or extend their methods, and contribute to or build upon their work.
+Ultimately, the need to install and master additional tools in order to share and run reproducible code can impede progress both on the individual level and on the broader scientific level.
+
+While the Davos package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (see Fig.~\ref{fig:code-sharing}).
+For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
+And by eliminating most of the setup costs of reconstructing the original researchers' computing environment, Davos also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
+
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), Davos is most comparable to virtual environments as it similarly provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+However, when used in conjunction with Jupyter notebooks, Davos offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
+
+First, \texttt{smuggle} statements and onion comments enable researchers to specify their notebooks' dependencies directly within the code that requires them (see Secs.~\ref{subsec:smuggle} and  \ref{subsec:onion}).
+This eliminates the need to either manually create and maintain separate configuration files or use an additional tool to generate them, and to then distribute these files alongside their primary code base for users to download.
+
+Second, Davos automatically checks for, installs, isolates, and imports any required packages at runtime.
+This allows users to download and immediately run a Davos-enhanced notebook without any prerequisite setup (beyond that needed to run a standard Jupyter notebook).
+By contrast, before running a notebook whose dependencies are managed via a virtual environment, the user would first need to run a series of shell commands to manually create a new environment, populate it with packages from the researcher's configuration file (which the user must also have obtained), and then either use the \texttt{ipykernel} package to register the environment as a Jupyter kernel, or activate and deactivate the environment before and after (respectively) each time the notebook was launched.
+Beyond reducing this initial setup cost, Davos's runtime-based approach to dependency management affords a second important benefit.
+While creating and configuring a virtual environment ensures that a specific set of packages is initially installed, it does not guarantee that they will \textit{remain} installed after that point.
+For example, a researcher who creates a virtual environment in which to run a set of data analyses---or a different user who later recreates that environment to reproduce them---might at some point install an additional package into the environment after its initial setup (e.g., to implement a new analysis idea).
+Depending on the requirements of this new package, this could cause one or more initially installed packages to be upgraded or downgraded to a different version.
+If the individual does not happen to notice this change when it occurs, differences between those packages' expected and installed versions may introduce bugs into previously written code or subtly alter its output when it is next run.
+Because \texttt{smuggle} statements and onion comments are evaluated every time a Davos-enhanced notebook is run, they function to ensure that the notebook's dependencies are always satisfied and that any such inadvertent changes would be automatically caught and corrected.
+
+Third, running a shared notebook that uses Davos to manage its dependencies often requires less (but never more) space on the user's system than running an identical notebook inside a virtual environment.
+While typical virtual environment directories will contain \textit{all} requirements listed in their configuration files, Davos's isolated project directories (by default; see Sec.~\ref{subsec:projects}) contain only those not already available in the user's existing Python environment.
+This is another feature made possible by Davos's runtime-based dependency management scheme.
+Davos can safely draw from packages in from the user's main environment to satisfy a notebook's dependencies, when possible, because if those packages were to be updated or removed at any point such that they no longer met the notebook's requirements, appropriate versions could (and would) be installed into the project directory the next time the notebook was executed.
+
+Finally, neither virtual environments nor Davos-enhanced notebooks can bundle specific versions of Python with which to run shared code.
+However, Davos's \texttt{require\_\-python()} function provides a simple mechanism for indicating a required or constrained Python version and alerting the user at runtime (by raising an exception) if their Python version is incompatible.
+In terms of Davos's ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (see Fig.~\ref{fig:code-sharing}) and should be preferred over Davos in cases where this is necessary.
+However, the functionality it provides over what is possible with a standard virtual environment is removing the \textit{expectation} that running a particular notebook will reproduce an expected outcome in situations where this is either impossible or not guaranteed.
+With this understanding, a user may choose to install a compatible Python version through some other means or elect to still run the code, but will not be surprised by a potential failure to execute successfully or output an expected result.
 

### 2023-09-30 paper/main.tex
updates to pitfalls and limitations section

@@
 Davos provides a convenient way to manage dependencies within
-a notebook, without requiring any software (beyond a web browser) to
+a notebook without requiring any software (beyond a web browser) to
 be installed on the students' or instructors' systems. For the same
@@
 dependencies, there are some edge cases and limitations that are worth
-considering. First, reproducibility is not solely about dependency management.
-In addition to ensuring that project dependencies are satisfied, the user
-running a given notebook must also execute the code in the indicated order. For
-example, the cells in a notebook may be manually run out of order. If different
-cells in a Davos-enhanced notebook made use of different versions of the same
-package, this could result in \textit{more} confusion or \textit{greater}
-replication failure rates relative to standard Jupyter notebooks. Therefore an
-important consideration when using Davos is that it is perhaps even more
-important to execute notebook cells in order than would be the case in the
-standard (non-Davos) setup. One approach to mitigating this risk for notebooks
-that use several versions of the same library would be to include
-\texttt{smuggle} statements in the same cell(s) where the library was called. A
-second approach would be for developers who wish to use Davos to include notes
-regarding which cells must be executed in sequence. This is already a common
-practice for notebooks that include system calls to install required packages
-and dependencies, and the same approach would work well for Davos-enhanced
-notebooks as well.
+considering.
+First, prior studies on reproducibility of Jupyter notebooks (e.g., \cite{PimeEtal19}) identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, which may differ from the order in which they were executed by the notebook's original author.
+This can result in various ``hidden state'' problems, such as variables referencing different objects than the currently running cell expects them to, given its point in the notebook's execution order.
+In theory, using Davos to \texttt{smuggle} different versions of the same package across different notebook cells could exacerbate this issue if a user executed those cells out of their intended order.
+Therefore an important consideration when using Davos is that it is perhaps even more important to execute notebook cells in order than would be the case in the standard (non-Davos) setup.
+However, a few ``best practices'' may be adopted to help mitigate this risk.
+First, when sharing a Davos-enhanced notebook in a state that is intended to be reproducible, code cells should appear in their intended execution order, such that users can successfully run them top to bottom.
+In a scenario where this is impossible, the intended order should be clearly indicated in code comments and/or markdown cells.
+This is already a common practice for notebooks that include system calls to install required packages and dependencies, and the same approach would work well in Davos-enhanced notebooks.
+Second, while Davos makes it possible to \texttt{smuggle} multiple versions of a package within the same notebook, users should prefer to split code that requires different versions of the same package into different notebooks.
+In addition to mitigating the issue described above, this will also allow Davos to store a single intended version of the package in each notebook's project directory, rather than reinstalling the package each time a different version is smuggled.
+Finally, in situations where it \textit{is} necessary or preferable to temporarily \texttt{smuggle} a different version of a particular package than is used throughout the rest of the notebook (e.g., Fig.~\ref{fig:illustrative-example}), the code to \texttt{smuggle} that temporary version, perform all necessary operations, and (re-)\texttt{smuggle} the ``default'' version should be contained within a single notebook cell, such that (absent any errors in its execution) the same version is always installed and imported before and after the cell is run.
+For example, in Figure~\ref{fig:illustrative-example}, lines 14--19 should be run within a single cell, and lines 42--44 should be run in a single cell.
 
@@
 unsupported by Davos. We anticipate adding support for other package management
-systems, including \texttt{conda}, in a future release.
+systems, including \texttt{conda} \cite{Anac12}, in a future release.
 
@@
 
-Our Project infrastructure (Sec.~\ref{subsec:projects}) provides a ``safe'' way
+Davos's ``projects'' system (Sec.~\ref{subsec:projects}) provides a safe way
 of managing project dependencies without interfering with the user's Python
-environment. However, our implementation of this functionality cannot
-anticipate every possible development environment. As of this writing, we
-support many common notebook environments, including classic Jupyter Notebooks,
-Google Colaboratory, Kaggle Notebooks, Visual Studio Code, among others.
-However, some environments (e.g., Visual Studio Code) implement their own
-mechanisms for rendering and running notebook code. In cases where our Project
-infrastructure is not equipped to handle a particular development or runtime
-environment, Davos will fall back to installing packages in a ``default''
-environment that is shared across all notebooks.  This enables Davos to protect against
-modifying the runtime environment, but it also means that packages may be installed
-or overwritten across notebooks that use different versions of those packages.
+environment. By default, each Davos-enhanced notebook creates and uses its own
+notebook-specific project directory, which is named based on the notebook's absolute
+path. However, programmatically determining the path to the currently running
+notebook may not be possible in some environments.
+For example, Davos queries the Jupyter Server API to determine the notebook's name, but some non-browser applications may implement mechanisms for communicating with the IPython kernel without starting a Jupyter server.
+As of this writing, Davos fully supports most common notebook environments, including classic Jupyter Notebooks,
+JupyterLab, Google Colaboratory, Binder, Kaggle Notebooks, JetBrains IDEs (PyCharm, DataSpell, etc.), and Visual Studio Code, among others.
+However, in cases where Davos fails to determine the current notebook's path, it will issue a warning and fall back to using a generic project named ``davos-fallback.'' This project is shared across all such occurrences and exists to ensure that even if some component of Davos's project system fails, smuggling packages will still not affect the user's main Python environment.
+If this occurs, the user can also manually set Davos to use the ``normal'' default project for the current by setting \texttt{davos.project} to its absolute or relative path.
 

### 2023-09-30 paper/main.tex
updates to conclusion
removed stray comments, added an mbox

@@
 to the Python compiler, in order to handle special constructs like
-\mbox{\texttt{!}-prefixed} shell commands and \mbox{\texttt{\%}-pre}\-fixed ``magic'' commands. Davos uses
+\mbox{\texttt{!}-pre}\-fixed shell commands and \mbox{\texttt{\%}-pre}\-fixed ``magic'' commands. Davos uses
 this same process to invisibly transform \texttt{smuggle} statements into
@@
 
-%The example code throughout Section \ref{subsec:onion} illustrates how Davos is most typically used:
-%By including a series of \texttt{smuggle} statements and onion comments with version specifiers or other options in an IPython notebook, researchers can share their code and its dependencies in a single file that can be easily run without any additional tools or setup, creates and manages its own isolated environment, automatically installs its required packages at runtime, and ensures that the package versions with which it is run do not change unexpectedly.
 The example code throughout Section \ref{subsec:onion} illustrates a typical use case that we envision for Davos: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
@@
 temporarily switching between different versions of the same package within a single runtime.
-%carefully controlling which versions of each package are used in different parts of the notebook.
 The example shows how a dataset and model that require
@@
 We therefore want to make sure upfront (in line 6) that the notebook's Python version falls within the range of versions that both of these two versions of \texttt{pandas} support.
-%Line 6 therefore ensures upfront that the notebook's Python version falls within the overlap between the ranges of Python versions that these two versions of \texttt{pandas} support.
 If it does not, the function in line 6 will raise an error that includes a message to this effect (lines 4--5).
@@
 The newly smuggled version would then be used both in the notebook itself and by \texttt{joblib} internally.
-% (Note that outside the context of an illustrative example, one could avoid a kernel restart here altogether simply by smuggling \texttt{NumPy} before \texttt{joblib}.)
 
@@
 In lines 30--37, we demonstrate another aspect of Davos's functionality that supports more advanced installation scenarios.
-%The \texttt{ipywidgets}~\cite{FredEtal15} package (also known as Jupyter Widgets) provides a Python API for creating various JavaScript widgets within a notebook, and the \texttt{widgetsnbextension} package provides the JavaScript machinery needed by the the notebook frontend to display them.
 The \texttt{ipywidgets}~\cite{FredEtal15} package (also known as Jupyter Widgets) provides a Python API for creating interactive JavaScript widgets within a notebook.
 It depends on the \texttt{widgetsnbextension} package, which provides the JavaScript machinery needed by the notebook frontend to display these widgets.
-%A complication is that, while \texttt{ipywidgets} must be installed in a location that is accessible from the IPython kernel (i.e., the Python runtime of the notebook itself), \texttt{widgetsnbextension} must be made accessible to the Jupyter notebook server, which is a separate Python runtime.
-%A complication is that, while \texttt{ipywidgets} must be installed in an environment accessible from the IPython kernel (i.e., importable into the notebook itself), \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server.
 A complication is that \texttt{ipywidgets} must be installed in a location that is accessible from the IPython kernel (i.e., the Python runtime within the notebook itself), while \texttt{widgetsnbextension} must be installed in the environment that houses the Jupyter notebook server (a separate Python runtime that serves and manages the notebook frontend client).
@@
 First, in line 30, we set the \texttt{davos.project} attribute to \texttt{None} to temporarily
-%disable Davos's project isolation system and
 allow installing smuggled packages outside of the notebook's project directory.
@@
 latest approaches and implementations.
-
-\todo{mention notebook reproducibility, cell order, multiple package versions re: reviewer's comment; note importance of running lines 14--19 \& 38--40 in single cell}
 
@@
 The Davos package supports reproducible research by providing
-a novel, lightweight system for sharing notebook-based code. But
-perhaps the most exciting uses of the Davos package are those
+a novel, lightweight system for sharing notebook-based code. It
+expands on Python's ``batteries included'' philosophy to enable running shared
+notebooks with no setup required, and defines a simple, self-documenting format for
+specifying dependencies in the spirit of ``literate programming'' paradigm Jupyter notebooks promote.
+But perhaps the most exciting uses of the Davos package are those
 that we have \textit{not} yet considered or imagined. We hope that the

### 2023-09-30 paper/main.tex
teletype Davos throughout (except Fig 1 caption bold text)

@@
 
-\title{Davos: a Python package ``smuggler'' for constructing
+\title{\texttt{Davos}: a Python package ``smuggler'' for constructing
   lightweight reproducible notebooks}
@@
   science. Here, we propose a lighter-weight solution: the
-  Davos package.  When used in combination with a
-  notebook-based Python project, Davos provides a mechanism
+  \texttt{Davos} package.  When used in combination with a
+  notebook-based Python project, \texttt{Davos} provides a mechanism
   for specifying the correct versions of the project's
@@
   and automatically installing them in an isolated environment
-  when the code is run. The Davos package further
+  when the code is run. The \texttt{Davos} package further
   ensures that these packages and specific versions are used every
@@
   system-level properties of the computing environment.  $\Delta_1$
-  represents the increased reproducibility Davos provides over standard
+  represents the increased reproducibility \texttt{Davos} provides over standard
   Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
-  Davos's lower setup cost compared to standard virtual environments
+  \texttt{Davos}'s lower setup cost compared to standard virtual environments
   despite more stringently ensuring reproducibility.}
@@
 
-We designed Davos to occupy a ``sweet spot'' within this space.
-Davos is a notebook-installable package that adds functionality to the
+We designed \texttt{Davos} to occupy a ``sweet spot'' within this space.
+\texttt{Davos} is a notebook-installable package that adds functionality to the
 default notebook experience. Like standard Jupyter notebooks,
-Davos-enhanced notebooks allow researchers to include text, executable
+\texttt{Davos}-enhanced notebooks allow researchers to include text, executable
 code, and media within a single file. No further setup or installation is
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like virtual environments, Davos provides a convenient
+notebook. And like virtual environments, \texttt{Davos} provides a convenient
 mechanism for fully specifying (and installing, as needed) a complete set of
@@
 
-The Davos package is named after Davos Seaworth, a smuggler referred
+The \texttt{Davos} package is named after Davos Seaworth, a smuggler referred
 to as ``the Onion Knight'' from the series \textit{A Song of Ice and Fire} by
 George R. R. Martin~\cite{Mart98}. The \texttt{smuggle} keyword provided by
-Davos is a play on Python's \texttt{import} keyword: whereas importing
+\texttt{Davos} is a play on Python's \texttt{import} keyword: whereas importing
 can load a package into the Python workspace within the existing rules and
@@
 character Davos Seaworth (who became famous for smuggling onions through a
-blockade on his homeland), the Davos package uses ``onion comments'' to precisely control how
+blockade on his homeland), the \texttt{Davos} package uses ``onion comments'' to precisely control how
 packages are smuggled into the Python workspace.
@@
 \includegraphics[width=\textwidth]{figs/package_structure}
-\caption{\small \textbf{Package structure.} The Davos package
+\caption{\small \textbf{Package structure.} The \texttt{Davos} package
   comprises two interdependent subpackages.  The \texttt{davos.core}
@@
   and onion comments, installing and validating packages, isolating and managing
-  installed packages, and configuring Davos's behavior.  The
+  installed packages, and configuring \texttt{Davos}'s behavior.  The
   \texttt{davos.implementations} subpackage includes
@@
 
-The Davos package consists of two interdependent subpackages
+The \texttt{Davos} package consists of two interdependent subpackages
 (see Fig.~\ref{fig:package-structure}). The first,
@@
 different projects (see Sec.~\ref{subsec:projects}), and a runtime
-interface for configuring Davos's behavior (see Sec.~\ref{subsec:config}).
+interface for configuring \texttt{Davos}'s behavior (see Sec.~\ref{subsec:config}).
 However, certain critical aspects of this
@@
 depending on properties of the notebook environment in which
-Davos is used (e.g., whether the frontend is provided by
+\texttt{Davos} is used (e.g., whether the frontend is provided by
 Jupyter or Google Colaboratory, or which version of
@@
 organized into modules by the conditions that trigger their use. At
-runtime, Davos detects various features in the notebook
+runtime, \texttt{Davos} detects various features in the notebook
 environment and selectively imports a single version of each helper
@@
 consistent location. An additional benefit of this design is that it
-allows maintainers and users to extend Davos to
+allows maintainers and users to extend \texttt{Davos} to
 support new, updated, or custom notebook variants by adding new
@@
 
-Functionally, importing Davos in an IPython notebook enables
+Functionally, importing \texttt{Davos} in an IPython notebook enables
 an additional Python keyword: ``\texttt{smuggle}'' (see
@@
 packages on the fly.  If a smuggled package does not exist in the
-user's Python environment, Davos will download and install it automatically,
+user's Python environment, \texttt{Davos} will download and install it automatically,
 expose its contents to Python's \texttt{import} machinery, and load it
@@
 
-Importantly, packages installed by Davos are made available for use in the
+Importantly, packages installed by \texttt{Davos} are made available for use in the
 notebook without affecting the user's Python environment or existing packages.
@@
 at runtime each time the notebook is run, without risking interfering with
-dependencies of the user's other Python programs, or other Davos-enhanced
+dependencies of the user's other Python programs, or other \texttt{Davos}-enhanced
 notebooks.
@@
 
-For greater control over the behavior of \texttt{smuggle} statements, Davos
+For greater control over the behavior of \texttt{smuggle} statements, \texttt{Davos}
 defines an additional construct called the ``onion comment.'' An onion comment
 is a special type of inline comment that may be placed on a line containing a
-\texttt{smuggle} statement to customize how Davos searches for the smuggled
+\texttt{smuggle} statement to customize how \texttt{Davos} searches for the smuggled
 package locally and, if necessary, downloads and installs it. Onion comments
 follow a simple format based on the ``type comment'' syntax introduced in PEP
-484~\cite{vanREtal14}, and are designed to make managing packages with Davos
+484~\cite{vanREtal14}, and are designed to make managing packages with \texttt{Davos}
 intuitive and familiar. To construct an onion comment, users provide the name
@@
 used when importing it). In such cases, an onion comment can be used to ensure
-that Davos installs the proper package if it cannot be found locally:
+that \texttt{Davos} installs the proper package if it cannot be found locally:
 \begin{center}
@@
 how, where, and when smuggled packages are installed. Critically, if an onion
-comment includes a version specifier~\cite{CoghStuf13}, Davos will ensure that
+comment includes a version specifier~\cite{CoghStuf13}, \texttt{Davos} will ensure that
 the version of the package loaded into the notebook matches the specific
 version requested (or satisfies the given version constraints). If the smuggled
-package exists locally, Davos will extract its version information from its
+package exists locally, \texttt{Davos} will extract its version information from its
 metadata and compare it to the specifier provided. If the two are incompatible
-(or no local installation is found), Davos will download, install, and load a
+(or no local installation is found), \texttt{Davos} will download, install, and load a
 suitable version of the package instead:
@@
 \end{center}
-Davos processes onion comments internally before forwarding arguments to the
+\texttt{Davos} processes onion comments internally before forwarding arguments to the
 installer program. In addition to preventing shared notebooks from executing
-arbitrary code in a user's shell, this enables Davos to adjust its behavior
+arbitrary code in a user's shell, this enables \texttt{Davos} to adjust its behavior
 based on how particular flags will affect the behavior of the installer
 program. For example, including \texttt{pip}'s \texttt{--no-input} flag will also
-temporarily enable Davos's non-interactive mode (see Sec.~\ref{subsec:config}).
+temporarily enable \texttt{Davos}'s non-interactive mode (see Sec.~\ref{subsec:config}).
 Similarly, if an onion comment contains either \texttt{-I}/\texttt{--ignore-installed},
-\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall}, Davos will
+\texttt{-U}/\texttt{--upgrade}, or \texttt{--force-reinstall}, \texttt{Davos} will
 install and load a new copy of the smuggled package without first checking
@@
 (such as \texttt{-h}/\texttt{--help} or \texttt{--dry-run}) are disallowed. Additionally,
-when using a Davos ``project'' to isolate smuggled packages (the default behavior;
+when using a \texttt{Davos} ``project'' to isolate smuggled packages (the default behavior;
 see Sec.~\ref{subsec:projects}), onion comments may not contain options that
@@
 the user disables project-based isolation and specifies \texttt{--target <dir>},
-Davos will ensure that \texttt{<dir>} is included in the module search path (i.e.,
+\texttt{Davos} will ensure that \texttt{<dir>} is included in the module search path (i.e.,
 \texttt{sys.path}), prepending it if necessary, so the package can be loaded.
@@
 
-To prevent Davos-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
-Davos projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
-Like a standard virtual environment, a Davos project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
-However, unlike standard virtual environments, Davos projects do not need to be manually created, activated, or deactivated, and they function to \textit{extend} the user's existing Python environment rather than replace it.
-
-When Davos is imported into a notebook, a project directory for that notebook is automatically created (if it does not exist already).
+To prevent \texttt{Davos}-enhanced notebooks from having unwanted side effects on the user's environment, any packages installed via \texttt{smuggle} statements are automatically isolated using a custom, virtual environment-like system called ``projects.''
+\texttt{Davos} projects are similar to standard Python virtual environments (e.g., created with the standard library's \texttt{venv} module or a third-party tool like \texttt{virtualenv}~\cite{BickEtal07}) but with a few noteworthy differences that make them generally lighter-weight and simpler to use.
+Like a standard virtual environment, a \texttt{Davos} project consists of a directory (within a hidden \texttt{.davos} folder in the user's home directory) that houses third-party packages needed for a particular Python project, workflow, or task.
+However, unlike standard virtual environments, \texttt{Davos} projects do not need to be manually created, activated, or deactivated, and they function to \textit{extend} the user's existing Python environment rather than replace it.
+
+When \texttt{Davos} is imported into a notebook, a project directory for that notebook is automatically created (if it does not exist already).
 When \texttt{smuggle} statements within that notebook are executed, any packages (or specific versions of packages) that are not already available in the user's Python environment are installed into the notebook's project directory (along with any missing dependencies of those packages).
-During each \texttt{smuggle} statement's execution, Davos also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the user's main environment.
-
-Thus, rather than constructing fully separate Python environments from scratch, Davos projects work by supplementing the user's runtime environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
+During each \texttt{smuggle} statement's execution, \texttt{Davos} also temporarily prepends the notebook's project directory to the module search path so that these project-installed packages are visible when searching for smuggled packages locally, and prioritized over those in the user's main environment.
+
+Thus, rather than constructing fully separate Python environments from scratch, \texttt{Davos} projects work by supplementing the user's runtime environment with any additional packages (or specific package versions) needed to satisfy the dependencies of their corresponding notebooks.
 In some cases, this might include every package smuggled into a notebook (e.g., if the notebook is run inside a freshly created, empty virtual environment).
 In other cases, the user's environment may already provide all required packages, and the notebook's project directory will go unused (in which case it will be deleted automatically when the notebook kernel is shut down).
-Regardless of the extent to which the existing environment is augmented, Davos's project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
+Regardless of the extent to which the existing environment is augmented, \texttt{Davos}'s project system ensures that all smuggled packages are installed locally and loaded successfully at runtime, while the contents of the user's Python environment are never altered.
 
 Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time the notebook is run, this design ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
-For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a Davos-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
-Since the user's existing version of the package satisfies this requirement, Davos will load it into the notebook.
-But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently re-runs this notebook, the local version will longer satisfy this requirement, so Davos will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
-From then on, any further changes to the user's \texttt{Numpy} installation would have no effect on Davos's behavior in this particular notebook, as a satisfactory version now exists in its project directory.
-(If the version specified in the onion comment were changed, Davos would update the version installed in the project directory accordingly.)
-For efficiency, Davos projects will generally not duplicate dependencies already satisfied by the user's Python environment.
-However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause Davos to install the smuggled package into the project directory whether or not it already exists locally.
-
-By default, each Davos-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file.
+For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a \texttt{Davos}-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
+Since the user's existing version of the package satisfies this requirement, \texttt{Davos} will load it into the notebook.
+But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently re-runs this notebook, the local version will longer satisfy this requirement, so \texttt{Davos} will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
+From then on, any further changes to the user's \texttt{Numpy} installation would have no effect on \texttt{Davos}'s behavior in this particular notebook, as a satisfactory version now exists in its project directory.
+(If the version specified in the onion comment were changed, \texttt{Davos} would update the version installed in the project directory accordingly.)
+For efficiency, \texttt{Davos} projects will generally not duplicate dependencies already satisfied by the user's Python environment.
+However, if desired, adding \texttt{pip}'s \texttt{--ignore-installed} flag to an onion comment in the notebook will cause \texttt{Davos} to install the smuggled package into the project directory whether or not it already exists locally.
+
+By default, each \texttt{Davos}-enhanced notebook will create and use its own notebook-specific project named for the absolute path to the notebook file.
 However, before smuggling its required packages, a notebook may be set to instead use an arbitrarily named, notebook-agnostic project by assigning any (non-empty) string to \texttt{davos.project} (see Sec.~\ref{subsec:config}).
-This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same Davos project, by setting \texttt{davos.project} to the same string in each one.
-It is also possible (though typically not recommended) to disable Davos's project system and instead install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
+This provides a convenient way for multiple related notebooks that share a common set of requirements to use the same \texttt{Davos} project, by setting \texttt{davos.project} to the same string in each one.
+It is also possible (though typically not recommended) to disable \texttt{Davos}'s project system and instead install smuggled packages directly into the user's Python environment by setting \texttt{davos.project} to \texttt{None}.
 
@@
 This object supports methods for interacting with the current project, including locating its directory within the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents.
-\texttt{Project} instances can also be created and managed programmatically, and Davos provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
-
-\subsubsection{Configuring and querying Davos}\label{subsec:config}
-
-After importing Davos into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of Davos's behavior.
-The majority of these are writeable options that can be modified to customize how, where, and when Davos installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example).
+\texttt{Project} instances can also be created and managed programmatically, and \texttt{Davos} provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
+
+\subsubsection{Configuring and querying \texttt{Davos}}\label{subsec:config}
+
+After importing \texttt{Davos} into a notebook, the top-level \texttt{davos} module exposes a set of attributes whose values determine various aspects of \texttt{Davos}'s behavior.
+The majority of these are writeable options that can be modified to customize how, where, and when \texttt{Davos} installs smuggled packages (see Sec.~\ref{sec:illustrative-example} for an illustrative example).
 These include:
@@
   statements and onion comments is enabled (\texttt{True}) or
-  disabled (\texttt{False}).  When Davos is first imported,
+  disabled (\texttt{False}).  When \texttt{Davos} is first imported,
   \texttt{davos.active} is set to \texttt{True} (see Sec.~\ref{subsec:implementation} for implementation details and additional information).
@@
 \item \texttt{.auto\_rerun}: This attribute controls how
-  Davos behaves when attempting to \texttt{smuggle} a new
+  \texttt{Davos} behaves when attempting to \texttt{smuggle} a new
   version of a package that was previously loaded (via an \texttt{import} or \texttt{smuggle} statement) and cannot be
@@
   previously loaded and to-be-smuggled versions.  If this attribute
-  is set to \texttt{True}, Davos will automatically restart
+  is set to \texttt{True}, \texttt{Davos} will automatically restart
   the notebook kernel and re-run all code up to (and including) the
   current \texttt{smuggle} statement. If set to \texttt{False} (the default),
-  Davos will instead issue a warning, pause execution, and
+  \texttt{Davos} will instead issue a warning, pause execution, and
   prompt the user to either restart and re-run the notebook, or
@@
 \item \texttt{.confirm\_install}: If set to \texttt{True} (default:
-  \texttt{False}), Davos will require user confirmation
+  \texttt{False}), \texttt{Davos} will require user confirmation
   before installing a smuggled package that is not already
   available locally. This is primarily useful if the user has disabled
-  Davos's ``project'' system for isolating smuggled packages (see
+  \texttt{Davos}'s ``project'' system for isolating smuggled packages (see
   Sec.~\ref{subsec:projects}) but still wants to carefully control what
@@
   \texttt{auto\_rerun} is set to \texttt{False} while in non-interactive
-  mode, Davos will raise an exception if a smuggled package
+  mode, \texttt{Davos} will raise an exception if a smuggled package
   cannot be reloaded, rather than prompting the user.
@@
 
-\item \texttt{.project}: This attribute's value is a \texttt{Project} instance representing the Davos project associated with the current notebook.
-  As described in Section~\ref{subsec:projects}, Davos projects serve to isolate packages installed by \texttt{smuggle} statements from the user's main Python environment, and the \texttt{Project} class provides an interface for inspecting and managing projects at runtime.
+\item \texttt{.project}: This attribute's value is a \texttt{Project} instance representing the \texttt{Davos} project associated with the current notebook.
+  As described in Section~\ref{subsec:projects}, \texttt{Davos} projects serve to isolate packages installed by \texttt{smuggle} statements from the user's main Python environment, and the \texttt{Project} class provides an interface for inspecting and managing projects at runtime.
   This attribute's default value is a notebook-specific project named for the absolute path to the notebook file.
   To change the project used in the current notebook (e.g., in order to use the same project in multiple related notebooks), this attribute may be assigned a different \texttt{Project} instance or, for simplicity, the name of the desired project as a string or \texttt{pathlib.Path} (either of which will be converted to a \texttt{Project} on assignment).
-  Alternatively, setting \texttt{davos.project} to \texttt{None} will disable project-based isolation for the current notebook and cause Davos to install any missing packages directly into the main Python environment.
+  Alternatively, setting \texttt{davos.project} to \texttt{None} will disable project-based isolation for the current notebook and cause \texttt{Davos} to install any missing packages directly into the main Python environment.
   This attribute can be reset to its default value using the top-level \texttt{use\_default\_project()} function (see Sec.~\ref{subsec:toplevel}).
-  For more information about Davos projects, see Section \ref{subsec:projects}.
+  For more information about \texttt{Davos} projects, see Section \ref{subsec:projects}.
 
 \item \texttt{.suppress\_stdout}: If this attribute is set to
-  \texttt{True} (default: \texttt{False}), Davos suppresses
+  \texttt{True} (default: \texttt{False}), \texttt{Davos} suppresses
   printed (console) outputs from both itself and the installer program.
@@
 \noindent The attributes above can be modified directly or via the \texttt{davos.configure()} function, which allows setting multiple options simultaneously (see Sec.~\ref{subsec:toplevel} for more information or Sec.~\ref{sec:illustrative-example} for example usage).
-In addition to these writeable options, the top-level \texttt{davos} module also provides several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and contain potentially useful information about the notebook environment or Davos's internal state:
+In addition to these writeable options, the top-level \texttt{davos} module also provides several read-only attributes that can be displayed in the notebook or checked programmatically at runtime, and contain potentially useful information about the notebook environment or \texttt{Davos}'s internal state:
 
@@
 
-\item \texttt{.all\_projects}: This attribute contains a list of all Davos projects that exist on the user's local system (see Sec.~\ref{subsec:projects} for more information about Davos projects).
+\item \texttt{.all\_projects}: This attribute contains a list of all \texttt{Davos} projects that exist on the user's local system (see Sec.~\ref{subsec:projects} for more information about \texttt{Davos} projects).
   Each item in this list is either a \texttt{Project} or \texttt{AbstractProject} instance.
   \texttt{Abstract\-Project}s represent notebook-specific projects whose associated notebooks no longer exist.
-  They support the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting Davos-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
-
-\item \texttt{.environment}: This attribute's value is a string denoting the set of environment-dependent ``helper functions'' used by Davos in the current notebook.
-  As described in Section \ref{sec:architecture}, Davos internally chooses between interchangeable implementations of certain core features based on various properties of the notebook's frontend and IPython kernel.
+  They support the same functionality as \texttt{Project} objects (including methods for inspecting, renaming, and deleting them) and serve primarily to help users identify and clean up extraneous projects left behind after deleting \texttt{Davos}-enhanced notebooks (e.g., see Sec.~\ref{subsec:toplevel}).
+
+\item \texttt{.environment}: This attribute's value is a string denoting the set of environment-dependent ``helper functions'' used by \texttt{Davos} in the current notebook.
+  As described in Section \ref{sec:architecture}, \texttt{Davos} internally chooses between interchangeable implementations of certain core features based on various properties of the notebook's frontend and IPython kernel.
   As of this writing, three unique combinations of helper functions are required to support existing notebook environments, ergo this attribute has three possible values: \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, or \texttt{"Colaboratory"}.
-  However, this attribute could take on additional values in the future as new notebook interfaces are created and IPython's internals are updated, and as additional versions of helper functions are added to Davos to support them.
+  However, this attribute could take on additional values in the future as new notebook interfaces are created and IPython's internals are updated, and as additional versions of helper functions are added to \texttt{Davos} to support them.
 
@@
 
-\subsubsection{Other top-level Davos functions}\label{subsec:toplevel}
-
-The Davos package also provides a handful of functions available in the top-level \texttt{davos} namespace.
+\subsubsection{Other top-level \texttt{Davos} functions}\label{subsec:toplevel}
+
+The \texttt{Davos} package also provides a handful of functions available in the top-level \texttt{davos} namespace.
 Some of these functions serve primarily as conveniences, while others provide additional functionality:
@@
 
-\item \texttt{get\_project(project\_name, create=False)}: This function can be passed the name of a Davos project (\texttt{project\_name}) to get the \texttt{Project} or \texttt{AbstractProject} instance representing it.
+\item \texttt{get\_project(project\_name, create=False)}: This function can be passed the name of a \texttt{Davos} project (\texttt{project\_name}) to get the \texttt{Project} or \texttt{AbstractProject} instance representing it.
   The optional \texttt{create} argument determines the function's behavior when no project with the given name exists: if \texttt{create=False} (the default), the function will return \texttt{None}; if \texttt{create=True}, a project with the given name will be created and returned.
 
-\item \texttt{prune\_projects(yes=False)}: This function allows users to quickly ``clean up'' their local Davos projects by deleting notebook-specific projects whose corresponding notebooks no longer exist (i.e., \texttt{AbstractProject}s).
+\item \texttt{prune\_projects(yes=False)}: This function allows users to quickly ``clean up'' their local \texttt{Davos} projects by deleting notebook-specific projects whose corresponding notebooks no longer exist (i.e., \texttt{AbstractProject}s).
   As with standard virtual environments, periodically removing unused project directories can be useful for reclaiming disk space from dependencies of code that is no longer in use.
@@
   Alternatively, passing \texttt{yes=True} will immediately remove all unused projects without prompting for confirmation.
-  Note that if Davos's non-interactive mode is enabled (see Sec.~\ref{subsec:config}), \texttt{yes=True} must be explicitly passed, otherwise the function will raise an exception.
+  Note that if \texttt{Davos}'s non-interactive mode is enabled (see Sec.~\ref{subsec:config}), \texttt{yes=True} must be explicitly passed, otherwise the function will raise an exception.
   This serves as a safeguard against accidentally deleting projects, since non-interactive mode disables all user input and confirmation.
@@
 
-\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, pre\-re\-leases=\\None)}: Through \texttt{smuggle} statements and onion comments, Davos can automatically ensure that all Python packages needed to run a notebook are installed, and that the same versions of those packages are used no matter when or by whom the notebook is run.
-  However, because Davos operates at runtime, one thing it cannot do automatically is install and switch to a specific version of Python itself.
+\item \texttt{require\_python(version\_spec, warn=False, extra\_msg=None, pre\-re\-leases=\\None)}: Through \texttt{smuggle} statements and onion comments, \texttt{Davos} can automatically ensure that all Python packages needed to run a notebook are installed, and that the same versions of those packages are used no matter when or by whom the notebook is run.
+  However, because \texttt{Davos} operates at runtime, one thing it cannot do automatically is install and switch to a specific version of Python itself.
   Distributing shared code along with a precise Python version for running it requires a heavier-weight solution, such as a Conda environment or Docker container (see Fig.~\ref{fig:code-sharing}).
-  Yet a Davos-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a particular Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
-  The \texttt{davos.require\_python()} function can be added to the top of a Davos-enhanced notebook to communicate to users that the notebook's code should be run with a specific or constrained Python version (see Sec.~\ref{sec:illustrative-example} for example usage).
+  Yet a \texttt{Davos}-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a particular Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
+  The \texttt{davos.require\_python()} function can be added to the top of a \texttt{Davos}-enhanced notebook to communicate to users that the notebook's code should be run with a specific or constrained Python version (see Sec.~\ref{sec:illustrative-example} for example usage).
   The function may be passed a version identifier (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
@@
 
-\item \texttt{use\_default\_project()}: By default, each Davos-enhanced notebook will create and use a notebook-specific project named based on its absolute path.
+\item \texttt{use\_default\_project()}: By default, each \texttt{Davos}-enhanced notebook will create and use a notebook-specific project named based on its absolute path.
   If a user manually changes the project used by the current notebook (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to switch back to using the notebook's default project and reset \texttt{davos.project} to its default value.
-  See Section \ref{subsec:projects} for more information about Davos projects and Section \ref{sec:illustrative-example} for an illustrative example.
+  See Section \ref{subsec:projects} for more information about \texttt{Davos} projects and Section \ref{sec:illustrative-example} for an illustrative example.
 
@@
 
-Although Davos is designed to \textit{appear} to add a new
+Although \texttt{Davos} is designed to \textit{appear} to add a new
 keyword to Python's vocabulary, this illusion is actually created through
@@
 for processing and executing users' code.  Specifically, when
-Davos is first imported, or when it is activated after having been
+\texttt{Davos} is first imported, or when it is activated after having been
 set to an inactive state, two actions are triggered.  First, the
 \texttt{smuggle()} function is injected into the IPython user
-namespace.  Second, the Davos parser is registered as a
+namespace.  Second, the \texttt{Davos} parser is registered as a
 custom IPython input transformer.
@@
 to the Python compiler, in order to handle special constructs like
-\mbox{\texttt{!}-pre}\-fixed shell commands and \mbox{\texttt{\%}-pre}\-fixed ``magic'' commands. Davos uses
+\mbox{\texttt{!}-pre}\-fixed shell commands and \mbox{\texttt{\%}-pre}\-fixed ``magic'' commands. \texttt{Davos} uses
 this same process to invisibly transform \texttt{smuggle} statements into
-syntactically valid Python code. The Davos parser uses a
+syntactically valid Python code. The \texttt{Davos} parser uses a
 regular expression to match lines of code containing \texttt{smuggle}
@@
 The call to the \texttt{smuggle()} function carries out
-Davos's central logic by determining whether the smuggled
+\texttt{Davos}'s central logic by determining whether the smuggled
 package must be installed, carrying out the installation if necessary,
@@
 is also possible (though never necessary) to call it
-directly. Deactivating Davos will delete the name
+directly. Deactivating \texttt{Davos} will delete the name
 ``\texttt{smuggle}'' from the namespace, unless its value has been
 overwritten and no longer refers to the \texttt{smuggle()}
-function. It will also deregister the Davos parser from the
+function. It will also deregister the \texttt{Davos} parser from the
 set of input transformers run when each notebook cell is
@@
   high level, the \texttt{smuggle()} function may be conceptualized as
-  following two basic steps.  First (left), Davos ensures that the
+  following two basic steps.  First (left), \texttt{Davos} ensures that the
   correct version of the desired package is available locally, installing
   it automatically (into the notebook's project directory) if needed.  Second (right),
-  Davos loads the package into the notebook and updates the current
+  \texttt{Davos} loads the package into the notebook and updates the current
   runtime environment.}
@@
 \includegraphics[width=\textwidth]{figs/illustrative_example}
-\caption{\small \textbf{Example use case for Davos.}
+\caption{\small \textbf{Example use case for \texttt{Davos}.}
   Snippets from this example are also excerpted in the main text of
@@
 
-The example code throughout Section \ref{subsec:onion} illustrates a typical use case that we envision for Davos: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
+The example code throughout Section \ref{subsec:onion} illustrates a typical use case that we envision for \texttt{Davos}: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
 When added to the top of a Jupyter notebook, this allows researchers to bundle their code and its dependencies into a single file that can be easily shared and run without any additional tools or setup, automatically installs its required packages at runtime, isolates them from the user's main Python environment, and ensures their versions do not change unexpectedly over time.
-In this section, we have contrived a more complex scenario to highlight some of Davos's more advanced features, and illustrate how they may be used to handle certain challenges that can arise when writing, running, and sharing reproducible scientific code.
+In this section, we have contrived a more complex scenario to highlight some of \texttt{Davos}'s more advanced features, and illustrate how they may be used to handle certain challenges that can arise when writing, running, and sharing reproducible scientific code.
 
@@
 The example provided in Figure~\ref{fig:illustrative-example} demonstrates how
-Davos can be used to circumvent these incompatibilities by
+\texttt{Davos} can be used to circumvent these incompatibilities by
 temporarily switching between different versions of the same package within a single runtime.
@@
 
-After installing and importing Davos (lines 1--2), we first use the \texttt{davos.require\_\-python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
+After installing and importing \texttt{Davos} (lines 1--2), we first use the \texttt{davos.require\_\-python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
 As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
@@
 It is worth noting, however, that beyond illustrative purposes, the benefit of specifying only a maximum version for \texttt{joblib} rather than an exact version is relatively minor.
-The main advantage to relaxing a version constraint in an onion comment (when a package's behavior does not differ meaningfully between versions) is that doing so increases the likelihood that a satisfactory version will already be available in the user's Python environment, and therefore Davos will not need to install a new copy in the notebook's project directory.
+The main advantage to relaxing a version constraint in an onion comment (when a package's behavior does not differ meaningfully between versions) is that doing so increases the likelihood that a satisfactory version will already be available in the user's Python environment, and therefore \texttt{Davos} will not need to install a new copy in the notebook's project directory.
 For large packages, this can be a worthwhile consideration; however \texttt{joblib} is very lightweight---less than 0.5 MB pre-built, with no required dependencies.
@@
 Line 11 then enables
-Davos's \texttt{auto\_rerun} option (see Sec.~\ref{subsec:config}) before smuggling the next
+\texttt{Davos}'s \texttt{auto\_rerun} option (see Sec.~\ref{subsec:config}) before smuggling the next
 two packages: \texttt{NumPy} and
@@
 imported during the same interpreter session---including internally by other packages.
-Enabling \texttt{auto\_rerun} allows Davos to handle kernel restarts automatically and continue running the code seamlessly without user intervention.
+Enabling \texttt{auto\_rerun} allows \texttt{Davos} to handle kernel restarts automatically and continue running the code seamlessly without user intervention.
 \begin{center}
@@
 The \texttt{joblib} package has an optional dependency on \texttt{NumPy} for memoizing and parallelizing array operations, and will \texttt{import numpy} internally to enable these features if the package is available.
-If the user already has \texttt{NumPy} installed in their Python environment when \texttt{joblib} is smuggled in line 9, their installed version is different from the one specified in the onion comment on line 12, and there were changes made to \texttt{NumPy}'s C extensions between those two versions, then Davos will automatically restart the kernel and re-run the lines above.
+If the user already has \texttt{NumPy} installed in their Python environment when \texttt{joblib} is smuggled in line 9, their installed version is different from the one specified in the onion comment on line 12, and there were changes made to \texttt{NumPy}'s C extensions between those two versions, then \texttt{Davos} will automatically restart the kernel and re-run the lines above.
 The newly smuggled version would then be used both in the notebook itself and by \texttt{joblib} internally.
@@
 the new one.
-When Davos automatically does so and re-runs the code above, having now converted the dataset to a CSV file means the old version does not need to be reinstalled (line 14).
+When \texttt{Davos} automatically does so and re-runs the code above, having now converted the dataset to a CSV file means the old version does not need to be reinstalled (line 14).
 
@@
 statements to load the packages into the notebook's namespace. If they
-differ, Davos will download the requested versions in place
+differ, \texttt{Davos} will download the requested versions in place
 of the installed versions, ensuring that they are used both in the notebook itself and by \texttt{UMAP} internally.
@@
 
-In lines 30--37, we demonstrate another aspect of Davos's functionality that supports more advanced installation scenarios.
+In lines 30--37, we demonstrate another aspect of \texttt{Davos}'s functionality that supports more advanced installation scenarios.
 The \texttt{ipywidgets}~\cite{FredEtal15} package (also known as Jupyter Widgets) provides a Python API for creating interactive JavaScript widgets within a notebook.
@@
 In this particular case, however, a combination of factors make this relatively safe and inconsequential.
-First, the package we need to install directly into the notebook server environment (\texttt{widgetsnbextension}) is smuggled without an accompanying onion comment (line 34), meaning that Davos will not replace any version the user may already have installed.
-Second, the package has no dependencies of its own, so if Davos does install it, no other packages will be installed or updated as a side effect.
+First, the package we need to install directly into the notebook server environment (\texttt{widgetsnbextension}) is smuggled without an accompanying onion comment (line 34), meaning that \texttt{Davos} will not replace any version the user may already have installed.
+Second, the package has no dependencies of its own, so if \texttt{Davos} does install it, no other packages will be installed or updated as a side effect.
 Third, the package itself provides no functionality outside of rendering Jupyter widgets, so its presence would not alter any other code's expected behavior.
 
-Next, in lines 31--33, we change the \texttt{pip} executable Davos uses to install smuggled packages (see Sec.~\ref{subsec:config}), storing the default executable's path in a variable before doing so.
-When Davos's project system is disabled, using a \texttt{pip} executable from a particular Python environment will cause smuggled packages to be installed into (and subsequently loaded from) that environment.
+Next, in lines 31--33, we change the \texttt{pip} executable \texttt{Davos} uses to install smuggled packages (see Sec.~\ref{subsec:config}), storing the default executable's path in a variable before doing so.
+When \texttt{Davos}'s project system is disabled, using a \texttt{pip} executable from a particular Python environment will cause smuggled packages to be installed into (and subsequently loaded from) that environment.
 The default \texttt{pip\_executable} will install packages into the environment used to run the IPython kernel.
@@
 \texttt{scikit-learn} in line 44. Taken together, the code in
-Figure~\ref{fig:illustrative-example} shows how Davos can
+Figure~\ref{fig:illustrative-example} shows how \texttt{Davos} can
 enable users to load in data and models that are incompatible with
@@
 
-We designed Davos for use in research settings, where code for numerous different tasks---from processing data, to running statistical analyses, to generating figures and tables for publication---is frequently shared among collaborators while working on a project, and eventually with the broader scientific community and general public upon a its completion.
+We designed \texttt{Davos} for use in research settings, where code for numerous different tasks---from processing data, to running statistical analyses, to generating figures and tables for publication---is frequently shared among collaborators while working on a project, and eventually with the broader scientific community and general public upon a its completion.
 In these contexts, ensuring that shared code yields consistent, reproducible outputs across users and over time is crucially important, yet the tools available to researchers for doing so can be complex to set up and challenging to properly use.
@@
 
-While the Davos package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (see Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (see Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
-And by eliminating most of the setup costs of reconstructing the original researchers' computing environment, Davos also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
-
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), Davos is most comparable to virtual environments as it similarly provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
-However, when used in conjunction with Jupyter notebooks, Davos offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
+And by eliminating most of the setup costs of reconstructing the original researchers' computing environment, \texttt{Davos} also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
+
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments as it similarly provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
 
@@
 
-Second, Davos automatically checks for, installs, isolates, and imports any required packages at runtime.
-This allows users to download and immediately run a Davos-enhanced notebook without any prerequisite setup (beyond that needed to run a standard Jupyter notebook).
+Second, \texttt{Davos} automatically checks for, installs, isolates, and imports any required packages at runtime.
+This allows users to download and immediately run a \texttt{Davos}-enhanced notebook without any prerequisite setup (beyond that needed to run a standard Jupyter notebook).
 By contrast, before running a notebook whose dependencies are managed via a virtual environment, the user would first need to run a series of shell commands to manually create a new environment, populate it with packages from the researcher's configuration file (which the user must also have obtained), and then either use the \texttt{ipykernel} package to register the environment as a Jupyter kernel, or activate and deactivate the environment before and after (respectively) each time the notebook was launched.
-Beyond reducing this initial setup cost, Davos's runtime-based approach to dependency management affords a second important benefit.
+Beyond reducing this initial setup cost, \texttt{Davos}'s runtime-based approach to dependency management affords a second important benefit.
 While creating and configuring a virtual environment ensures that a specific set of packages is initially installed, it does not guarantee that they will \textit{remain} installed after that point.
@@
 If the individual does not happen to notice this change when it occurs, differences between those packages' expected and installed versions may introduce bugs into previously written code or subtly alter its output when it is next run.
-Because \texttt{smuggle} statements and onion comments are evaluated every time a Davos-enhanced notebook is run, they function to ensure that the notebook's dependencies are always satisfied and that any such inadvertent changes would be automatically caught and corrected.
-
-Third, running a shared notebook that uses Davos to manage its dependencies often requires less (but never more) space on the user's system than running an identical notebook inside a virtual environment.
-While typical virtual environment directories will contain \textit{all} requirements listed in their configuration files, Davos's isolated project directories (by default; see Sec.~\ref{subsec:projects}) contain only those not already available in the user's existing Python environment.
-This is another feature made possible by Davos's runtime-based dependency management scheme.
-Davos can safely draw from packages in from the user's main environment to satisfy a notebook's dependencies, when possible, because if those packages were to be updated or removed at any point such that they no longer met the notebook's requirements, appropriate versions could (and would) be installed into the project directory the next time the notebook was executed.
-
-Finally, neither virtual environments nor Davos-enhanced notebooks can bundle specific versions of Python with which to run shared code.
-However, Davos's \texttt{require\_\-python()} function provides a simple mechanism for indicating a required or constrained Python version and alerting the user at runtime (by raising an exception) if their Python version is incompatible.
-In terms of Davos's ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (see Fig.~\ref{fig:code-sharing}) and should be preferred over Davos in cases where this is necessary.
+Because \texttt{smuggle} statements and onion comments are evaluated every time a \texttt{Davos}-enhanced notebook is run, they function to ensure that the notebook's dependencies are always satisfied and that any such inadvertent changes would be automatically caught and corrected.
+
+Third, running a shared notebook that uses \texttt{Davos} to manage its dependencies often requires less (but never more) space on the user's system than running an identical notebook inside a virtual environment.
+While typical virtual environment directories will contain \textit{all} requirements listed in their configuration files, \texttt{Davos}'s isolated project directories (by default; see Sec.~\ref{subsec:projects}) contain only those not already available in the user's existing Python environment.
+This is another feature made possible by \texttt{Davos}'s runtime-based dependency management scheme.
+\texttt{Davos} can safely draw from packages in from the user's main environment to satisfy a notebook's dependencies, when possible, because if those packages were to be updated or removed at any point such that they no longer met the notebook's requirements, appropriate versions could (and would) be installed into the project directory the next time the notebook was executed.
+
+Finally, neither virtual environments nor \texttt{Davos}-enhanced notebooks can bundle specific versions of Python with which to run shared code.
+However, \texttt{Davos}'s \texttt{require\_\-python()} function provides a simple mechanism for indicating a required or constrained Python version and alerting the user at runtime (by raising an exception) if their Python version is incompatible.
+In terms of \texttt{Davos}'s ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (see Fig.~\ref{fig:code-sharing}) and should be preferred over \texttt{Davos} in cases where this is necessary.
 However, the functionality it provides over what is possible with a standard virtual environment is removing the \textit{expectation} that running a particular notebook will reproduce an expected outcome in situations where this is either impossible or not guaranteed.
@@
 
-Beyond research applications, Davos is also useful in
+Beyond research applications, \texttt{Davos} is also useful in
 pedagogical settings. For example, in programming courses, instructors
-and students may use the Davos package to ensure their
+and students may use the \texttt{Davos} package to ensure their
 notebooks will run correctly on others' machines. When combined with
 online notebook-based platforms like Google Colaboratory,
-Davos provides a convenient way to manage dependencies within
+\texttt{Davos} provides a convenient way to manage dependencies within
 a notebook without requiring any software (beyond a web browser) to
 be installed on the students' or instructors' systems. For the same
-reasons, Davos also provides an elegant means of sharing
+reasons, \texttt{Davos} also provides an elegant means of sharing
 ready-to-run notebook-based demonstrations or tutorials that install
@@
 
-Since its initial release, Davos has found use in a variety of applications. In
+Since its initial release, \texttt{Davos} has found use in a variety of applications. In
 addition to managing computing environments for multiple prior and ongoing
-research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, Davos is being
+research studies~\citep{MannEtal23a, OwenMann23, ZimaEtal23}, \texttt{Davos} is being
 used by both students and instructors in programming and research methods courses such
@@
 Academy~\cite{vanVEtal21} also included an ``experimental'' module that uses
-Davos to manage dependencies related to a large language model-based
+\texttt{Davos} to manage dependencies related to a large language model-based
 tutor~\cite{MannEtal23b}.
@@
 operators to the Python language could be specifically useful to
-researchers. With Davos, we accomplish this by leveraging
+researchers. With \texttt{Davos}, we accomplish this by leveraging
 IPython notebooks' internal code parsing and execution machinery. We
@@
 keyword-like objects (e.g., based around common typos). We also note
-that this implementation approach means Davos's functionality
+that this implementation approach means \texttt{Davos}'s functionality
 is currently restricted to IPython notebook environments. However,
@@
 including a draft proposal~\cite{Shan20}. In addition to enabling
-Davos to be extended for use outside of notebooks, this could
-lead to exciting new tools that, like Davos, extend the
+\texttt{Davos} to be extended for use outside of notebooks, this could
+lead to exciting new tools that, like \texttt{Davos}, extend the
 Python language in useful and more secure ways.
@@
 
-While Davos enables developers to conveniently specify all project
+While \texttt{Davos} enables developers to conveniently specify all project
 dependencies, there are some edge cases and limitations that are worth
@@
 This can result in various ``hidden state'' problems, such as variables referencing different objects than the currently running cell expects them to, given its point in the notebook's execution order.
-In theory, using Davos to \texttt{smuggle} different versions of the same package across different notebook cells could exacerbate this issue if a user executed those cells out of their intended order.
-Therefore an important consideration when using Davos is that it is perhaps even more important to execute notebook cells in order than would be the case in the standard (non-Davos) setup.
+In theory, using \texttt{Davos} to \texttt{smuggle} different versions of the same package across different notebook cells could exacerbate this issue if a user executed those cells out of their intended order.
+Therefore an important consideration when using \texttt{Davos} is that it is perhaps even more important to execute notebook cells in order than would be the case in the standard (non-\texttt{Davos}) setup.
 However, a few ``best practices'' may be adopted to help mitigate this risk.
-First, when sharing a Davos-enhanced notebook in a state that is intended to be reproducible, code cells should appear in their intended execution order, such that users can successfully run them top to bottom.
+First, when sharing a \texttt{Davos}-enhanced notebook in a state that is intended to be reproducible, code cells should appear in their intended execution order, such that users can successfully run them top to bottom.
 In a scenario where this is impossible, the intended order should be clearly indicated in code comments and/or markdown cells.
-This is already a common practice for notebooks that include system calls to install required packages and dependencies, and the same approach would work well in Davos-enhanced notebooks.
-Second, while Davos makes it possible to \texttt{smuggle} multiple versions of a package within the same notebook, users should prefer to split code that requires different versions of the same package into different notebooks.
-In addition to mitigating the issue described above, this will also allow Davos to store a single intended version of the package in each notebook's project directory, rather than reinstalling the package each time a different version is smuggled.
+This is already a common practice for notebooks that include system calls to install required packages and dependencies, and the same approach would work well in \texttt{Davos}-enhanced notebooks.
+Second, while \texttt{Davos} makes it possible to \texttt{smuggle} multiple versions of a package within the same notebook, users should prefer to split code that requires different versions of the same package into different notebooks.
+In addition to mitigating the issue described above, this will also allow \texttt{Davos} to store a single intended version of the package in each notebook's project directory, rather than reinstalling the package each time a different version is smuggled.
 Finally, in situations where it \textit{is} necessary or preferable to temporarily \texttt{smuggle} a different version of a particular package than is used throughout the rest of the notebook (e.g., Fig.~\ref{fig:illustrative-example}), the code to \texttt{smuggle} that temporary version, perform all necessary operations, and (re-)\texttt{smuggle} the ``default'' version should be contained within a single notebook cell, such that (absent any errors in its execution) the same version is always installed and imported before and after the cell is run.
@@
 
-A second limitation of Davos relates to how packages are installed and managed.
-As of this writing, Davos can install packages using \texttt{pip}, but not
+A second limitation of \texttt{Davos} relates to how packages are installed and managed.
+As of this writing, \texttt{Davos} can install packages using \texttt{pip}, but not
 other standard Python package management systems such as \texttt{conda}.
 Therefore packages that are not installable via \texttt{pip} are currently
-unsupported by Davos. We anticipate adding support for other package management
+unsupported by \texttt{Davos}. We anticipate adding support for other package management
 systems, including \texttt{conda} \cite{Anac12}, in a future release.
 
-A third limitation of Davos is that it cannot be used to manage projects that
+A third limitation of \texttt{Davos} is that it cannot be used to manage projects that
 depend on non-Python software. For example, system software or libraries from
 other languages (e.g., in a mixed Python and R notebook), cannot be
-\texttt{smuggle}d by Davos. A notebook that utilizes or depends on non-Python
-software would therefore need to use existing non-Davos approaches to managing
+\texttt{smuggle}d by \texttt{Davos}. A notebook that utilizes or depends on non-Python
+software would therefore need to use existing non-\texttt{Davos} approaches to managing
 those requirements.
 
-Davos's ``projects'' system (Sec.~\ref{subsec:projects}) provides a safe way
+\texttt{Davos}'s ``projects'' system (Sec.~\ref{subsec:projects}) provides a safe way
 of managing project dependencies without interfering with the user's Python
-environment. By default, each Davos-enhanced notebook creates and uses its own
+environment. By default, each \texttt{Davos}-enhanced notebook creates and uses its own
 notebook-specific project directory, which is named based on the notebook's absolute
@@
 notebook may not be possible in some environments.
-For example, Davos queries the Jupyter Server API to determine the notebook's name, but some non-browser applications may implement mechanisms for communicating with the IPython kernel without starting a Jupyter server.
-As of this writing, Davos fully supports most common notebook environments, including classic Jupyter Notebooks,
+For example, \texttt{Davos} queries the Jupyter Server API to determine the notebook's name, but some non-browser applications may implement mechanisms for communicating with the IPython kernel without starting a Jupyter server.
+As of this writing, \texttt{Davos} fully supports most common notebook environments, including classic Jupyter Notebooks,
 JupyterLab, Google Colaboratory, Binder, Kaggle Notebooks, JetBrains IDEs (PyCharm, DataSpell, etc.), and Visual Studio Code, among others.
-However, in cases where Davos fails to determine the current notebook's path, it will issue a warning and fall back to using a generic project named ``davos-fallback.'' This project is shared across all such occurrences and exists to ensure that even if some component of Davos's project system fails, smuggling packages will still not affect the user's main Python environment.
-If this occurs, the user can also manually set Davos to use the ``normal'' default project for the current by setting \texttt{davos.project} to its absolute or relative path.
+However, in cases where \texttt{Davos} fails to determine the current notebook's path, it will issue a warning and fall back to using a generic project named ``davos-fallback.'' This project is shared across all such occurrences and exists to ensure that even if some component of \texttt{Davos}'s project system fails, smuggling packages will still not affect the user's main Python environment.
+If this occurs, the user can also manually set \texttt{Davos} to use the ``normal'' default project for the current by setting \texttt{davos.project} to its absolute or relative path.
 
@@
 
-The Davos package supports reproducible research by providing
+The \texttt{Davos} package supports reproducible research by providing
 a novel, lightweight system for sharing notebook-based code. It
@@
 specifying dependencies in the spirit of ``literate programming'' paradigm Jupyter notebooks promote.
-But perhaps the most exciting uses of the Davos package are those
+But perhaps the most exciting uses of the \texttt{Davos} package are those
 that we have \textit{not} yet considered or imagined. We hope that the
-research and scientific Python communities will find Davos to provide a convenient
+research and scientific Python communities will find \texttt{Davos} to provide a convenient
 means of managing project dependencies to facilitate code sharing and collaboration. We

### 2023-09-30 paper/main.tex
fix version strings in metadata table
implement @jeremymanning's suggestions -- thanks!

@@
 \hline
-C1 & Current code version &  v0.2.4 \\
+C1 & Current code version &  v0.2.3 \\
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.4} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.3} \\
 \hline
@@
 
-We designed \texttt{Davos} for use in research settings, where code for numerous different tasks---from processing data, to running statistical analyses, to generating figures and tables for publication---is frequently shared among collaborators while working on a project, and eventually with the broader scientific community and general public upon a its completion.
-In these contexts, ensuring that shared code yields consistent, reproducible outputs across users and over time is crucially important, yet the tools available to researchers for doing so can be complex to set up and challenging to properly use.
+We designed \texttt{Davos} for use in research settings, where code for numerous different tasks---from processing data, to running statistical analyses, to generating figures and tables for publication---is frequently shared between collaborators while working on a project, and eventually with the broader scientific community and general public upon its completion.
+In these contexts, ensuring that shared code yields consistent, reproducible outputs across users and over time is critical, yet the tools available to researchers for doing so can be complex to set up and challenging to properly use.
 This has the dual effect of discouraging scientists from sharing their code in a reproducible way (or at all), and making it significantly harder (or impossible) for others to successfully reproduce their results, adopt or extend their methods, and contribute to or build upon their work.
@@
 
-While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (see Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
-And by eliminating most of the setup costs of reconstructing the original researchers' computing environment, \texttt{Davos} also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
-
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments as it similarly provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+And by eliminating most of the setup costs of reconstructing the original researchers' computing environment(s), \texttt{Davos} also lowers barriers to entry for members of the scientific community and the public who seek to run shared code.
+
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
 However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
@@
 While typical virtual environment directories will contain \textit{all} requirements listed in their configuration files, \texttt{Davos}'s isolated project directories (by default; see Sec.~\ref{subsec:projects}) contain only those not already available in the user's existing Python environment.
-This is another feature made possible by \texttt{Davos}'s runtime-based dependency management scheme.
-\texttt{Davos} can safely draw from packages in from the user's main environment to satisfy a notebook's dependencies, when possible, because if those packages were to be updated or removed at any point such that they no longer met the notebook's requirements, appropriate versions could (and would) be installed into the project directory the next time the notebook was executed.
+This is another feature made possible by \texttt{Davos}'s runtime-based dependency management system.
+\texttt{Davos} can safely draw from packages in the user's main environment to satisfy a notebook's dependencies, when possible, because if those packages were to be updated or removed at any point such that they no longer met the notebook's requirements, appropriate versions would be installed into the project directory the next time the notebook was executed.
 
@@
 However, \texttt{Davos}'s \texttt{require\_\-python()} function provides a simple mechanism for indicating a required or constrained Python version and alerting the user at runtime (by raising an exception) if their Python version is incompatible.
-In terms of \texttt{Davos}'s ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (see Fig.~\ref{fig:code-sharing}) and should be preferred over \texttt{Davos} in cases where this is necessary.
-However, the functionality it provides over what is possible with a standard virtual environment is removing the \textit{expectation} that running a particular notebook will reproduce an expected outcome in situations where this is either impossible or not guaranteed.
+In terms of \texttt{Davos}'s ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (Fig.~\ref{fig:code-sharing}).
+However, the functionality \texttt{Davos} provides over what is possible with a standard virtual environment is to remove the \textit{expectation} that running a particular notebook will reproduce an expected outcome in situations where this is either impossible or not guaranteed.
 With this understanding, a user may choose to install a compatible Python version through some other means or elect to still run the code, but will not be surprised by a potential failure to execute successfully or output an expected result.
@@
 there have been early-stage discussions of providing this sort of
-syntactic customizability as a core feature of the Python language,
+syntactic customizability as a core feature of the Python language itself,
 including a draft proposal~\cite{Shan20}. In addition to enabling
@@
 notebooks with no setup required, and defines a simple, self-documenting format for
-specifying dependencies in the spirit of ``literate programming'' paradigm Jupyter notebooks promote.
+specifying dependencies in the spirit of the ``literate programming'' paradigm Jupyter notebooks promote.
 But perhaps the most exciting uses of the \texttt{Davos} package are those

### 2023-09-30 paper/main.tex
cleaned up a bunch of LaTeX stuff

@@
 This object supports methods for interacting with the current project, including locating its directory within the file system, listing all installed packages' names and versions, changing the project's name, and deleting its contents.
-\texttt{Project} instances can also be created and managed programmatically, and \texttt{Davos} provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and \ref{subsec:toplevel}).
+\texttt{Project} instances can also be created and managed programmatically, and \texttt{Davos} provides additional utilities for viewing and working with all existing projects (see Secs.~\ref{subsec:config} and~\ref{subsec:toplevel}).
 
@@
   This attribute can be reset to its default value using the top-level \texttt{use\_default\_project()} function (see Sec.~\ref{subsec:toplevel}).
-  For more information about \texttt{Davos} projects, see Section \ref{subsec:projects}.
+  For more information about \texttt{Davos} projects, see Section~\ref{subsec:projects}.
 
@@
 \item \texttt{.environment}: This attribute's value is a string denoting the set of environment-dependent ``helper functions'' used by \texttt{Davos} in the current notebook.
-  As described in Section \ref{sec:architecture}, \texttt{Davos} internally chooses between interchangeable implementations of certain core features based on various properties of the notebook's frontend and IPython kernel.
+  As described in Section~\ref{sec:architecture}, \texttt{Davos} internally chooses between interchangeable implementations of certain core features based on various properties of the notebook's frontend and IPython kernel.
   As of this writing, three unique combinations of helper functions are required to support existing notebook environments, ergo this attribute has three possible values: \texttt{"IPython<7.0"}, \texttt{"IPython>=7.0"}, or \texttt{"Colaboratory"}.
@@
 
-\item \texttt{configure(**kwargs)}: This function provides an alternate way of assigning values to the writeable attributes listed in Section \ref{subsec:config} and can be used to configure multiple options at once (see Sec.~\ref{sec:illustrative-example} for example usage).
+\item \texttt{configure(**kwargs)}: This function provides an alternate way of assigning values to the writeable attributes listed in Section~\ref{subsec:config} and can be used to configure multiple options at once (see Sec.~\ref{sec:illustrative-example} for example usage).
   The function accepts attribute names as keyword-only arguments to which their desired values are passed.
@@
   Distributing shared code along with a precise Python version for running it requires a heavier-weight solution, such as a Conda environment or Docker container (see Fig.~\ref{fig:code-sharing}).
-  Yet a \texttt{Davos}-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a particular Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7 \cite{Smit17} and at least 19 modules are slated for removal in Python 3.13 \cite{HeimCann19}).
+  Yet a \texttt{Davos}-enhanced notebook may still \texttt{smuggle} certain packages that depend on users having a particular Python version or range of versions (e.g., even just within the standard library, the \texttt{dataclass} module was first added in Python 3.7~\cite{Smit17} and at least 19 modules are slated for removal in Python 3.13~\cite{HeimCann19}).
   The \texttt{davos.require\_python()} function can be added to the top of a \texttt{Davos}-enhanced notebook to communicate to users that the notebook's code should be run with a specific or constrained Python version (see Sec.~\ref{sec:illustrative-example} for example usage).
-  The function may be passed a version identifier (e.g., \texttt{"3.10.5"}) or any valid version specifier \cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
+  The function may be passed a version identifier (e.g., \texttt{"3.10.5"}) or any valid version specifier~\cite{CoghStuf13} (e.g., \texttt{"\raisebox{0.5ex}{\texttildelow}=3.11"}, \texttt{">=3.9;<3.12"}, etc.) and will raise an exception if the user's Python version is incompatible.
   Alternatively, a ``soft'' or suggested constraint can be imposed by passing \texttt{warn=True} to issue a warning rather than raise an error.
@@
   If a user manually changes the project used by the current notebook (i.e., by setting the value of the \texttt{davos.project} attribute; see Sec.~\ref{subsec:config}), this function can be called to switch back to using the notebook's default project and reset \texttt{davos.project} to its default value.
-  See Section \ref{subsec:projects} for more information about \texttt{Davos} projects and Section \ref{sec:illustrative-example} for an illustrative example.
+  See Section~\ref{subsec:projects} for more information about \texttt{Davos} projects and Section~\ref{sec:illustrative-example} for an illustrative example.
 
@@
 
-The example code throughout Section \ref{subsec:onion} illustrates a typical use case that we envision for \texttt{Davos}: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
+The example code throughout Section~\ref{subsec:onion} illustrates a typical use case that we envision for \texttt{Davos}: a series of smuggle statements and onion comments with version specifiers or other options collectively describes and automatically constructs a reproducible environment for running the code that follows it.
 When added to the top of a Jupyter notebook, this allows researchers to bundle their code and its dependencies into a single file that can be easily shared and run without any additional tools or setup, automatically installs its required packages at runtime, isolates them from the user's main Python environment, and ensures their versions do not change unexpectedly over time.
@@
 After installing and importing \texttt{Davos} (lines 1--2), we first use the \texttt{davos.require\_\-python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
-As described above, the example code in Figure \ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
+As described above, the example code in Figure~\ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
 We therefore want to make sure upfront (in line 6) that the notebook's Python version falls within the range of versions that both of these two versions of \texttt{pandas} support.
@@
 allow installing smuggled packages outside of the notebook's project directory.
-As noted in Section \ref{subsec:projects}, this is typically discouraged, as doing so can risk interfering with the user's Python environment if existing package versions are overwritten.
+As noted in Section~\ref{subsec:projects}, this is typically discouraged, as doing so can risk interfering with the user's Python environment if existing package versions are overwritten.
 In this particular case, however, a combination of factors make this relatively safe and inconsequential.
@@
 original creator using the \texttt{joblib} package, as
-\texttt{scikit-learn}'s documentation recommends \cite{skle22}. Because
+\texttt{scikit-learn}'s documentation recommends~\cite{skle22}. Because
 \texttt{joblib} uses the \texttt{pickle} protocol internally, the
@@
 
-First, \texttt{smuggle} statements and onion comments enable researchers to specify their notebooks' dependencies directly within the code that requires them (see Secs.~\ref{subsec:smuggle} and  \ref{subsec:onion}).
+First, \texttt{smuggle} statements and onion comments enable researchers to specify their notebooks' dependencies directly within the code that requires them (see Secs.~\ref{subsec:smuggle} and~\ref{subsec:onion}).
 This eliminates the need to either manually create and maintain separate configuration files or use an additional tool to generate them, and to then distribute these files alongside their primary code base for users to download.
@@
 considering.
-First, prior studies on reproducibility of Jupyter notebooks (e.g., \cite{PimeEtal19}) identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, which may differ from the order in which they were executed by the notebook's original author.
+First, prior studies on reproducibility of Jupyter notebooks~\cite[e.g.,][]{PimeEtal19}) identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, which may differ from the order in which they were executed by the notebook's original author.
 This can result in various ``hidden state'' problems, such as variables referencing different objects than the currently running cell expects them to, given its point in the notebook's execution order.
@@
 unsupported by \texttt{Davos}. We anticipate adding support for other package management
-systems, including \texttt{conda} \cite{Anac12}, in a future release.
+systems, including \texttt{conda}~\cite{Anac12}, in a future release.
 
@@
 
-Our work was supported in part by NSF grant number 2145172 to JRM.
+Our work was supported in part by NSF grant number 2145172 to JRM\@.
 The content is solely the responsibility of the authors and does not

### 2023-10-01 paper/main.tex
rewrote first limitation section

@@
 considering.
-First, prior studies on reproducibility of Jupyter notebooks~\cite[e.g.,][]{PimeEtal19}) identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, which may differ from the order in which they were executed by the notebook's original author.
-This can result in various ``hidden state'' problems, such as variables referencing different objects than the currently running cell expects them to, given its point in the notebook's execution order.
-In theory, using \texttt{Davos} to \texttt{smuggle} different versions of the same package across different notebook cells could exacerbate this issue if a user executed those cells out of their intended order.
-Therefore an important consideration when using \texttt{Davos} is that it is perhaps even more important to execute notebook cells in order than would be the case in the standard (non-\texttt{Davos}) setup.
-However, a few ``best practices'' may be adopted to help mitigate this risk.
-First, when sharing a \texttt{Davos}-enhanced notebook in a state that is intended to be reproducible, code cells should appear in their intended execution order, such that users can successfully run them top to bottom.
-In a scenario where this is impossible, the intended order should be clearly indicated in code comments and/or markdown cells.
-This is already a common practice for notebooks that include system calls to install required packages and dependencies, and the same approach would work well in \texttt{Davos}-enhanced notebooks.
-Second, while \texttt{Davos} makes it possible to \texttt{smuggle} multiple versions of a package within the same notebook, users should prefer to split code that requires different versions of the same package into different notebooks.
-In addition to mitigating the issue described above, this will also allow \texttt{Davos} to store a single intended version of the package in each notebook's project directory, rather than reinstalling the package each time a different version is smuggled.
-Finally, in situations where it \textit{is} necessary or preferable to temporarily \texttt{smuggle} a different version of a particular package than is used throughout the rest of the notebook (e.g., Fig.~\ref{fig:illustrative-example}), the code to \texttt{smuggle} that temporary version, perform all necessary operations, and (re-)\texttt{smuggle} the ``default'' version should be contained within a single notebook cell, such that (absent any errors in its execution) the same version is always installed and imported before and after the cell is run.
-For example, in Figure~\ref{fig:illustrative-example}, lines 14--19 should be run within a single cell, and lines 42--44 should be run in a single cell.
+First, prior studies on reproducibility of Jupyter notebooks~\cite[e.g.,][]{PimeEtal19} identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, and therefore potentially in a different order than they were executed by the notebook's original author.
+This can result in situations where, for example, a cell's execution fails because its code calls a function that has not yet been defined, or accesses a variable that refers to a different object than is expected at that point in the notebook.
+In theory, using \texttt{Davos} to \texttt{smuggle} multiple versions of the same package in different cells of a notebook could exacerbate this issue if a user executed those cells out of their intended order, such that their currently imported version of a core dependency was different from what a particular cell expected or required.
+Therefore, an important consideration when using \texttt{Davos} to facilitate complex, multi-package-version runtimes in this way is that executing notebook cells in order is perhaps even more important than it would be in a standard (i.e., non-\texttt{Davos}-enhanced) notebook.
+While (as noted in Sections~\ref{sec:illustrative-example} and~\ref{sec:illustrative-example}) we consider this an ``advanced feature'' of Davos rather than typical usage, we propose a relatively simple set of ``best practices'' that substantially mitigate the risk of creating ambiguous states within a notebook.
+First, any \texttt{Davos}-enhanced notebook (or simply any notebook) that is intended to be run by more than one individual should be organized with its code cells in their intended execution order from top to bottom.
+If an edge case arises in which this is not possible, the intended order should be clearly indicated in code comments and/or markdown cells.
+Second, when smuggling multiple different versions of a package within a notebook, one version of the package may be designated the ``main'' version, and any others designated as ``alternate'' versions.
+The main version should be the primary version used throughout the notebook, while alternates are those temporarily required for a specific task or functionality.
+For example, in Figure~\ref{fig:illustrative-example}, \texttt{pandas} v1.3.5 and \texttt{scikit-learn} v1.1.3 are the main versions of their respective packages as they are used throughout the remainder of the code once they are loaded.
+Meanwhile \texttt{pandas<0.25.0} and \texttt{scikit-learn<0.22.0} are alternate versions because they are temporarily smuggled for the specific purpose of loading an outmoded dataset and model and then immediately replaced with main versions after their use is complete.
+Any time an alternate package version needed, the \texttt{smuggle} statement used to install and load it, the operations it is required to perform, and a second \texttt{smuggle} to (re-)install and load the main package version should be placed within a single cell.
+This ensures that (barring other unrelated errors in the cell's execution) the main version will always be installed and imported when any given notebook cell is run.
+In other words, in Figure~\ref{fig:illustrative-example}, lines 14--19 should be run within a single cell, and lines 42--44 should be run in a single cell.
 
@@
 As of this writing, \texttt{Davos} can install packages using \texttt{pip}, but not
-other standard Python package management systems such as \texttt{conda}.
+other standard Python package management systems such as \texttt{conda}~\cite{Anac12}.
 Therefore packages that are not installable via \texttt{pip} are currently
 unsupported by \texttt{Davos}. We anticipate adding support for other package management
-systems, including \texttt{conda}~\cite{Anac12}, in a future release.
+systems, including \texttt{conda}, in a future release.
 

### 2023-10-01 paper/main.tex

@@
 notebooks with no setup required, and defines a simple, self-documenting format for
-specifying dependencies in the spirit of the ``literate programming'' paradigm Jupyter notebooks promote.
+specifying dependencies in keeping with the ``literate programming'' paradigm that Jupyter notebooks support.
+We designed \texttt{Davos} to fill a niche we believe will help facilitate contributing to and engaging with open science resources.
 But perhaps the most exciting uses of the \texttt{Davos} package are those

### 2023-10-01 paper/main.tex

@@
 
-Additionally, because \texttt{smuggle} statements in a given notebook are evaluated every time the notebook is run, this design ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
+Because \texttt{smuggle} statements in a given notebook are evaluated every time the notebook is run, this ensures that the notebook's requirements will remain satisfied even if the user's Python environment changes.
 For example, suppose a user has \texttt{NumPy}~\cite{HarrEtal20} v1.24.3 installed in their current Python environment and runs a \texttt{Davos}-enhanced notebook that smuggles \texttt{NumPy} with ``\texttt{numpy==1.24.3}'' specified in an onion comment (see Sec.~\ref{subsec:onion}).
-Since the user's existing version of the package satisfies this requirement, \texttt{Davos} will load it into the notebook.
+Since the user's existing version of the package satisfies this requirement, \texttt{Davos} will load it into the notebook's runtime environment.
 But if the user later upgrades their environment's \texttt{NumPy} version to v1.25.0 (perhaps as a result of installing a different package that depends on it) and subsequently re-runs this notebook, the local version will longer satisfy this requirement, so \texttt{Davos} will install \texttt{NumPy} v1.24.3 into the notebook's project directory and load that version instead.
@@
   This serves as a safeguard against accidentally deleting projects, since non-interactive mode disables all user input and confirmation.
-  Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook filepaths), as they are not linked to specific notebooks whose existence determines whether or not they are still needed.
+  Also note that this function will not delete notebook-agnostic projects (i.e., manually created projects whose names are not notebook file paths), as they are not linked to specific notebooks whose existence determines whether or not they are still needed.
   These (and any) projects may be deleted individually by calling their \texttt{Project} objects' \texttt{.remove()} method.
@@
 
-After installing and importing \texttt{Davos} (lines 1--2), we first use the \texttt{davos.require\_\-python()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
+After installing and importing \texttt{Davos} (lines 1--2), we first use the \texttt{davos.re\-qui\-re\_\-py\-thon()} function to constrain the Python version used to run the notebook (see Sec.~\ref{subsec:toplevel}).
 As described above, the example code in Figure~\ref{fig:illustrative-example} loads two different versions of the \texttt{pandas} library: first, an older version needed to access a dataset saved in an outmoded format, then a newer one to use throughout the remainder of the notebook.
@@
 word counts are then passed to a topic model~\cite{BleiEtal03} using a
-pre-trained \texttt{LatentDirichletAllocation} instance.
+pre-trained \texttt{Latent\-Dir\-ich\-let\-Allocation} instance.
 \begin{center}
@@
 In order to successfully load the model that includes the pre-trained
-\texttt{Latent\-Dirichlet\-Allocation} instance, in line 42, we first
+\texttt{Latent\-Dir\-ich\-let\-Allocation} instance, in line 42, we first
 \texttt{smuggle} a version of \texttt{scikit-learn} prior to v0.22.0 (i.e.,
@@
 
-\section{Impact}
+\section{Impact}\label{sec:impact}
 
@@
 considering.
-First, prior studies on reproducibility of Jupyter notebooks~\cite[e.g.,][]{PimeEtal19} identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in a non-linear order, and therefore potentially in a different order than they were executed by the notebook's original author.
+First, prior studies on reproducibility of Jupyter notebooks~\cite[e.g.,][]{PimeEtal19} identified a key challenge in the fact that, unlike Python scripts, notebook cells may be manually executed in an arbitrary order, and therefore potentially in a different order than they were executed by the notebook's original author.
 This can result in situations where, for example, a cell's execution fails because its code calls a function that has not yet been defined, or accesses a variable that refers to a different object than is expected at that point in the notebook.
@@
 Therefore, an important consideration when using \texttt{Davos} to facilitate complex, multi-package-version runtimes in this way is that executing notebook cells in order is perhaps even more important than it would be in a standard (i.e., non-\texttt{Davos}-enhanced) notebook.
-While (as noted in Sections~\ref{sec:illustrative-example} and~\ref{sec:illustrative-example}) we consider this an ``advanced feature'' of Davos rather than typical usage, we propose a relatively simple set of ``best practices'' that substantially mitigate the risk of creating ambiguous states within a notebook.
+While (as noted in Sections~\ref{sec:illustrative-example} and~\ref{sec:impact}) we consider this an ``advanced feature'' of Davos rather than typical usage, we propose a relatively simple set of ``best practices'' that substantially mitigate the risk of creating ambiguous states within a notebook.
 First, any \texttt{Davos}-enhanced notebook (or simply any notebook) that is intended to be run by more than one individual should be organized with its code cells in their intended execution order from top to bottom.
@@
 Meanwhile \texttt{pandas<0.25.0} and \texttt{scikit-learn<0.22.0} are alternate versions because they are temporarily smuggled for the specific purpose of loading an outmoded dataset and model and then immediately replaced with main versions after their use is complete.
-Any time an alternate package version needed, the \texttt{smuggle} statement used to install and load it, the operations it is required to perform, and a second \texttt{smuggle} to (re-)install and load the main package version should be placed within a single cell.
+Any time an alternate package version is needed, the \texttt{smuggle} statement used to install and load it, the operations it is required to perform, and a second \texttt{smuggle} to (re-)install and load the main package version should all be contained within a single notebook cell.
 This ensures that (barring other unrelated errors in the cell's execution) the main version will always be installed and imported when any given notebook cell is run.
-In other words, in Figure~\ref{fig:illustrative-example}, lines 14--19 should be run within a single cell, and lines 42--44 should be run in a single cell.
+In other words, in Figure~\ref{fig:illustrative-example}, lines 14--19 should be run within a single cell, and lines 42--44 should also be run in a single cell.
 

### 2023-10-01 paper/main.tex
add zenodo link to metadata table
added zenodo link to meta-data table, added explicit discussion of lockfiles and Poetry

@@
 \begin{table}[H]
-\begin{tabular}{|l|p{6.5cm}|p{6.5cm}|}
+  \footnotesize
+\begin{tabular}{|l|p{6cm}|p{8cm}|}
 \hline
@@
 \hline
-C2 & Permanent link to code/repository used for this code version & \url{https://github.com/ContextLab/davos/tree/v0.2.3} \\
+C2 & Permanent link to code/repository used for this code version & \url{https://doi.org/10.5281/zenodo.8233890} \\
 \hline
-C3 & Code Ocean compute capsule & \\
+C3 & Code Ocean compute capsule & N/A\\
 \hline
@@
 unsupported by \texttt{Davos}. We anticipate adding support for other package management
-systems, including \texttt{conda}, in a future release.
+systems, including \texttt{conda}, in a future release.  Because \texttt{Davos} relies on
+\texttt{pip} to install packages, it is also subject to the same limitations as
+\texttt{pip} itself. For example, \texttt{pip}-installing a package that depends on
+a previously \texttt{smuggle}d package may result in the previously smuggled package
+being upgraded or downgraded to a different version. Whereas lockfiles, or lockfile-based
+systems like \texttt{Poetry}~\citep{poetry}, place stronger guarantees that each package will
+have a stable version, we have opted for a more flexible (but, consequently, less
+deterministic) implementation for \texttt{Davos}.  This enables us to support
+more advanced use cases, such as those described in Section~\ref{sec:illustrative-example},
+but at the cost of managing potential conflicts between \texttt{smuggle}d
+packages.
 

### 2023-10-23 paper/main.tex
addressed R2 concerns

@@
 
-\begin{figure}[tp]
-\centering
-\includegraphics[width=0.65\textwidth]{figs/shareable_code_2d}
-\caption{\small \textbf{Systems for sharing code within the Python
-  ecosystem.} The $x$-axis denotes the ``burden'' placed on users to
-  install and configure the given system (systems placed further to the right, that fall within the redder shading, impose a higher setup cost on the user). The $y$-axis denotes the
-  degree to which the system guarantees that the code will run
-  similarly for different users (systems placed higher up, that fall within the bluer shading, offer stronger guarantees).
-  From left to right, bottom to top: plain-text \textbf{Python
-  scripts} (\texttt{.py} files) provide the most basic ``system''
-  for sharing raw code. Scripts may reference external packages, but
-  those packages must be manually installed on other users' systems.
-  Further, any checking needed to verify that the correct versions of
-  those packages were installed must also be performed manually.
-  \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
-  text, executable code, and media (including rendered figures, code
-  output, etc.). When the \textbf{Davos package} is imported
-  into a Jupyter notebook, the notebook's functionality is extended to
-  automatically install any required external packages (at their
-  correct versions, when specified) into an isolated directory kept separate
-  from the user's existing set of packages. \textbf{Virtual environments}
-  similarly allow users to install required packages into an isolated
-  directory, and \textbf{shareable Python environments} extend this to include
-  a specific version of Python itself. However, both of these systems require
-  users to create, populate, and manage environments manually. This
-  typically entails distributing a configuration file (e.g., a
+\begin{figure}[tp] \centering
+\includegraphics[width=0.6\textwidth]{figs/shareable_code_2d} \caption{\small
+\textbf{Systems for ensuring code reproducibility within the Python ecosystem.}
+The $x$-axis denotes the ``burden'' placed on users to install and configure
+the given system (systems placed further to the right, that fall within the
+redder shading, impose a higher setup cost on the user). The $y$-axis denotes
+the degree to which the system guarantees that the code will run similarly for
+different users (systems placed higher up, that fall within the bluer shading,
+offer stronger guarantees). From left to right, bottom to top: plain-text
+\textbf{Python scripts} (\texttt{.py} files) provide the most basic ``system''
+for sharing raw code. Scripts may reference external packages, but those
+packages must be manually installed on other users' systems. Further, any
+checking needed to verify that the correct versions of those packages were
+installed must also be performed manually. \textbf{Jupyter notebooks}
+(\texttt{.ipynb} files) comprise embedded text, executable code, and media
+(including rendered figures, code output, etc.). When the \textbf{Davos
+package} is imported into a Jupyter notebook, the notebook's functionality is
+extended to automatically install any required external packages (at their
+correct versions, when specified) into an isolated directory kept separate from
+the user's existing set of packages. \textbf{Virtual environments} (along with
+dependency specification files) similarly allow users to install required
+packages into an isolated directory, and \textbf{shareable Python environments}
+extend this to include a specific version of Python itself. However, both of
+these systems require users to create, populate, and manage environments
+manually. This typically entails distributing a configuration file (e.g., a
 \texttt{requirements.txt}, \texttt{pyproject.toml}~\cite{CannEtal16}, or
@@
 the file and build the environment. \textbf{Containers} provide a means of
-  defining an isolated environment that includes a complete operating
-  system (independent of the user's operating system), in addition to
-  (optionally) specifying a virtual environment or other
-  configurations needed to provide the necessary computing
-  environment. Containers are typically defined using
-  specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that instruct the
-  virtualization engine regarding how to build the containerized
-  environment. \textbf{Virtual machines} provide a complete
-  hardware-level simulation of the computing environment. In addition
-  to simulating specific hardware, virtual machines (typically
-  specified using binary image files) must also define operating
-  system-level properties of the computing environment. $\Delta_1$
-  represents the increased reproducibility \texttt{Davos} provides over standard
-  Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
-  \texttt{Davos}'s lower setup cost compared to standard virtual environments
-  despite more stringently ensuring reproducibility.}
-\label{fig:code-sharing}
-\end{figure}
+defining an isolated environment that includes a complete operating system
+(independent of the user's operating system), in addition to (optionally)
+specifying a virtual environment or other configurations needed to provide the
+necessary computing environment. Containers are typically defined using
+specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that
+instruct the virtualization engine regarding how to build the containerized
+environment. \textbf{Virtual machines} provide a complete hardware-level
+simulation of the computing environment. In addition to simulating specific
+hardware, virtual machines (typically specified using binary image files) must
+also define operating system-level properties of the computing environment.
+$\Delta_1$ represents the increased reproducibility \texttt{Davos} provides
+over standard Jupyter notebooks for no greater setup cost. $\Delta_2$
+represents \texttt{Davos}'s lower setup cost compared to standard virtual
+environments despite more stringently ensuring reproducibility.}
+\label{fig:code-sharing} \end{figure}
 
@@
 
-At another extreme, virtual machines~\cite{Gold74, AltiEtal05, Rose99}
-provide a hardware-level simulation of the desired system. Virtual
-machines are typically isolated, such that installing or running
-software on a virtual machine does not impact the user's primary
-operating system or computing environment.
-Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
-``isolated'' experience. Although containerized environments do not
-specify hardware-level operations, they are typically packaged with a
-complete operating system, in addition to a complete copy of Python
-and any relevant package dependencies. Shareable Python
-environments~\cite[e.g.,][]{Anac12} also provide a computing
-environment that is largely separated from the user's main
-environment. They incorporate a copy of Python and the target
-software's dependencies, but do not specify or
-reproduce an operating system for the runtime environment.
-Virtual environments~\cite[e.g.,][]{BickEtal07, Eust19} work similarly, but
-reuse an existing copy of Python rather than bundling their own.
-Each of these systems (virtual machines, containers, Python environments, and virtual environments)
-guarantees (to differing degrees---at the hardware level, operating
-system level, Python environment level, and package environment level, respectively) that the
-relevant code will run similarly for different users. However, each of
-these systems also relies on additional software that can be complex
-or resource-intensive to install and use, creating potential barriers
-to both contributing to and taking advantage of open science
-resources.
+At another extreme, virtual machines~\cite{Gold74, AltiEtal05, Rose99} provide
+a hardware-level simulation of the desired system. Virtual machines are
+typically isolated, such that installing or running software on a virtual
+machine does not impact the user's primary operating system or computing
+environment. Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
+``isolated'' experience. Although containerized environments do not specify
+hardware-level operations, they are typically packaged with a complete
+operating system, in addition to a complete copy of Python and any relevant
+package dependencies. Shareable Python environments~\cite[e.g.,][]{Anac12} also
+provide a computing environment that is largely separated from the user's main
+environment. They incorporate a copy of Python and the target software's
+dependencies, but do not specify or reproduce an operating system for the
+runtime environment. Virtual environments~\cite[e.g.,][]{BickEtal07, Eust19}
+work similarly, but reuse an existing copy of Python rather than bundling their
+own. Each of these systems (virtual machines, containers, Python environments,
+and virtual environments) guarantees (to differing degrees---at the hardware
+level, operating system level, Python environment level, and package
+environment level, respectively) that the relevant code will run similarly for
+different users. However, each of these systems either relies on additional
+software that can be complex or resource-intensive to install and use, or
+requires additional setup, creating potential barriers to both contributing to
+and taking advantage of open science resources. For example, what is typically
+``shared'' with the end user in these cases is a set of instructions or
+configuration files for \textit{building} the desired computing environment,
+rather than the environment itself.
 
@@
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like virtual environments, \texttt{Davos} provides a convenient
-mechanism for fully specifying (and installing, as needed) a complete set of
-Python dependencies, including specific package versions, which are contained
-and isolated from the rest of the user's system.
+notebook. And like virtual environments (when bundled with dependency
+specification files), \texttt{Davos} provides a convenient mechanism for fully
+specifying (and installing, as needed) a complete set of Python dependencies,
+including specific package versions, which are contained and isolated from the
+rest of the user's system.
 
@@
 
-While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments (bundled with separate dependency specification files), containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
@@
 
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments (bundled with separate dependency specification files) in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
 However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
@@
 being upgraded or downgraded to a different version. Whereas lockfiles, or lockfile-based
-systems like \texttt{Poetry}~\citep{poetry}, place stronger guarantees that each package will
+systems like \texttt{Poetry}~\cite{Eust19}, place stronger guarantees that each package will
 have a stable version, we have opted for a more flexible (but, consequently, less

### 2023-10-25 paper/main.tex
additional minor clarifications and updates to address R2 comments

@@
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like virtual environments (when bundled with dependency
-specification files), \texttt{Davos} provides a convenient mechanism for fully
-specifying (and installing, as needed) a complete set of Python dependencies,
-including specific package versions, which are contained and isolated from the
-rest of the user's system.
+notebook. And like virtual environments or Python environments (when these
+tools are bundled with dependency specification files), \texttt{Davos} provides
+a convenient mechanism for fully specifying (and installing, as needed) a
+complete set of Python dependencies, including specific package versions, which
+are contained and isolated from the rest of the user's system.
 
@@
 
-While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments (bundled with separate dependency specification files), containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as specification files for building virtual environments, Python environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
@@
 
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments (bundled with separate dependency specification files) in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to specification files for building virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
 However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.

### 2023-10-25 paper/main.tex
correction to fig 1 caption
more edits to fig 1 caption

@@
 dependency specification files) similarly allow users to install required
-packages into an isolated directory, and \textbf{shareable Python environments}
-extend this to include a specific version of Python itself. However, both of
-these systems require users to create, populate, and manage environments
-manually. This typically entails distributing a configuration file (e.g., a
-\texttt{requirements.txt}, \texttt{pyproject.toml}~\cite{CannEtal16}, or
-\texttt{environment.yml} file) that specifies all project dependencies
-(including version numbers) alongside the primary code base. Users can then
-install a third-party tool~\cite[e.g.,][]{BickEtal07, Eust19, Anac12} to read
-the file and build the environment. \textbf{Containers} provide a means of
-defining an isolated environment that includes a complete operating system
-(independent of the user's operating system), in addition to (optionally)
-specifying a virtual environment or other configurations needed to provide the
-necessary computing environment. Containers are typically defined using
-specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that
-instruct the virtualization engine regarding how to build the containerized
-environment. \textbf{Virtual machines} provide a complete hardware-level
-simulation of the computing environment. In addition to simulating specific
-hardware, virtual machines (typically specified using binary image files) must
-also define operating system-level properties of the computing environment.
-$\Delta_1$ represents the increased reproducibility \texttt{Davos} provides
-over standard Jupyter notebooks for no greater setup cost. $\Delta_2$
-represents \texttt{Davos}'s lower setup cost compared to standard virtual
-environments despite more stringently ensuring reproducibility.}
+packages into an isolated directory, and \textbf{Python environments} (again,
+along with dependency specification files) extend this to include a specific
+version of Python itself. However, both of these systems require users to
+create, populate, and manage environments manually. This typically entails
+distributing a configuration file (e.g., a \texttt{requirements.txt},
+\texttt{pyproject.toml}~\cite{CannEtal16}, or \texttt{environment.yml} file)
+that specifies all project dependencies (including version numbers) alongside
+the primary code base. Users can then install a third-party
+tool~\cite[e.g.,][]{BickEtal07, Eust19, Anac12} to read the file and build the
+environment. \textbf{Containers} provide a means of defining an isolated
+environment that includes a complete operating system (independent of the
+user's operating system), in addition to (optionally) specifying a virtual
+environment or other configurations needed to provide the necessary computing
+environment. Containers are typically defined using specification files (e.g.,
+a plain-text \texttt{Dockerfile}~\cite{Merk14}) that instruct the
+virtualization engine regarding how to build the containerized environment.
+\textbf{Virtual machines} provide a complete hardware-level simulation of the
+computing environment. In addition to simulating specific hardware, virtual
+machines (typically specified using binary image files) must also define
+operating system-level properties of the computing environment. $\Delta_1$
+represents the increased reproducibility \texttt{Davos} provides over standard
+Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
+\texttt{Davos}'s lower setup cost compared to standard virtual environments.}
 \label{fig:code-sharing} \end{figure}

### 2023-10-26 paper/main.tex
additional edits made with PCF based on our in-person discussion.  also reverted fig 1 + last sentence of fig 1 caption per our conversation.

@@
 Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
-\texttt{Davos}'s lower setup cost compared to standard virtual environments.}
-\label{fig:code-sharing} \end{figure}
+\texttt{Davos}'s lower setup cost compared to standard virtual environments
+despite more stringently ensuring reproducibility.} \label{fig:code-sharing}
+\end{figure}
 
@@
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like virtual environments or Python environments (when these
-tools are bundled with dependency specification files), \texttt{Davos} provides
-a convenient mechanism for fully specifying (and installing, as needed) a
+notebook. And like separate dependency specification files used to build
+virtual environments or Python environments, \texttt{Davos} provides a
+convenient mechanism for fully specifying (and installing, as needed) a
 complete set of Python dependencies, including specific package versions, which

### 2023-10-26 paper/old.tex
made change requested by PCF

--- 2023-10-25 paper/main.tex
@@
 
-\begin{figure}[tp] \centering
-\includegraphics[width=0.6\textwidth]{figs/shareable_code_2d} \caption{\small
-\textbf{Systems for ensuring code reproducibility within the Python ecosystem.}
-The $x$-axis denotes the ``burden'' placed on users to install and configure
-the given system (systems placed further to the right, that fall within the
-redder shading, impose a higher setup cost on the user). The $y$-axis denotes
-the degree to which the system guarantees that the code will run similarly for
-different users (systems placed higher up, that fall within the bluer shading,
-offer stronger guarantees). From left to right, bottom to top: plain-text
-\textbf{Python scripts} (\texttt{.py} files) provide the most basic ``system''
-for sharing raw code. Scripts may reference external packages, but those
-packages must be manually installed on other users' systems. Further, any
-checking needed to verify that the correct versions of those packages were
-installed must also be performed manually. \textbf{Jupyter notebooks}
-(\texttt{.ipynb} files) comprise embedded text, executable code, and media
-(including rendered figures, code output, etc.). When the \textbf{Davos
-package} is imported into a Jupyter notebook, the notebook's functionality is
-extended to automatically install any required external packages (at their
-correct versions, when specified) into an isolated directory kept separate from
-the user's existing set of packages. \textbf{Virtual environments} (along with
-dependency specification files) similarly allow users to install required
-packages into an isolated directory, and \textbf{shareable Python environments}
-extend this to include a specific version of Python itself. However, both of
-these systems require users to create, populate, and manage environments
-manually. This typically entails distributing a configuration file (e.g., a
+\begin{figure}[tp]
+\centering
+\includegraphics[width=0.65\textwidth]{figs/shareable_code_2d}
+\caption{\small \textbf{Systems for sharing code within the Python
+  ecosystem.} The $x$-axis denotes the ``burden'' placed on users to
+  install and configure the given system (systems placed further to the right, that fall within the redder shading, impose a higher setup cost on the user). The $y$-axis denotes the
+  degree to which the system guarantees that the code will run
+  similarly for different users (systems placed higher up, that fall within the bluer shading, offer stronger guarantees).
+  From left to right, bottom to top: plain-text \textbf{Python
+  scripts} (\texttt{.py} files) provide the most basic ``system''
+  for sharing raw code. Scripts may reference external packages, but
+  those packages must be manually installed on other users' systems.
+  Further, any checking needed to verify that the correct versions of
+  those packages were installed must also be performed manually.
+  \textbf{Jupyter notebooks} (\texttt{.ipynb} files) comprise embedded
+  text, executable code, and media (including rendered figures, code
+  output, etc.). When the \textbf{Davos package} is imported
+  into a Jupyter notebook, the notebook's functionality is extended to
+  automatically install any required external packages (at their
+  correct versions, when specified) into an isolated directory kept separate
+  from the user's existing set of packages. \textbf{Virtual environments}
+  similarly allow users to install required packages into an isolated
+  directory, and \textbf{shareable Python environments} extend this to include
+  a specific version of Python itself. However, both of these systems require
+  users to create, populate, and manage environments manually. This
+  typically entails distributing a configuration file (e.g., a
   \texttt{requirements.txt}, \texttt{pyproject.toml}~\cite{CannEtal16}, or
@@
   the file and build the environment. \textbf{Containers} provide a means of
-defining an isolated environment that includes a complete operating system
-(independent of the user's operating system), in addition to (optionally)
-specifying a virtual environment or other configurations needed to provide the
-necessary computing environment. Containers are typically defined using
-specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that
-instruct the virtualization engine regarding how to build the containerized
-environment. \textbf{Virtual machines} provide a complete hardware-level
-simulation of the computing environment. In addition to simulating specific
-hardware, virtual machines (typically specified using binary image files) must
-also define operating system-level properties of the computing environment.
-$\Delta_1$ represents the increased reproducibility \texttt{Davos} provides
-over standard Jupyter notebooks for no greater setup cost. $\Delta_2$
-represents \texttt{Davos}'s lower setup cost compared to standard virtual
-environments despite more stringently ensuring reproducibility.}
-\label{fig:code-sharing} \end{figure}
+  defining an isolated environment that includes a complete operating
+  system (independent of the user's operating system), in addition to
+  (optionally) specifying a virtual environment or other
+  configurations needed to provide the necessary computing
+  environment. Containers are typically defined using
+  specification files (e.g., a plain-text \texttt{Dockerfile}~\cite{Merk14}) that instruct the
+  virtualization engine regarding how to build the containerized
+  environment. \textbf{Virtual machines} provide a complete
+  hardware-level simulation of the computing environment. In addition
+  to simulating specific hardware, virtual machines (typically
+  specified using binary image files) must also define operating
+  system-level properties of the computing environment. $\Delta_1$
+  represents the increased reproducibility \texttt{Davos} provides over standard
+  Jupyter notebooks for no greater setup cost. $\Delta_2$ represents
+  \texttt{Davos}'s lower setup cost compared to standard virtual environments
+  despite more stringently ensuring reproducibility.}
+\label{fig:code-sharing}
+\end{figure}
 
@@
 
-At another extreme, virtual machines~\cite{Gold74, AltiEtal05, Rose99} provide
-a hardware-level simulation of the desired system. Virtual machines are
-typically isolated, such that installing or running software on a virtual
-machine does not impact the user's primary operating system or computing
-environment. Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
-``isolated'' experience. Although containerized environments do not specify
-hardware-level operations, they are typically packaged with a complete
-operating system, in addition to a complete copy of Python and any relevant
-package dependencies. Shareable Python environments~\cite[e.g.,][]{Anac12} also
-provide a computing environment that is largely separated from the user's main
-environment. They incorporate a copy of Python and the target software's
-dependencies, but do not specify or reproduce an operating system for the
-runtime environment. Virtual environments~\cite[e.g.,][]{BickEtal07, Eust19}
-work similarly, but reuse an existing copy of Python rather than bundling their
-own. Each of these systems (virtual machines, containers, Python environments,
-and virtual environments) guarantees (to differing degrees---at the hardware
-level, operating system level, Python environment level, and package
-environment level, respectively) that the relevant code will run similarly for
-different users. However, each of these systems either relies on additional
-software that can be complex or resource-intensive to install and use, or
-requires additional setup, creating potential barriers to both contributing to
-and taking advantage of open science resources. For example, what is typically
-``shared'' with the end user in these cases is a set of instructions or
-configuration files for \textit{building} the desired computing environment,
-rather than the environment itself.
+At another extreme, virtual machines~\cite{Gold74, AltiEtal05, Rose99}
+provide a hardware-level simulation of the desired system. Virtual
+machines are typically isolated, such that installing or running
+software on a virtual machine does not impact the user's primary
+operating system or computing environment.
+Containers~\cite[e.g.,][]{Merk14, KurtEtal17} provide a similar
+``isolated'' experience. Although containerized environments do not
+specify hardware-level operations, they are typically packaged with a
+complete operating system, in addition to a complete copy of Python
+and any relevant package dependencies. Shareable Python
+environments~\cite[e.g.,][]{Anac12} also provide a computing
+environment that is largely separated from the user's main
+environment. They incorporate a copy of Python and the target
+software's dependencies, but do not specify or
+reproduce an operating system for the runtime environment.
+Virtual environments~\cite[e.g.,][]{BickEtal07, Eust19} work similarly, but
+reuse an existing copy of Python rather than bundling their own.
+Each of these systems (virtual machines, containers, Python environments, and virtual environments)
+guarantees (to differing degrees---at the hardware level, operating
+system level, Python environment level, and package environment level, respectively) that the
+relevant code will run similarly for different users. However, each of
+these systems also relies on additional software that can be complex
+or resource-intensive to install and use, creating potential barriers
+to both contributing to and taking advantage of open science
+resources.
 
@@
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like virtual environments or Python environments (when these
-tools are bundled with dependency specification files), \texttt{Davos} provides
-a convenient mechanism for fully specifying (and installing, as needed) a
-complete set of Python dependencies, including specific package versions, which
-are contained and isolated from the rest of the user's system.
+notebook. And like virtual environments, \texttt{Davos} provides a convenient
+mechanism for fully specifying (and installing, as needed) a complete set of
+Python dependencies, including specific package versions, which are contained
+and isolated from the rest of the user's system.
 
@@
 
-While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as specification files for building virtual environments, Python environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as virtual environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
@@
 
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to specification files for building virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
 However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.

### 2023-10-27 paper/main.tex
checking in edits to hand off to PCF

@@
 correct versions, when specified) into an isolated directory kept separate from
-the user's existing set of packages. \textbf{Virtual environments} (along with
-dependency specification files) similarly allow users to install required
-packages into an isolated directory, and \textbf{Python environments} (again,
-along with dependency specification files) extend this to include a specific
-version of Python itself. However, both of these systems require users to
-create, populate, and manage environments manually. This typically entails
-distributing a configuration file (e.g., a \texttt{requirements.txt},
+the user's existing set of packages. \textbf{Virtual environments} similarly
+allow users to isolate installed packages in a specific directory, and can be
+populated with packages from a shared dependency specification
+file~\citep[e.g., a requirements.txt or pyproject.toml; ][]{CannEtal16}.
+\textbf{Python environments} (again, shared in the form of a dependency
+specification file; e.g., an environment.yml) extend this idea to allow
+automatically installing a specific version of Python itself. However, both of
+virtual environments and Python environments require users to create, populate,
+and manage environments manually. This typically entails distributing a
+configuration file (e.g., a \texttt{requirements.txt},
 \texttt{pyproject.toml}~\cite{CannEtal16}, or \texttt{environment.yml} file)
@@
 provide a computing environment that is largely separated from the user's main
-environment. They incorporate a copy of Python and the target software's
+environment. They incorporate (i.e., automatically install) a copy of Python and the target software's
 dependencies, but do not specify or reproduce an operating system for the
@@
 required from the user, beyond what is needed to run a standard Jupyter
-notebook. And like separate dependency specification files used to build
-virtual environments or Python environments, \texttt{Davos} provides a
-convenient mechanism for fully specifying (and installing, as needed) a
-complete set of Python dependencies, including specific package versions, which
-are contained and isolated from the rest of the user's system.
+notebook. And like separate dependency specification files that list packages
+for populating virtual environments or Python environments, \texttt{Davos}
+provides a convenient mechanism for fully specifying (and installing, as
+needed) a complete set of Python dependencies, including specific package
+versions, which are contained and isolated from the rest of the user's system.
 

### 2023-10-27 paper/main.tex
added clarification re: virtual environments & note re: pyproject.toml in section 4

@@
 populated with packages from a shared dependency specification
-file~\citep[e.g., a requirements.txt or pyproject.toml; ][]{CannEtal16}.
+file (e.g., a \texttt{requirements.txt} or \texttt{pyproject.toml~\cite{CannEtal16})}.
 \textbf{Python environments} (again, shared in the form of a dependency
-specification file; e.g., an environment.yml) extend this idea to allow
-automatically installing a specific version of Python itself. However, both of
+specification file; e.g., an \texttt{environment.yml}) extend this idea to allow
+installing a specific version of Python itself. However, both
 virtual environments and Python environments require users to create, populate,
@@
 
-While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as specification files for building virtual environments, Python environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
+While the \texttt{Davos} package by no means offers a universal solution to this problem, it can, in many cases, provide an effective yet more accessible alternative to existing systems for sharing reproducible Python code, such as instructions and specification files for building and populating virtual environments, Python environments, containers, and virtual machines (Fig.~\ref{fig:code-sharing}).
 For researchers, this can lower barriers to collaborating with peers and contributing to publicly available open science resources.
@@
 
-Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to specification files for building virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
+Among common systems for sharing reproducible Python code (see Fig.~\ref{fig:code-sharing}), \texttt{Davos} is most comparable to instructions and specification files for building and populating virtual environments in that it provides a lightweight mechanism for specifying and sharing a complete set of packages (and specific package versions) required by a particular project, and installing those packages into an isolated directory on the user's file system.
 However, when used in conjunction with Jupyter notebooks, \texttt{Davos} offers a number of advantages over standard virtual environments that make it both easier to use and more effective at ensuring reproducibility of shared code.
@@
 
-Finally, neither virtual environments nor \texttt{Davos}-enhanced notebooks can bundle specific versions of Python with which to run shared code.
+Finally, neither specification files used to install packages into virtual environments nor \texttt{smuggle} statements and onion comments included \texttt{Davos}-enhanced notebooks can be used to automatically install a specific version of Python with which to run shared code.
 However, \texttt{Davos}'s \texttt{require\_\-python()} function provides a simple mechanism for indicating a required or constrained Python version and alerting the user at runtime (by raising an exception) if their Python version is incompatible.
+We note that a similar a similar constraint can be imposed by setting the ``\texttt{requires-python}'' attribute in a \texttt{pyproject.toml} file, though creating a virtual environment from a \texttt{pyproject.toml} would require installing an additional third-party tool (such as~\cite{Eust19}).
 In terms of \texttt{Davos}'s ability to ensure that shared code can be executed reproducibly by other users, this falls short of the capabilities of more complex tools that can provide complete copies of Python (Fig.~\ref{fig:code-sharing}).
